### 2023-01-31 src/tex/ms.tex
[showyourwork] first commit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@adonath}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
    Phasellus eu tellus sit amet tortor gravida placerat.
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
    Praesent eget sem vel leo ultrices bibendum.
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
    Curabitur auctor semper nulla donec varius orci eget risus.
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
Donec vehicula augue eu neque, morbi tristique senectus et netus et.
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
Phasellus eu tellus sit amet tortor gravida placerat.
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
Praesent eget sem vel leo ultrices bibendum.
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
Curabitur auctor semper nulla donec varius orci eget risus.
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \documentclass[twocolumn]{aastex631}
+
+% Filler text
+\usepackage{blindtext}
+\usepackage{amsmath}
+\usepackage[utf8]{inputenc}
 \usepackage{showyourwork}
+\usepackage{amssymb}
+cd ..
+\DeclareMathOperator*{\argmax}{arg\,max}
+\newcommand{\chandra}{\textit{Chandra}~}
+\newcommand{\xmm}{\textit{XMM}~}
+\newcommand{\fermi}{\textit{Fermi}-LAT~}
+\newcommand{\jolideco}{\textit{Jolideco}~}
+\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
+
+\newcommand{\vlk}[1]{{\color{blue} [VLK: #1]}}
 
@@
 % Title
-\title{An open source scientific article}
+    \title{\jolideco: Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise}
 
 % Author list
-\author{@adonath}
+    \author[0000-0003-4568-7005]{Axel Donath}
+    \author[0000-0002-0905-7375]{Aneta Siemiginowska}
+    \author[0000-0002-3869-7996]{Vinay Kashyap}
+    \author[0000-0000-0000-0000]{David van Dyk}
 
@@
     \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
-    Phasellus eu tellus sit amet tortor gravida placerat.
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
-    Praesent eget sem vel leo ultrices bibendum.
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
-    Curabitur auctor semper nulla donec varius orci eget risus.
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-    Duis eget orci sit amet orci dignissim rutrum.
+        We present a new method for (Jo)int (li)kelihood  (Deco)nvolution (\jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
+        The method reconstructs an image from a set of observations
+        by optimizing the a-posteriori joint Poisson likelihood of all
+        observations under an patch based image prior. The patch
+        prior is parameterised by a standard Gaussian Mixture model (GMM)
+        learned from astronomical images at other wavelenghts and
+        adapted to the structures expected to see in the image.
+        By applying the method to simulated data we show that
+        the combination of mutiple observations leads to an
+        improved reconstruction quality in the regime with S/N ratio of.
+        We show also that the method yields superior reconstruction quality
+        to alternative standard methods such as the Richardson-Lucy method.
     \end{abstract}
@@
     % Main body with filler text
+
     \section{Introduction}
-\label{sec:intro}
+    The quality of all astronomical images is affected by the limited angular resolution of the instrument
+    or telescope. In addition the images are affected by the presence of noise and non-uniform exposure.
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
-Donec vehicula augue eu neque, morbi tristique senectus et netus et.
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
-Phasellus eu tellus sit amet tortor gravida placerat.
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
-Praesent eget sem vel leo ultrices bibendum.
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
-Curabitur auctor semper nulla donec varius orci eget risus.
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-Duis eget orci sit amet orci dignissim rutrum.
+    In literature there have been multiple efforts to
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+    Any astronomical observation is affected by the limited angular resolution of the telescope.
 
-\bibliography{bib}
+    \begin{itemize}
+        \item Richardson \& Lucy (RL)\cite{Richardson1972} \cite{Lucy1974}
+        \item Joint likelihood RL: \cite{Ingaramo2014} has found that RL take the best out of each image and create a "merged" image
+        \item  Problem of RL decomposing structures into point sources: \cite{Reeves1994} \cite{Fish1995}
+        \item Multi-scale LIRA prior of course: \cite{Esch2004, Connors2011}, advantage of error estimates / Bayesian sampling.
+However prior is rather "ad-hoc", no physical information / assumptions.
+Just "smoothness"
+        \item What abput d3po and d4po? Priors based on physical assumptions, decomposition into point and diffuse flux, but in 3d/4d \cite{Selig2015}\cite{Pumpe2018}
+    \end{itemize}
 
+    % \begin{figure*}
+    %     \script{rl_decomposition.py}
+    %     \begin{centering}
+    %         \includegraphics[width=\textwidth]{figures/richardson-lucy-decomposition.pdf}
+    %         \caption{
+    %             Decomposition of the RL algorithm for various number of iterations. \todo{Improve figure}
+    %         }
+    %         \label{fig:rl_decomposition}
+    %     \end{centering}
+    % \end{figure*}
+
+    \subsection{A note on Deep Learning Methods}
+    \cite{Li2014} have introduced a baseline architecture for a deep convolutional neural network for image deblurring.
+    The convolutional nature of the network does not make it suitable for the task. As convolution introduces smoothing.
+    However the network can learn an "inverse kernel", which needs to be larger because of the uncertainty principle (\todo{reference...}).
+    The large kernels are introduced by separability assumption...
+    In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possibly for most network architectures.
+
+    \section{Method}
+    \subsection{Poisson Joint Likelihood}
+    Our goal is to recover an image $\mathbf{x}$ from a set of multiple
+    low counts observations.
+    Most generally we assume our total dataset consists of $M$ individual
+    observations of the same region of the sky, which are jointly
+    modelled. The assumption is that the underlying \textit{true} emission image,
+    we are looking for does not change with time. Under this assumption these
+    datasets can be for example:
+
+    \begin{itemize}
+        \item Different observations of one instrument or telescope at different times and observation conditions.
+E.g., multiple observations of \chandra with different offset angles and exposure times.
+        \item Observations of different telescopes, which operate in the same wavelength range. E.g., a \chandra
+        and \xmm observation of the same region in the sky.
+        \item A single observation of one telescope with different data quality categories and different associated instrument
+        response functions. E.g., event classes for \fermi.
+    \end{itemize}
+
+    Or a even an arbitrary combination of the possibilities listed above.
+
+    For each individual observation $m$ the predicted counts can be modelled by forward
+    folding the unknown flux image $\mathbf{x}$ with the individual (per observation) instrument response:
+
+    \begin{equation}
+        \label{eq:model}
+        \mathbf{\lambda}_m = \mathrm{PSF}_m \circledast \left(\mathbf{E}_m \cdot (\mathbf{x} + \mathbf{B}_m) \right)
+    \end{equation}
+
+    Where the expected counts $\lambda_i$ are given by the convolution of the true underlying
+    flux distribution $\mathbf{x}$ with the $\mathrm{PSF}$. Additionally
+    the observation specific exposure $\mathbf{E}$ and background emission $\mathbf{B}$ can be
+    taken into account.
+
+    Given a single observation $m$ of a true underlying flux distribution
+    $\mathbf{x}$ and assuming the noise in each pixel $i$ in the recorded counts image
+    $\mathbf{d}$ follows a Poisson distribution, the total likelihood $\mathcal{L}_m$
+    of obtaining the measured image from a model image of the expected
+    counts $\lambda_i$ with $N$ pixels is given by:
+
+    \begin{equation}
+        \label{eq:poisson}
+        \mathcal{L}_m\left( \mathbf{d} | \mathbf{\lambda} \right) = \prod_i^N \frac{{e^{ - d_i } \lambda_i ^ {d_i}}}{{d_i!}}
+    \end{equation}
+
+    By taking the logarithm and dropping the constant terms one can transform the
+    product into a sum over pixels, which is also often called the \textit{Cash}
+    \citep{Cash1979} fit statistics:
+
+    \begin{equation}
+        \label{eq:cash}
+        \mathcal{C}\left( \mathbf{d} | \mathbf{\lambda} \right) = \sum_i^N \lambda_i - d_i \log{\lambda_i}
+    \end{equation}
+
+    Bayes rule:
+
+    \begin{equation}
+        \label{eq:bayes}
+        P(\theta|\textbf{D}) = P(\theta ) \frac{\mathcal{C}(\textbf{D} |\theta)}{P(\textbf{D})}
+    \end{equation}
+
+    The total objective function $\mathcal{L}$ is given by:
+    \begin{equation}
+        \label{eq:total}
+        \mathcal{L}\left( \mathbf{d_m} | \mathbf{x} \right) = \sum_m^M \mathcal{C}\left( \mathbf{d_m} | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x})
+    \end{equation}
+
+    Where $\mathcal{C}\left( \mathbf{d_m} | \mathbf{x} \right)$ represents the summed log-likelihood
+    for an individual observation $m$. Additionally the function includes a prior term $\mathcal{P}(\mathbf{x})$
+    and a factor $\beta$ to adjust the weight of the prior with respect to the likelihood term. \todo{To be clarified: the weight
+    does not really make it a prior, more a regularisation term...}
+
+    \subsection{Priors}
+    Just include patch priors, or LIRA as well, or uniform?
+
+    \subsubsection{Patch-Prior}
+    To improve the reconstruction quality of images for inverse problems,
+    such as denoising, inpainting or deconvolution it is useful to have prior
+    assumptions on the statistics of the image to guide the optimization based
+    image reconstruction process. However images are high
+    dimensional and thus difficult to capture the global image statistics
+    taking into account all pixel to pixel correlations.
+
+    By recognising that on smal scale images often contain basic structure such as 
+    edges, corners, periodic patterns or region of constant brightness. 
+    The idea of patch priors was first introduced by \cite{Zoran2011}.
+    Their main idea was to learn the statistics of natural images on a small
+    spatial scales instead. For this they proposed to split images from a
+    representative dataset into small patches of size 8x8 pixels.
+
+    Then they learned a 64 dimensional Gaussian Mixture Model (GMM) on the
+    extracted patches, treating each pixel as an independent dimension in
+    the model, with $k=200$ components. They showed that the GMM prior led to much improved
+    image reconstructions, compared to comparable approaches (which ones?).
+
+    One of the main advantages of the GMM is the possibility to
+    evaluate its log-likelihood in closed form. It is given by:
+
+    \begin{equation}
+        \ell_{GMM}(\theta) = \sum_{i=1}^n \log \left( \sum_{k=1}^K \pi_k N(x_i;\mu_k, \sigma_k^2) \right )
+    \end{equation}
+
+    With parameters $\theta = \{\mu_1,\ldots,\mu_K,\sigma_1,\ldots,\sigma_K,\pi_1,\ldots,\pi_K\}$.
+    To use the learned GMM as prior for the reconstruction of another image, the image is split into
+    overlapping patches. For each of the patches the log-likelihood for each of the GMM components is
+    evaluated. The resulting grid of overlapping patches is illustrated in Figure~\ref{fig:patches}.
+
+    For each 8x8 pixel patch the likelihood of all components of the GMM is evaluated. Then 
+    \begin{equation}
+        \hat{k} = \argmax{\ell_{GMM}(\theta)}
+    \end{equation}
+
+    \begin{equation}
+        \mathcal{P}(x) = \sum_n \log{p_{\hat{k}}(\mathbf{P}_n x)}
+    \end{equation}
+
+    $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch
+    from the image $\mathbf{x}$ to be reconstructed.
+    $p(\mathbf{P}_n x)$ is the probability of that patch
+    under the GMM.
+
+    \begin{figure}[ht!]
+        \script{patches.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/patches.pdf}
+            \caption{
+                Grid of overlapping patches of size 8x8 pixels. The overlap size was chosen to be 2 pixels.
+            }
+            \label{fig:patches}
+        \end{centering}
+    \end{figure}
+
+    \cite{Bouman2016} later adapted the patch prior reconstruction to be used
+    with radio astronomy data.
+    They have shown that the reconstructed image only weakly depends on the choice
+    of the reference data on which the the patch prior is learned. They found
+    equivalent results for GMMs learned on natural images and specifically
+    simulated images of black hole ring structures.
+
+    \subsubsection{Image Normalisation}
+    Astromomical images typically show a much higher dynamic range compared to 
+    natural images. This is mostly due to the existence of point sources, which rarely occur
+    in natural images, but a very common in astronomical images because of objects 
+    at hig distances.
+    The GMM patch prior is learned on normalized images, where the intensity values
+    are constrained between 0 and 1. To evaluate For the likelihood term the image
+    intensity need to be conserved.
+
+    The choice of the image normalisation allows to adjust the contrast of the image
+    and e.g. enhance low intensity structures, which also enhances the regularising
+    effect of the patch prior.
+
+    \todo{Which normalisation to choose, atan, asinh, log, inverse-cdf?}
+
+    \subsubsection{Cycle Spinning}
+    To avoid artifact due to the choice of the grid of overlapping patches we propose
+    three variations:
+
+    \begin{itemize}
+        \item Cycle spining by randomly shifting the image by a given number of pixels in x and y direction
+        \item Sub pixel cycle spinning, by randomly distributing the bightness of a given pixel to a 4 pixel grid
+        \item A randomly chosen patch grid, such that each pixel is at least covered once.
+        The random grid of patches was proposed by \cite{Parameswaran2018}.
+    \end{itemize}
+
+    \subsection{Cross Validation}
+    The use of multiple dataset allows to sue cross-validation to prevent overfitting.
+    One of the standard techniques in "machine learning"...
+
+    \subsection{Calibration of Predicted Counts}
+    Each dataset comes with systematic errors on absolute position and background normalisation
+
+    \begin{itemize}
+        \item allow for systematic shifts between observations 
+        \item allow for background scaling per observation $\alpha_m$
+    \end{itemize}
+
+    \begin{equation}
+        \label{eq:model-npred-calibration}
+        \mathbf{\lambda}_m = \mathrm{PSF}_m \circledast \left(\mathbf{E}_m \cdot (\phi_m(\mathbf{x}| \delta_x, \delta_y) + \alpha_m \cdot \mathbf{B}_m) \right)
+    \end{equation}
+
+    Show example residual images before and after calibration...
+
+    \section{Implementation}
+    \subsection{Jolideco Framework}
+    The goal of the reconstruction process is to optimize the a-posteriori
+    likelihood defined by Equation~\ref{eq:total}. Given that each pixel
+    in the reconstructed image represents an independent parameter
+    this represents a high dimensional optimization problem.
+    Differentiable programming frameworks such as \texttt{PyTorch}
+    allow for solving these kind of high dimensional modeling problems, by using
+    back-propagation and adapted optimization methods such as stochastic gradient
+    decent.
+
+    The \jolideco method was implemented as an independent Python package, 
+    based on \texttt{PyTorch} as optimization back-end. We tried to define a modular,
+    object oriented code structure, to allow parts of the algorithm to be
+    flexible and interchangeable, such as choice of image normalisation scales,
+    the choice of GMM models, optimization methods and serilisation formats for the 
+    reconstruction results as well as corresponding diagnostic information
+    such as the trace of the posterior and prior likelihood values.
+
+    The package is available at \url{https://github.com/jolideco/jolideco}
+
+    \begin{itemize}
+        \item direct maximum a posteriori optimization using Pytorch etc.
+        \item auto gradient computation
+        \item ML optimizers such as ADAM
+        \item GPU support
+    \end{itemize}
+
+    In addition we use \texttt{Scikit-Learn}~\citep{Skimage2014} to learn the GMM.
+
+    We use \texttt{Astropy}~\citep{Astropy2018} for FITS serialisation and
+    handling WCS transforms.
+
+    We use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and
+    \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
+
+    For optimization and internal data handling we use \texttt{PyTorch}~\citep{Pytorch2019}.
+
+    \subsection{Jolideco GMM Library}
+    We provide a selection of learned GMMs to be used with the patch prior for reproducibility and download. 
+    Convenience for future users. \url{https://github.com/jolideco/jolideco-gmm-library}
+
+    \subsubsection{Zoran \& Weiss}
+    As baseline reference GMM we use the original model provided by \cite{Zoran2011}. The model was learned
+    from the Berkley image database, by splitting the images into 8x8 patches.
+
+    \subsubsection{GLEAM data}
+    High signal to noise Radio data from \cite{HurleyWalker2022}
+
+    \subsubsection{NRAO Jets, Jets, Jets}
+    For the specific application of jet analysis we learned a GMM patch prior from jet images. It encodes the prior knowledge of the preferred direction of the jet.
+
+    \begin{itemize}
+        \item One with horizontal direction, where the image to be analysed should be rotated. E.g. if prior knowledge from radio data is available.
+        \item One with randomised direction, if now prior knowledge is available.
+    \end{itemize}
+
+    \subsection{Computational Performance}
+    We conduct as as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations
+    as well as large images. Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
+
+    \section{Experiments}
+    \subsection{Test Datasets}
+    \todo{Vinay writes this?}
+    \vlk{yes}
+
+    \vlk{We have devised four distinct arrangements of combinations of point and extended sources of differents shapes to test the algorithms.  The arrangements are 
+    \begin{itemize}
+        \item[ ``Gauss":] A set of four point sources arranged around an extended Gaussian source
+        \item[``Points":] Point sources arranged with different separations
+        \item[``Shield":] Disk shaped flat extended source with superposed point sources and linear jet-like features
+        \item[``Spiral":] Extended thin double-spiral with a flat disk at the center and point sources adjacent to it
+    \end{itemize}
+    The arrangements are shown in Figure~TBD, and the details of the locations and brightness of each component is listed in Table~TBD.
+    }
+
+    We use the test datasets provided by Vinay et al.
+    First we evaluate the performance of the method on a set of simulated observations.
+    For this we assume:
+
+    \begin{itemize}
+        \item An instrument with good angular resolution, but low effective area (e.g. like Chandra)
+        \item An instrument with worse angularr resolution, bur higher effective area (e.g. like XMM)
+    \end{itemize}
+
+    For both scenarios we assume a Gaussian PSF of sizes $\sigma = 2$ pixels and  $\sigma = 5$.
+    As true flux we consider the following scenarios:
+
+    \begin{itemize}
+        \item Point source with varying distances and brightness
+        \item Disk and point sources of varying brightness
+        \item Spiral and point sources of varying brightness
+    \end{itemize}
+
+    Background levels of $\lambda_{Bkg}= 0.001, 0.01 \textrm{and} 0.1 \textrm{counts/pixel}$.
+
+    Show results of experiments on simulated toy datasets
+
+    \subsection{Results}
+
+    The package is available at \url{https://github.com/jolideco/jolideco-comparison}
+
+    \section{Application Examples}
+    Show results from real observations
+
+    \subsection{Deep \chandra Observation}
+
+    \subsection{Combined \xmm and \chandra Observation}
+
+    \subsection{\fermi Event Classes}
+
+    \section{Reproducibility}
+
+    The paper is available at \url{https://github.com/jolideco/jolideco-paper}
+
+    \section{Summary \& Conclusions}
+    In this work we presented a new method for image deconvolution and denoising in the presence of Poisoon noise.
+    Jolideco is great...
+
+    Extend \jolideco to handl spectral dimension at the same time.
+
+    \section*{Acknowledgements}
+    This work was conducted under the auspices of the CHASC International Astrostatistics Center.
+    CHASC is supported by NSF grants DMS-21-13615, DMS-21-13397, and DMS-21-13605; by the UK Engineering
+    and Physical Sciences Research Council [EP/W015080/1]; and by NASA 18-APRA18-0019.
+    We thank CHASC members for many helpful discussions, especially Xiao-Li Meng and Katy McKeough.
+    DvD was also supported in part by a Marie-Skodowska-Curie RISE Grant (H2020-MSCA-RISE-2019-873089)
+    provided by the European Commission.
+    Aneta Siemiginowska, Vinay Kashyap, and Doug Burke further acknowledge support from NASA
+    contract to the Chandra X-ray Center NAS8-03060.
+
+    \newpage
+    \bibliography{bib.bib}
 \end{document}

### 2023-01-31 src/scripts/config.py
Add files

@@ -1,0 +1,45 @@
+"""General configuration for mpl plotting scripts"""
+from pathlib import Path
+import matplotlib.pyplot as plt
+from astropy import units as u
+import numpy as np
+from cycler import cycler
+from astropy.units import imperial
+
+BASE_PATH = Path(__file__).parent.parent
+
+FONTSIZE = 10
+
+FIGURE_WIDTH_AA = {
+    "single-column": 90 * u.mm,
+    "two-column": 180 * u.mm,
+    "intermediate": 120 * u.mm,
+}
+
+CMAP = plt.get_cmap("viridis")
+
+COLORS = CMAP([0, 0.25, 0.5, 0.75, 1])
+COLORS = np.append(COLORS, [[216 / 255, 27 / 255, 96 / 255, 1.]], axis=0)
+
+PROP_CYCLER = [
+    cycler(color=COLORS) +
+    cycler(linestyle=["-", "--", ":", "-.", ".", "-.-"])
+]
+
+
+class FigureSizeAA:
+    """Figure size A&A"""
+
+    def __init__(self, aspect_ratio=1, width_aa="single-column"):
+        self.width = FIGURE_WIDTH_AA[width_aa]
+        self.height = self.width / aspect_ratio
+
+    @property
+    def inch(self):
+        """Figure size in inch"""
+        return self.width.to_value(imperial.inch), self.height.to_value(imperial.inch)
+
+    @property
+    def mm(self):
+        """Figure size in mm"""
+        return self.width.value, self.height.value

### 2023-01-31 src/scripts/image-norms.py

@@ -1,0 +1,18 @@
+import config
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+
+figsize = config.FigureSizeAA(aspect_ratio=1.618)
+
+fig = plt.figure(figsize=figsize.inch)
+ax = fig.add_axes([0.1, 0.1, 0.88, 0.88])
+
+x = np.linspace(0, 2, 100)
+ax.plot(x, x, label="Linear")
+ax.plot(x, x**0.5, label="Square Root")
+ax.plot(x, np.arcsinh(x), label="Arcsinh")
+ax.plot(x, np.clip(x, 0, 1), label="Clip")
+
+plt.legend()
+plt.savefig(paths.figures / "image-norms.pdf", facecolor="w", dpi=300)

### 2023-01-31 src/scripts/patches.py

@@ -1,0 +1,44 @@
+import matplotlib.pyplot as plt
+from matplotlib.patches import Rectangle
+import paths
+import config
+
+figsize = config.FigureSizeAA(aspect_ratio=2)
+
+fig = plt.figure(figsize=figsize.inch)
+ax = fig.add_axes([0, 0, 1, 1])
+
+image_size = (64, 32)
+patch_size = (8, 8)
+
+for x in range(0, 2 * image_size[0], 6):
+    for y in range(0, 2 * image_size[1], 6):
+        rectangle = Rectangle(
+            xy=(x, y),
+            width=patch_size[0],
+            height=patch_size[1],
+            facecolor=config.COLORS[1],
+            edgecolor="k",
+            alpha=0.2,
+        )
+
+        ax.add_patch(rectangle)
+
+rectangle = Rectangle(
+    xy=(12, 12),
+    width=patch_size[0],
+    height=patch_size[1],
+    facecolor="None",
+    edgecolor=config.COLORS[-1],
+    lw=1,
+)
+ax.add_patch(rectangle)
+
+ax.text(x=16, y=20.5, s="8 x 8 Patch", color=config.COLORS[-1], ha="center")
+
+offset = patch_size[0] // 2
+ax.set_xlim(offset, image_size[0] - offset - offset // 2)
+ax.set_ylim(offset, image_size[1] - offset)
+ax.set_aspect("equal")
+plt.axis("off")
+plt.savefig(paths.figures / "patches.pdf", facecolor="w", dpi=300)

### 2023-01-31 src/scripts/rl_decomposition.py

@@ -1,0 +1,201 @@
+import matplotlib.pyplot as plt
+from matplotlib import gridspec
+import numpy as np
+from skimage.restoration import richardson_lucy
+from astropy.visualization import simple_norm
+from scipy.ndimage import gaussian_filter
+from astropy.convolution import Gaussian2DKernel, Tophat2DKernel, convolve_fft
+import paths
+import config
+
+
+def disk_source_gauss_psf(
+    shape=(32, 32),
+    shape_psf=(17, 17),
+    sigma_psf=3,
+    source_level=1_000,
+    source_radius=6,
+    background_level=0,
+    random_state=None,
+):
+    """Get disk source with Gaussian PSF test data.
+    The exposure has a gradient of 50% from left to right.
+
+    Parameters
+    ----------
+    shape : tuple
+        Shape of the data array.
+    shape_psf : tuple
+        Shape of the psf array.
+    sigma_psf : float
+        Width of the psf in pixels.
+    source_level : float
+        Total integrated counts of the source
+    source_radius : float
+        Radius of the disk source
+    background_level : float
+        Background level in counts / pixel.
+    random_state : `~numpy.random.RandomState`
+        Random state
+
+    Returns
+    -------
+    data : dict of `~numpy.ndarray`
+        Data dictionary
+    """
+    if random_state is None:
+        random_state = np.random.RandomState(None)
+
+    background = background_level * np.ones(shape)
+    exposure = np.ones(shape)
+
+    flux = (
+        source_level
+        * Tophat2DKernel(
+        radius=source_radius, x_size=shape[1], y_size=shape[1], mode="oversample"
+    ).array
+    )
+
+    psf = Gaussian2DKernel(sigma_psf, x_size=shape_psf[1], y_size=shape_psf[1])
+    npred = np.clip(convolve_fft((flux + background) * exposure, psf), 0, np.inf)
+
+    counts = random_state.poisson(npred)
+    return {
+        "counts": counts,
+        "psf": psf.array,
[…]

### 2023-01-31 src/scripts/config.py
Add example scripts

@@ -9,6 +9,7 @@ from astropy.units import imperial
 BASE_PATH = Path(__file__).parent.parent
 
 FONTSIZE = 10
+DPI = 300
 
 FIGURE_WIDTH_AA = {
     "single-column": 90 * u.mm,

### 2023-01-31 src/scripts/example-chandra.py

@@ -1,0 +1,8 @@
+import config
+import matplotlib.pyplot as plt
+
+figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+
+fig, ax = plt.subplots(figsize=figsize.inch)
+
+plt.savefig("example-chandra.pdf", dpi=config.DPI)

### 2023-01-31 src/scripts/example-xmm-chandra.py

@@ -1,0 +1,8 @@
+import config
+import matplotlib.pyplot as plt
+
+figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+
+fig, ax = plt.subplots(figsize=figsize.inch)
+
+plt.savefig("example-xmm-chandra.pdf", dpi=config.DPI)

### 2023-01-31 src/scripts/example-chandra.py
[showyourwork] overleaf sync

@@ -1,8 +1,9 @@
 import config
+import paths
 import matplotlib.pyplot as plt
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
 
 fig, ax = plt.subplots(figsize=figsize.inch)
 
-plt.savefig("example-chandra.pdf", dpi=config.DPI)
+plt.savefig(paths.figures /"example-chandra.pdf", dpi=config.DPI)

### 2023-01-31 src/scripts/example-fermi-lat.py

@@ -1,0 +1,9 @@
+import config
+import matplotlib.pyplot as plt
+import paths
+
+figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+
+fig, ax = plt.subplots(figsize=figsize.inch)
+
+plt.savefig(paths.figures / "example-fermi-lat.pdf", dpi=config.DPI)

### 2023-01-31 src/scripts/example-xmm-chandra.py

@@ -1,8 +1,9 @@
 import config
 import matplotlib.pyplot as plt
+import paths
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
 
 fig, ax = plt.subplots(figsize=figsize.inch)
 
-plt.savefig("example-xmm-chandra.pdf", dpi=config.DPI)
+plt.savefig(paths.figures /"example-xmm-chandra.pdf", dpi=config.DPI)

### 2023-01-31 src/scripts/config.py
Update figure scripts

@@ -17,14 +17,22 @@ FIGURE_WIDTH_AA = {
     "intermediate": 120 * u.mm,
 }
 
-CMAP = plt.get_cmap("viridis")
+CMAP_NAME = "viridis"
+CMAP = plt.get_cmap(CMAP_NAME)
 
-COLORS = CMAP([0, 0.25, 0.5, 0.75, 1])
-COLORS = np.append(COLORS, [[216 / 255, 27 / 255, 96 / 255, 1.]], axis=0)
+COLORS = {
+    "white": "#ffffff",
+    "red": [216 / 255, 27 / 255, 96 / 255, 1.],
+}
+
+for idx, color in enumerate(CMAP([0, 0.25, 0.5, 0.75, 1])):
+    COLORS[f"{CMAP_NAME}-{idx}"] = color
+
+COLORS_CYCLE = [f"{CMAP_NAME}-{idx}" for idx in range(5)]
 
 PROP_CYCLER = [
-    cycler(color=COLORS) +
-    cycler(linestyle=["-", "--", ":", "-.", ".", "-.-"])
+    cycler(color=[value for key, value in COLORS.items() if key in COLORS_CYCLE]) +
+    cycler(linestyle=["-", "--", ":", "-.", "."])
 ]
 
 

### 2023-01-31 src/scripts/patches.py

@@ -17,8 +17,8 @@ for x in range(0, 2 * image_size[0], 6):
             xy=(x, y),
             width=patch_size[0],
             height=patch_size[1],
-            facecolor=config.COLORS[1],
-            edgecolor="k",
+            facecolor=config.COLORS["viridis-1"],
+            edgecolor="None",
             alpha=0.2,
         )
 
@@ -29,12 +29,12 @@ rectangle = Rectangle(
     width=patch_size[0],
     height=patch_size[1],
     facecolor="None",
-    edgecolor=config.COLORS[-1],
+    edgecolor=config.COLORS["red"],
     lw=1,
 )
 ax.add_patch(rectangle)
 
-ax.text(x=16, y=20.5, s="8 x 8 Patch", color=config.COLORS[-1], ha="center")
+ax.text(x=16, y=20.5, s="8 x 8 Patch", color=config.COLORS["red"], ha="center")
 
 offset = patch_size[0] // 2
 ax.set_xlim(offset, image_size[0] - offset - offset // 2)

### 2023-01-31 src/scripts/image-norms.py
Add jolideco dependency

@@ -2,6 +2,7 @@ import config
 import matplotlib.pyplot as plt
 import numpy as np
 import paths
+from jolideco.utils.norms import NORMS_REGISTRY
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618)
 

### 2023-01-31 src/scripts/example-chandra.py
[showyourwork] overleaf sync

@@ -1,9 +1,12 @@
 import config
-import paths
 import matplotlib.pyplot as plt
+import paths
+from astropy.io import fits
+from astropy.wcs import WCS
 
-figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+figsize = config.FigureSizeAA(aspect_ratio=2.5, width_aa="two-column")
 
-fig, ax = plt.subplots(figsize=figsize.inch)
+wcs = WCS()
+fig, ax = plt.subplots(figsize=figsize.inch, ncols=3, subplot_kw={"projection": wcs})
 
-plt.savefig(paths.figures /"example-chandra.pdf", dpi=config.DPI)
+plt.savefig(paths.figures / "example-chandra.pdf", dpi=config.DPI)

### 2023-01-31 src/scripts/image-norms.py

@@ -6,14 +6,28 @@ from jolideco.utils.norms import NORMS_REGISTRY
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618)
 
+init_kwargs = {
+    "fixed-max": {"max_value": 10},
+    "asinh": {"alpha": 0.1, "beta": 10},
+    "atan": {},
+}
+
 fig = plt.figure(figsize=figsize.inch)
-ax = fig.add_axes([0.1, 0.1, 0.88, 0.88])
+ax = fig.add_axes([0.15, 0.2, 0.80, 0.77])
 
-x = np.linspace(0, 2, 100)
-ax.plot(x, x, label="Linear")
-ax.plot(x, x**0.5, label="Square Root")
-ax.plot(x, np.arcsinh(x), label="Arcsinh")
-ax.plot(x, np.clip(x, 0, 1), label="Clip")
+x = np.linspace(0, 15, 100)
 
+for name, norm_cls in NORMS_REGISTRY.items():
+    print(name)
+    if name not in init_kwargs:
+        continue
+
+    norm = norm_cls(**init_kwargs[name])
+    ax.plot(x, norm(x), label=name)
+
+ax.set_xlim(0, 15)
+ax.set_ylim(0, 1.2)
+ax.set_xlabel("Pixel value")
+ax.set_ylabel("Normalised pixel value")
 plt.legend()
 plt.savefig(paths.figures / "image-norms.pdf", facecolor="w", dpi=300)

### 2023-01-31 src/scripts/example-chandra.py
Improve image norm and chandra plot

@@ -1,12 +1,63 @@
 import config
 import matplotlib.pyplot as plt
+import numpy as np
 import paths
 from astropy.io import fits
+from astropy.visualization import simple_norm
 from astropy.wcs import WCS
 
-figsize = config.FigureSizeAA(aspect_ratio=2.5, width_aa="two-column")
+figsize = config.FigureSizeAA(aspect_ratio=13 / 4.0, width_aa="two-column")
+
+
+fig = plt.figure(figsize=(13, 4))
+# norm = simple_norm(npred.data, stretch="asinh", asinh_a=0.01, max_cut=350)
 
 wcs = WCS()
-fig, ax = plt.subplots(figsize=figsize.inch, ncols=3, subplot_kw={"projection": wcs})
+height = 0.8
+ax_counts = fig.add_axes([0.01, 0.12, 0.4, height], projection=wcs)
+ax_npred = fig.add_axes([0.28, 0.12, 0.4, height], projection=wcs)
+ax_npred_rl = fig.add_axes([0.55, 0.12, 0.4, height], projection=wcs)
+ax_cbar = fig.add_axes([0.9, 0.12, 0.02, height])
+
+ax_counts.set_title("Counts")
+ax_npred.set_title("Reconstruction Jolideco")
+ax_npred_rl.set_title("Reconstruction RL $N_{iter} = 100$")
+
+
+# crop = slice(None)
+# psf_data = dataset_4683["psf"][crop, crop] * norm.vmax
+# size = psf_data.shape[0] * height / counts.data.shape[0]
+
+# ax_psf = fig.add_axes([0.05, 0.7, size, size])
+# ax_psf.imshow(psf_data, cmap=cmap, interpolation="gaussian", norm=norm)
+# ax_psf.set_title("PSF", color="white", fontweight="bold")
+# ax_psf.set_xticks([])
+# ax_psf.set_yticks([])
+
+# for spine in ax_psf.spines.values():
+#     spine.set_edgecolor("white")
+#     spine.set_lw(1.2)
+
+# counts.plot(
+#     ax=ax_counts,
+#     norm=norm,
+#     cmap=cmap,
+#     interpolation="None",
+# )
+# npred.plot(ax=ax_npred, norm=norm, interpolation="gaussian", cmap=cmap)
+# npred_rl.plot(ax=ax_npred_rl, norm=norm, interpolation="gaussian", cmap=cmap)
[…]

### 2023-01-31 src/scripts/image-norms.py

@@ -18,7 +18,6 @@ ax = fig.add_axes([0.15, 0.2, 0.80, 0.77])
 x = np.linspace(0, 15, 100)
 
 for name, norm_cls in NORMS_REGISTRY.items():
-    print(name)
     if name not in init_kwargs:
         continue
 

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amssymb}
-cd ..
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
     \subsubsection{Image Normalisation}
-    Astromomical images typically show a much higher dynamic range compared to 
-    natural images. This is mostly due to the existence of point sources, which rarely occur
-    in natural images, but a very common in astronomical images because of objects 
-    at hig distances.
+    Astronomical images typically show a much higher dynamic range compared to 
+    natural images. This is mostly due to the existence of real point sources, which rarely occur
+    in natural images, but a very common in astronomical images because of compact objects 
+    at high distances. The high dynamic range challenges any image reconstruction
+    algorithm.
+
     The GMM patch prior is learned on normalized images, where the intensity values
-    are constrained between 0 and 1. To evaluate For the likelihood term the image
-    intensity need to be conserved.
+    are constrained between 0 and 1. To evaluate the GMM patch prior on the 
+    model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
+    in the same dynamic range between 0 and 1.
+
+    \begin{figure}[ht!]
+        \script{image-norms.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/image-norms.pdf}
+            \caption{
+                Various image norms with different dynamic behaviour.
+            }
+            \label{fig:patches}
+        \end{centering}
+    \end{figure}
 
@@
     \subsection{Deep \chandra Observation}
+    \begin{figure*}[ht!]
+        \script{example-chandra.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/example-chandra.pdf}
+            \caption{
+                Chandra Example
+            }
+            \label{fig:example-chandra}
+        \end{centering}
+    \end{figure*}
 
     \subsection{Combined \xmm and \chandra Observation}
+    \begin{figure*}[ht!]
+        \script{example-xmm-chandra.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/example-xmm-chandra.pdf}
+            \caption{
+                Chandra Example
+            }
+            \label{fig:example-xmm-chandra}
+        \end{centering}
+    \end{figure*}
 
     \subsection{\fermi Event Classes}
+    \begin{figure*}[ht!]
+        \script{example-fermi-lat.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
+            \caption{
+                Chandra Example
+            }
+            \label{fig:example-fermi-lat}
+        \end{centering}
+    \end{figure*}
 

### 2023-01-31 src/scripts/config.py
Adapt image norm plot

@@ -1,10 +1,11 @@
 """General configuration for mpl plotting scripts"""
 from pathlib import Path
+
 import matplotlib.pyplot as plt
-from astropy import units as u
 import numpy as np
-from cycler import cycler
+from astropy import units as u
 from astropy.units import imperial
+from cycler import cycler
 
 BASE_PATH = Path(__file__).parent.parent
 
@@ -22,7 +23,7 @@ CMAP = plt.get_cmap(CMAP_NAME)
 
 COLORS = {
     "white": "#ffffff",
-    "red": [216 / 255, 27 / 255, 96 / 255, 1.],
+    "red": [216 / 255, 27 / 255, 96 / 255, 1.0],
 }
 
 for idx, color in enumerate(CMAP([0, 0.25, 0.5, 0.75, 1])):
@@ -30,10 +31,9 @@ for idx, color in enumerate(CMAP([0, 0.25, 0.5, 0.75, 1])):
 
 COLORS_CYCLE = [f"{CMAP_NAME}-{idx}" for idx in range(5)]
 
-PROP_CYCLER = [
-    cycler(color=[value for key, value in COLORS.items() if key in COLORS_CYCLE]) +
-    cycler(linestyle=["-", "--", ":", "-.", "."])
-]
+PROP_CYCLER = cycler(
+    color=[value for key, value in COLORS.items() if key in COLORS_CYCLE]
+) + cycler(linestyle=["-", "--", ":", "-.", "."])
 
 
 class FigureSizeAA:

### 2023-01-31 src/scripts/image-norms.py

@@ -17,12 +17,17 @@ ax = fig.add_axes([0.15, 0.2, 0.80, 0.77])
 
 x = np.linspace(0, 15, 100)
 
-for name, norm_cls in NORMS_REGISTRY.items():
+props = config.PROP_CYCLER()
+
+for name, norm_clas in NORMS_REGISTRY.items():
     if name not in init_kwargs:
         continue
 
+    prop = next(props)
+
+    norm_cls = NORMS_REGISTRY[name]
     norm = norm_cls(**init_kwargs[name])
-    ax.plot(x, norm(x), label=name)
+    ax.plot(x, norm(x), label=name, **prop)
 
 ax.set_xlim(0, 15)
 ax.set_ylim(0, 1.2)

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     low counts observations.
-    Most generally we assume our total dataset consists of $M$ individual
+    Most generally we assume our total dataset consists of $J$ individual
     observations of the same region of the sky, which are jointly
@@
 
-    Or a even an arbitrary combination of the possibilities listed above.
+    Or even an arbitrary combination of the possibilities listed above.
 
-    For each individual observation $m$ the predicted counts can be modelled by forward
+    For each individual observation $j$ the predicted counts can be modelled by forward
     folding the unknown flux image $\mathbf{x}$ with the individual (per observation) instrument response:
@@
         \label{eq:model}
-        \mathbf{\lambda}_m = \mathrm{PSF}_m \circledast \left(\mathbf{E}_m \cdot (\mathbf{x} + \mathbf{B}_m) \right)
+        \boldsymbol{\lambda}_j = \mathrm{PSF}_j \circledast \left(\mathbf{E}_j \cdot (\mathbf{x} + \mathbf{B}_j) \right)
     \end{equation}
 
-    Where the expected counts $\lambda_i$ are given by the convolution of the true underlying
-    flux distribution $\mathbf{x}$ with the $\mathrm{PSF}$. Additionally
-    the observation specific exposure $\mathbf{E}$ and background emission $\mathbf{B}$ can be
+    Where the expected counts $\lambda_j$ are given by the convolution of the unknown 
+    flux image $\mathbf{x}$ with the observation specific point spread function $\mathrm{PSF}_j$. Additionally
+    the observation specific exposure $\mathbf{E}_j$ and background emission $\mathbf{B_j}$ can be
     taken into account.
 
-    Given a single observation $m$ of a true underlying flux distribution
+    Given a single observation $j$ of an unknown flux image
     $\mathbf{x}$ and assuming the noise in each pixel $i$ in the recorded counts image
-    $\mathbf{d}$ follows a Poisson distribution, the total likelihood $\mathcal{L}_m$
+    $\mathbf{D_j}$ follows a Poisson distribution, the likelihood $\ell_j$
     of obtaining the measured image from a model image of the expected
-    counts $\lambda_i$ with $N$ pixels is given by:
+    counts $\boldsymbol{\lambda_j}$ with $N$ pixels is given by:
 
@@
         \label{eq:poisson}
-        \mathcal{L}_m\left( \mathbf{d} | \mathbf{\lambda} \right) = \prod_i^N \frac{{e^{ - d_i } \lambda_i ^ {d_i}}}{{d_i!}}
+        \ell\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - D_{j,i} } \lambda_i ^ {D_{j,i}}}}{{D_{j,i}!}}
     \end{equation}
@@
         \label{eq:cash}
-        \mathcal{C}\left( \mathbf{d} | \mathbf{\lambda} \right) = \sum_i^N \lambda_i - d_i \log{\lambda_i}
+        \mathcal{C}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \sum_{i=1}^N \lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}
     \end{equation}
+
+    By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given a unknown flux image $\mathbf{x}$:
+
+    \begin{equation}
+        \label{eq:total}
+        \mathcal{L}\left( \mathbf{D} | \mathbf{x} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)
+    \end{equation}
+
+    Using the Maximum Likelihood Estimation (MLE) we could estimate
+
+    \todo{this sum corresponds to the loop over datasets in machine learning... }
+
+    \subsection{Priors}
+    Just include patch priors, or LIRA as well, or uniform?
 
@@
         \label{eq:bayes}
-        P(\theta|\textbf{D}) = P(\theta ) \frac{\mathcal{C}(\textbf{D} |\theta)}{P(\textbf{D})}
+        P(\mathbf{x}|\textbf{D}) = \mathcal{P}(\mathbf{x} ) \frac{\mathcal{L}(\textbf{D} |\mathbf{x})}{ \mathcal{P} (\textbf{D})}
     \end{equation}
@@
         \label{eq:total}
-        \mathcal{L}\left( \mathbf{d_m} | \mathbf{x} \right) = \sum_m^M \mathcal{C}\left( \mathbf{d_m} | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x})
+        \mathcal{L}\left( \mathbf{d} | \mathbf{x} \right) = \sum_m^M \mathcal{C}\left( \mathbf{d_m} | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x})
     \end{equation}
@@
     does not really make it a prior, more a regularisation term...}
-
-    \subsection{Priors}
-    Just include patch priors, or LIRA as well, or uniform?
 
@@
 
-    \subsection{Calibration of Predicted Counts}
-    Each dataset comes with systematic errors on absolute position and background normalisation
-
-    \begin{itemize}
-        \item allow for systematic shifts between observations 
-        \item allow for background scaling per observation $\alpha_m$
-    \end{itemize}
+    \subsection{Systematic Errors of Predicted Counts}
+    Each measured counts image $\mathbf{D_j}$ is associated with systematic errors.
+    This includes e.g. the absolute position of the sources in the image and the
+    normalisation of the background image, which can vary from observation to observation.
+    To account for this we extend the model for the predicted
+    counts introduced in Eq.~\ref{eq:model}, by a background normalisation factor
+    $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$,
+    which is specific for each observation. This gives the following modified model definition:
 
@@
         \label{eq:model-npred-calibration}
-        \mathbf{\lambda}_m = \mathrm{PSF}_m \circledast \left(\mathbf{E}_m \cdot (\phi_m(\mathbf{x}| \delta_x, \delta_y) + \alpha_m \cdot \mathbf{B}_m) \right)
+        \mathbf{\lambda}_j = \mathrm{PSF}_j \circledast \left(\mathbf{E}_j \cdot (\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j}) + \alpha_j \cdot \mathbf{B}_j) \right)
     \end{equation}
 
-    Show example residual images before and after calibration...
+    In practice one observation is used as a reference and its corresponding
+    systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during
+    optimization.
 
@@
     flexible and interchangeable, such as choice of image normalisation scales,
-    the choice of GMM models, optimization methods and serilisation formats for the 
+    the choice of GMM models, optimization methods and serialisation formats for the 
     reconstruction results as well as corresponding diagnostic information
-    such as the trace of the posterior and prior likelihood values.
-
+    such as the trace of the posterior and prior and likelihood values.
     The package is available at \url{https://github.com/jolideco/jolideco}
@@
 
-    In addition we use \texttt{Scikit-Learn}~\citep{Skimage2014} to learn the GMM.
-
-    We use \texttt{Astropy}~\citep{Astropy2018} for FITS serialisation and
-    handling WCS transforms.
-
-    We use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and
+    We also use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and
     \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
-
+    To learn the Gaussian Mixture Models from patches we the standard implementation
+    provided in the \texttt{Scikit-Learn}~\citep{Skimage2014} package. To handle the 
+    serialisation of images to the FITS data format and to handle world coordinate
+    systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
     For optimization and internal data handling we use \texttt{PyTorch}~\citep{Pytorch2019}.
@@
     as well as large images. Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
+
+    \subsection{Optimization Strategy}
+
+    \begin{itemize}
+        \item First run with uniform prior, to get a rough estimate
+        \item First optimize the systematic error parameters
+        \item The go for the optimization uisng the patch prior, which can be computationally costly
+    \end{itemize}
 

### 2023-02-07 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator{\arcsinh}{arcsinh}
 \newcommand{\chandra}{\textit{Chandra}~}
@@
 
-    In literature there have been multiple efforts to
+    In literature there have been multiple efforts to correct the degrading of the images
+    and maximise the scientific use.
 
-    Any astronomical observation is affected by the limited angular resolution of the telescope.
+    Any astronomical observation is affected by the limited angular resolution of the telescope. However the problem is not specific to astronomy and has been tried to 
+    be solved for fluoresence image or others...
 
     \begin{itemize}
-        \item Richardson \& Lucy (RL)\cite{Richardson1972} \cite{Lucy1974}
+        \item Standard baseline method is Richardson \& Lucy (RL), see \cite{Richardson1972} and \cite{Lucy1974}
         \item Joint likelihood RL: \cite{Ingaramo2014} has found that RL take the best out of each image and create a "merged" image
@@
     In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possibly for most network architectures.
+Except for e.g.
+normalising flows \todo{there are refences where NFs have bee used as priors...}
 
@@
     flux image $\mathbf{x}$ with the observation specific point spread function $\mathrm{PSF}_j$. Additionally
-    the observation specific exposure $\mathbf{E}_j$ and background emission $\mathbf{B_j}$ can be
-    taken into account.
+    an observation specific image of the exposure $\mathbf{E}_j$ and background emission $\mathbf{B_j}$ can be
+    optionally taken into account.
 
@@
     $\mathbf{x}$ and assuming the noise in each pixel $i$ in the recorded counts image
-    $\mathbf{D_j}$ follows a Poisson distribution, the likelihood $\ell_j$
+    $\mathbf{D_j}$ follows a Poisson distribution, the likelihood $\mathcal{P}$
     of obtaining the measured image from a model image of the expected
@@
         \label{eq:poisson}
-        \ell\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - D_{j,i} } \lambda_i ^ {D_{j,i}}}}{{D_{j,i}!}}
+        \mathcal{P}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - D_{j,i} } \lambda_i ^ {D_{j,i}}}}{{D_{j,i}!}}
     \end{equation}
@@
 
-    By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given a unknown flux image $\mathbf{x}$:
+    By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
+
+    \begin{equation}
+        \label{eq:joint}
+        \mathcal{L}\left( \mathbf{D} | \mathbf{x} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)
+    \end{equation}
+
+    Using Maximum Likelihood Estimation (MLE) we could try to estimate $\mathbf{x}$ directly,
+    using some minimization procedure. However in general this represents an \textit{ill posed}
+    inverse problem.
+Solutions for $\mathbf{x}$ which yield similar likelihood values $\mathcal{L}_{\mathrm{Joint}}(\hat{\mathbf{x}})$ look very different from each other and might also look different compared to a
+    given ground truth, if available. Both the convolution operation as well as the level of noise lead
+    to a loss of information in the data which cannot easily be recovered.
+
+    \todo{this sum corresponds to the loop over datasets in machine learning... }
+
+    \subsection{A Posterirori Joint Likelihood}
+    When reconstructing images in the context of inverse problems we are operating
+    in a high dimensional parameter space, because each pixel represents
+    an independent parameter in the optimization process. By using prior information
+    we can introduce correlation between the parameters, reduce the \textit{effective}
+    dimensionality of the problem and guide the optimization process towards unique 
+    and more stable solutions.
+
+    Using Bayes rule we can estimate the a posteriori likelihood under a given prior instead:
+
+    \begin{equation}
+        \label{eq:bayes}
+        \mathcal{P}(\mathbf{x}|\textbf{D}) = \mathcal{P}(\mathbf{x} ) \frac{\mathcal{P}(\textbf{D} |\mathbf{x})}{ \mathcal{P} (\textbf{D})}
+    \end{equation}
+
+    And use a Maximum a Posteriori (MAP) approach to find an estimate for $\mathbf{x}$.
+    Taking the logarithm of Eq.~\ref{eq:bayes}, replacing the definition of the likelihood $\mathcal{P}(\mathbf{D}|\mathbf{x})$ with Eq.~\ref{eq:joint} and dropping the term $\mathcal{P}(\mathbf{D})$
+    which is independent of $\mathbf{x}$, we get the following expression for the log-posterior
+    likelihood $\mathcal{L}$ :
 
@@
         \label{eq:total}
-        \mathcal{L}\left( \mathbf{D} | \mathbf{x} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)
+        \mathcal{L}\left(\mathbf{x} | \mathbf{D} \right) = \sum_m^M \mathcal{C}\left( \mathbf{D_m} | \mathbf{x} \right) - \beta \cdot \mathcal{L}(\mathbf{x})
     \end{equation}
 
-    Using the Maximum Likelihood Estimation (MLE) we could estimate
+    Where $\mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)$ represents the summed log-likelihood
+    for an individual observation $j$. Additionally the function includes a prior term $\mathcal{P}(\mathbf{x})$
+    and a factor $\beta$ to adjust the weight of the prior with respect to the data likelihood term.
 
-    \todo{this sum corresponds to the loop over datasets in machine learning... }
+    \subsection{Patch Based Priors}
+    In general it is difficult to capture global image statistics in a prior likelihood
+    taking into account all pixel to pixel correlations. The size of the corresponding
+    correlation matrix would grow with the number of pixels squared. However
+    astronomical images typically show local correlations between pixels.
+    This means on smaller scales images often contain basic structure such as 
+    edges, corners, periodic patterns or small regions of constant brightness.
 
-    \subsection{Priors}
-    Just include patch priors, or LIRA as well, or uniform?
+    \cite{Zoran2011} build on this assumption for natural images and introduced the approach of
+    learning local image statistics based on patch priors. Their main idea
+    was to learn the statistics of natural images on a small
+    spatial scales instead. For this they proposed to split images from a
+    representative prior dataset into small patches of size 8x8~pixels.
+    Then they learned a 64 dimensional Gaussian Mixture Model (GMM) on the
+    extracted patches, treating each pixel as an independent dimension in
+    the model, with $k=200$ Gaussian components. They showed that the patch based GMM
+    prior led to much improved image reconstructions for multiple inverse problems 
+    such as denoising, deblurring and inpainting.
 
-    Bayes rule:
+    One of the main advantages of the GMM is the possibility to evaluate its log-likelihood
+    in closed form. It is given by:
 
     \begin{equation}
-        \label{eq:bayes}
-        P(\mathbf{x}|\textbf{D}) = \mathcal{P}(\mathbf{x} ) \frac{\mathcal{L}(\textbf{D} |\mathbf{x})}{ \mathcal{P} (\textbf{D})}
+        \ell_{GMM}(\theta) = \sum_{i=1}^n \log \left( \sum_{k=1}^K \pi_k N(x_i;\mu_k, \Sigma_k^2) \right )
     \end{equation}
 
-    The total objective function $\mathcal{L}$ is given by:
-    \begin{equation}
-        \label{eq:total}
-        \mathcal{L}\left( \mathbf{d} | \mathbf{x} \right) = \sum_m^M \mathcal{C}\left( \mathbf{d_m} | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x})
-    \end{equation}
-
-    Where $\mathcal{C}\left( \mathbf{d_m} | \mathbf{x} \right)$ represents the summed log-likelihood
-    for an individual observation $m$. Additionally the function includes a prior term $\mathcal{P}(\mathbf{x})$
-    and a factor $\beta$ to adjust the weight of the prior with respect to the likelihood term. \todo{To be clarified: the weight
-    does not really make it a prior, more a regularisation term...}
-
-    \subsubsection{Patch-Prior}
-    To improve the reconstruction quality of images for inverse problems,
-    such as denoising, inpainting or deconvolution it is useful to have prior
-    assumptions on the statistics of the image to guide the optimization based
-    image reconstruction process. However images are high
-    dimensional and thus difficult to capture the global image statistics
-    taking into account all pixel to pixel correlations.
-
-    By recognising that on smal scale images often contain basic structure such as 
-    edges, corners, periodic patterns or region of constant brightness. 
-    The idea of patch priors was first introduced by \cite{Zoran2011}.
-    Their main idea was to learn the statistics of natural images on a small
-    spatial scales instead. For this they proposed to split images from a
-    representative dataset into small patches of size 8x8 pixels.
-
-    Then they learned a 64 dimensional Gaussian Mixture Model (GMM) on the
-    extracted patches, treating each pixel as an independent dimension in
-    the model, with $k=200$ components. They showed that the GMM prior led to much improved
-    image reconstructions, compared to comparable approaches (which ones?).
-
-    One of the main advantages of the GMM is the possibility to
-    evaluate its log-likelihood in closed form. It is given by:
-
-    \begin{equation}
-        \ell_{GMM}(\theta) = \sum_{i=1}^n \log \left( \sum_{k=1}^K \pi_k N(x_i;\mu_k, \sigma_k^2) \right )
-    \end{equation}
-
+    Mean value is subtracted, which represents the assumption that image structure is independent
+    of the pixel amplitude.
     With parameters $\theta = \{\mu_1,\ldots,\mu_K,\sigma_1,\ldots,\sigma_K,\pi_1,\ldots,\pi_K\}$.
@@
     \end{equation}
+
+    The argmax is needed because of the locality...
 
@@
 
-    \subsubsection{Image Normalisation}
+    \subsubsection{Image Normalisation and Dynamic Range}
     Astronomical images typically show a much higher dynamic range compared to 
-    natural images. This is mostly due to the existence of real point sources, which rarely occur
-    in natural images, but a very common in astronomical images because of compact objects 
-    at high distances. The high dynamic range challenges any image reconstruction
-    algorithm.
+    natural images. This is mostly due to the existence of point sources, which
+    rarely occur in natural images. Astronomical point sources typically relate
+    to compact bright objects, such as active galactic nuclei at high distances,
+    or binary objects and stars at Galactic distances.
 
-    The GMM patch prior is learned on normalized images, where the intensity values
+    The high dynamic range of astronomical images challenges any deconvolution method.
+    To recover point sources accurately it is required to keep correlations with
+    neighbouring pixels low, while for extended source the opposite is true. Ideally
+    those contradicting requirements can be handled with a flexible prior assumption,
+    which adapts to the data, such as the patch based GMM prior.
+
+    The GMM patch prior is learned from other images whose pixel intensities
+    have no physical relationship of the intensities of the Poisson data we are
+    dealing with. Thus the GMM is learned on normalized images, where the intensity values
     are constrained between 0 and 1. To evaluate the GMM patch prior on the 
     model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
-    in the same dynamic range between 0 and 1.
+    in the same dynamic range between 0 and 1. Multiple common choices for such a
+    mapping function are shown in Fig.~\ref{fig:image-norms}.
 
@@
             }
-            \label{fig:patches}
+            \label{fig:image-norms}
         \end{centering}
@@
 
+    There are arguments for $\arcsinh(\mathbf{x})$, see e.g. \cite{Lupton2004}.
+
     \subsubsection{Cycle Spinning}
@@
     \begin{itemize}
-        \item Cycle spining by randomly shifting the image by a given number of pixels in x and y direction
-        \item Sub pixel cycle spinning, by randomly distributing the bightness of a given pixel to a 4 pixel grid
+        \item Cycle spinning by randomly shifting the image by a given number of pixels in x and y direction, e.g. used in \cite{Esch2004}
+        \item Sub pixel cycle spinning, by randomly distributing the brightness of a given pixel to a 4 pixel grid \todo{This is something I came up with to allow for point sources to have sub-pixel positions, but I never showed it actually works...}
         \item A randomly chosen patch grid, such that each pixel is at least covered once.
-        The random grid of patches was proposed by \cite{Parameswaran2018}.
+        The random grid of patches was proposed by \cite{Parameswaran2018}. This has the advantage of potentially speeding up the computation as well.
     \end{itemize}
@@
     \subsection{Cross Validation}
-    The use of multiple dataset allows to sue cross-validation to prevent overfitting.
+    Cross validation (CV) is an established method for model selection in statistics
+    and machine learning to prevent over-fitting the data. To perform CV the available
+    data is slit into a "training" and "validation" dataset. While optimizing the
+    log-likelihood value is monitored
+
+    The use of multiple dataset allows to use cross-validation to prevent overfitting.
     One of the standard techniques in "machine learning"...
+
+    Cross validation is feasible once sufficient data is available, which is e.g. the 
+    case for deep \chandra~observations.
+
+    CV as stopping rule for RL was proposed by \cite{Reeves1995}...
 
@@
     Each measured counts image $\mathbf{D_j}$ is associated with systematic errors.
-    This includes e.g. the absolute position of the sources in the image and the
-    normalisation of the background image, which can vary from observation to observation.
+    This includes e.g. the absolute position of the sources in the image (astrometry) and the normalisation of the background model, which can vary between observations.
     To account for this we extend the model for the predicted
@@
     $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$,
-    which is specific for each observation. This gives the following modified model definition:
+    which is specific for each observation. This yields the following modified model definition:
 
@@
     systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during
-    optimization.
+    optimization. An example of the effect of the positional shift and background
+    normalisation can be seen in Fig.~\ref{fig:npred-systematics}.
+
+    \subsubsection{Statistical Errors}
+    \begin{itemize}
+        \item Bootstrapping observations
+        \item Bootstrapping events
+        \item Hessian diagonal
+    \end{itemize}
 
@@
     this represents a high dimensional optimization problem.
-    Differentiable programming frameworks such as \texttt{PyTorch}
+    Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019}
     allow for solving these kind of high dimensional modeling problems, by using
-    back-propagation and adapted optimization methods such as stochastic gradient
-    decent.
+    back-propagation and adapted optimization methods for high dimensional
+    models such as stochastic gradient decent.
 
-    The \jolideco method was implemented as an independent Python package, 
+    We implemented the \jolideco method as an independent Python package, 
     based on \texttt{PyTorch} as optimization back-end. We tried to define a modular,
@@
 
-    \begin{itemize}
-        \item direct maximum a posteriori optimization using Pytorch etc.
-        \item auto gradient computation
-        \item ML optimizers such as ADAM
-        \item GPU support
-    \end{itemize}
-
     We also use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and
@@
     systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
-    For optimization and internal data handling we use \texttt{PyTorch}~\citep{Pytorch2019}.
+    For optimization and internal data handling we use \texttt{PyTorch}.
 
     \subsection{Jolideco GMM Library}
-    We provide a selection of learned GMMs to be used with the patch prior for reproducibility and download. 
-    Convenience for future users. \url{https://github.com/jolideco/jolideco-gmm-library}
+    On radio data \cite{Bouman2016} found the results to be mostly independent 
+    of the choice of data the GMM prior was learned on. In the low counts and high
+    noise regime we expect a much higher dependence of the results on choice of the
+    data the GMM was learned on. For testing we learned and provide a selection of GMMs to be used with the patch prior for download \footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
 
@@
     from the Berkley image database, by splitting the images into 8x8 patches. 
+    It was downloaded from \url{https://people.csail.mit.edu/danielzoran/epllcode.zip}.
 
-    \subsubsection{GLEAM data}
-    High signal to noise Radio data from \cite{HurleyWalker2022}
+    \subsubsection{GLEAM Radio Data}
+    A prior learned from astronomical data for analysis of Galactic sources with 
+    rich morphology, such as supernova remnants, pulsar winds etc.
+    High signal to noise Radio data from \cite{HurleyWalker2022}.
+    There is physical correlation between e.g. the very high energy gamma range
+    and radio as emission is produced from the same electron populations.
+    We download
 
     \subsubsection{NRAO Jets, Jets, Jets}
-    For the specific application of jet analysis we learned a GMM patch prior from jet images. It encodes the prior knowledge of the preferred direction of the jet.
+    For the specific application of jet detection in extract galactic data we we learned a GMM patch prior from jet images. It encodes the prior knowledge of the preferred direction of the jet.
 
@@
     We conduct as as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations
-    as well as large images. Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
+    as well as large images.
+
+    \begin{itemize}
+        \item Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
+        \item we tried the binary search tree as proposed in \cite{Parameswaran2018},
+        but without success, most likely because the native \texttt{Pytorch} support
+        for parallelisation speeds up the standard GMM quite a bit...
+        \item Could use a Neural Net for GMM component selection as proposed in
+        \item GPU support via \texttt{Pytorch}
+
+    \end{itemize}
 
     \subsection{Optimization Strategy}
-
+    In practice we employ the following optimization strategy:
     \begin{itemize}
+        \item the optimizer sees $\log{\mathbf{x}}$
         \item First run with uniform prior, to get a rough estimate
-        \item First optimize the systematic error parameters
-        \item The go for the optimization uisng the patch prior, which can be computationally costly
+        \item Then optimize the parameters associated to the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
+        \item Then we go for a full optimization using the patch prior, which can be computationally costly
+        \item we use ADAM (stochastic gradient decent), without decay
+        \item learning rate scheduling? So far just a fixed step size value of $1e-3$
     \end{itemize}
@@
 
-    The paper is available at \url{https://github.com/jolideco/jolideco-paper}
+    The paper is available at \url{https://github.com/jolideco/jolideco-paper} and can be reproduced using \cite{Luger2021}.
 
@@
 
-    Extend \jolideco to handl spectral dimension at the same time.
+    \begin{itemize}
+        \item Extend \jolideco to handle spectral dimension at the same time.
+        \item Use normalising flows for patch priors see e.g. https://arxiv.org/abs/2205.12021
+        \item 
+    \end{itemize}
 

### 2023-03-07 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amssymb}
+\usepackage{siunitx}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 \newcommand{\jolideco}{\textit{Jolideco}~}
+\newcommand{\aposteriori}{a~posteriori~}
+\newcommand{\gammaray}{$\gamma$-ray\xspace}
+\newcommand{\xray}{X-ray\xspace}
 \newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
@@
 % Title
-    \title{\jolideco: Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise}
+    \title{Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise}
 
@@
     \begin{abstract}
-        We present a new method for (Jo)int (li)kelihood  (Deco)nvolution (\jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
-        The method reconstructs an image from a set of observations
-        by optimizing the a-posteriori joint Poisson likelihood of all
-        observations under an patch based image prior. The patch
-        prior is parameterised by a standard Gaussian Mixture model (GMM)
-        learned from astronomical images at other wavelenghts and
-        adapted to the structures expected to see in the image.
+        We present a new method for Joint Likelihood Deconvolution (Jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
+        The method reconstructs a single flux image from a set of observations
+        by optimizing the \aposteriori joint Poisson likelihood of all
+        observations under a patch based image prior. The patch
+        prior is parameterised by a standard Gaussian Mixture model (GMM), which is
+        learned from astronomical images at other wavelengths.
+        During reconstruction the GMM adapted to the structures
+        in the data by finding the the most likely combination of 
+        patches. 
         By applying the method to simulated data we show that
-        the combination of mutiple observations leads to an
+        the combination of multiple observations leads to an
         improved reconstruction quality in the regime with S/N ratio of.
@@
         to alternative standard methods such as the Richardson-Lucy method.
+        We also show that the method can be highly adapted to various 
+        analysis scenarios by learning problem specific GMM priors
+        such as images of extragalactic or Galactic sources.
     \end{abstract}
@@
     \section{Introduction}
-    The quality of all astronomical images is affected by the limited angular resolution of the instrument
-    or telescope. In addition the images are affected by the presence of noise and non-uniform exposure.
+    The angular resolution of any physical or astronomical imaging process is inherently limited by the instrument or telescope used.
+Furthermore, the quality of the resulting image is affected by background or instrumental measurement noise and non-uniform exposure.
+This is especially true in the low signal-to-noise regime.
+E.g.
+\xray and \gammaray~astronomy
 
@@
     Any astronomical observation is affected by the limited angular resolution of the telescope. However the problem is not specific to astronomy and has been tried to 
-    be solved for fluoresence image or others...
+    be solved for fluorescence microscopy or others...
+
+    We assume non-blind deconvolution, so the there is prior information of the PSF
 
@@
         \item Standard baseline method is Richardson \& Lucy (RL), see \cite{Richardson1972} and \cite{Lucy1974}
+         \item  Problem of RL decomposing structures into point sources: \cite{Reeves1994} \cite{Fish1995}
+         \item regularised RL , e.g. total variation \citep{Dey2006} or maximum entropy \citep{Bi1994} \todo{other references?}
         \item Joint likelihood RL: \cite{Ingaramo2014} has found that RL take the best out of each image and create a "merged" image
-        \item  Problem of RL decomposing structures into point sources: \cite{Reeves1994} \cite{Fish1995}
         \item Multi-scale LIRA prior of course: \cite{Esch2004, Connors2011}, advantage of error estimates / Bayesian sampling.
@@
 Just "smoothness"
-        \item What abput d3po and d4po? Priors based on physical assumptions, decomposition into point and diffuse flux, but in 3d/4d \cite{Selig2015}\cite{Pumpe2018}
+        \item What abput d3po and d4po?
+Priors based on physical assumptions, decomposition into point and diffuse flux, but in 3d/4d \cite{Selig2015}\cite{Pumpe2018}.
+The smoothness assumption works for large scale emission, but leads to artifacts in the galactic plane...
     \end{itemize}
@@
 Except for e.g.
-normalising flows \todo{there are refences where NFs have bee used as priors...}
+normalising flows \todo{there are references where NFs have bee used as priors...}
+
+    \begin{itemize}
+    \item diversity of astronomical images is high, one would need lots of training data
+    \item Given a set of training images one could generate training data by forward folding with a known PSF model
+    and adding Poisson noise
+    \item however this would require training a new network for each PSF and noise level just to learn the task.
+    This is a high computational effort. 
+    \item By allowing multiple inputs one could still try to estimate a common flux image \todo{so far I have not heard
+    about something like this...}
+    \end{itemize}
+
+    Shown to work for e.g. deconvolution of Galaxy images SDSS \todo{reference?} and post-processing of regularised RL results \todo{Starck et al.}
 
@@
 
-    For each individual observation $j$ the predicted counts can be modelled by forward
-    folding the unknown flux image $\mathbf{x}$ with the individual (per observation) instrument response:
+    For each individual observation $j$ the predicted counts can be modelled by \textit{forward folding} the unknown flux image $\mathbf{x}$ through the individual instrument response:
 
@@
         \label{eq:model}
-        \boldsymbol{\lambda}_j = \mathrm{PSF}_j \circledast \left(\mathbf{E}_j \cdot (\mathbf{x} + \mathbf{B}_j) \right)
+        \boldsymbol{\lambda}_j(\mathbf{x}) = \mathrm{PSF}_j \circledast \left(\mathbf{E}_j \cdot (\mathbf{x} + \mathbf{B}_j) \right)
     \end{equation}
@@
         \label{eq:poisson}
-        \mathcal{P}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - D_{j,i} } \lambda_i ^ {D_{j,i}}}}{{D_{j,i}!}}
+        P\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - D_{j,i} } \lambda_{i,j} ^ {D_{j,i}}}}{{D_{j,i}!}}
     \end{equation}
@@
         \label{eq:cash}
-        \mathcal{C}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \sum_{i=1}^N \lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}
+        \mathcal{C}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \frac{1}{N}\sum_{i=1}^N \lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}
     \end{equation}
 
+    To account for the possibility of different datasets having a different number of pixels we divide by $N$ (\todo{Does this need more justification...?}).
     By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
@@
 
-    Using Maximum Likelihood Estimation (MLE) we could try to estimate $\mathbf{x}$ directly,
-    using some minimization procedure. However in general this represents an \textit{ill posed}
+    Using Maximum Likelihood Estimation (MLE) we could try to get an estimate $\hat{\mathbf{x}}$ directly,
+    using some optimization procedure. However in general this represents an \textit{ill posed}
     inverse problem.
-Solutions for $\mathbf{x}$ which yield similar likelihood values $\mathcal{L}_{\mathrm{Joint}}(\hat{\mathbf{x}})$ look very different from each other and might also look different compared to a
-    given ground truth, if available. Both the convolution operation as well as the level of noise lead
+Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}_1})$ look very different from each other and might also look different compared to a given ground truth, if available.
+    Both the convolution operation as well as the level of noise lead
     to a loss of information in the data which cannot easily be recovered.
+    The likelihood surface shows many local, close-by minima. Depending on the initial estimate for $\mathbf{x}$ and the minimization algorithm the MLE based estimate
+    is likely to only find such a local minimum. This is fundamentally the reason for RL decomposing estimates into point sources, described in the previous section.
 
-    \todo{this sum corresponds to the loop over datasets in machine learning... }
+    \todo{this sum corresponds to the loop over data sets in machine learning... }
 
-    \subsection{A Posterirori Joint Likelihood}
+    \subsection{A Posteriori Joint Likelihood}
     When reconstructing images in the context of inverse problems we are operating
-    in a high dimensional parameter space, because each pixel represents
+    in a high dimensional parameter space, because each pixel in the image represents
     an independent parameter in the optimization process. By using prior information
-    we can introduce correlation between the parameters, reduce the \textit{effective}
+    we can introduce correlations between the parameters, to reduce the \textit{effective}
     dimensionality of the problem and guide the optimization process towards unique 
@@
 
-    Using Bayes rule we can estimate the a posteriori likelihood under a given prior instead:
+    Using Bayes rule we can estimate the \aposteriori likelihood under a given prior:
 
@@
         \label{eq:bayes}
-        \mathcal{P}(\mathbf{x}|\textbf{D}) = \mathcal{P}(\mathbf{x} ) \frac{\mathcal{P}(\textbf{D} |\mathbf{x})}{ \mathcal{P} (\textbf{D})}
+        P(\mathbf{x}|\textbf{D}) = P(\mathbf{x} ) \frac{P(\textbf{D} |\mathbf{x})}{P(\textbf{D})}
     \end{equation}
 
-    And use a Maximum a Posteriori (MAP) approach to find an estimate for $\mathbf{x}$.
-    Taking the logarithm of Eq.~\ref{eq:bayes}, replacing the definition of the likelihood $\mathcal{P}(\mathbf{D}|\mathbf{x})$ with Eq.~\ref{eq:joint} and dropping the term $\mathcal{P}(\mathbf{D})$
+    And use a Maximum A Posteriori (MAP) approach to find an estimate for $\mathbf{x}$.
+    Taking the logarithm of Eq.~\ref{eq:bayes}, replacing the definition of the likelihood
+    $P(\mathbf{D}|\mathbf{x})$ with Eq.~\ref{eq:joint} and dropping the normalisation term $P(\mathbf{D})$
     which is independent of $\mathbf{x}$, we get the following expression for the log-posterior
@@
         \label{eq:total}
-        \mathcal{L}\left(\mathbf{x} | \mathbf{D} \right) = \sum_m^M \mathcal{C}\left( \mathbf{D_m} | \mathbf{x} \right) - \beta \cdot \mathcal{L}(\mathbf{x})
+        \mathcal{L}\left(\mathbf{x} | \mathbf{D} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x})
     \end{equation}
@@
     Where $\mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)$ represents the summed log-likelihood
-    for an individual observation $j$. Additionally the function includes a prior term $\mathcal{P}(\mathbf{x})$
-    and a factor $\beta$ to adjust the weight of the prior with respect to the data likelihood term.
+    for an individual observation $j$. Additionally the function includes a log-prior
+    term $\mathcal{P}(\mathbf{x})$ and a factor $\beta$ to adjust the weight of the prior with respect to the joint log likelihood term.
+The parameter $\beta$ can be seen as a hyper-parameter, chosen by the user
+    to quantify their belief in the correctness of the chosen prior distribution.
+    \todo{this is somewhat dissatisfying...but in practice very common...see e.g. any kind of regularisation...if there is enough data cross validation could be used to tune this hyper-parameter}.
 
@@
     taking into account all pixel to pixel correlations. The size of the corresponding
-    correlation matrix would grow with the number of pixels squared. However
-    astronomical images typically show local correlations between pixels.
-    This means on smaller scales images often contain basic structure such as 
-    edges, corners, periodic patterns or small regions of constant brightness.
+    correlation matrix would grow with the number of pixels squared and thus quickly
+    becomes computationally untraceable. However astronomical images typically only
+    show local correlations between pixels. This is because the spatial
+    scale of astrophysical processes in an image is always limited by the finite
+    interaction time and the fact that the interaction cannot propagate
+    faster than the speed of light. This means on smaller scales astronomical
+    images often contain basic structures such as edges, corners, filaments or
+    periodic patterns formed by local astrophysical processes.
 
-    \cite{Zoran2011} build on this assumption for natural images and introduced the approach of
-    learning local image statistics based on patch priors. Their main idea
-    was to learn the statistics of natural images on a small
-    spatial scales instead. For this they proposed to split images from a
-    representative prior dataset into small patches of size 8x8~pixels.
-    Then they learned a 64 dimensional Gaussian Mixture Model (GMM) on the
-    extracted patches, treating each pixel as an independent dimension in
-    the model, with $k=200$ Gaussian components. They showed that the patch based GMM
-    prior led to much improved image reconstructions for multiple inverse problems 
-    such as denoising, deblurring and inpainting.
+    \todo{This is interesting, but move to intro...}
+    \cite{Zoran2011} build on very similar assumption for natural images.
+    Instead of assuming a fixed local correlation structures, such as smoothness
+    they proposed to learn the local correlation structure on millions of patches
+    extracted from natural images.
 
-    One of the main advantages of the GMM is the possibility to evaluate its log-likelihood
-    in closed form. It is given by:
+    For this they proposed to split training images from representative
+    data sets into small patches of size 8x8~pixels and fit a 64 dimensional
+    Gaussian Mixture Model (GMM) to the distribution of extracted patches. Each pixel of the patch 
+    is thereby treated as an independent dimension in the model. In total
+    they chose to use $k=200$ Gaussian components.
+
+    To use the GMM in reconstruction they introduce the expected patch likelihood (EPLL).
+
+    They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as de-noising, de-blurring and inpainting.
+
+    Using half quadratic splitting and the Wiener filter solution, which is not possible
+    in our case. Instead we choose a direct optimization by relying on differentiable
+    programming later.
+
+    In practice we are interested in the likelihood of a given structure in a patch and
+    So we subtract the mean value of a given patch. This represents the assumption that
+    the image structure is independent of the total flux contained in the patch.
+
+    One of the main advantages of the GMM is the possibility to evaluate its likelihood
+    in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
 
     \begin{equation}
-        \ell_{GMM}(\theta) = \sum_{i=1}^n \log \left( \sum_{k=1}^K \pi_k N(x_i;\mu_k, \Sigma_k^2) \right )
+        \label{eq:gmm}
+        P_{GMM}(\mathbf{x}_n) = \sum_{k=1}^K \pi_k N(\mathbf{x}_n| \boldsymbol{\mu}_k, \boldsymbol{\Sigma}_k^2)
     \end{equation}
 
-    Mean value is subtracted, which represents the assumption that image structure is independent
-    of the pixel amplitude.
-    With parameters $\theta = \{\mu_1,\ldots,\mu_K,\sigma_1,\ldots,\sigma_K,\pi_1,\ldots,\pi_K\}$.
-    To use the learned GMM as prior for the reconstruction of another image, the image is split into
-    overlapping patches. For each of the patches the log-likelihood for each of the GMM components is
-    evaluated. The resulting grid of overlapping patches is illustrated in Figure~\ref{fig:patches}.
+    Where $N$ is a Gaussian distribution, $\boldsymbol{\mu}_k$ the vector of means for
+    a given component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix
+    and $\pi_k$ the weight the component. The different weights are required to sum to unity such that $\sum_{k=1}^N\pi_k = 1$.
 
-    For each 8x8 pixel patch the likelihood of all components of the GMM is evaluated. Then 
+    From Equation~\ref{eq:gmm} we can also derive the log-likelihood for a specific choice of the component $k$:
+
     \begin{equation}
-        \hat{k} = \argmax{\ell_{GMM}(\theta)}
+    \begin{split}
+    \mathcal{P}_{GMM}(k| \mathbf{x}_n) = -\frac{1}{2} \left[ \right. d \log(2\pi)
+    + \log(|\boldsymbol \Sigma_{k}|)\\
+    + (\mathbf{x}_n - \boldsymbol{\mu}_{k})^T \Sigma^{-1}_{k}(\mathbf{x}_n - \boldsymbol{\mu}_{k}) \left. \right]
+    \end{split}
     \end{equation}
 
-    The argmax is needed because of the locality...
+    If we split the image into non-overlapping patches, we can find for each noisy patch $\mathbf{x}_n$ the GMM component $\hat{k}_n$, which maximises the log-likelihood of the GMM:
 
     \begin{equation}
-        \mathcal{P}(x) = \sum_n \log{p_{\hat{k}}(\mathbf{P}_n x)}
+        \hat{k}_n = \underset{k \in \{1, ..., N\} }{\argmax}{\mathcal{P}_{GMM}(k| \mathbf{x}_n)}
+    \end{equation}
+    \vspace{0.2em}
+
+    As the number of components in the GMM is limited we can do this simply by evaluating the likelihood for each of the components and choose the one with
+    the maximum value of the log-likelihood. To finally evaluate the log-likelihood
+    of the total image we can sum up the log-likelihood of the individual patches:
+
+    \begin{equation}
+        \mathcal{P}(\mathbf{x}, \mathbf{k}) = \sum_{n = 1}^N \mathcal{P}_{GMM}(\hat{k}_n | \mathbf{P}_n \mathbf{x})
     \end{equation}
 
-    $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch
-    from the image $\mathbf{x}$ to be reconstructed.
-    $p(\mathbf{P}_n x)$ is the probability of that patch
-    under the GMM.
+    Where $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch
+    from the image $\mathbf{x}$ to be reconstructed. This way the index $k$ that identifies the GMM component becomes a hyper-parameter in the model and is optimized along with the image $\mathbf{x}$.
+
+    \begin{itemize}
+        \item the case of non-overlapping patches is rather simple
+        \item for overlapping patches we have to make a few more approximations
+        \item either we neglect the correlation between overlapping patches
+        \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of "per patch optimization". However optimization on discrete 
+        values is not easily possible in Pytorch. However here is one idea:
+        group the GMM components by similarity and introduce a single continues
+        parameter $z$, which interpolates between similar components. 
+        \item we also compute the mean of the likelihood for the overlapping parts
+    \end{itemize}
+
+    To use the learned GMM as prior for the reconstruction of another image, the image is split into overlapping patches.
+For each of the patches the log-likelihood for each of the GMM components is evaluated.
+The resulting grid of overlapping patches is illustrated in Figure~\ref{fig:patches}.
 
@@
     neighbouring pixels low, while for extended source the opposite is true. Ideally
-    those contradicting requirements can be handled with a flexible prior assumption,
-    which adapts to the data, such as the patch based GMM prior.
+    those contradicting requirements can be handled with a single flexible prior assumption,
+    which adapts to the data, such as the patch based GMM prior introduced in the previous
+    section.
 
@@
     have no physical relationship of the intensities of the Poisson data we are
-    dealing with. Thus the GMM is learned on normalized images, where the intensity values
-    are constrained between 0 and 1. To evaluate the GMM patch prior on the 
+    dealing with. To overcome this the GMM is learned on normalized images,
+    where the intensity values are constrained between 0 and 1.
+    To evaluate the GMM patch prior on the 
     model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
@@
 
-    There are arguments for $\arcsinh(\mathbf{x})$, see e.g. \cite{Lupton2004}.
+    There are arguments for $\arcsinh(\mathbf{x})$, see e.g. \cite{Lupton2004}, which we use.
 
@@
         \item A randomly chosen patch grid, such that each pixel is at least covered once.
-        The random grid of patches was proposed by \cite{Parameswaran2018}. This has the advantage of potentially speeding up the computation as well.
+        The random grid of patches was proposed by \cite{Parameswaran2018}.
+This has the advantage of potentially speeding up the computation as well.
+\todo{It is available in the implementation, but a bit "ad hoc", maybe just not mention...}
     \end{itemize}
@@
     Each measured counts image $\mathbf{D_j}$ is associated with systematic errors.
-    This includes e.g. the absolute position of the sources in the image (astrometry) and the normalisation of the background model, which can vary between observations.
-    To account for this we extend the model for the predicted
+    This includes e.g. the pointing accuracy of the telescopes: when repeatedly pointed
+    to the same object or when using different types of telescopes for observation, the
+    position of an astronomical object might vary in the image between different
+    observations. The process of correcting for these inaccuracies is called \textit{astrometry}.
+    A second example of systematic errors is the variation of background emission
+    between multiple observations.
+
+    To account for both systematic effects we extend the model for the predicted
     counts introduced in Eq.~\ref{eq:model}, by a background normalisation factor
@@
     \subsection{Jolideco GMM Library}
+    \label{ssec:jolideco-gmm-library}
     On radio data \cite{Bouman2016} found the results to be mostly independent 
-    of the choice of data the GMM prior was learned on. In the low counts and high
-    noise regime we expect a much higher dependence of the results on choice of the
-    data the GMM was learned on. For testing we learned and provide a selection of GMMs to be used with the patch prior for download \footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
+    of the choice of data the GMM prior was learned on. In the low signal-to-noise
+    regime we typically expect a higher dependence of the results on the choice of the
+    data the GMM was learned on. The choice of the prior becomes more important
+    and to avoid introducing a strong bias it should be adapted to the analysis 
+    scenario. For this reason and for purposes of testing we learned and
+    provide a selection of GMMs to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
 
     \subsubsection{Zoran \& Weiss}
-    As baseline reference GMM we use the original model provided by \cite{Zoran2011}. The model was learned
-    from the Berkley image database, by splitting the images into 8x8 patches. 
-    It was downloaded from \url{https://people.csail.mit.edu/danielzoran/epllcode.zip}.
+    As baseline reference GMM we use the original model provided by \cite{Zoran2011}. The model was learned from the Berkley image database, which contains natural images. 
+    The model was learned by splitting the images into 8x8 patches and provided by the authors as part of the source code for download\footnote{\url{https://people.csail.mit.edu/danielzoran/epllcode.zip}}.
 
     \subsubsection{GLEAM Radio Data}
+    \label{sssec:gleam-radio-data}
     A prior learned from astronomical data for analysis of Galactic sources with 
@@
     and radio as emission is produced from the same electron populations.
-    We download
+    We downloaded the GLEAM data using the Gleam VO Client\footnote{\url{https://github.com/ICRAR/gleamvo-client}}. We restrcted the choice
+    of data to the Galactic Plane between $b=\pm10\deg$ and $\ell = \pm180\deg$.
+    In total we extracted \todo{insert number} patches and trained a GMM with 128
+    components.
 
     \subsubsection{NRAO Jets, Jets, Jets}
-    For the specific application of jet detection in extract galactic data we we learned a GMM patch prior from jet images. It encodes the prior knowledge of the preferred direction of the jet.
+    \todo{Include the jet prior?}
+    For the specific application of jet detection and analysis in extract galactic data we learned a GMM patch prior from radio jet images.
+It represents the prior knowledge of both the morphology and preferred direction of the jet.
+As reference data we chose
+    a PR image released under the name \textit{Jets, jets jets}  by the NRAO collaboration containing ~150 example jets from their data\footnote{\url{https://public.nrao.edu/gallery/quicklook-samples/}}.
 
-    \begin{itemize}
-        \item One with horizontal direction, where the image to be analysed should be rotated. E.g. if prior knowledge from radio data is available.
-        \item One with randomised direction, if now prior knowledge is available.
-    \end{itemize}
+    We first split the compiled image into 150 individual examples.
+For each image we ran a blob detection algorithm and line fit to find the preferred direction of the jet.
+Using this information we aligned all images to the same horizontal reference direction of the jet split all images into patches of size 8x8 pixels.
+In total we extracted \todo{insert number} patches and used those to train a GMM with 32 components.
+The prior is useful in a scenario were the direction of the jet known from e.g.
+previous radio observations.
+
+    Alternatively we used a \textit{data augmentation} approach to learn a GMM prior with a randomized direction of the jet. For this we rotated the jet image after alignment by 
+    a random angle. Then again we split each image into patches of size 8x8 pixels. In total we created \todo{insert number} patches and learned a GMM with 64 components. The prior
+    is adapted to the analysis scenario of jet detection, where no no prior knowledge on the
+    direction is available.
 
     \subsection{Computational Performance}
-    We conduct as as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations
+    We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations
     as well as large images.
@@
         \item Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
-        \item we tried the binary search tree as proposed in \cite{Parameswaran2018},
+        \item We tried the binary search tree as proposed in \cite{Parameswaran2018},
         but without success, most likely because the native \texttt{Pytorch} support
         for parallelisation speeds up the standard GMM quite a bit...
-        \item Could use a Neural Net for GMM component selection as proposed in
+        \item Could use a Neural Net for GMM component selection as proposed in \cite{Rosenbaum15}
         \item GPU support via \texttt{Pytorch}
@@
         \item First run with uniform prior, to get a rough estimate
-        \item Then optimize the parameters associated to the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
+        \item (optional) Then optimize the parameters associated to the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
         \item Then we go for a full optimization using the patch prior, which can be computationally costly
         \item we use ADAM (stochastic gradient decent), without decay
-        \item learning rate scheduling? So far just a fixed step size value of $1e-3$
+        \item  (optional) learning rate scheduling? So far just a fixed step size value of $1e-3$
     \end{itemize}
@@
 
+    All the examples can be found at \url{https://github.com/jolideco/jolideco-examples}
+
     \subsection{Deep \chandra Observation}
+    Chandra is a space-based X-ray observatory that has been operational since 1999.
+It comprises nested cylindrical paraboloid and hyperboloid surfaces that create an imaging optical system for X-rays.
+In the focal plane, it has multiple instruments designed for various scientific purposes, such as the high-resolution camera (HRC) and the Advanced CCD Imaging Spectrometer (ACIS).
+Chandra has a typical angular resolution of 0.5 arcseconds and can cover energy ranges from \qty[mode = text]{0.1}{keV} to  \qty[mode = text]{10}{keV}.
+
+    \todo{which object}?
+    Figure~\ref{fig:example-chandra} shows the result.
+
     \begin{figure*}[ht!]
@@
 
-    \subsection{\fermi Event Classes}
+    \subsection{\fermi Event Types}
+    As a last application example we apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
+    The LAT is a pair conversion gamma-ray telescope on board of the Fermi satellite. It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
+    For the example we chose a source with complex morphology, the supernova remnant \textit{Vela Junior}.
+    We use 14 years (from 2008 August 4 to 2023 August 4) of \texttt{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV}.
+    We selected data between  and applied a zenith angle cut of \ang{105}.
+
+    We chose the patch prior learned on the GLEAM data, described in the Section~\ref{sssec:gleam-radio-data}
+    and a linear scaling. 
+    As a background model we included the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits}.
+
+    For the data reduction we use the fermitools \todo{add version} and Gammapy v1.0 \cite{Gammapyv1.0}.
+    While the fermitools output an energy dependent counts, exposure and background cube, we use Gammapy
+    to reduce to and image, assuming a power law with index $\Gamma=1.77$ \citep{Ajello2017} as spectral model to compute the effective PSF and exposure.
+To preserve the information on the angular resolution we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}
+
+    Figure~\ref{fig:example-fermi-lat} shows the result. \jolideco clearly improves the noise level as well as
+    angular resolution. It reveals mophological details consistent with the HESS measurement.
+
     \begin{figure*}[ht!]
@@
     \section{Reproducibility}
-
-    The paper is available at \url{https://github.com/jolideco/jolideco-paper} and can be reproduced using \cite{Luger2021}.
+    In order to facilitate reproducibility we make source code for the paper and figures  available at \url{https://github.com/jolideco/jolideco-paper}.
+    The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021}. See instructions 
+    All data is available on Zenodo \todo{how do we do this exactly...?}
 
@@
         \item Extend \jolideco to handle spectral dimension at the same time.
-        \item Use normalising flows for patch priors see e.g. https://arxiv.org/abs/2205.12021
-        \item 
+        \item Use normalising flows for patch priors see \cite{Altekrueger2022}
+        \item Use other mixture models, such as Student T or generalised Gaussian. 
+        \item one could try deep image priors \citep{Ulyanov2017}
+        \item Extend to use GMM patch prior on multiple scales, see \cite{Papyan2015}
     \end{itemize}
@@
     CHASC is supported by NSF grants DMS-21-13615, DMS-21-13397, and DMS-21-13605; by the UK Engineering
-    and Physical Sciences Research Council [EP/W015080/1]; and by NASA 18-APRA18-0019.
+    and Physical Sciences Research Council [EP/W015080/1]; and by NASA APRA Grant 80-NSSC21-K0285.
     We thank CHASC members for many helpful discussions, especially Xiao-Li Meng and Katy McKeough.

### 2023-03-07 src/scripts/config.py
[showyourwork] overleaf sync

@@ -1,6 +1,7 @@
 """General configuration for mpl plotting scripts"""
 from pathlib import Path
 
+import matplotlib.colors as mcolors
 import matplotlib.pyplot as plt
 import numpy as np
 from astropy import units as u
@@ -31,9 +32,9 @@ for idx, color in enumerate(CMAP([0, 0.25, 0.5, 0.75, 1])):
 
 COLORS_CYCLE = [f"{CMAP_NAME}-{idx}" for idx in range(5)]
 
-PROP_CYCLER = cycler(
-    color=[value for key, value in COLORS.items() if key in COLORS_CYCLE]
-) + cycler(linestyle=["-", "--", ":", "-.", "."])
+PROP_CYCLER = cycler(color=mcolors.TABLEAU_COLORS) + cycler(
+    linestyle=["-", "--", ":", "-.", "."]
+)
 
 
 class FigureSizeAA:

### 2023-03-07 src/scripts/gmm-eigen-images.py

@@ -1,0 +1,14 @@
+import config
+import matplotlib.pyplot as plt
+import paths
+from jolideco.priors import GaussianMixtureModel
+
+figsize = config.FigureSizeAA(aspect_ratio=1.618)
+
+fig = plt.figure(figsize=figsize.inch)
+
+gmm = GaussianMixtureModel.from_registry("nrao-jets-v0.1")
+
+
+plt.legend()
+plt.savefig(paths.figures / "gmm-eigen-images.pdf", facecolor="w", dpi=300)

### 2023-03-07 src/scripts/patches.py

@@ -1,7 +1,7 @@
-import matplotlib.pyplot as plt
-from matplotlib.patches import Rectangle
-import paths
 import config
+import matplotlib.pyplot as plt
+import paths
+from matplotlib.patches import Rectangle
 
 figsize = config.FigureSizeAA(aspect_ratio=2)
 
@@ -17,7 +17,7 @@ for x in range(0, 2 * image_size[0], 6):
             xy=(x, y),
             width=patch_size[0],
             height=patch_size[1],
-            facecolor=config.COLORS["viridis-1"],
+            facecolor="tab:blue",
             edgecolor="None",
             alpha=0.2,
         )
@@ -29,7 +29,7 @@ rectangle = Rectangle(
     width=patch_size[0],
     height=patch_size[1],
     facecolor="None",
-    edgecolor=config.COLORS["red"],
+    edgecolor="tab:red",
     lw=1,
 )
 ax.add_patch(rectangle)

### 2023-03-07 src/scripts/config.py
Adapt color handling

@@ -22,19 +22,19 @@ FIGURE_WIDTH_AA = {
 CMAP_NAME = "viridis"
 CMAP = plt.get_cmap(CMAP_NAME)
 
-COLORS = {
-    "white": "#ffffff",
-    "red": [216 / 255, 27 / 255, 96 / 255, 1.0],
-}
+# COLORS = {
+#     "white": "#ffffff",
+#     "red": [216 / 255, 27 / 255, 96 / 255, 1.0],
+# }
 
-for idx, color in enumerate(CMAP([0, 0.25, 0.5, 0.75, 1])):
-    COLORS[f"{CMAP_NAME}-{idx}"] = color
+# for idx, color in enumerate(CMAP([0, 0.25, 0.5, 0.75, 1])):
+#     COLORS[f"{CMAP_NAME}-{idx}"] = color
 
-COLORS_CYCLE = [f"{CMAP_NAME}-{idx}" for idx in range(5)]
+# COLORS_CYCLE = [f"{CMAP_NAME}-{idx}" for idx in range(5)]
 
-PROP_CYCLER = cycler(color=mcolors.TABLEAU_COLORS) + cycler(
-    linestyle=["-", "--", ":", "-.", "."]
-)
+# PROP_CYCLER = cycler(color=mcolors.TABLEAU_COLORS) + cycler(
+#     linestyle=["-", "--", ":", "-.", "."]
+# )
 
 
 class FigureSizeAA:

### 2023-03-07 src/scripts/image-norms.py

@@ -17,17 +17,14 @@ ax = fig.add_axes([0.15, 0.2, 0.80, 0.77])
 
 x = np.linspace(0, 15, 100)
 
-props = config.PROP_CYCLER()
 
 for name, norm_clas in NORMS_REGISTRY.items():
     if name not in init_kwargs:
         continue
 
-    prop = next(props)
-
     norm_cls = NORMS_REGISTRY[name]
     norm = norm_cls(**init_kwargs[name])
-    ax.plot(x, norm(x), label=name, **prop)
+    ax.plot(x, norm(x), label=name)
 
 ax.set_xlim(0, 15)
 ax.set_ylim(0, 1.2)

### 2023-03-07 src/scripts/patches.py

@@ -34,7 +34,7 @@ rectangle = Rectangle(
 )
 ax.add_patch(rectangle)
 
-ax.text(x=16, y=20.5, s="8 x 8 Patch", color=config.COLORS["red"], ha="center")
+ax.text(x=16, y=20.5, s="8 x 8 Patch", color="tab:red", ha="center")
 
 offset = patch_size[0] // 2
 ax.set_xlim(offset, image_size[0] - offset - offset // 2)

### 2023-04-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amssymb}
+\let\tablenum\relaxgit 
 \usepackage{siunitx}
@@
     Furthermore, the quality of the resulting image is affected by background or instrumental measurement noise and non-uniform exposure.
-This is especially true in the low signal-to-noise regime.
-E.g.
-\xray and \gammaray~astronomy
+This is especially true in the low signal-to-noise regime, where images are affected by Poisson noise.
 
-    In literature there have been multiple efforts to correct the degrading of the images
-    and maximise the scientific use.
+    Such as images taken by \xray and \gammaray~astronomy but also to other fields such as
 
-    Any astronomical observation is affected by the limited angular resolution of the telescope. However the problem is not specific to astronomy and has been tried to 
-    be solved for fluorescence microscopy or others...
+    To maximise the scientific use of available data it is desirable to correct for the instrumental imprint on the data.
 
-    We assume non-blind deconvolution, so the there is prior information of the PSF
+    We assume non-blind deconvolution, so the there is prior information of the point spread function (PSF).
+The PSF can be estimated empirically from observation of known point sources, such as distant activate galactic nuclei or a model of the PSF can obtained from simulation of the instrument.
+
+    This class of problems is called inverse problems.
+
+    \subsection{Related Work}
+    In literature there have been multiple efforts to correct the degrading of the images using statistical methods.
+    The standard baseline method for image deconvolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974}.
+They used expectation maximisation to solve.
+We will refer to this method as "RL".
+
+    One of the significant challenges in image deconvolution is the problem of Rayleigh-Lynden Bell (RL) decomposition of structures into point sources.
+This problem was first introduced by Reeves et al.
+\cite{Reeves1994} and later analyzed by Fish et al.
+\cite{Fish1995}.
+Regularized RL methods, such as total variation \citep{Dey2006} and maximum entropy \citep{Bi1994}, have been proposed to overcome this issue.
+
+    Multi-scale LIRA prior has been used in image deconvolution to incorporate error estimates and Bayesian sampling.
+This prior has been used in various studies, including those by Esch et al.
+\cite{Esch2004} and Connors et al.
+\cite{Connors2011}.
+However, the prior is ad-hoc and lacks physical information or assumptions, limiting its applicability.
+
+    Another approach to image deconvolution is joint likelihood RL, which has been shown to be effective in creating a merged image from multiple images \cite{Ingaramo2014}.
+In this approach, RL takes the best out of each image and merges them to create a more accurate representation of the object.
+
+    An alternative approach to solve the problem in the framework of information field theory.
+
+    Recently, image deconvolution using physical assumptions and decomposition into point and diffuse flux in 3D/4D has gained attention.
+Pumpe et al.
+\cite{Pumpe2018} and Selig et al.
+\cite{Selig2015} proposed priors based on physical assumptions, which have been shown to work well for large-scale emission.
+However, the smoothness assumption in these methods can lead to artifacts in the galactic plane.
+
+    The challenge is due to fundamentally contradicting goals: deconvolution favoring point sources will decompose extend structures,
+    while introducing local correlations will lead to
 
     \begin{itemize}
-        \item Standard baseline method is Richardson \& Lucy (RL), see \cite{Richardson1972} and \cite{Lucy1974}
          \item  Problem of RL decomposing structures into point sources: \cite{Reeves1994} \cite{Fish1995}
@@
     \subsection{A note on Deep Learning Methods}
+    In the past decade Machine learning (ML) especially deep convolutional neural networks became the \textit{de facto} standard
+    for de-blurring and super-resolution of natural images \todo{reference review?}.
+However their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
+For a variety of reasons this approach is not suitable for astronomical x-ray and \gammaray data.
+
+    Astronomical data is rare and expensive and there is no ground truth.
+One could rely on transfer learning and simulated data.
+E.g.
+radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise.
+However astronomical images have a large dynamic range and show a high diversity in morphological structure, which would still require al large amount of training data.
+However this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \todo{reference} or as a post processing step of results obtained with regularised RL \todo{Reference by Starck et al.}.
+
+    In addition to the challenge of obtaining training data, it is known that the PSF of instruments such as \chandra is highly variable.
+It varies with observation conditions and depends e.g.
+on energy as well as offset angle from the pointing direction.
+To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models, which would require a very large computational effort.
+
     \cite{Li2014} have introduced a baseline architecture for a deep convolutional neural network for image deblurring.
@@
 
-    Shown to work for e.g. deconvolution of Galaxy images SDSS \todo{reference?} and post-processing of regularised RL results \todo{Starck et al.}
-
     \section{Method}
     \subsection{Poisson Joint Likelihood}
-    Our goal is to recover an image $\mathbf{x}$ from a set of multiple
-    low counts observations.
-    Most generally we assume our total dataset consists of $J$ individual
-    observations of the same region of the sky, which are jointly
-    modelled. The assumption is that the underlying \textit{true} emission image,
-    we are looking for does not change with time. Under this assumption these
-    datasets can be for example:
+    Our goal is to recover an image $\mathbf{x}$ from a set of multiple low counts observations.
+Most generally we assume our total dataset consists of $J$ individual observations of the same region of the sky, which are jointly modelled.
+The assumption is that the underlying \textit{true} emission image, we are looking for does not change with time.
+Under this assumption these datasets can be for example:
 
@@
         parameter $z$, which interpolates between similar components.
+        \item Another idea is to use "Gumbel Softmax"...
         \item we also compute the mean of the likelihood for the overlapping parts
@@
 
-    \begin{figure}[ht!]
+    \begin{figure}
         \script{patches.py}
@@
 
+    \begin{equation}
+        \tilde{\mathbf{x}}_n = f \left(\frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n} \right)
+    \end{equation}
+
+    With a given non-linearity:
+
+    \begin{equation}
+        f(x) = \arcsinh{x / \alpha}
+    \end{equation}
+
+    \todo{The patch normalisation remains to be decided, but it would be advantageous to get rid of the hyper-parameter associated with the total image normalisation}.
     The GMM patch prior is learned from other images whose pixel intensities
@@
 
-    \begin{figure}[ht!]
+    \begin{figure}
         \script{image-norms.py}
@@
     a random angle. Then again we split each image into patches of size 8x8 pixels. In total we created \todo{insert number} patches and learned a GMM with 64 components. The prior
-    is adapted to the analysis scenario of jet detection, where no no prior knowledge on the
+    is adapted to the analysis scenario of jet detection, where no prior knowledge on the
     direction is available.
+
+    \begin{figure}
+        \script{gmm-eigen-images.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/gmm-eigen-images.pdf}
+            \caption{
+                Eigenimages of the covariance matrices of the 32 components of the GMM learned from the NRAO jets. \todo{Provide other examples...?!?}
+            }
+            \label{fig:gmm-eigen-images}
+        \end{centering}
+    \end{figure}
+
+    \subsubsection{Chandra SNRs}
+
+    Learn prior from \chandra images of supernova remnants (SNRs).  Self-similarity
 
@@
     \subsection{Optimization Strategy}
+    Maximising the \aposteriori likelihood defined Eq.\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
+To improve the convergence rate of the optimization process we employ the following optimization strategy: the optimization strategy begins with the optimizer viewing $\log{\mathbf{x}}$, and the first step involves running a rough estimate using a uniform prior.
+This step is optional, but if chosen, the next step involves optimizing the parameters associated with the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
+Following this, a full optimization is performed using the patch prior, which can be computationally expensive.
+The optimization algorithm used is ADAM, a stochastic gradient descent method, without decay.
+Finally, there is an optional step of learning rate scheduling, although so far, a fixed step size value of $1e-3$ has been used.
+
     In practice we employ the following optimization strategy:
@@
     \section{Experiments}
-    \subsection{Test Datasets}
+    \subsection{Test Datasets}\label{sec:testmodels}
     \todo{Vinay writes this?}
@@
     \begin{itemize}
-        \item[ ``Gauss":] A set of four point sources arranged around an extended Gaussian source
-        \item[``Points":] Point sources arranged with different separations
-        \item[``Shield":] Disk shaped flat extended source with superposed point sources and linear jet-like features
-        \item[``Spiral":] Extended thin double-spiral with a flat disk at the center and point sources adjacent to it
+        \item[(A)] {\bf asterism:} A set of four point sources arranged around an extended Gaussian source
+        \item[(B)] {\bf points:} Point sources arranged with different separations
+        \item[(C)] {\bf shield:} Disk shaped flat extended source with superposed point sources and linear jet-like features
+        \item[(D)] {\bf spiral:} Extended thin double-spiral with a flat disk at the center and point sources adjacent to it
     \end{itemize}
     The arrangements are shown in Figure~TBD, and the details of the locations and brightness of each component is listed in Table~TBD.
+
+    \begin{figure*}
+        \centering\includegraphics{figures/chandra_gauss_fwhm4710_128x128_aster1+point1+disk1+spiral3.pdf}
+        \caption{Illustrating the source patterns used to make test datasets.
+The patterns shown are for the {\sl (A)} {\tt asterism}, {\sl (B)} {\tt points}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}), convolved with a sharp PSF (Gaussian with $\sigma=2$~pix).
+All images are of size $128{\times}128$.
+The dashed red and magenta boxes depict $32{\times}32$ and $64{\times}64$ regions of interest.
+Note that the boxes are displaced to the lower left corner in Case B, and leftwards in Case D.}
+        \label{fig:simulated_models_chandra}
+    \end{figure*}
+     \begin{figure*}
+        \centering\includegraphics{figures/xmm_gauss_fwhm14130_128x128_aster1+point1+disk1+spiral3.pdf}
+        \caption{As in Figure~\ref{fig:simulated_models_chandra}, convolved with a diffuse PSF (Gaussian with $\sigma=6$~pix).}
+        \label{fig:simulated_models_xmm}
+    \end{figure*}
     }
@@
 
-    \begin{figure*}[ht!]
+    \begin{figure*}
         \script{example-chandra.py}
@@
     \subsection{Combined \xmm and \chandra Observation}
-    \begin{figure*}[ht!]
+    \begin{figure*}
         \script{example-xmm-chandra.py}
@@
     and a linear scaling. 
-    As a background model we included the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits}.
+    As a background model we included the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and nearby sources from the 3FHL catalog \cite{Ajello2017}.
 
@@
     to reduce to and image, assuming a power law with index $\Gamma=1.77$ \citep{Ajello2017} as spectral model to compute the effective PSF and exposure.
-To preserve the information on the angular resolution we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}
+To preserve the information on the angular resolution we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}.
 
-    Figure~\ref{fig:example-fermi-lat} shows the result. \jolideco clearly improves the noise level as well as
-    angular resolution. It reveals mophological details consistent with the HESS measurement.
+    Figure~\ref{fig:example-fermi-lat} shows the result. \jolideco clearly improves the noise level as well as angular resolution. It reveals mophological details consistent with the HESS measurement.
 
-    \begin{figure*}[ht!]
+    \begin{figure*}
         \script{example-fermi-lat.py}
@@
 
-    \section{Reproducibility}
+    \section{Paper Reproducibility}
     In order to facilitate reproducibility we make source code for the paper and figures  available at \url{https://github.com/jolideco/jolideco-paper}.
@@
     All data is available on Zenodo \todo{how do we do this exactly...?}
+
+    For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
+
+    For the Chandra data reduction we used a custom \texttt{Snakemake} workflow \footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
 
@@
         \item Extend to use GMM patch prior on multiple scales, see \cite{Papyan2015}
+        \item Exclude point sources either via separate component or "J-invariance"
     \end{itemize}
@@
     and Physical Sciences Research Council [EP/W015080/1]; and by NASA APRA Grant 80-NSSC21-K0285.
+
     We thank CHASC members for many helpful discussions, especially Xiao-Li Meng and Katy McKeough.
@@
     provided by the European Commission.
+
     Aneta Siemiginowska, Vinay Kashyap, and Doug Burke further acknowledge support from NASA
     contract to the Chandra X-ray Center NAS8-03060.
+
+    Some of the computations in this paper were conducted on the Smithsonian High Performance
+    Cluster (SI/HPC), Smithsonian Institution \url{https://doi.org/10.25572/SIHPC}.
 

### 2023-04-10 src/scripts/image-norms.py
[showyourwork] overleaf sync

@@ -23,7 +23,7 @@ for name, norm_clas in NORMS_REGISTRY.items():
         continue
 
     norm_cls = NORMS_REGISTRY[name]
-    norm = norm_cls(**init_kwargs[name])
+    norm = norm_cls.evaluate_numpy(**init_kwargs[name])
     ax.plot(x, norm(x), label=name)
 
 ax.set_xlim(0, 15)

### 2023-04-10 src/scripts/image-norms.py
[showyourwork] overleaf sync

@@ -23,8 +23,8 @@ for name, norm_clas in NORMS_REGISTRY.items():
         continue
 
     norm_cls = NORMS_REGISTRY[name]
-    norm = norm_cls.evaluate_numpy(**init_kwargs[name])
-    ax.plot(x, norm(x), label=name)
+    norm = norm_cls(**init_kwargs[name])
+    ax.plot(x, norm.evaluate_numpy(x), label=name)
 
 ax.set_xlim(0, 15)
 ax.set_ylim(0, 1.2)

### 2023-04-12 src/scripts/example-fermi-lat.py
[showyourwork] overleaf sync

@@ -15,6 +15,7 @@ filename_jolideco = path / "vela-junior-above-10GeV-data-result-jolideco.fits"
 filenames_data = (path / "input").glob("*.fits")
 filename_npred = path / "vela-junior-above-10GeV-data-npred.fits"
 
+print(gammapy.__version__)
 
 npred = Map.read(filename_npred)
 

### 2023-04-12 src/scripts/example-fermi-lat.py
Implement fermi example plot

@@ -2,9 +2,47 @@ import config
 import matplotlib.pyplot as plt
 import numpy as np
 import paths
+from astropy import units as u
+from astropy.io import fits
 from gammapy.maps import Map
 
 SMOOTH_WIDTH = 5
+FONT_SIZE = 8
+
+plt.rcParams.update({"font.size": FONT_SIZE})
+
+
+def format_axes(ax, hide_yaxis=False):
+    """Format axes for a map plot"""
+    lon = ax.coords["glon"]
+    lat = ax.coords["glat"]
+
+    lon.set_ticks_position("b")
+    lon.set_ticklabel_position("b")
+
+    lat.set_ticks_position("l")
+    lat.set_ticklabel_position("l")
+
+    lon.set_major_formatter("d.d")
+    lat.set_major_formatter("d.d")
+
+    lon.set_ticks(spacing=1.0 * u.deg)
+    lat.set_ticks(spacing=0.5 * u.deg)
+
+    if hide_yaxis:
+        lat.set_axislabel("")
+        lat.set_ticklabel_visible(False)
+
+
+def add_cbar(im, ax, fig, label=""):
+    """Add cbar to a given axis and figure"""
+    bbox = ax.get_position()
+    loright = bbox.corners()[-2]
+    rect = [loright[0] + 0.01, loright[1], 0.02, bbox.height]
+    cax = fig.add_axes(rect)
+    cax.set_ylabel(label)
+    return fig.colorbar(im, cax=cax, orientation="vertical")
+
 
 path = (
     paths.jolideco_repo_fermi_lat_example
@@ -15,37 +53,41 @@ filename_jolideco = path / "vela-junior-above-10GeV-data-result-jolideco.fits"
 filenames_data = (path / "input").glob("*.fits")
 filename_npred = path / "vela-junior-above-10GeV-data-npred.fits"
 
-print(gammapy.__version__)
-
 npred = Map.read(filename_npred)
 
-figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+aspect_ratio = 3.8
+figsize = config.FigureSizeAA(aspect_ratio=aspect_ratio, width_aa="two-column")
 
-fig, ax = plt.subplots(figsize=figsize.inch)
+fig = plt.figure(figsize=figsize.inch)
 
[…]

### 2023-04-13 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             \caption{
-                Chandra Example
+                The \jolideco method applied to the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
+The left image shows the counts above \qty[mode = text]{10}{GeV}.
+The different event classes are stacked into a single image.
+                The image in the center show the flux reconstructed by the \jolideco methods. The image on the right shows the normalised residuals.
             }

### 2023-04-13 src/scripts/example-fermi-lat.py

@@ -38,10 +38,10 @@ def add_cbar(im, ax, fig, label=""):
     """Add cbar to a given axis and figure"""
     bbox = ax.get_position()
     loright = bbox.corners()[-2]
-    rect = [loright[0] + 0.01, loright[1], 0.02, bbox.height]
+    rect = [loright[0] + 0.005, loright[1], 0.02, bbox.height]
     cax = fig.add_axes(rect)
-    cax.set_ylabel(label)
-    return fig.colorbar(im, cax=cax, orientation="vertical")
+    cbar = fig.colorbar(im, cax=cax, orientation="vertical")
+    cbar.set_label(label)
 
 
 path = (
@@ -68,10 +68,10 @@ y_bottom = 0.22
 ax_counts = fig.add_axes([0.08, y_bottom, width, height], projection=wcs)
 format_axes(ax_counts)
 
-ax_flux = fig.add_axes([0.4, y_bottom, width, height], projection=wcs)
+ax_flux = fig.add_axes([0.37, y_bottom, width, height], projection=wcs)
 format_axes(ax_flux, hide_yaxis=True)
 
-ax_residuals = fig.add_axes([0.7, y_bottom, width, height], projection=wcs)
+ax_residuals = fig.add_axes([0.69, y_bottom, width, height], projection=wcs)
 format_axes(ax_residuals, hide_yaxis=True)
 
 
@@ -99,7 +99,7 @@ add_cbar(
     ax_residuals.images[0],
     ax_residuals,
     fig,
-    label="(Counts - $N_{Pred}$) / $\sqrt{N_{Pred}}$",
+    label="$(N_{Counts} - N_{Pred}) / \sqrt{N_{Pred}}$",
 )
 
 # crop = slice(None)
@@ -115,23 +115,6 @@ add_cbar(
 # for spine in ax_psf.spines.values():
 #     spine.set_edgecolor("white")
 #     spine.set_lw(1.2)
-
-# counts.plot(
-#     ax=ax_counts,
-#     norm=norm,
-#     cmap=cmap,
-#     interpolation="None",
-# )
-# npred.plot(ax=ax_npred, norm=norm, interpolation="gaussian", cmap=cmap)
-# npred_rl.plot(ax=ax_npred_rl, norm=norm, interpolation="gaussian", cmap=cmap)
-
-# lon = ax_npred.coords["ra"]
-# lat = ax_npred.coords["dec"]
[…]

### 2023-04-18 src/scripts/comparison-scenarios.py
Add comparison scenario plot

@@ -1,0 +1,47 @@
+import config
+import numpy as np
+import paths
+from astropy.io import fits
+from matplotlib import pyplot as plt
+from matplotlib.gridspec import GridSpec
+
+scenarios = {
+    "point1": {"max_cut": 1.0},
+    "aster3": {"max_cut": 1.0},
+    "disk3": {"max_cut": 1.0},
+    "spiral3": {"max_cut": 1.0},
+}
+
+bg = "bg1"
+instrument = "chandra"
+
+methods = [
+    "pylira",
+    "jolideco-uniform-prior=n=10",
+    "jolideco-uniform-prior=n=1000",
+    "jolideco-patch-prior-gleam-v0.1",
+    "jolideco-patch-prior-zoran-weiss",
+]
+
+figsize = config.FigureSizeAA(aspect_ratio=1.2, width_aa="two-column")
+
+fig, axes = plt.subplots(nrows=4, ncols=5, figsize=figsize.inch)
+
+path_base = paths.jolideco_repo_comparison / "results"
+
+for idx, scenario in enumerate(scenarios):
+    for jdx, method in enumerate(methods):
+        path = path_base / scenario / bg / instrument / method
+        filename = path / f"{scenario}-{bg}-{method}-{instrument}-result.fits.gz"
+
+        with fits.open(filename) as hdul:
+            if "pylira" in method:
+                data = hdul[0].data
+            else:
+                data = hdul["FLUX"].data
+
+        axes[idx, jdx].imshow(data, cmap="viridis", origin="lower")
+        axes[idx, jdx].set_axis_off()
+
+
+plt.savefig(paths.figures / "comparison-scenarios.pdf", dpi=config.DPI)

### 2023-04-18 src/scripts/paths.py

@@ -32,3 +32,4 @@ output = tex / "output"
 # Joideco repos
 jolideco_repo_gmm_library = root / "../jolideco-gmm-prior-library"
 jolideco_repo_fermi_lat_example = root / "../jolideco-fermi-examples"
+jolideco_repo_comparison = root / "../jolideco-comparison"

### 2023-04-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \label{ssec:jolideco-gmm-library}
-    On radio data \cite{Bouman2016} found the results to be mostly independent 
-    of the choice of data the GMM prior was learned on. In the low signal-to-noise
-    regime we typically expect a higher dependence of the results on the choice of the
-    data the GMM was learned on. The choice of the prior becomes more important
-    and to avoid introducing a strong bias it should be adapted to the analysis 
-    scenario. For this reason and for purposes of testing we learned and
-    provide a selection of GMMs to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
+    On radio data \cite{Bouman2016} found the results to be mostly independent of the choice of data the GMM prior was learned on.
+The strength of the GMM prior is its high \textit{expressiveness}, meaning the prior contains a large variety of patch shapes and adapts to the data in the optimization process.
+However in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of the data the GMM was learned on.
+The choice of the prior becomes more important and to avoid introducing a strong bias it should be adapted to the analysis scenario.
+For this reason and for purposes of testing we learned and provide a selection of GMMs (a \textit{Library}) to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
 
     \subsubsection{Zoran \& Weiss}
-    As baseline reference GMM we use the original model provided by \cite{Zoran2011}. The model was learned from the Berkley image database, which contains natural images. 
+    As baseline reference GMM we use the original model provided by \cite{Zoran2011}.
+The model was learned from the Berkley image database, which contains natural images.
 The model was learned by splitting the images into 8x8 patches and provided by the authors as part of the source code for download\footnote{\url{https://people.csail.mit.edu/danielzoran/epllcode.zip}}.
+    More details of how the model was learned are given in the original publication.
 
@@
     \label{sssec:gleam-radio-data}
+
     A prior learned from astronomical data for analysis of Galactic sources with 
-    rich morphology, such as supernova remnants, pulsar winds etc.
+    rich morphology, such as supernova remnants, pulsar winds etc., but also include point sources. A good "all purpose" prior.
     High signal to noise Radio data from \cite{HurleyWalker2022}.
@@
     and radio as emission is produced from the same electron populations.
-    We downloaded the GLEAM data using the Gleam VO Client\footnote{\url{https://github.com/ICRAR/gleamvo-client}}. We restrcted the choice
+    We downloaded the GLEAM data using the Gleam VO Client\footnote{\url{https://github.com/ICRAR/gleamvo-client}}. We restricted the choice
     of data to the Galactic Plane between $b=\pm10\deg$ and $\ell = \pm180\deg$.
@@
     \subsubsection{Chandra SNRs}
-
-    Learn prior from \chandra images of supernova remnants (SNRs).  Self-similarity
+    Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}.
+Structures appear on multiple angular scales.
+This means the prior could even be learned from the data itself if sufficiently free of noise.
+For analysis of Galactic sources with complex morphology and typically radially symmetric features such as supernova remnants (SNRs) we learned a prior from images of the bright \chandra SNRs \textit{Cas A} and \textit{G292.0+01.8}.
+In total we extracted \todo{insert #} patches and learned a GMM with 128 components.
 
@@
     \end{itemize}
-    The arrangements are shown in Figure~TBD, and the details of the locations and brightness of each component is listed in Table~TBD.
+    The arrangements are shown in Figure~TBD, and the details of the locations and brightness of each component is listed in Table~TBD.}
 
@@
     \end{figure*}
+
     \begin{figure*}
@@
     \end{figure*}
-    }
 
@@
 
+    \subsection{Methods}
+    We compare the performance of 5 different methods:
+
+    \begin{itemize}
+        \item Pylira \citep{Esch2004, scipy_proceeding}
+        \item \jolideco with a uniform prior and 10 iterations. This can be considered as a reference similar to RL.
+        \item \jolideco with a uniform prior and 10 iterations. This can be considered as a reference similar to RL.
+        \item \jolideco with a patch prior learned on Gleam data and sum patch norm
+        \item \jolideco with a patch prior from \cite{Zoran2011} and the mean subracted patch norm. This is for comparison to the original method and the method used on \cite{Bouman2016}.
+    \end{itemize}
+
     \subsection{Results}
+    All the results are available at \url{https://jolideco.github.io/jolideco-comparison}.
+    \subsubsection{Comparing Scenarios}
+    \jolideco shows excellent performance of a variety of morphological shapes. 
+    it converges to the reference solution for very high signal to noise.
 
-    The package is available at \url{https://github.com/jolideco/jolideco-comparison}
+    \subsubsection{Comparing Background Levels}
+    Methods
+
+    \subsubswction{Comparing Instruments}
 
     \section{Application Examples}
-    Show results from real observations
-
-    All the examples can be found at \url{https://github.com/jolideco/jolideco-examples}
-
     \subsection{Deep \chandra Observation}
-    Chandra is a space-based X-ray observatory that has been operational since 1999.
+    As a first application example we choose a set of short exposure observations of the SNR \textit{E0102} by the \chandra telescope.
+\chandra is a space-based X-ray observatory that has been operational since 1999.
 It comprises nested cylindrical paraboloid and hyperboloid surfaces that create an imaging optical system for X-rays.
 In the focal plane, it has multiple instruments designed for various scientific purposes, such as the high-resolution camera (HRC) and the Advanced CCD Imaging Spectrometer (ACIS).
-Chandra has a typical angular resolution of 0.5 arcseconds and can cover energy ranges from \qty[mode = text]{0.1}{keV} to  \qty[mode = text]{10}{keV}.
+Chandra has a typical angular resolution of 0.5 arcseconds and covers the energy range from \qty[mode = text]{0.1}{keV} to  \qty[mode = text]{10}{keV}.
 
-    \todo{which object}?
-    Figure~\ref{fig:example-chandra} shows the result.
+    In total we choose 25 observations with the ACIS instrument and no grating.
+For \chandra the instrument response varies with the observation offset \todo{reference}.
+With \jolideco we can handle the correct PSF for each observation.
+We assume a spatially constant background and exposure, however the exposure is scaled to a reference observation.
+The data reduction was done using ciao v4.15 and the custom snakemake workflow.
+PSFs were simulated for each observation independently using \textit{marx} \todo{reference} and the \textit{simulate\_psf} script.
+List of observation IDs can be found online.
+Energy range was selected from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a bins sice of 0.5 "native" bins, corresponding to a bin size of \qty[mode = text]{0.001}{}.
+For the spectrum we fitted a model a circular region \todo{which one?} and used it for the PSF simulation.
+
+    For \jolideco we used the GMM prior learned on Chandra SNRs and an oversampling factor of 2.
+For each observation we allow the background level and position calibration to vary.
+Figure~\ref{fig:example-chandra} shows the final result.
+\jolideco clearly improve the angular resolution.
+
+    To check the quality of the model we compute a map of approximate residual significance defined by:
+
+    \begin{equation}
+        \label{eq:approx-sigma}
+        \sigma = \frac{N_{\mathrm{Counts}} - N_{\mathrm{Pred}}} {\sqrt{N_{\mathrm{Pred}}}}
+    \end{equation}
+
+    \url{https://github.com/jolideco/jolideco-chandra-examples}
 
@@
     \subsection{Combined \xmm and \chandra Observation}
+    As a second application example we combine data from \chandra and \xmm.
+    \url{https://github.com/jolideco/jolideco-chandra-nustar-examples}
+
     \begin{figure*}
@@
     As a last application example we apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
-    The LAT is a pair conversion gamma-ray telescope on board of the Fermi satellite. It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
-    For the example we chose a source with complex morphology, the supernova remnant \textit{Vela Junior}.
-    We use 14 years (from 2008 August 4 to 2023 August 4) of \texttt{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV}.
-    We selected data between  and applied a zenith angle cut of \ang{105}.
+    The LAT is a pair conversion gamma-ray telescope on board of the Fermi satellite.
+It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
+For the example we chose again a Galactic source with complex morphology: the supernova remnant \textit{Vela Junior}.
+We use 14 years (from 2008 August 4 to 2023 August 4) of \texttt{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
+To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}, as
+    defined by the \fermi collaboration.
+We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
+For the first part of the data reduction we use the standard \textit{fermitools} \todo{add version and reference}.
 
-    We chose the patch prior learned on the GLEAM data, described in the Section~\ref{sssec:gleam-radio-data}
-    and a linear scaling. 
-    As a background model we included the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and nearby sources from the 3FHL catalog \cite{Ajello2017}.
+    As the \textit{fermitools} output an energy dependent counts, exposure and PSF cube, we use the \textit{Gammapy} package to further reduce the data.
+In a first step we compute an image of the expected background emission.
+For this we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and nearby sources from the 3FHL catalog \cite{Ajello2017}.
+We fit the model components to the data, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on \textit{Vela Junior}.
+Finally we reduce this model to an image by summing over the energy dimension.
 
-    For the data reduction we use the fermitools \todo{add version} and Gammapy v1.0 \cite{Gammapyv1.0}.
-    While the fermitools output an energy dependent counts, exposure and background cube, we use Gammapy
-    to reduce to and image, assuming a power law with index $\Gamma=1.77$ \citep{Ajello2017} as spectral model to compute the effective PSF and exposure.
-To preserve the information on the angular resolution we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}.
+    Assuming a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for \textit{Vela Junior} we also compute an effective PSF and exposure image by integrating over the energy dimension of the cube and weighting with the spectral model.
 
-    Figure~\ref{fig:example-fermi-lat} shows the result. \jolideco clearly improves the noise level as well as angular resolution. It reveals mophological details consistent with the HESS measurement.
+    We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
+Because of the limited statistics we did not use any oversampling but kept the pixel size of the counts image.
+
+    Figure~\ref{fig:example-fermi-lat} shows the result.
+\jolideco clearly improves the noise level as well as angular resolution.
+It reveals mophological details consistent with the HESS measurement \todo{Add HESS image or erosita for comparison?
+But this is not an analysis...}
+    The calibration of the predicted counts finds different background model norms and positional shifts in order of \todo{add value} for the different event classes.
+This way it corrects for systematic errors in the reconstruction of the position.
+As a check we compute a map of residuals based on  predicted counts, also
+
+    \url{https://github.com/jolideco/jolideco-fermi-examples}
 
@@
             \caption{
-                The \jolideco method applied to the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
+                The \jolideco method applied to \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
 The left image shows the counts above \qty[mode = text]{10}{GeV}.
 The different event classes are stacked into a single image.
-                The image in the center show the flux reconstructed by the \jolideco methods. The image on the right shows the normalised residuals.
+                The image in the center show the flux reconstructed by the \jolideco methods. The image on the right shows the 
+                residuals as compute by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels.
+More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.
+\todo{Move color bar to top and make images larger}
             }
@@
 
-    \section{Summary \& Conclusions}
+    \section{Summary \& Outlook}
     In this work we presented a new method for image deconvolution and denoising in the presence of Poisoon noise.
@@
 
+    We consider the \jolideco method as a first step into the territory of machine learning inspired methods for image data 
+    dominated by Poisson noise. By applying patch based transfer learning.
+
+    While we achieved already superior results to any other method we have identified multiple directions for improvement and variations of the method.
+Firstly it is possibly to rely on more general mixture models such as a Student-T or a generalised Gaussian mixture model.
+Those more flexible functional shapes can account for tails in the distributions.
+Improved results
+    on natural images have been reported e.g. by \cite{}.
+
+    To further improve the expressiveness of the prior \cite{Altekrueger2022} used normalising flows to model the distribution of patches.
+
     \begin{itemize}
         \item Extend \jolideco to handle spectral dimension at the same time.
-        \item Use normalising flows for patch priors see \cite{Altekrueger2022}
-        \item Use other mixture models, such as Student T or generalised Gaussian. 
         \item one could try deep image priors \citep{Ulyanov2017}

### 2023-04-19 src/scripts/comparison-scenarios.py
Update comparison scenarios script

@@ -2,20 +2,22 @@ import config
 import numpy as np
 import paths
 from astropy.io import fits
+from astropy.visualization import simple_norm
 from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 
 scenarios = {
-    "point1": {"max_cut": 1.0},
-    "aster3": {"max_cut": 1.0},
-    "disk3": {"max_cut": 1.0},
-    "spiral3": {"max_cut": 1.0},
+    "point1": {"max_cut": 340.0, "asinh_a": 0.05},
+    "aster3": {"max_cut": 200.0, "asinh_a": 0.05},
+    "disk3": {"max_cut": 200.0, "asinh_a": 0.05},
+    "spiral3": {"max_cut": 100.0, "asinh_a": 0.05},
 }
 
 bg = "bg1"
 instrument = "chandra"
 
 methods = [
+    "gt",
     "pylira",
     "jolideco-uniform-prior=n=10",
     "jolideco-uniform-prior=n=1000",
@@ -23,24 +25,60 @@ methods = [
     "jolideco-patch-prior-zoran-weiss",
 ]
 
+titles = {
+    "gt": "Ground Truth",
+    "pylira": "Pylira",
+    "jolideco-uniform-prior=n=10": "Jolideco\n(uniform, n=10)",
+    "jolideco-uniform-prior=n=1000": "Jolideco\n(uniform, n=1000)",
+    "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
+    "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
+}
+
 figsize = config.FigureSizeAA(aspect_ratio=1.2, width_aa="two-column")
 
-fig, axes = plt.subplots(nrows=4, ncols=5, figsize=figsize.inch)
+
+gridspec_kw = {
+    "left": 0.05,
+    "right": 0.95,
+    "bottom": 0.05,
+    "top": 0.92,
+    "wspace": 0.05,
+    "hspace": 0.05,
+}
+
+fig, axes = plt.subplots(
+    nrows=len(scenarios),
+    ncols=len(methods),
+    figsize=figsize.inch,
+    gridspec_kw=gridspec_kw,
+)
 
 path_base = paths.jolideco_repo_comparison / "results"
 
 for idx, scenario in enumerate(scenarios):
     for jdx, method in enumerate(methods):
[…]

### 2023-04-19 src/scripts/comparison-scenarios.py
[showyourwork] overleaf sync

@@ -7,16 +7,17 @@ from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 
 scenarios = {
-    "point1": {"max_cut": 340.0, "asinh_a": 0.05},
-    "aster3": {"max_cut": 200.0, "asinh_a": 0.05},
-    "disk3": {"max_cut": 200.0, "asinh_a": 0.05},
-    "spiral3": {"max_cut": 100.0, "asinh_a": 0.05},
+    "point1": {"max_cut": 340.0, "asinh_a": 0.02},
+    "aster3": {"max_cut": 200.0, "asinh_a": 0.02},
+    "disk3": {"max_cut": 200.0, "asinh_a": 0.02},
+    "spiral3": {"max_cut": 100.0, "asinh_a": 0.02},
 }
 
 bg = "bg1"
 instrument = "chandra"
 
 methods = [
+    "data",
     "gt",
     "pylira",
     "jolideco-uniform-prior=n=10",
@@ -26,21 +27,24 @@ methods = [
 ]
 
 titles = {
+    "data": "Data",
     "gt": "Ground Truth",
     "pylira": "Pylira",
-    "jolideco-uniform-prior=n=10": "Jolideco\n(uniform, n=10)",
-    "jolideco-uniform-prior=n=1000": "Jolideco\n(uniform, n=1000)",
+    "jolideco-uniform-prior=n=10": "Jolideco\n(Unif., n=10)",
+    "jolideco-uniform-prior=n=1000": "Jolideco\n(Unif., n=1000)",
     "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
     "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
 }
 
-figsize = config.FigureSizeAA(aspect_ratio=1.2, width_aa="two-column")
+figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
 
+upsampling_factor = 2
+DATA_SHAPE = (128, 128)
 
 gridspec_kw = {
     "left": 0.05,
-    "right": 0.95,
-    "bottom": 0.05,
+    "right": 0.98,
+    "bottom": 0.02,
     "top": 0.92,
     "wspace": 0.05,
     "hspace": 0.05,
@@ -53,24 +57,57 @@ fig, axes = plt.subplots(
     gridspec_kw=gridspec_kw,
 )
 
[…]

### 2023-04-19 src/scripts/comparison-scenarios.py
Update comparison plot

@@ -6,31 +6,34 @@ from astropy.visualization import simple_norm
 from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 
-scenarios = {
-    "point1": {"max_cut": 340.0, "asinh_a": 0.02},
-    "aster3": {"max_cut": 200.0, "asinh_a": 0.02},
-    "disk3": {"max_cut": 200.0, "asinh_a": 0.02},
-    "spiral3": {"max_cut": 100.0, "asinh_a": 0.02},
+scenario_titles = {
+    "A": {
+        "name": "point1",
+        "plot": {"max_cut": 340.0, "asinh_a": 0.02},
+    },
+    "B": {
+        "name": "aster3",
+        "plot": {"max_cut": 200.0, "asinh_a": 0.02},
+    },
+    "C": {
+        "name": "disk3",
+        "plot": {"max_cut": 200.0, "asinh_a": 0.02},
+    },
+    "D": {
+        "name": "spiral3",
+        "plot": {"max_cut": 100.0, "asinh_a": 0.02},
+    },
 }
 
 bg = "bg1"
 instrument = "chandra"
 
-methods = [
-    "data",
-    "gt",
-    "pylira",
-    "jolideco-uniform-prior=n=10",
-    "jolideco-uniform-prior=n=1000",
-    "jolideco-patch-prior-gleam-v0.1",
-    "jolideco-patch-prior-zoran-weiss",
-]
 
-titles = {
+method_titles = {
     "data": "Data",
     "gt": "Ground Truth",
     "pylira": "Pylira",
-    "jolideco-uniform-prior=n=10": "Jolideco\n(Unif., n=10)",
+    "jolideco-uniform-prior=n=10": "Jolideco\n(Uni, n=10)",
     "jolideco-uniform-prior=n=1000": "Jolideco\n(Unif., n=1000)",
     "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
     "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
@@ -51,8 +54,8 @@ gridspec_kw = {
 }
 
 fig, axes = plt.subplots(
-    nrows=len(scenarios),
-    ncols=len(methods),
+    nrows=len(scenario_titles),
+    ncols=len(method_titles),
     figsize=figsize.inch,
     gridspec_kw=gridspec_kw,
 )
[…]

### 2023-04-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 For analysis of Galactic sources with complex morphology and typically radially symmetric features such as supernova remnants (SNRs) we learned a prior from images of the bright \chandra SNRs \textit{Cas A} and \textit{G292.0+01.8}.
-In total we extracted \todo{insert #} patches and learned a GMM with 128 components.
+In total we extracted \todo{insert number} patches and learned a GMM with 128 components.
 
@@
 
+    \begin{figure*}
+        \script{comparison-scenarios.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/comparison-scenarios.pdf}
+            \caption{
+                Comparison of different deconvolution methods for different scenarios.
+The left column shows the raw simulated data and the second most column from the left the ground truth to comapare to.
+The simulation used a background level of "bg1 and a Gaussian PSF of \todo{x pixels}.
+The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration.
+            }
+            \label{fig:comparison-scenarios}
+        \end{centering}
+    \end{figure*}
+
     \subsubsection{Comparing Background Levels}
@@
 
-    \subsubswction{Comparing Instruments}
+    \subsubsection{Comparing Instruments}
 

### 2023-04-20 src/scripts/comparison-signal-noise.py
Add signal to noise comparison

@@ -7,36 +7,35 @@ from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 
 scenario_titles = {
-    "A": {
-        "name": "point1",
-        "plot": {"max_cut": 340.0, "asinh_a": 0.02},
+    "D1": {
+        "name": "spiral1",
+        "plot": {"max_cut": 10.0, "asinh_a": 0.02},
     },
-    "B": {
-        "name": "aster3",
-        "plot": {"max_cut": 200.0, "asinh_a": 0.02},
+    "D2": {
+        "name": "spiral2",
+        "plot": {"max_cut": 30.0, "asinh_a": 0.02},
     },
-    "C": {
-        "name": "disk3",
-        "plot": {"max_cut": 200.0, "asinh_a": 0.02},
-    },
-    "D": {
+    "D3": {
         "name": "spiral3",
+        "plot": {"max_cut": 30.0, "asinh_a": 0.02},
+    },
+    "D4": {
+        "name": "spiral4",
         "plot": {"max_cut": 100.0, "asinh_a": 0.02},
+    },
+    "D5": {
+        "name": "spiral5",
+        "plot": {"max_cut": 5000.0, "asinh_a": 0.02},
     },
 }
 
-bg = "bg1"
 instrument = "chandra"
+method = "jolideco-patch-prior-gleam-v0.1"
 
-
-method_titles = {
-    "data": "Data",
-    "gt": "Ground Truth",
-    "pylira": "Pylira",
-    "jolideco-uniform-prior=n=10": "Jolideco\n(Uni, n=10)",
-    "jolideco-uniform-prior=n=1000": "Jolideco\n(Unif., n=1000)",
-    "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
-    "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
+bg_titles = {
+    "bg1": "Bkg 1",
+    "bg2": "Bkg 2",
+    "bg3": "Bkg 3",
 }
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
@@ -45,8 +44,8 @@ upsampling_factor = 2
 DATA_SHAPE = (128, 128)
 
 gridspec_kw = {
-    "left": 0.05,
-    "right": 0.98,
+    "left": 0.08,
+    "right": 0.99,
[…]

### 2023-04-20 src/scripts/comparison-signal-noise.py
[showyourwork] overleaf sync

@@ -134,4 +134,4 @@ for idx, scenario_title in enumerate(scenario_titles):
             )
 
 
-plt.savefig(paths.figures / "comparison-singal-noise.pdf", dpi=config.DPI)
+plt.savefig(paths.figures / "comparison-signal-noise.pdf", dpi=config.DPI)

### 2023-04-20 src/scripts/comparison-scenarios.py
Adapt scenario titles

@@ -7,19 +7,19 @@ from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 
 scenario_titles = {
-    "A": {
+    "A1": {
         "name": "point1",
         "plot": {"max_cut": 340.0, "asinh_a": 0.02},
     },
-    "B": {
+    "B3": {
         "name": "aster3",
         "plot": {"max_cut": 200.0, "asinh_a": 0.02},
     },
-    "C": {
+    "C3": {
         "name": "disk3",
         "plot": {"max_cut": 200.0, "asinh_a": 0.02},
     },
-    "D": {
+    "D3": {
         "name": "spiral3",
         "plot": {"max_cut": 100.0, "asinh_a": 0.02},
     },

### 2023-04-20 src/scripts/comparison-scenarios.py
Adapt label positions

@@ -125,7 +125,7 @@ for idx, scenario_title in enumerate(scenario_titles):
 
         if method == "data":
             axes[idx, jdx].text(
-                x=-30,
+                x=-40,
                 y=DATA_SHAPE[0] / 2.0,
                 s=scenario_title,
                 fontsize=12,

### 2023-04-20 src/scripts/example-fermi-lat.py
Fix residual computation

@@ -44,6 +44,11 @@ def add_cbar(im, ax, fig, label=""):
     cbar.set_label(label)
 
 
+def smooth_map(smooth_width, map):
+    """Return a smoothed map"""
+    return map.smooth(width=smooth_width) * smooth_width**2
+
+
 path = (
     paths.jolideco_repo_fermi_lat_example
     / "results/vela-junior-above-10GeV-data/jolideco"
@@ -89,12 +94,12 @@ flux = Map.from_geom(npred.geom, data=flux_data)
 flux.plot(ax=ax_flux, cmap="viridis", interpolation="gaussian")
 add_cbar(ax_flux.images[0], ax_flux, fig, label="Flux / $(10^{-14} cm^{-2} s^{-1})$")
 
+norm = np.pi * SMOOTH_WIDTH**2
+diff = (stacked - npred).smooth(SMOOTH_WIDTH) * norm
 
-residuals = (stacked.smooth(SMOOTH_WIDTH) - npred.smooth(SMOOTH_WIDTH)) / np.sqrt(
-    npred.smooth(SMOOTH_WIDTH)
-)
+residuals = diff / np.sqrt(npred.smooth(SMOOTH_WIDTH) * norm)
 
-residuals.plot(ax=ax_residuals, cmap="RdBu", vmin=-0.5, vmax=0.5)
+residuals.plot(ax=ax_residuals, cmap="RdBu", vmin=-2, vmax=2)
 add_cbar(
     ax_residuals.images[0],
     ax_residuals,

### 2023-04-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration.
+                All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
             }
@@
     \subsubsection{Comparing Background Levels}
-    Methods
+       \begin{figure*}
+        \script{comparison-signal-noise.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/comparison-signal-noise.pdf}
+            \caption{
+                Comparison of Jolideco (GLEAM v0.1) for different signal to noise ratios.
+                All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
+            }
+            \label{fig:comparison-signal-noise}
+        \end{centering}
+    \end{figure*}
 
@@
         \label{eq:approx-sigma}
-        \sigma = \frac{N_{\mathrm{Counts}} - N_{\mathrm{Pred}}} {\sqrt{N_{\mathrm{Pred}}}}
+        \sigma \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
     \end{equation}
+
+    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
+    \todo{To account for the Poisson statistics it would be more precise to compute a "TS" map, but for an approximate estimation it should  be fine... }
 

### 2023-04-20 src/scripts/example-fermi-lat.py
[showyourwork] overleaf sync

@@ -94,10 +94,11 @@ flux = Map.from_geom(npred.geom, data=flux_data)
 flux.plot(ax=ax_flux, cmap="viridis", interpolation="gaussian")
 add_cbar(ax_flux.images[0], ax_flux, fig, label="Flux / $(10^{-14} cm^{-2} s^{-1})$")
 
-norm = np.pi * SMOOTH_WIDTH**2
-diff = (stacked - npred).smooth(SMOOTH_WIDTH) * norm
+norm_factor = np.pi * SMOOTH_WIDTH**2
+diff = (stacked - npred).smooth(SMOOTH_WIDTH) * norm_factor
 
-residuals = diff / np.sqrt(npred.smooth(SMOOTH_WIDTH) * norm)
+residuals = diff / np.sqrt(npred.smooth(SMOOTH_WIDTH) * norm_factor)
+
 
 residuals.plot(ax=ax_residuals, cmap="RdBu", vmin=-2, vmax=2)
 add_cbar(

### 2023-04-20 src/scripts/example-fermi-lat.py
[showyourwork] overleaf sync

@@ -4,6 +4,7 @@ import numpy as np
 import paths
 from astropy import units as u
 from astropy.io import fits
+from astropy.visualization import simple_norm
 from gammapy.maps import Map
 
 SMOOTH_WIDTH = 5
@@ -99,8 +100,8 @@ diff = (stacked - npred).smooth(SMOOTH_WIDTH) * norm_factor
 
 residuals = diff / np.sqrt(npred.smooth(SMOOTH_WIDTH) * norm_factor)
 
-
-residuals.plot(ax=ax_residuals, cmap="RdBu", vmin=-2, vmax=2)
+norm = simple_norm(residuals.data, stretch="linear", min_cut=-2, max_cut=2)
+residuals.plot(ax=ax_residuals, cmap="RdBu", norm=norm, interpolation="gaussian")
 add_cbar(
     ax_residuals.images[0],
     ax_residuals,

### 2023-04-20 src/scripts/comparison-instruments.py
Add instrument comparison plot

@@ -1,0 +1,140 @@
+import config
+import numpy as np
+import paths
+from astropy.io import fits
+from astropy.visualization import simple_norm
+from matplotlib import pyplot as plt
+from matplotlib.gridspec import GridSpec
+
+scenario_titles = {
+    "D1": {
+        "name": "spiral1",
+        "plot": {"max_cut": 10.0, "asinh_a": 0.02},
+    },
+    "D2": {
+        "name": "spiral2",
+        "plot": {"max_cut": 30.0, "asinh_a": 0.02},
+    },
+    "D3": {
+        "name": "spiral3",
+        "plot": {"max_cut": 30.0, "asinh_a": 0.02},
+    },
+    "D4": {
+        "name": "spiral4",
+        "plot": {"max_cut": 100.0, "asinh_a": 0.02},
+    },
+    "D5": {
+        "name": "spiral5",
+        "plot": {"max_cut": 5000.0, "asinh_a": 0.02},
+    },
+}
+
+instrument = "chandra"
+method = "jolideco-patch-prior-gleam-v0.1"
+
+bg = "bg1"
+
+instrument_titles = {
+    "chandra": '"Chandra"',
+    "xmm": '"XMM"',
+    "joint": "Joint",
+}
+
+figsize = config.FigureSizeAA(aspect_ratio=1.8, width_aa="two-column")
+
+upsampling_factor = 2
+DATA_SHAPE = (128, 128)
+
+gridspec_kw = {
+    "left": 0.13,
+    "right": 0.99,
+    "bottom": 0.02,
+    "top": 0.92,
+    "wspace": 0.05,
+    "hspace": 0.05,
+}
+
+fig, axes = plt.subplots(
+    nrows=len(instrument_titles),
+    ncols=len(scenario_titles),
+    figsize=figsize.inch,
+    gridspec_kw=gridspec_kw,
+)
+
+
+def read_and_stack_counts(scenario, bg, instrument):
+    """Read and stack couns files"""
+    path = paths.jolideco_repo_comparison / "data"
+
+    filenames = path.glob(
+        f"{instrument}_gauss_fwhm4710_128x128_sim*_{bg}_{scenario}_iter*.fits"
+    )
+
+    data_all = []
+
+    for filename in filenames:
+        data_all.append(fits.getdata(filename))
+
+    return np.mean(data_all, axis=0)
+
+
+def read_flux_ref(scenario):
+    """Reda reference flux"""
[…]

### 2023-04-20 src/scripts/example-fermi-lat.py

@@ -87,6 +87,8 @@ for filename in filenames_data:
     counts = Map.read(filename, hdu="COUNTS").sum_over_axes(keepdims=False)
     stacked.stack(counts)
 
+print(f"Total counts: {stacked.data.sum()}")
+
 stacked.plot(ax=ax_counts, cmap="viridis", interpolation="None")
 add_cbar(ax_counts.images[0], ax_counts, fig, label="Counts")
 
@@ -99,6 +101,10 @@ norm_factor = np.pi * SMOOTH_WIDTH**2
 diff = (stacked - npred).smooth(SMOOTH_WIDTH) * norm_factor
 
 residuals = diff / np.sqrt(npred.smooth(SMOOTH_WIDTH) * norm_factor)
+
+residuals_per_pix = (stacked - npred) / np.sqrt(npred)
+print(f"Mean residuals : {residuals_per_pix.data.mean():.3f}")
+print(f"Sigma residuals: {residuals_per_pix.data.std():.3f}")
 
 norm = simple_norm(residuals.data, stretch="linear", min_cut=-2, max_cut=2)
 residuals.plot(ax=ax_residuals, cmap="RdBu", norm=norm, interpolation="gaussian")

### 2023-04-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \subsubsection{NRAO Jets, Jets, Jets}
-    \todo{Include the jet prior?}
+    \todo{Include the jet prior or not?}
     For the specific application of jet detection and analysis in extract galactic data we learned a GMM patch prior from radio jet images.
@@
     \subsubsection{Chandra SNRs}
+    \label{sssec:chandra-snrs}. Because of the limited statistics we did not use any oversampling but kept the pixel
     Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}.
@@
 
+    \begin{figure*}
+        \script{comparison-instruments.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/comparison-instruments.pdf}
+            \caption{
+                Comparison of different deconvolution methods for different scenarios.
+The left column shows the raw simulated data and the second most column from the left the ground truth to comapare to.
+The simulation used a background level of "bg1 and a Gaussian PSF of \todo{x pixels}.
+The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration.
+                All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
+            }
+            \label{fig:comparison-instruments}
+        \end{centering}
+    \end{figure*}
+
     \section{Application Examples}
@@
     Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
-    \todo{To account for the Poisson statistics it would be more precise to compute a "TS" map, but for an approximate estimation it should  be fine... }
+    \todo{To account for the Poisson statistics it would be more precise to compute a "TS" map, but for an approximate estimation it should  be fine...I have a derivation for this formula }
 
@@
 
-    Figure~\ref{fig:example-fermi-lat} shows the result.
+    Figure~\ref{fig:example-fermi-lat} shows the data, result and residuals. The \fermi data is sparse, with very limited statistics.
     \jolideco clearly improves the noise level as well as angular resolution.
-It reveals mophological details consistent with the HESS measurement \todo{Add HESS image or erosita for comparison?
+It reveals morphological details consistent with the HESS measurement \todo{Add HESS image or erosita for comparison?
 But this is not an analysis...}
@@
 This way it corrects for systematic errors in the reconstruction of the position.
-As a check we compute a map of residuals based on  predicted counts, also
+As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit \textit{Gaussian} distribution.
 
@@
 
+    We invite the community of x-ray and \gammaray astronomers to use the method on combined data.
+
     \section*{Acknowledgements}

### 2023-04-23 src/scripts/comparison-signal-noise.py
Adjust signal noise plot

@@ -1,4 +1,5 @@
 import config
+import matplotlib.lines as lines
 import numpy as np
 import paths
 from astropy.io import fits
@@ -32,29 +33,32 @@ scenario_titles = {
 instrument = "chandra"
 method = "jolideco-patch-prior-gleam-v0.1"
 
-bg_titles = {
-    "bg1": "Bkg 1",
-    "bg2": "Bkg 2",
-    "bg3": "Bkg 3",
-}
+bg_titles = [
+    ("bg1", "Data"),
+    ("bg1", "Reconstruction"),
+    ("bg2", "Data"),
+    ("bg2", "Reconstruction"),
+    ("bg3", "Data"),
+    ("bg3", "Reconstruction"),
+]
 
-figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
+figsize = config.FigureSizeAA(aspect_ratio=1.2, width_aa="two-column")
 
 upsampling_factor = 2
 DATA_SHAPE = (128, 128)
 
 gridspec_kw = {
-    "left": 0.08,
+    "left": 0.05,
     "right": 0.99,
-    "bottom": 0.02,
-    "top": 0.92,
+    "bottom": 0.01,
+    "top": 0.91,
     "wspace": 0.05,
     "hspace": 0.05,
 }
 
 fig, axes = plt.subplots(
-    nrows=len(bg_titles),
-    ncols=len(scenario_titles),
+    nrows=len(scenario_titles),
+    ncols=len(bg_titles),
     figsize=figsize.inch,
     gridspec_kw=gridspec_kw,
 )
@@ -102,12 +106,20 @@ def read_flux(scenario, bg, instrument):
     return data
 
 
+def move_axis(ax):
+    """Move axis"""
+    box = ax.get_position()
+    box.x0 = box.x0 - 0.007
+    box.x1 = box.x1 - 0.007
+    ax.set_position(box)
+
+
 for idx, scenario_title in enumerate(scenario_titles):
     scenario = scenario_titles[scenario_title]["name"]
     norm_kwargs = scenario_titles[scenario_title]["plot"]
 
-    for jdx, bg in enumerate(bg_titles):
-        if scenario == "data":
+    for jdx, (bg, bg_title) in enumerate(bg_titles):
+        if bg_title == "Data":
             data = read_and_stack_counts(scenario, bg, instrument)
         elif scenario == "gt":
             data = read_flux_ref(scenario)
[…]

### 2023-04-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \begin{equation}
+        \label{eq:patch-norm}
         \tilde{\mathbf{x}}_n = f \left(\frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n} \right)
@@
     \section{Experiments}
-    \subsection{Test Datasets}\label{sec:testmodels}
+    \subsection{Test Datasets}
+    \label{subsec:test-datasets}
     \todo{Vinay writes this?}
@@
         \item An instrument with good angular resolution, but low effective area (e.g. like Chandra)
-        \item An instrument with worse angularr resolution, bur higher effective area (e.g. like XMM)
+        \item An instrument with worse angular resolution, bur higher effective area (e.g. like XMM)
     \end{itemize}
@@
     \subsection{Methods}
-    We compare the performance of 5 different methods:
+    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we use the following setup:
 
     \begin{itemize}
-        \item Pylira \citep{Esch2004, scipy_proceeding}
-        \item \jolideco with a uniform prior and 10 iterations. This can be considered as a reference similar to RL.
-        \item \jolideco with a uniform prior and 10 iterations. This can be considered as a reference similar to RL.
-        \item \jolideco with a patch prior learned on Gleam data and sum patch norm
-        \item \jolideco with a patch prior from \cite{Zoran2011} and the mean subracted patch norm. This is for comparison to the original method and the method used on \cite{Bouman2016}.
+        \item \textit{LIRA} method \citep{Esch2004} via the \textit{Pylira} Python wrapper \cite{ scipy_proceeding}.
+We rely on the default prior definition and allow the scale for the background to vary.
+We use 500 iterations as a "burn-in" period to allow the MCMC chain to converge.
+        \item \jolideco with a uniform prior and 10 iterations.
+This setup we consider as a base line method reference similar to RL.
+While the optimization procedure is different, we still expect to see similar behaviour for the local correlations of pixels.
+This ad hoc approach of "early stopping" is often used in practice to "regularise" the RL method.
+        \item \jolideco with a uniform prior and 1000 iterations. Sames as above except without early stopping. This gives rise to the issue of RL decomposing extended emission into point sources. 
+        \item \jolideco with a patch prior learned on GLEAM data, described in Section~\ref{sssec:gleam-radio-data}.
+It also uses the standardised patch normalisation.
+described in Equation~\ref{eq:patch-norm}.
+We use cycle spinning, a stride of 4 pixels and 1000 iterations.
+Which optimizes "to the end" until there is no relevant change in the posterior log-likelihood.
+
+        \item \jolideco with a patch prior from \cite{Zoran2011} and the mean subtracted patch norm.
+This is for comparison to the original method and the method used on \cite{Bouman2016}.
+We use maximum image norm with the maximum values defined by the ground truth \todo{is this fair?}.
     \end{itemize}
 
+    We ran the comparison on the whole parameter grid, whoever in the following we can only discuss a subset of the results, which we consider the most relevant.
+All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
+
     \subsection{Results}
-    All the results are available at \url{https://jolideco.github.io/jolideco-comparison}.
-    \subsubsection{Comparing Scenarios}
+    \subsubsection{Comparing Methods}
     \jolideco shows excellent performance of a variety of morphological shapes. 
     it converges to the reference solution for very high signal to noise.
+
+    Figure \ref{fig:comparison-scenarios} shows the comparison of the methods for the subset of source scenarios described in Section~\ref{subsec:test-datasets}.
+
+    \par{\textbf{Pylira}}
+    Pylira shows 
+    \begin{itemize}
+        \item Shows good results for point sources
+        \item Slightly improved results on extended source, but still "speckly"
+        \item Pixels loose spatial correlation over larger scales..
+    \end{itemize}
+
+    \par{\textbf{Jolideco, Uniform Prior n=1000:}}
+    The uniform priors show the expected behaviour: decompose into point sources, when "optimized to the end".
+
+    \begin{itemize}
+        \item the uniform priors show the expected behaviour: decompose into point sources, when "optimized to the end".
+        \item yields very good results, if the true underlying source are only point sources
+        \item results are very bad, once extended emission is present. Result is "speckly" with no visible spatial correlation between nearby pixels.
+    \end{itemize}
+
+    \par{\textbf{Jolideco, Patch Prior GLEAM}}
+    \begin{itemize}
+        \item shows best results
+        \item slightly worse results on point sources only
+        \item visually very close to ground truth (!)
+        \item good compromise between sufficient separation of point sources and good reconstruction of extended sources.
+    \end{itemize}
 
@@
     \subsubsection{Comparing Background Levels}
+
+    \todo{We should give a single number for the S/N, how to compute? Per source, like spiral ring and point sources...}
+
+    \todo{Should we leave the background norm free?}
+    Figure \ref{fig:comparison-signal-noise} shows the comparison for the method "Jolideco GLEAM v0.1" for varying signal to noise ratio for the "D" scenario.
+
+    Some observations:
+
+    \begin{itemize}
+        \item as expected the reconstruction quality improves with stronger signal
+        \item there seems to be a "jump" in the reconstruction quality of the point sources. The weakest is much more blurry, but all the others look fine.
+        \item the method "fails" at the highest background level.
+    \end{itemize}
+
        \begin{figure*}
@@
     \subsubsection{Comparing Instruments}
+    Figure \ref{fig:comparison-instruments} shows the comparison for the method "Jolideco GLEAM v0.1" for varying instrument scenarios and fixed background level.
+
+    \begin{itemize}
+        \item surprising reconstruction quality for XMM with a strong signal
+        \item combining the data results in the best reconstruction
+        \item for a strong signal adding the "XMM" data improves the "Chandra" result for extende sources. It further reduces the "speckliness"
+        \item not understood: reconstruction of point source becomes worse as spiral becomes brighter.
+Maybe because the strong signal dominates the likelihood function?
+Not sure how to improve this...it is image dynamics...
+        \item confirm results by \cite{Ingaramo2014}, the method takes "the" best pout of two different measurements. 
+    \end{itemize}
 
@@
             \caption{
-                Comparison of different deconvolution methods for different scenarios.
-The left column shows the raw simulated data and the second most column from the left the ground truth to comapare to.
-The simulation used a background level of "bg1 and a Gaussian PSF of \todo{x pixels}.
-The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration.
+                Comparison of the different instrument scenarios. 
                 All results are available at \url{https://jolideco.github.io/jolideco-comparison}.

### 2023-04-23 src/scripts/comparison-instruments.py
Adapt instrument comparison

@@ -3,6 +3,7 @@ import numpy as np
 import paths
 from astropy.io import fits
 from astropy.visualization import simple_norm
+from matplotlib import lines
 from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 
@@ -29,46 +30,62 @@ scenario_titles = {
     },
 }
 
-instrument = "chandra"
 method = "jolideco-patch-prior-gleam-v0.1"
 
 bg = "bg1"
 
-instrument_titles = {
-    "chandra": '"Chandra"',
-    "xmm": '"XMM"',
-    "joint": "Joint",
-}
+instrument_titles = [
+    ("chandra", "Data"),
+    ("chandra", "Reconstruction"),
+    ("xmm", "Data"),
+    ("xmm", "Reconstruction"),
+    ("joint", "Data"),
+    ("joint", "Reconstruction"),
+]
 
-figsize = config.FigureSizeAA(aspect_ratio=1.8, width_aa="two-column")
+figsize = config.FigureSizeAA(aspect_ratio=1.2, width_aa="two-column")
 
 upsampling_factor = 2
 DATA_SHAPE = (128, 128)
 
 gridspec_kw = {
-    "left": 0.13,
+    "left": 0.05,
     "right": 0.99,
-    "bottom": 0.02,
-    "top": 0.92,
+    "bottom": 0.01,
+    "top": 0.91,
     "wspace": 0.05,
     "hspace": 0.05,
 }
 
 fig, axes = plt.subplots(
-    nrows=len(instrument_titles),
-    ncols=len(scenario_titles),
+    nrows=len(scenario_titles),
+    ncols=len(instrument_titles),
     figsize=figsize.inch,
     gridspec_kw=gridspec_kw,
 )
+
+
+def move_axis(ax):
+    """Move axis"""
+    box = ax.get_position()
+    box.x0 = box.x0 - 0.007
+    box.x1 = box.x1 - 0.007
+    ax.set_position(box)
 
 
 def read_and_stack_counts(scenario, bg, instrument):
     """Read and stack couns files"""
     path = paths.jolideco_repo_comparison / "data"
 
-    filenames = path.glob(
-        f"{instrument}_gauss_fwhm4710_128x128_sim*_{bg}_{scenario}_iter*.fits"
-    )
+    filenames = []
+
+    if instrument == "chandra" or instrument == "joint":
[…]

### 2023-04-25 src/scripts/comparison-scenarios.py
Update compare scenario plot

@@ -6,22 +6,23 @@ from astropy.visualization import simple_norm
 from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 
+asinh_a = 0.01
 scenario_titles = {
     "A1": {
         "name": "point1",
-        "plot": {"max_cut": 340.0, "asinh_a": 0.02},
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
     },
     "B3": {
         "name": "aster3",
-        "plot": {"max_cut": 200.0, "asinh_a": 0.02},
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
     },
     "C3": {
         "name": "disk3",
-        "plot": {"max_cut": 200.0, "asinh_a": 0.02},
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
     },
-    "D3": {
-        "name": "spiral3",
-        "plot": {"max_cut": 100.0, "asinh_a": 0.02},
+    "D4": {
+        "name": "spiral4",
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
     },
 }
 
@@ -32,11 +33,11 @@ instrument = "chandra"
 method_titles = {
     "data": "Data",
     "gt": "Ground Truth",
-    "pylira": "Pylira",
     "jolideco-uniform-prior=n=10": "Jolideco\n(Uni, n=10)",
     "jolideco-uniform-prior=n=1000": "Jolideco\n(Unif., n=1000)",
-    "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
+    "pylira": "Pylira",
     "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
+    "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
 }
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")
@@ -46,11 +47,11 @@ DATA_SHAPE = (128, 128)
 
 gridspec_kw = {
     "left": 0.05,
-    "right": 0.98,
+    "right": 0.90,
     "bottom": 0.02,
     "top": 0.92,
     "wspace": 0.05,
-    "hspace": 0.05,
+    "hspace": 0.02,
 }
 
 fig, axes = plt.subplots(
[…]

### 2023-04-25 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    \subsection{A note on Deep Learning Methods}
-    In the past decade Machine learning (ML) especially deep convolutional neural networks became the \textit{de facto} standard
-    for de-blurring and super-resolution of natural images \todo{reference review?}.
+    \subsection{Some notes on Deep Learning Methods}
+    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the \textit{de facto} standard for de-blurring and super-resolution of natural images \todo{reference review?}.
 However their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
-For a variety of reasons this approach is not suitable for astronomical x-ray and \gammaray data.
+For a variety of reasons, which we will outline in the following, this approach is not ideal for astronomical x-ray and \gammaray data.
 
-    Astronomical data is rare and expensive and there is no ground truth.
-One could rely on transfer learning and simulated data.
-E.g.
-radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise.
-However astronomical images have a large dynamic range and show a high diversity in morphological structure, which would still require al large amount of training data.
-However this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \todo{reference} or as a post processing step of results obtained with regularised RL \todo{Reference by Starck et al.}.
+    First astronomical x-ray and \gammaray data data is rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
+To circumvent this one could rely on transfer learning and simulated data.
+For example radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise to generate training data.
+However astronomical images still have a large dynamic range and show a high diversity in morphological structure, which would still require a large amount of training data.
+However this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
 
@@
 on energy as well as offset angle from the pointing direction.
-To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models, which would require a very large computational effort.
+To cover the whole parameter space of the PSF one would need to train either a network for each of the PSF models, or define a very large network, which would require a very large computational effort.
 
-    \cite{Li2014} have introduced a baseline architecture for a deep convolutional neural network for image deblurring.
-    The convolutional nature of the network does not make it suitable for the task. As convolution introduces smoothing.
-    However the network can learn an "inverse kernel", which needs to be larger because of the uncertainty principle (\todo{reference...}).
-    The large kernels are introduced by separability assumption...
-    In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possibly for most network architectures.
-Except for e.g.
-normalising flows \todo{there are references where NFs have bee used as priors...}
+    Some of the challenges of de-blurring with CNN are due to the convolutional nature of the networks.
+In a single layer, linear approximation, the network would need to learn the inverse filter of the PSF, corresponding to the well known \textit{Wiener filter} solution of the problem.
+This requires large convolution kernels or deep network architectures.
+\cite{Li2014} have introduced a baseline architecture for a deep CNN for image de-blurring by introducing large kernels under the separability assumption.
 
-    \begin{itemize}
-    \item diversity of astronomical images is high, one would need lots of training data
-    \item Given a set of training images one could generate training data by forward folding with a known PSF model
-    and adding Poisson noise
-    \item however this would require training a new network for each PSF and noise level just to learn the task.
-    This is a high computational effort. 
-    \item By allowing multiple inputs one could still try to estimate a common flux image \todo{so far I have not heard
-    about something like this...}
-    \end{itemize}
+    One last important challenge is obtaining uncertainty estimates for the reconstructed image from CNNs.
+In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possible for most network architectures, with the exception of for example normalising flows.
 
@@
     Our goal is to recover an image $\mathbf{x}$ from a set of multiple low counts observations.
-Most generally we assume our total dataset consists of $J$ individual observations of the same region of the sky, which are jointly modelled.
-The assumption is that the underlying \textit{true} emission image, we are looking for does not change with time.
+Most generally we assume our total dataset consists of $J$ individual observations of the same region of the sky, which we jointly model.
+The assumption is that the underlying, unknown \textit{true} emission image, we are interested in, does not change with time.
 Under this assumption these datasets can be for example:
@@
         \item Different observations of one instrument or telescope at different times and observation conditions.
-E.g., multiple observations of \chandra with different offset angles and exposure times.
-        \item Observations of different telescopes, which operate in the same wavelength range. E.g., a \chandra
-        and \xmm observation of the same region in the sky.
-        \item A single observation of one telescope with different data quality categories and different associated instrument
-        response functions. E.g., event classes for \fermi.
+E.g., multiple observations of \chandra of the same astrophysical object with different offset angles and exposure times
+        \item Observations from different telescopes, which operate in the same wavelength range. E.g., a \chandra and \xmm observation of the same region in the sky
+        \item A single observation of one telescope with different data quality categories and different associated instrument response functions, such as event classes for \fermi
     \end{itemize}
@@
     interaction time and the fact that the interaction cannot propagate
-    faster than the speed of light. This means on smaller scales astronomical
+    faster than the speed of light (structure in the CMB is an exception here). This means on smaller scales astronomical
     images often contain basic structures such as edges, corners, filaments or
@@
     to the same object or when using different types of telescopes for observation, the
-    position of an astronomical object might vary in the image between different
-    observations. The process of correcting for these inaccuracies is called \textit{astrometry}.
+    absolute position of an astronomical object might vary in the image between different
+    observations. The process of correcting for these inaccuracies is called \textit{astrometry} and a standard procedure in for example \chandra data analysis.
     A second example of systematic errors is the variation of background emission
@@
     counts introduced in Eq.~\ref{eq:model}, by a background normalisation factor
-    $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$,
-    which is specific for each observation. This yields the following modified model definition:
+    $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$, which is specific for each observation. This yields the following modified model definition:
 
@@
     \begin{itemize}
-        \item the optimizer sees $\log{\mathbf{x}}$
+        \item the optimizer sees $\log{\mathbf{x}}$, note this corresponds to an "implicit" prior of the flux being positive...
         \item First run with uniform prior, to get a rough estimate
@@
     \label{subsec:test-datasets}
+
+    \begin{table*}[t]
+      \centering
+      \begin{tabular}{l|cr}
+        \hline
+        Scenario & Description & Parameters \\
+        \hline
+        A1 & A grid of point sources & x, y \\
+        B1-3 & Extended Gaussian shaped source surrounded by point sources & $\sigma$ \\
+        C1-3 & Point Sources on top of a disk shaped source, jet like line features & $r_{\mathrm{Disk}}$ \\
+        D1-5 & A spiral-arm structure surrounded by point sources and a large ring like feature & 9 \\
+
+        \hline
+      \end{tabular}
+      \caption{Source scenarios, \todo{maybe we find a good structure for the table...would list the actual flux values per component}}
+      \label{tab:1}
+    \end{table*}
+
     \todo{Vinay writes this?}
@@
         \item An instrument with good angular resolution, but low effective area (e.g. like Chandra)
-        \item An instrument with worse angular resolution, bur higher effective area (e.g. like XMM)
+        \item An instrument with worse angular resolution, but higher effective area (e.g. like XMM)
     \end{itemize}
@@
     \subsection{Methods}
-    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we use the following setup:
+    \label{subsec:methods}
+    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we use the following definitions:
 
     \begin{itemize}
-        \item \textit{LIRA} method \citep{Esch2004} via the \textit{Pylira} Python wrapper \cite{ scipy_proceeding}.
+        \item \textbf{Pylira}: first we use the \textit{LIRA} method \citep{Esch2004} via the \textit{Pylira} Python wrapper \citep{Donath2022}.
 We rely on the default prior definition and allow the scale for the background to vary.
-We use 500 iterations as a "burn-in" period to allow the MCMC chain to converge.
-        \item \jolideco with a uniform prior and 10 iterations.
-This setup we consider as a base line method reference similar to RL.
+In total we run the the sampling process for 5000 iterations and use 500 iterations as a "burn-in" period to allow the MCMC chain to converge.
+Then we compute the mean of the posterior distribution ignoring the burn-in period.
+
+        \item \textbf{Jolideco (Uniform, n=10)}: second we use \jolideco with a uniform prior and 10 iterations.
+This setup we consider as a baseline method reference similar to RL.
 While the optimization procedure is different, we still expect to see similar behaviour for the local correlations of pixels.
 This ad hoc approach of "early stopping" is often used in practice to "regularise" the RL method.
-        \item \jolideco with a uniform prior and 1000 iterations. Sames as above except without early stopping. This gives rise to the issue of RL decomposing extended emission into point sources. 
-        \item \jolideco with a patch prior learned on GLEAM data, described in Section~\ref{sssec:gleam-radio-data}.
-It also uses the standardised patch normalisation.
-described in Equation~\ref{eq:patch-norm}.
+
+        \item \textbf{Jolideco (Uniform, n=1000)}: again we use \jolideco with a uniform prior but running for 1000 iterations.
+Sames as above except without early stopping.
+This gives rise to the issue of RL decomposing extended emission into point sources.
+
+        \item \textbf{Jolideco (Patch, GLEAM v0.1)}: \jolideco with a patch prior learned on GLEAM data, described in Section~\ref{sssec:gleam-radio-data}.
+It also uses the standardised patch normalisation as described by Equation~\ref{eq:patch-norm}.
 We use cycle spinning, a stride of 4 pixels and 1000 iterations.
@@
 
-        \item \jolideco with a patch prior from \cite{Zoran2011} and the mean subtracted patch norm.
+        \item \textbf{Jolideco (Patch, Zoran-Weiss)}: \jolideco with a patch prior from \cite{Zoran2011} and the mean subtracted patch norm.
 This is for comparison to the original method and the method used on \cite{Bouman2016}.
@@
     \subsubsection{Comparing Methods}
+    %
+    \begin{figure*}
+        \script{comparison-scenarios.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/comparison-scenarios.pdf}
+            \caption{
+                Comparison of different deconvolution methods for different selected scenarios, as described in Section~\ref{subsec:test-datasets}.
+The simulation of the data used a fixed background level of, a constant exposure and a Gaussian PSF of \todo{x pixels}, corresponding to the "Chandra" scenario.
+The left column shows the simulated counts data and the second most column from the left the underlying ground truth to compare.
+The other column show the reconstructed flux by the different methods and prior assumptions.
+The methods are described in detail in Section~\ref{subsec:methods}.
+                A more detailed representation of the results is available at \url{https://jolideco.github.io/jolideco-comparison}.
+            }
+            \label{fig:comparison-scenarios}
+        \end{centering}
+    \end{figure*}
+    %
+    First we compare the performance of methods on the different source scenarios.
+    Figure \ref{fig:comparison-scenarios} shows the comparison of the methods for a selected subset of scenarios A1, B3, C3 and D3.
+
+    On scenario A1 all methods show acceptable to excellent results for the isolated point sources in the upper right of the image.
+This demonstrates all methods take into account the PSF and background model model correctly.
+The early stopped uniform prior still shows an extension for those cases, because the optimization process has not finished.
+The \jolideco with the Zoran-Weiss patch prior also results in less sharp images, because the prior has been learned on natural images of landscapes, objects, every day scenes etc.
+which do not include point sources.
+The \jolideco with the prior learned from GLEAM data, which also includes point sources, shows much improved results.
+
+    In the lower left of the image the point sources become fainter and closer, challenging all methods in succeeding to separate those as independent sourcea.
+The uniform prior optimized "to end" shows excellent results, still separating the sources.
+
+    For scenario B3 all method recover the point sources arpund the central extend source. 
+    However large difference can be observed in the reconstruction of the Gaussian shaped extended sources.
+As expected the uniform prior decompose the emission into many point sources, neglecting the spatial correlation between them.
+\textbf{Pylira} shows slightly improved results with the gaps between the bright emission peeks being more filled, however still lacks a convincing result into reconstructing the source as a single object.
+The \jolideco method with the patch priors shows the best results both visually as well as measured by the SSI.
+The GLEAM v0.1 patch prior reconstructs the
+    sources almost perfectly, visually indistinguishable from the ground truth.
+The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a visible extension in the surrounding point sources.
+
+    Scenario C3 challenges the methods to reconstruct a weak extended source under four brighter point sources.
+While again all methods reconstruct the point sources well, the visual differences are large for the weal underlying extended emission.
+
     \jolideco shows excellent performance of a variety of morphological shapes. 
     it converges to the reference solution for very high signal to noise.
-
-    Figure \ref{fig:comparison-scenarios} shows the comparison of the methods for the subset of source scenarios described in Section~\ref{subsec:test-datasets}.
 
@@
 
+    \subsubsection{Comparing Signal-to-Noise Scenarios}
+    %
     \begin{figure*}
-        \script{comparison-scenarios.py}
+        \script{comparison-signal-noise.py}
         \begin{centering}
-            \includegraphics[width=\linewidth]{figures/comparison-scenarios.pdf}
+            \includegraphics[width=\linewidth]{figures/comparison-signal-noise.pdf}
             \caption{
-                Comparison of different deconvolution methods for different scenarios.
-The left column shows the raw simulated data and the second most column from the left the ground truth to comapare to.
-The simulation used a background level of "bg1 and a Gaussian PSF of \todo{x pixels}.
-The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration.
-                All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
+                Comparison of the \jolideco method with the GLEAM v0.1 prior for different background levels and signal strength represented by scenario D1-5.
+The images are grouped by background levels with each column group showing the counts data in the left column and the reconstruction in the right column.
+The rows show the scenarios D1-5 as described in Section~\ref{subsec:test-datasets}.
+The background levels correspond to \qty[mode = text]{0.001}{cts / pixel}, \qty[mode = text]{0.01}{cts / pixel} and \qty[mode = text]{0.1}{cts / pixel}.
+The complete results for the simulations and additional information are available at \url{https://jolideco.github.io/jolideco-comparison}.
+\todo{the background handling does not yet seem right...maybe we should let the background norm free}
             }
-            \label{fig:comparison-scenarios}
+            \label{fig:comparison-signal-noise}
         \end{centering}
     \end{figure*}
-
-    \subsubsection{Comparing Background Levels}
-
+    %
     \todo{We should give a single number for the S/N, how to compute? Per source, like spiral ring and point sources...}
@@
 
+    \subsubsection{Comparing Instrument Scenarios}
+    %
     \begin{figure*}
-        \script{comparison-signal-noise.py}
+        \script{comparison-instruments.py}
         \begin{centering}
-            \includegraphics[width=\linewidth]{figures/comparison-signal-noise.pdf}
+            \includegraphics[width=\linewidth]{figures/comparison-instruments.pdf}
             \caption{
-                Comparison of Jolideco (GLEAM v0.1) for different signal to noise ratios.
+                Comparison of the \jolideco method with the GLEAM v0.1 prior for the different instrument scenarios.
+The images are grouped by instrument scenario with each column group showing the counts data in the left column and the reconstruction in the right column.
+The rows show the scenarios D1-5 as described in Section\ref{subsec:test-datasets}.
                 All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
             }
-            \label{fig:comparison-signal-noise}
+            \label{fig:comparison-instruments}
         \end{centering}
     \end{figure*}
+    %
+    Finally we compare the results from the \jolideco method for the different instrument scenarios.
+Figure~\ref{fig:comparison-instruments} shows the data as well as flux images reconstructed using \jolideco and the GLEAM v0.1 patch prior.
+We consider the source scenario D1-5 and the instrument scenarios and of \chandra, \xmm and combining both for a single reconstructed image.
 
-    \subsubsection{Comparing Instruments}
-    Figure \ref{fig:comparison-instruments} shows the comparison for the method "Jolideco GLEAM v0.1" for varying instrument scenarios and fixed background level.
+    Using the \chandra data alone results in a solid reconstruction at all variations of the D scenario. As expected the reconstruction quality improves for higher signal to noise ratio.
+
+    Using just the data from the \xmm instrument scenario results in lower quality reconstructions.
+However the spiral arm structure is reconstructed at all levels of the signal.
+The spiral arm structure is not really visible from the data by eye, because it is heavily blurred by the limited angular resolution.
+
+    Combining the data results in the best reconstruction quality.
+This confirms the results from \cite{Ingaramo2014}, that combining multiple measurements for deconvolution with RL was "general tool for combining images with complementary strengths".
 
@@
 Not sure how to improve this...it is image dynamics...
-        \item confirm results by \cite{Ingaramo2014}, the method takes "the" best pout of two different measurements. 
+        \item confirm results by , the method takes "the" best pout of two different measurements. 
     \end{itemize}
-
-    \begin{figure*}
-        \script{comparison-instruments.py}
-        \begin{centering}
-            \includegraphics[width=\linewidth]{figures/comparison-instruments.pdf}
-            \caption{
-                Comparison of the different instrument scenarios. 
-                All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
-            }
-            \label{fig:comparison-instruments}
-        \end{centering}
-    \end{figure*}
 
@@
 We assume a spatially constant background and exposure, however the exposure is scaled to a reference observation.
-The data reduction was done using ciao v4.15 and the custom snakemake workflow.
+The data reduction was done using ciao v4.15 and the custom \textit{snakemake} workflow.
 PSFs were simulated for each observation independently using \textit{marx} \todo{reference} and the \textit{simulate\_psf} script.
@@
     \section{Summary \& Outlook}
-    In this work we presented a new method for image deconvolution and denoising in the presence of Poisoon noise.
-    Jolideco is great...
+    In this work we presented a new method for image de-convolution and de-noising in the presence of Poisson noise.
+From multiple observations of the same sky region we reconstructed a single flux image using the approximate MAP estimate of the joint likelihood under patch based GMM prior.
+We showed that the methods leads to improved results in variety of scenarios.
+Especially it leads to much improved results for extended source with a size similar to the PSF.
+In this case it allows to reliably recover features, that are well beyond the angular resolution of the instrument.
 
-    We consider the \jolideco method as a first step into the territory of machine learning inspired methods for image data 
-    dominated by Poisson noise. By applying patch based transfer learning.
+    We showed that the approach of joining multiple observations leads improved results and allows to maximize the use of existing observational data.
 
-    While we achieved already superior results to any other method we have identified multiple directions for improvement and variations of the method.
+    We consider the \jolideco method as a first step into the territory of \textit{ML inspired} methods for reconstruction of astronomical image data dominated by Poisson noise.
+While we achieved already superior results to any other existing method,
+    the \jolideco methods shows large potential for future extension and improvements.
+
     Firstly it is possibly to rely on more general mixture models such as a Student-T or a generalised Gaussian mixture model.
 Those more flexible functional shapes can account for tails in the distributions.
-Improved results
-    on natural images have been reported e.g. by \cite{}.
+Improved results on natural images have been reported e.g.
+by \cite{}.
 
-    To further improve the expressiveness of the prior \cite{Altekrueger2022} used normalising flows to model the distribution of patches.
+    To further improve the expressiveness of the prior \cite{Altekrueger2022} used normalising flows to model the distribution of patches in the context of CT image reconstruction.
 
@@
         \item Extend \jolideco to handle spectral dimension at the same time.
+        \item Extend \jolideco to handle multiple source components at the same time.
         \item one could try deep image priors \citep{Ulyanov2017}
@@
 
-    We invite the community of x-ray and \gammaray astronomers to use the method on combined data.
+    We statistically combined data from existing telescopes to obtain a new \textit{virtual instrument}, with improved angular resolution and sensitivity.
+We invite the community of x-ray and \gammaray astronomers to use the method an combine data for new scientific discoveries, beyond the current angular resolution of existing instruments.
 

### 2023-04-30 src/scripts/example-chandra.py
Add Chandra example

@@ -2,27 +2,221 @@ import config
 import matplotlib.pyplot as plt
 import numpy as np
 import paths
+from astropy import units as u
+from astropy.coordinates import SkyCoord
 from astropy.io import fits
 from astropy.visualization import simple_norm
-from astropy.wcs import WCS
+from gammapy.maps import Map
+from regions import RectangleSkyRegion
 
-figsize = config.FigureSizeAA(aspect_ratio=13 / 4.0, width_aa="two-column")
+SMOOTH_WIDTH = 5
+FONT_SIZE = 8
+
+plt.rcParams.update({"font.size": FONT_SIZE})
 
 
-fig = plt.figure(figsize=(13, 4))
-# norm = simple_norm(npred.data, stretch="asinh", asinh_a=0.01, max_cut=350)
+def format_axes(ax, hide_yaxis=False):
+    """Format axes for a map plot"""
+    lon = ax.coords["ra"]
+    lat = ax.coords["dec"]
 
-wcs = WCS()
-height = 0.8
-ax_counts = fig.add_axes([0.01, 0.12, 0.4, height], projection=wcs)
-ax_npred = fig.add_axes([0.28, 0.12, 0.4, height], projection=wcs)
-ax_npred_rl = fig.add_axes([0.55, 0.12, 0.4, height], projection=wcs)
-ax_cbar = fig.add_axes([0.9, 0.12, 0.02, height])
+    lon.set_ticks_position("b")
+    lon.set_ticklabel_position("b")
 
-ax_counts.set_title("Counts")
-ax_npred.set_title("Reconstruction Jolideco")
-ax_npred_rl.set_title("Reconstruction RL $N_{iter} = 100$")
+    lat.set_ticks_position("l")
+    lat.set_ticklabel_position("l")
 
+    lon.set_major_formatter("d.dd")
+    lat.set_major_formatter("d.ddd")
+
+    lon.set_ticks(spacing=1 * u.arcmin)
+    lat.set_ticks(spacing=10 * u.arcsec)
+
+    if hide_yaxis:
+        lat.set_axislabel("")
+        lat.set_ticklabel_visible(False)
+
+
+def add_cbar(im, ax, fig, label=""):
+    """Add cbar to a given axis and figure"""
+    bbox = ax.get_position()
+    loright = bbox.corners()[-2]
[…]

### 2023-04-30 src/scripts/paths.py

@@ -32,4 +32,5 @@ output = tex / "output"
 # Joideco repos
 jolideco_repo_gmm_library = root / "../jolideco-gmm-prior-library"
 jolideco_repo_fermi_lat_example = root / "../jolideco-fermi-examples"
+jolideco_repo_chandra_example = root / "../jolideco-chandra-examples"
 jolideco_repo_comparison = root / "../jolideco-comparison"

### 2023-04-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \subsection{Related Work}
-    In literature there have been multiple efforts to correct the degrading of the images using statistical methods.
-    The standard baseline method for image deconvolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974}.
-They used expectation maximisation to solve.
-We will refer to this method as "RL".
-
-    One of the significant challenges in image deconvolution is the problem of Rayleigh-Lynden Bell (RL) decomposition of structures into point sources.
-This problem was first introduced by Reeves et al.
-\cite{Reeves1994} and later analyzed by Fish et al.
-\cite{Fish1995}.
-Regularized RL methods, such as total variation \citep{Dey2006} and maximum entropy \citep{Bi1994}, have been proposed to overcome this issue.
+    In literature there are many proposed methods to solve the un-blind deconvolution problem for images affected by Poisson noise.
+All methods rely fundamentally on modeling an image generating process as a linear system.
+Given a known point spread function a prediction of the discrete measured image can be obtained via \textit{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
+However the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the likelihood function.
+
+    The standard baseline method for image de-convolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \textit{RL}).
+The method involves estimating the original image by iteratively convolving the observed image with the PSF and dividing by the result of convolving the estimated image with the transposed PSF.
+The iterations continue until the estimated image converges to a satisfactory solution.
+
+    In practice the RL method was found to have multiple, partly related issues: first there is no objective criterion when to stop the iteration.
+Usually the iteration was stopped when the reconstructed image seemed plausible to the eye.
+Second, when the number of iterations was too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\textit{speckles}).
+This problem was e.g.
+described and studied by \cite{Reeves1995} and \cite{Fish1995}.
+Lastly the RL method does not provided an associated estimate of the uncertainties of the reconstruction, which is desirable especailly in the Poisson domain to asses the significance of specific features found in the reconstruction.
+
+    To address the question of when to stop the RL iteration \cite{Reeves1995} proposed to use cross validation.
+The authors of \citep{Bi1994} proposed a bootstrapped based assessment of the significance of reconstructed image as as a stopping rule for RL.
+
+    To address the issue with RL decomposing extended emission structures into groups of point source, multiple additions to the RL method were proposed.
+Most importantly this lead to the introduction of regularised RL methods.
+    such as use of total variation \citep{Dey2006} or sparseness \todo{add reference}.
 
     Multi-scale LIRA prior has been used in image deconvolution to incorporate error estimates and Bayesian sampling.
-This prior has been used in various studies, including those by Esch et al.
-\cite{Esch2004} and Connors et al.
-\cite{Connors2011}.
+This prior has been used in various studies, including those by \cite{Esch2004} and \cite{Connors2011}.
 However, the prior is ad-hoc and lacks physical information or assumptions, limiting its applicability.
@@
     An alternative approach to solve the problem in the framework of information field theory.
-
 Recently, image deconvolution using physical assumptions and decomposition into point and diffuse flux in 3D/4D has gained attention.
-Pumpe et al.
-\cite{Pumpe2018} and Selig et al.
-\cite{Selig2015} proposed priors based on physical assumptions, which have been shown to work well for large-scale emission.
+\cite{Pumpe2018} and \cite{Selig2015} proposed priors based on physical assumptions, which have been shown to work well for large-scale emission.
 However, the smoothness assumption in these methods can lead to artifacts in the galactic plane.
 
-    The challenge is due to fundamentally contradicting goals: deconvolution favoring point sources will decompose extend structures,
-    while introducing local correlations will lead to
-
-    \begin{itemize}
-         \item  Problem of RL decomposing structures into point sources: \cite{Reeves1994} \cite{Fish1995}
-         \item regularised RL , e.g. total variation \citep{Dey2006} or maximum entropy \citep{Bi1994} \todo{other references?}
-        \item Joint likelihood RL: \cite{Ingaramo2014} has found that RL take the best out of each image and create a "merged" image
-        \item Multi-scale LIRA prior of course: \cite{Esch2004, Connors2011}, advantage of error estimates / Bayesian sampling.
-However prior is rather "ad-hoc", no physical information / assumptions.
-Just "smoothness"
-        \item What abput d3po and d4po?
-Priors based on physical assumptions, decomposition into point and diffuse flux, but in 3d/4d \cite{Selig2015}\cite{Pumpe2018}.
-The smoothness assumption works for large scale emission, but leads to artifacts in the galactic plane...
-    \end{itemize}
+    The challenge is due to fundamentally contradicting goals: deconvolution favoring point sources will decompose extend structures, while introducing local correlations will lead to
+
+    \cite{Zoran2011} build on very similar assumption for natural images.
+    Instead of assuming a fixed local correlation structures, such as smoothness
+    they proposed to learn the local correlation structure on millions of patches
+    extracted from natural images.
+
+    For this they proposed to split training images from representative
+    data sets into small patches of size 8x8~pixels and fit a 64 dimensional
+    Gaussian Mixture Model (GMM) to the distribution of extracted patches. Each pixel of the patch 
+    is thereby treated as an independent dimension in the model. In total
+    they chose to use $k=200$ Gaussian components.
+
+    To use the GMM in reconstruction they introduce the expected patch likelihood (EPLL).
+
+    They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as de-noising, de-blurring and inpainting.
+
+    \cite{Bouman2016} later adapted the patch prior reconstruction to be used
 
@@
 
-    \subsection{Some notes on Deep Learning Methods}
+    \subsection{Some Remarks on Deep Learning Methods}
     In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the \textit{de facto} standard for de-blurring and super-resolution of natural images \todo{reference review?}.
@@
 
-    \todo{this sum corresponds to the loop over data sets in machine learning... }
+    \todo{did you know this sum corresponds to the loop over data sets in machine learning...?}
 
@@
 
-    \subsection{Patch Based Priors}
-    In general it is difficult to capture global image statistics in a prior likelihood
-    taking into account all pixel to pixel correlations. The size of the corresponding
-    correlation matrix would grow with the number of pixels squared and thus quickly
-    becomes computationally untraceable. However astronomical images typically only
-    show local correlations between pixels. This is because the spatial
-    scale of astrophysical processes in an image is always limited by the finite
-    interaction time and the fact that the interaction cannot propagate
-    faster than the speed of light (structure in the CMB is an exception here). This means on smaller scales astronomical
-    images often contain basic structures such as edges, corners, filaments or
-    periodic patterns formed by local astrophysical processes.
-
-    \todo{This is interesting, but move to intro...}
-    \cite{Zoran2011} build on very similar assumption for natural images.
-    Instead of assuming a fixed local correlation structures, such as smoothness
-    they proposed to learn the local correlation structure on millions of patches
-    extracted from natural images.
-
-    For this they proposed to split training images from representative
-    data sets into small patches of size 8x8~pixels and fit a 64 dimensional
-    Gaussian Mixture Model (GMM) to the distribution of extracted patches. Each pixel of the patch 
-    is thereby treated as an independent dimension in the model. In total
-    they chose to use $k=200$ Gaussian components.
-
-    To use the GMM in reconstruction they introduce the expected patch likelihood (EPLL).
-
-    They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as de-noising, de-blurring and inpainting.
-
-    Using half quadratic splitting and the Wiener filter solution, which is not possible
-    in our case. Instead we choose a direct optimization by relying on differentiable
-    programming later.
-
-    In practice we are interested in the likelihood of a given structure in a patch and
-    So we subtract the mean value of a given patch. This represents the assumption that
-    the image structure is independent of the total flux contained in the patch.
-
-    One of the main advantages of the GMM is the possibility to evaluate its likelihood
-    in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
+    \subsection{Patch Based Image Prior}
+    In general it is difficult to capture global image statistics in a prior likelihood taking into account all pixel to pixel correlations.
+The size of the corresponding correlation matrix would grow with the number of pixels squared and thus quickly becomes computationally untraceable.
+However astronomical images typically only show local correlations between pixels.
+This is because the spatial scale of astrophysical processes in an image is always limited by the finite interaction time and the fact that the interaction cannot propagate faster than the speed of light (structure in the CMB might be an exception here).
+This means on smaller scales astronomical images often contain basic structures such as edges, corners, filaments or periodic patterns formed by local astrophysical processes.
+For this reason we adopt the same patch based image prior approach as introduced by \cite{Zoran2011}.
+We use a pre-trained Gaussian Mixture Model (GMM) to evaluate and approximate a patch based prior for the reconstructed image $\mathbf{x}$.
+
+    One convenient property of the GMM is the possibility to evaluate its likelihood in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
 
@@
         \label{eq:gmm}
-        P_{GMM}(\mathbf{x}_n) = \sum_{k=1}^K \pi_k N(\mathbf{x}_n| \boldsymbol{\mu}_k, \boldsymbol{\Sigma}_k^2)
-    \end{equation}
-
-    Where $N$ is a Gaussian distribution, $\boldsymbol{\mu}_k$ the vector of means for
-    a given component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix
-    and $\pi_k$ the weight the component. The different weights are required to sum to unity such that $\sum_{k=1}^N\pi_k = 1$.
+        P_{GMM}(\mathbf{x}_n) = \sum_{k=1}^K \pi_k \mathcal{N}(\mathbf{x}_n| \boldsymbol{\mu}_k, \boldsymbol{\Sigma}_k^2)
+    \end{equation}
+
+    Where $\mathcal{N}$ is a Gaussian distribution, $K$ the total number of components, $\boldsymbol{\mu}_k$ the vector of means for a given component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix
+    and $\pi_k$ the weight of the component. The different weights are required to sum to unity such that $\sum_{k=1}^N\pi_k = 1$.
 
@@
     Where $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch
-    from the image $\mathbf{x}$ to be reconstructed. This way the index $k$ that identifies the GMM component becomes a hyper-parameter in the model and is optimized along with the image $\mathbf{x}$.
+    from the image $\mathbf{x}$ to be reconstructed.
+This way the index $k$ that identifies the GMM component becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
 
@@
 
-    \cite{Bouman2016} later adapted the patch prior reconstruction to be used
     with radio astronomy data.
@@
     simulated images of black hole ring structures.
+
+    Using half quadratic splitting and the Wiener filter solution, which is not possible
+    in our case. Instead we choose a direct optimization by relying on differentiable
+    programming later.
 
@@
     mapping function are shown in Fig.~\ref{fig:image-norms}.
+
+    In practice we are interested in the likelihood of a given structure in a patch and
+    So we subtract the mean value of a given patch. This represents the assumption that
+    the image structure is independent of the total flux contained in the patch.
 
@@
     \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
-    To learn the Gaussian Mixture Models from patches we the standard implementation
+    To learn the Gaussian Mixture Models from patches we use the standard implementation
     provided in the \texttt{Scikit-Learn}~\citep{Skimage2014} package. To handle the 
-    serialisation of images to the FITS data format and to handle world coordinate
+    serialisation of images to the \textit{FITS} data format and to handle world coordinate
     systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
@@
 
-    \vlk{We have devised four distinct arrangements of combinations of point and extended sources of differents shapes to test the algorithms.  The arrangements are 
+    \vlk{We have devised four distinct arrangements of combinations of point and extended sources of different shapes to test the algorithms.  The arrangements are 
     \begin{itemize}
@@
     \label{subsec:methods}
-    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we use the following definitions:
+    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we use the following methods:
 
@@
 Which optimizes "to the end" until there is no relevant change in the posterior log-likelihood.
+In addition we use and upsampling factor of 2.
 
@@
 
-    We ran the comparison on the whole parameter grid, whoever in the following we can only discuss a subset of the results, which we consider the most relevant.
+    We ran the comparison on the whole parameter grid of methods, source scenarios, background levels and instrument scenarios.
+However in the following we only discuss a subset of the results, which we consider the most relevant.
 All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
@@
     First we compare the performance of methods on the different source scenarios.
-    Figure \ref{fig:comparison-scenarios} shows the comparison of the methods for a selected subset of scenarios A1, B3, C3 and D3.
+    Figure \ref{fig:comparison-scenarios} shows the comparison of the methods for a selected subset of scenarios A1, B3, C3 and D4.
 
@@
 The early stopped uniform prior still shows an extension for those cases, because the optimization process has not finished.
-The \jolideco with the Zoran-Weiss patch prior also results in less sharp images, because the prior has been learned on natural images of landscapes, objects, every day scenes etc.
-which do not include point sources.
-The \jolideco with the prior learned from GLEAM data, which also includes point sources, shows much improved results.
-
-    In the lower left of the image the point sources become fainter and closer, challenging all methods in succeeding to separate those as independent sourcea.
+Optimizing for 1000 iterations clearly improves the result and shows almost perfect point sources corresponding to the size of approximately one pixel.
+The \jolideco method with the Zoran-Weiss patch prior results in less sharp images, because the prior has been learned on natural images of landscapes and every day objects and scenes, which do not include point sources.
+The \jolideco method with the prior learned from GLEAM data, which also includes point sources, shows much improved results.
+However not as sharp as the results obtained with the uniform prior.
+
+    In the lower left of the image the point sources become fainter and move closer, challenging all methods in succeeding to separate those as independent sources.
 The uniform prior optimized "to end" shows excellent results, still separating the sources.
 
-    For scenario B3 all method recover the point sources arpund the central extend source. 
+    For scenario B3 all method recover the point sources and the central extend source. 
     However large difference can be observed in the reconstruction of the Gaussian shaped extended sources.
@@
     Scenario C3 challenges the methods to reconstruct a weak extended source under four brighter point sources.
-While again all methods reconstruct the point sources well, the visual differences are large for the weal underlying extended emission.
+While again all methods reconstruct the point sources well, the visual differences are large for the weak underlying extended emission.
+The uniform prior with 1000 iterations
 
@@
     %
+    As a second experiment we explored the dependency of the results on background level and signal strength.
+Figure~\ref{fig:comparison-signal-noise} shows the results for the \jolideco method with the GLEAM prior in the scenario D1-5.
+As expected the reconstruction quality improves with signal strength.
+The method seems to converge to the ground truth for very high signal-to-noise ratio.
+
     \todo{We should give a single number for the S/N, how to compute? Per source, like spiral ring and point sources...}
 
-    \todo{Should we leave the background norm free?}
-    Figure \ref{fig:comparison-signal-noise} shows the comparison for the method "Jolideco GLEAM v0.1" for varying signal to noise ratio for the "D" scenario.
-
     Some observations:
@@
     \begin{itemize}
-        \item as expected the reconstruction quality improves with stronger signal
+        \item 
         \item there seems to be a "jump" in the reconstruction quality of the point sources. The weakest is much more blurry, but all the others look fine.
@@
 
-    \subsection{Combined \xmm and \chandra Observation}
-    As a second application example we combine data from \chandra and \xmm.
-    \url{https://github.com/jolideco/jolideco-chandra-nustar-examples}
-
-    \begin{figure*}
-        \script{example-xmm-chandra.py}
-        \begin{centering}
-            \includegraphics[width=\linewidth]{figures/example-xmm-chandra.pdf}
-            \caption{
-                Chandra Example
-            }
-            \label{fig:example-xmm-chandra}
-        \end{centering}
-    \end{figure*}
+    % \subsection{Combined \xmm and \chandra Observation}
+    % As a second application example we combine data from \chandra and \xmm.
+    % \url{https://github.com/jolideco/jolideco-chandra-nustar-examples}
+
+    % \begin{figure*}
+    %     \script{example-xmm-chandra.py}
+    %     \begin{centering}
+    %         \includegraphics[width=\linewidth]{figures/example-xmm-chandra.pdf}
+    %         \caption{
+    %             Chandra Example
+    %         }
+    %         \label{fig:example-xmm-chandra}
+    %     \end{centering}
+    % \end{figure*}
 

### 2023-05-01 src/scripts/scenarios.py
Add scenario illustration

@@ -1,0 +1,117 @@
+import config
+import numpy as np
+import paths
+from astropy.io import fits
+from astropy.visualization import simple_norm
+from matplotlib import pyplot as plt
+from matplotlib.gridspec import GridSpec
+
+asinh_a = 0.01
+
+scenario_titles = {
+    "Scenario A": {
+        "name": "point1",
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
+    },
+    "Scenario B": {
+        "name": "aster3",
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
+    },
+    "Scenario C": {
+        "name": "disk3",
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
+    },
+    "Scenario D": {
+        "name": "spiral4",
+        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
+    },
+}
+
+
+instrument_titles = {
+    "ground truth": "Ground\n  Truth",
+    "chandra": '"Chandra"',
+    "xmm": '"XMM"',
+}
+
+figsize = config.FigureSizeAA(aspect_ratio=1.32, width_aa="two-column")
+
+upsampling_factor = 2
+DATA_SHAPE = (128, 128)
+
+gridspec_kw = {
+    "left": 0.14,
+    "right": 0.98,
+    "bottom": 0.12,
+    "top": 0.95,
+    "wspace": 0.05,
+    "hspace": 0.02,
+}
+
+fig, axes = plt.subplots(
+    nrows=len(instrument_titles),
+    ncols=len(scenario_titles),
+    figsize=figsize.inch,
+    gridspec_kw=gridspec_kw,
+)
+
+
+def add_cbar(im, ax, fig, label=""):
+    """Add cbar to a given axis and figure"""
+    bbox = ax.get_position()
+    loleft = bbox.corners()[0]
+    rect = [loleft[0], loleft[1] - 0.04, bbox.width, 0.02]
+    cax = fig.add_axes(rect)
+    cbar = fig.colorbar(im, cax=cax, orientation="horizontal")
+    cbar.set_label(label, size=9)
+    cbar.set_ticks([0, 10, 100])
+    cax.tick_params(labelsize=9)
+
+
+def read_flux_ref(instrument, scenario):
+    """Reda reference flux"""
+    path = paths.jolideco_repo_comparison / "data"
+
+    if instrument == "ground truth":
[…]

### 2023-05-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         We present a new method for Joint Likelihood Deconvolution (Jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
-        The method reconstructs a single flux image from a set of observations
-        by optimizing the \aposteriori joint Poisson likelihood of all
-        observations under a patch based image prior. The patch
-        prior is parameterised by a standard Gaussian Mixture model (GMM), which is
-        learned from astronomical images at other wavelengths.
-        During reconstruction the GMM adapted to the structures
-        in the data by finding the the most likely combination of 
-        patches. 
-        By applying the method to simulated data we show that
-        the combination of multiple observations leads to an
-        improved reconstruction quality in the regime with S/N ratio of.
-        We show also that the method yields superior reconstruction quality
-        to alternative standard methods such as the Richardson-Lucy method.
-        We also show that the method can be highly adapted to various 
-        analysis scenarios by learning problem specific GMM priors
-        such as images of extragalactic or Galactic sources.
+The method reconstructs a single flux image from a set of observations by optimizing the \aposteriori joint Poisson likelihood of all observations under a patch based image prior.
+The patch prior is parameterised by a Gaussian Mixture model (GMM) and learned from astronomical images with high signal to noise ratio, such as the James Webb Telescope.
+During the reconstruction process the patch prior adapts  to the structures in the data by finding the most likely GMM component for each patch in the image.
+By applying the method to simulated data we show that both the combination of multiple observations as well as the patch based prior lead to an much improved reconstruction quality in many different source scenarios as well as signal to noise regimes.
+We show also that the method yields superior reconstruction quality to alternative standard methods such as the Richardson-Lucy method.
+We also show that the method can be highly adapted to various analysis scenarios by learning problem specific GMM prior  such as images of extragalactic or Galactic sources.
     \end{abstract}
@@
     \section{Introduction}
-    The angular resolution of any physical or astronomical imaging process is inherently limited by the instrument or telescope used.
+    The resolution of any physical or astronomical imaging process is inherently limited by the instrument or telescope used.
 Furthermore, the quality of the resulting image is affected by background or instrumental measurement noise and non-uniform exposure.
 This is especially true in the low signal-to-noise regime, where images are affected by Poisson noise.
-
-    Such as images taken by \xray and \gammaray~astronomy but also to other fields such as
-
-    To maximise the scientific use of available data it is desirable to correct for the instrumental imprint on the data.
-
-    We assume non-blind deconvolution, so the there is prior information of the point spread function (PSF).
-The PSF can be estimated empirically from observation of known point sources, such as distant activate galactic nuclei or a model of the PSF can obtained from simulation of the instrument.
-
-    This class of problems is called inverse problems.
+This includes images taken by \xray and \gammaray~telescopes but also images obtained with positron emission tomography or single-photon emission computed tomography.
+
+    To maximise the scientific use of available data it is desirable to correct for the instrumental imprint on the data as well as reduce its noise level.
+The process of improving the resolution of an image in post-processing is called de-blurring or de-convolution, as the the data is obtained via a forward convolution through the point spread function (PSF) of the instrument.
+In general this class of problems is called inverse problems.
+If there is prior information available on the shape of the PSF, we typically refer to the process more precisely as un-blind de-convolution.
+In case of astronomical observations the PSF can for example be estimated empirically from observation of known point sources, such as distant activate galactic nuclei or a model of the PSF can obtained from simulation of the telescope or instrument.
 
     \subsection{Related Work}
-    In literature there are many proposed methods to solve the un-blind deconvolution problem for images affected by Poisson noise.
-All methods rely fundamentally on modeling an image generating process as a linear system.
+    In literature there have been many efforts to solve the un-blind deconvolution problem for images affected by Poisson noise.
+Most methods rely fundamentally on modeling the image generating process as a linear process.
 Given a known point spread function a prediction of the discrete measured image can be obtained via \textit{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
-However the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the likelihood function.
+However the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function.
 
@@
 
-    In practice the RL method was found to have multiple, partly related issues: first there is no objective criterion when to stop the iteration.
-Usually the iteration was stopped when the reconstructed image seemed plausible to the eye.
-Second, when the number of iterations was too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\textit{speckles}).
+    However in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion when to stop the optimization process.
+Usually the iteration is stopped when the reconstructed image seems plausible to the eye.
+Second, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\textit{speckles}).
 This problem was e.g.
 described and studied by \cite{Reeves1995} and \cite{Fish1995}.
-Lastly the RL method does not provided an associated estimate of the uncertainties of the reconstruction, which is desirable especailly in the Poisson domain to asses the significance of specific features found in the reconstruction.
+Lastly the RL method does not provided an associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain to measure the significance of specific features found in the reconstructed image.
 
@@
     reconstruction results as well as corresponding diagnostic information
-    such as the trace of the posterior and prior and likelihood values.
+    such as the trace of the posterior and prior likelihood values.
     The package is available at \url{https://github.com/jolideco/jolideco}
@@
     As baseline reference GMM we use the original model provided by \cite{Zoran2011}.
-The model was learned from the Berkley image database, which contains natural images.
+The model was learned from the Berkley image database \todo{reference}, which contains natural images and image and every day scenes and objects.
 The model was learned by splitting the images into 8x8 patches and provided by the authors as part of the source code for download\footnote{\url{https://people.csail.mit.edu/danielzoran/epllcode.zip}}.
@@
     \label{sssec:gleam-radio-data}
-
-    A prior learned from astronomical data for analysis of Galactic sources with 
-    rich morphology, such as supernova remnants, pulsar winds etc., but also include point sources. A good "all purpose" prior.
-    High signal to noise Radio data from \cite{HurleyWalker2022}.
-    There is physical correlation between e.g. the very high energy gamma range
-    and radio as emission is produced from the same electron populations.
-    We downloaded the GLEAM data using the Gleam VO Client\footnote{\url{https://github.com/ICRAR/gleamvo-client}}. We restricted the choice
-    of data to the Galactic Plane between $b=\pm10\deg$ and $\ell = \pm180\deg$.
-    In total we extracted \todo{insert number} patches and trained a GMM with 128
-    components.
+    As an alternative we consider a prior learned from astronomical radio data.
+For this we relied on high signal to noise radio data from the \textit{GLEAM} survey \cite{HurleyWalker2022}.
+We downloaded the data using the Gleam VO Client\footnote{\url{https://github.com/ICRAR/gleamvo-client}}.
+We restricted the choice of data to the Galactic Plane between $b=\pm10\deg$ and $\ell = \pm180\deg$ to avoid a bias towards extra-galactic point sources and represent structures of Galactic sources with rich morphology, such as supernova remnants, pulsar winds etc.
+The data set still includes Galactic as well as extra-galactic point sources in the background.
+There is also physical correlation between e.g.
+the very high energy \gammaray and radio range as their emission is produced by the same electron populations.
+
+    In total we extracted \todo{insert number} patches and trained a GMM with 128 components. We used "data augmentation" by introducing a random shift of the sub-pixel position.
+
+    \subsubsection{JWST Cas A Image}
+    As a last GM prior we use the promotional image of JWST realeased by...
+    The image is particularly suited becasue of the excellent angular resolution, extrating many patches for the same object
+    as well as the high signal to noise ratio.
 
@@
 The optimization algorithm used is ADAM, a stochastic gradient descent method, without decay.
-Finally, there is an optional step of learning rate scheduling, although so far, a fixed step size value of $1e-3$ has been used.
+Finally, there is an optional step of learning rate scheduling, although so far, a fixed step size value of $\mathrm{lr}=10^{-3}$ has been used.
 
@@
     \begin{figure*}
-        \centering\includegraphics{figures/chandra_gauss_fwhm4710_128x128_aster1+point1+disk1+spiral3.pdf}
+        \centering\includegraphics{figures/scenarios.pdf}
         \caption{Illustrating the source patterns used to make test datasets.
@@
 The dashed red and magenta boxes depict $32{\times}32$ and $64{\times}64$ regions of interest.
-Note that the boxes are displaced to the lower left corner in Case B, and leftwards in Case D.}
+Note that the boxes are displaced to the lower left corner in Case B, and leftwards in Case D.
+        convolved with a diffuse PSF (Gaussian with $\sigma=6$~pix), \todo{add back boxes if we have time}.
+        }
         \label{fig:simulated_models_chandra}
-    \end{figure*}
-
-    \begin{figure*}
-        \centering\includegraphics{figures/xmm_gauss_fwhm14130_128x128_aster1+point1+disk1+spiral3.pdf}
-        \caption{As in Figure~\ref{fig:simulated_models_chandra}, convolved with a diffuse PSF (Gaussian with $\sigma=6$~pix).}
-        \label{fig:simulated_models_xmm}
     \end{figure*}
@@
 However not as sharp as the results obtained with the uniform prior.
-
 In the lower left of the image the point sources become fainter and move closer, challenging all methods in succeeding to separate those as independent sources.
@@
 
+    Es expected once the signal strength becomes very large there is no dependency of the result on the background level anymore (scenario D5)
+
     \todo{We should give a single number for the S/N, how to compute? Per source, like spiral ring and point sources...}
@@
     \subsection{Deep \chandra Observation}
-    As a first application example we choose a set of short exposure observations of the SNR \textit{E0102} by the \chandra telescope.
-\chandra is a space-based X-ray observatory that has been operational since 1999.
-It comprises nested cylindrical paraboloid and hyperboloid surfaces that create an imaging optical system for X-rays.
-In the focal plane, it has multiple instruments designed for various scientific purposes, such as the high-resolution camera (HRC) and the Advanced CCD Imaging Spectrometer (ACIS).
-Chandra has a typical angular resolution of 0.5 arcseconds and covers the energy range from \qty[mode = text]{0.1}{keV} to  \qty[mode = text]{10}{keV}.
-
-    In total we choose 25 observations with the ACIS instrument and no grating.
-For \chandra the instrument response varies with the observation offset \todo{reference}.
-With \jolideco we can handle the correct PSF for each observation.
-We assume a spatially constant background and exposure, however the exposure is scaled to a reference observation.
-The data reduction was done using ciao v4.15 and the custom \textit{snakemake} workflow.
-PSFs were simulated for each observation independently using \textit{marx} \todo{reference} and the \textit{simulate\_psf} script.
-List of observation IDs can be found online.
-Energy range was selected from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a bins sice of 0.5 "native" bins, corresponding to a bin size of \qty[mode = text]{0.001}{}.
-For the spectrum we fitted a model a circular region \todo{which one?} and used it for the PSF simulation.
-
-    For \jolideco we used the GMM prior learned on Chandra SNRs and an oversampling factor of 2.
-For each observation we allow the background level and position calibration to vary.
-Figure~\ref{fig:example-chandra} shows the final result.
-\jolideco clearly improve the angular resolution.
-
-    To check the quality of the model we compute a map of approximate residual significance defined by:
-
-    \begin{equation}
-        \label{eq:approx-sigma}
-        \sigma \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
-    \end{equation}
-
-    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
-    \todo{To account for the Poisson statistics it would be more precise to compute a "TS" map, but for an approximate estimation it should  be fine...I have a derivation for this formula }
-
-    \url{https://github.com/jolideco/jolideco-chandra-examples}
 
@@
             \caption{
-                Chandra Example
+               The \jolideco method applied to \chandra data of the SNR E0102.
+The left large image shows the summed counts from 25 observations.
+The right large image  shows the result from the \jolideco de-convolution process.
+The flux is given as counts relative to the reference observation with ID=1308.
+               The panels \textit{Zoom A} and \textit{Zoom B} show a zoomed-in version of two example regions in the SNR, marked with the white rectangles in the large images.
             }
@@
     \end{figure*}
+
+    As a first application example for real data we choose a set of 25 short exposure observations of the SNR \textit{E0102} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
+In total we chose 25 observations (same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}) taken with with the ACIS instrument and no grating.
+For \chandra the instrument response varies with the observation offset and energy \todo{reference}.
+With \jolideco we can handle  PSF for each observation.
+We assume a spatially constant background of \qty[mode = text]{1e-5}{ct/pixels}.
+    We also assumed the exposure to be spatially constant.
+Its absolute value for each observation we expressed as the ratio of observation time with respect to the reference observation.
+As reference we chose the observation id 1308.
+    We reduced the data \textit{ciao} v4.15 and a custom \textit{snakemake} workflow (see Section~\ref{sec:reproducibility}).
+The PSF were simulated for each observation independently using \textit{marx} \todo{reference} and the \textit{simulate\_psf} script.
+The complete list of observation IDs can be found online.
+We selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a bins size of 0.25 "native" bins, corresponding to a bin size of \qty[mode = text]{0.001}{$\deg$/pixel} \todo{How large is the Chandra PSF compared to this?}.
+As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
+We converted the spectral from XSPEC to sherpa script using the helper script \textit{convert\_xspec\_script}.
+
+    For \jolideco we used the GMM prior learned on the JWST image Cas-A and an oversampling factor of 2.
+For each observation we allow the background level and position calibration to vary.
+Figure~\ref{fig:example-chandra} shows the final result.
+\jolideco improves both the angular resolution as well as signal to noise ratio of the counts image.
+
+    \textit{Zoom A} shows an example for a filamentous structure in more detail.
+\jolideco maintains the extended structure along the filament, while sharpening in the perpendicular direction.
+Looking at the upper right one can also see that weak background emission is suppressed, also improving the contrast of the image.
+\textit{Zoom B} shows a another circular filamentous structure of the SNR.
+In the counts data the structure is barely visible, while the image reconstructed by \jolideco shows a circular structure with a bright emission spot.
+
+    \todo{Showing residuals does not really make sense here the SNR seems to extend with time...this is clearly visible in the residuals..or ist the the exposure time calibration that changes?
+One could run on the Zoom A individually and the per obs shift might account for the motion with time...}
+
+    \url{https://github.com/jolideco/jolideco-chandra-examples}
 
@@
     \subsection{\fermi Event Types}
-    As a last application example we apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
-    The LAT is a pair conversion gamma-ray telescope on board of the Fermi satellite.
-It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
-For the example we chose again a Galactic source with complex morphology: the supernova remnant \textit{Vela Junior}.
-We use 14 years (from 2008 August 4 to 2023 August 4) of \texttt{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
-To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}, as
-    defined by the \fermi collaboration.
-We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
-For the first part of the data reduction we use the standard \textit{fermitools} \todo{add version and reference}.
-
-    As the \textit{fermitools} output an energy dependent counts, exposure and PSF cube, we use the \textit{Gammapy} package to further reduce the data.
-In a first step we compute an image of the expected background emission.
-For this we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and nearby sources from the 3FHL catalog \cite{Ajello2017}.
-We fit the model components to the data, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on \textit{Vela Junior}.
-Finally we reduce this model to an image by summing over the energy dimension.
-
-    Assuming a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for \textit{Vela Junior} we also compute an effective PSF and exposure image by integrating over the energy dimension of the cube and weighting with the spectral model.
-
-    We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
-Because of the limited statistics we did not use any oversampling but kept the pixel size of the counts image.
-
-    Figure~\ref{fig:example-fermi-lat} shows the data, result and residuals. The \fermi data is sparse, with very limited statistics.
-    \jolideco clearly improves the noise level as well as angular resolution.
-It reveals morphological details consistent with the HESS measurement \todo{Add HESS image or erosita for comparison?
-But this is not an analysis...}
-    The calibration of the predicted counts finds different background model norms and positional shifts in order of \todo{add value} for the different event classes.
-This way it corrects for systematic errors in the reconstruction of the position.
-As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit \textit{Gaussian} distribution.
-
-    \url{https://github.com/jolideco/jolideco-fermi-examples}
-
       \begin{figure*}
@@
     \end{figure*}
+    As a second example we apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
+    The LAT is a pair conversion \gammaray telescope on board of the Fermi satellite.
+It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
+For this example we chose again a Galactic source with complex morphology: the supernova remnant \textit{Vela Junior}.
+We use 14 years (from 2008 August 4 to 2023 August 4) of \texttt{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
+To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}, as defined by the \fermi collaboration.
+We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
+For the first part of the data reduction we use the standard \textit{fermitools} \todo{add version and reference}.
+
+    The \textit{fermitools} output an energy dependent counts, exposure and PSF cube.
+To further reduce the data to images we use the \textit{Gammapy} package.
+To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \cite{Ajello2017}.
+We first fit the model components to the data, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on \textit{Vela Junior}.
+Finally we reduce this model to an image by summing over the energy dimension.
+    To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for \textit{Vela Junior} and integrate over the energy dimension of the cube while weighting with the spectral model.
+
+    We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
+Because of the limited statistics we did not use any oversampling but keep the pixel size of the counts image.
+Figure~\ref{fig:example-fermi-lat} shows the data, result and residuals.
+The \fermi data is sparse, with very limited statistics.
+\jolideco clearly improves the noise level as well as angular resolution of the data.
+It reveals morphological details consistent with the HESS measurement \todo{Add HESS image or EROSITA for comparison?
+But this is not an analysis...}
+    The calibration of the predicted counts finds different background model norms and positional shifts in order of \todo{add value} for the different event classes.
+This way it corrects for systematic errors in the reconstruction of the position.
+
+     To check the quality of the model we compute a map of approximate residual significance defined by:
+
+    \begin{equation}
+        \label{eq:approx-sigma}
+        \sigma \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
+    \end{equation}
+
+    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
+    \todo{To account for the Poisson statistics it would be more precise to compute a "TS" map, but for an approximate estimation it should  be fine...I have a derivation for this formula }
+
+    As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit \textit{Gaussian} distribution.
+
+    More details of the example \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
 
     \section{Paper Reproducibility}
-    In order to facilitate reproducibility we make source code for the paper and figures  available at \url{https://github.com/jolideco/jolideco-paper}.
-    The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021}. See instructions 
+    In order to facilitate reproducibility of our results we provide the source code for the paper and figures at \url{https://github.com/jolideco/jolideco-paper}.
+The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021}, following the instructions in the \texttt{README.md} file in the same repository.
 All data is available on Zenodo \todo{how do we do this exactly...?}
 
-    For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
-
-    For the Chandra data reduction we used a custom \texttt{Snakemake} workflow \footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
+    For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow 
+    available at \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
+
+    For the Chandra data reduction we used a custom \texttt{Snakemake} workflow available at \footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
 

### 2023-05-01 src/scripts/example-chandra.py
[showyourwork] overleaf sync

@@ -118,7 +118,7 @@ add_cbar(ax_counts.images[0], ax_counts, fig, label="Counts")
 
 flux_data = fits.getdata(filename_jolideco, hdu="VELA-JUNIOR")
 flux = Map.from_geom(npred.geom.upsample(2), data=flux_data)
-flux.plot(ax=ax_flux, cmap="viridis", interpolation="gaussian", vmax=3.5)
+flux.plot(ax=ax_flux, cmap="viridis", interpolation="gaussian")
 add_cbar(ax_flux.images[0], ax_flux, fig, label="Flux / A.U.")
 
 norm_factor = np.pi * SMOOTH_WIDTH**2

### 2023-05-04 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{showyourwork}
+\usepackage[autostyle]{csquotes}
 \usepackage{amssymb}
@@
 During the reconstruction process the patch prior adapts  to the structures in the data by finding the most likely GMM component for each patch in the image.
-By applying the method to simulated data we show that both the combination of multiple observations as well as the patch based prior lead to an much improved reconstruction quality in many different source scenarios as well as signal to noise regimes.
+By applying the method to simulated data we show that both the combination of multiple observations as well as the patch based prior lead to a much improved reconstruction quality in many different source scenarios as well as signal to noise regimes.
 We show also that the method yields superior reconstruction quality to alternative standard methods such as the Richardson-Lucy method.
-We also show that the method can be highly adapted to various analysis scenarios by learning problem specific GMM prior  such as images of extragalactic or Galactic sources.
+We also show that the method can be highly adapted to various real analysis scenarios by learning problem specific GMM prior  such as images of extragalactic or Galactic sources.
     \end{abstract}
@@
 This is especially true in the low signal-to-noise regime, where images are affected by Poisson noise.
-This includes images taken by \xray and \gammaray~telescopes but also images obtained with positron emission tomography or single-photon emission computed tomography.
+This includes images taken by \xray and \gammaray~telescopes but also medical images obtained with methods such as positron emission tomography or single-photon emission computed tomography.
 
     To maximise the scientific use of available data it is desirable to correct for the instrumental imprint on the data as well as reduce its noise level.
-The process of improving the resolution of an image in post-processing is called de-blurring or de-convolution, as the the data is obtained via a forward convolution through the point spread function (PSF) of the instrument.
-In general this class of problems is called inverse problems.
-If there is prior information available on the shape of the PSF, we typically refer to the process more precisely as un-blind de-convolution.
+The process of improving the resolution of an image in post-processing is often called deblurring or deconvolution, as it aims to invert the effect of the data being degraded by a forward convolution through the point spread function (PSF) of the instrument.
+In general this class of problems is categorised as \textit{inverse problems}.
+If there is prior information available on the shape of the PSF, we typically refer to the process more precisely as unblind deconvolution.
 In case of astronomical observations the PSF can for example be estimated empirically from observation of known point sources, such as distant activate galactic nuclei or a model of the PSF can obtained from simulation of the telescope or instrument.
 
+    \newpage
     \subsection{Related Work}
-    In literature there have been many efforts to solve the un-blind deconvolution problem for images affected by Poisson noise.
+    In literature there have been many efforts to solve the unblind deconvolution problem for images affected by Poisson noise.
 Most methods rely fundamentally on modeling the image generating process as a linear process.
@@
 
-    The standard baseline method for image de-convolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \textit{RL}).
+    The standard baseline method for image deconvolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \textit{RL}).
 The method involves estimating the original image by iteratively convolving the observed image with the PSF and dividing by the result of convolving the estimated image with the transposed PSF.
@@
 
-    They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as de-noising, de-blurring and inpainting.
+    They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
 
@@
     \subsection{Some Remarks on Deep Learning Methods}
-    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the \textit{de facto} standard for de-blurring and super-resolution of natural images \todo{reference review?}.
+    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the \textit{de facto} standard for deblurring and super-resolution of natural images \todo{reference review?}.
 However their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
@@
 
-    Some of the challenges of de-blurring with CNN are due to the convolutional nature of the networks.
+    Some of the challenges of deblurring with CNN are due to the convolutional nature of the networks.
 In a single layer, linear approximation, the network would need to learn the inverse filter of the PSF, corresponding to the well known \textit{Wiener filter} solution of the problem.
 This requires large convolution kernels or deep network architectures.
-\cite{Li2014} have introduced a baseline architecture for a deep CNN for image de-blurring by introducing large kernels under the separability assumption.
+\cite{Li2014} have introduced a baseline architecture for a deep CNN for image deblurring by introducing large kernels under the separability assumption.
 
@@
     Or even an arbitrary combination of the possibilities listed above.
+It could also be the combination of observations in different energy ranges, however in this case the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for the astronomical data we are dealing with.
 
@@
 This means on smaller scales astronomical images often contain basic structures such as edges, corners, filaments or periodic patterns formed by local astrophysical processes.
-For this reason we adopt the same patch based image prior approach as introduced by \cite{Zoran2011}.
+For this reason we adopt the idea of a patch based image prior approach as introduced by \cite{Zoran2011}.
 We use a pre-trained Gaussian Mixture Model (GMM) to evaluate and approximate a patch based prior for the reconstructed image $\mathbf{x}$.
@@
     from the image $\mathbf{x}$ to be reconstructed.
-This way the index $k$ that identifies the GMM component becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
+This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
 
@@
 
-    \subsubsection{Image Normalisation and Dynamic Range}
+    \subsubsection{Patch Normalisation and Dynamic Range}
     Astronomical images typically show a much higher dynamic range compared to 
@@
     or binary objects and stars at Galactic distances.
+In addition the visible matter in the universe is sparse such that astronomical images typically show sparse bright emission on a dark background.
+
+    \cite{Zoran2011} used a patch normalisation where the mean of the patch is subtracted.
+This means the same morphological features are present in the GMM at various levels of contrast.
+While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, only at the cost of introducing a lot more components to the GMM, which is unfeasible in practice due to limited availability of training data and computational resources.
 
     The high dynamic range of astronomical images challenges any deconvolution method.
-    To recover point sources accurately it is required to keep correlations with
-    neighbouring pixels low, while for extended source the opposite is true. Ideally
-    those contradicting requirements can be handled with a single flexible prior assumption,
-    which adapts to the data, such as the patch based GMM prior introduced in the previous
-    section.
+To recover point sources accurately it is required to keep correlations with neighbouring pixels low, while for extended source the opposite is true.
+Ideally those contradicting requirements can be handled with a single flexible prior assumption, which adapts to the data, such as the patch based GMM prior introduced in the previous section.
 
@@
 
-    \begin{figure}
-        \script{image-norms.py}
-        \begin{centering}
-            \includegraphics[width=\linewidth]{figures/image-norms.pdf}
-            \caption{
-                Various image norms with different dynamic behaviour.
-            }
-            \label{fig:image-norms}
-        \end{centering}
-    \end{figure}
+    % \begin{figure}
+    %     \script{image-norms.py}
+    %     \begin{centering}
+    %         \includegraphics[width=\linewidth]{figures/image-norms.pdf}
+    %         \caption{
+    %             Various image norms with different dynamic behaviour.
+    %         }
+    %         \label{fig:image-norms}
+    %     \end{centering}
+    % \end{figure}
 
@@
 
-    \subsection{Cross Validation}
-    Cross validation (CV) is an established method for model selection in statistics
-    and machine learning to prevent over-fitting the data. To perform CV the available
-    data is slit into a "training" and "validation" dataset. While optimizing the
-    log-likelihood value is monitored
-
-    The use of multiple dataset allows to use cross-validation to prevent overfitting.
+    \subsection{Choice and Tuning of Hyperparameters}
+    \subsubsection{Cross Validation}
+    Cross validation (CV) is an established method for model selection in statisticd and machine learning to prevent a model from overfitting to the training data.
+To perform CV the available data is slit into a "training" and "validation" dataset.
+While optimizing the log-likelihood value is monitored  The use of multiple dataset allows to use cross-validation to prevent overfitting.
 One of the standard techniques in "machine learning"...
@@
     CV as stopping rule for RL was proposed by \cite{Reeves1995}...
+
+    \subsubsection{Other Approaches}
+
+    Self supervised Poisson loss? J-invariance has been shown to work, Grid Search? Calibration on similar data with ground truth?
 
@@
 
-    \subsubsection{Statistical Errors}
+    \subsection{Statistical Errors}
     \begin{itemize}
@@
     \subsection{Jolideco Framework}
-    The goal of the reconstruction process is to optimize the a-posteriori
-    likelihood defined by Equation~\ref{eq:total}. Given that each pixel
-    in the reconstructed image represents an independent parameter
-    this represents a high dimensional optimization problem.
-    Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019}
-    allow for solving these kind of high dimensional modeling problems, by using
-    back-propagation and adapted optimization methods for high dimensional
-    models such as stochastic gradient decent.
-
-    We implemented the \jolideco method as an independent Python package, 
-    based on \texttt{PyTorch} as optimization back-end. We tried to define a modular,
-    object oriented code structure, to allow parts of the algorithm to be
-    flexible and interchangeable, such as choice of image normalisation scales,
-    the choice of GMM models, optimization methods and serialisation formats for the 
-    reconstruction results as well as corresponding diagnostic information
-    such as the trace of the posterior and prior likelihood values.
+    The goal of the reconstruction process is to optimize the a-posteriori likelihood defined by Equation~\ref{eq:total}.
+Given that each pixel in the reconstructed image represents an independent parameter this represents a high dimensional optimization problem.
+Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019} allow for solving these kind of high dimensional modeling problems, by using back-propagation and adapted optimization methods for high dimensional models such as stochastic gradient decent.
+
+    We implemented the \jolideco method as an independent Python package, based on \texttt{PyTorch} as optimization back-end.
+We tried to define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of image normalisation scales, the choice of GMM models, optimization methods and serialisation formats for the reconstruction results as well as corresponding diagnostic information such as the trace of the posterior and prior likelihood values.
 The package is available at \url{https://github.com/jolideco/jolideco}
 
-    We also use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and
-    \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
-    To learn the Gaussian Mixture Models from patches we use the standard implementation
-    provided in the \texttt{Scikit-Learn}~\citep{Skimage2014} package. To handle the 
-    serialisation of images to the \textit{FITS} data format and to handle world coordinate
-    systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
+    We also use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
+To learn the Gaussian Mixture Models from patches we use the standard implementation provided in the \texttt{Scikit-Learn}~\citep{Skimage2014} package.
+To handle the serialisation of images to the \textit{FITS} data format and to handle world coordinate systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
 For optimization and internal data handling we use \texttt{PyTorch}.
@@
     \subsubsection{Zoran \& Weiss}
-    As baseline reference GMM we use the original model provided by \cite{Zoran2011}.
-The model was learned from the Berkley image database \todo{reference}, which contains natural images and image and every day scenes and objects.
-The model was learned by splitting the images into 8x8 patches and provided by the authors as part of the source code for download\footnote{\url{https://people.csail.mit.edu/danielzoran/epllcode.zip}}.
+    As baseline reference we use the original GMM provided by \cite{Zoran2011}.
+The model was learned from the Berkeley image database \citep{Martin2001} which contains natural images and images of every day scenes and objects.
+The model was learned by splitting the training images into patches of size 8x8 pixels.
+This resulted in a training set of $2 \cdot 10^{6}$ patches, which were used to fit a GMM with 200 components.
+The model is provided by the authors as part of the source code for download\footnote{\url{https://people.csail.mit.edu/danielzoran/epllcode.zip}}.
 More details of how the model was learned are given in the original publication.
@@
 
-    \subsubsection{JWST Cas A Image}
+    \subsubsection{JWST Cassiopeia A}
+    The James Webb Space Telescope is the it delivers data a very high resolution and excellent signal to noise ratio. We extracted 2 million patches out of the image...
+    Would be 
+    Of \textit{Cassiopeia A}
     As a last GM prior we use the promotional image of JWST realeased by...
@@
 
-    \subsubsection{NRAO Jets, Jets, Jets}
-    \todo{Include the jet prior or not?}
-    For the specific application of jet detection and analysis in extract galactic data we learned a GMM patch prior from radio jet images.
+    Taken from \url{https://webbtelescope.org/contents/media/images/2023/121/01GWQBBY77MHGFV3M3N63KDCEJ}
+
+    % \subsubsection{NRAO Jets, Jets, Jets}
+    % \todo{Include the jet prior or not?}
+    % For the specific application of jet detection and analysis in extract galactic data we learned a GMM patch prior from radio jet images.
 It represents the prior knowledge of both the morphology and preferred direction of the jet.
 As reference data we chose
-    a PR image released under the name \textit{Jets, jets jets}  by the NRAO collaboration containing ~150 example jets from their data\footnote{\url{https://public.nrao.edu/gallery/quicklook-samples/}}.
-
-    We first split the compiled image into 150 individual examples.
+    % a PR image released under the name \textit{Jets, jets jets}  by the NRAO collaboration containing ~150 example jets from their data\footnote{\url{https://public.nrao.edu/gallery/quicklook-samples/}}.
+
+    % We first split the compiled image into 150 individual examples.
 For each image we ran a blob detection algorithm and line fit to find the preferred direction of the jet.
@@
 
-    Alternatively we used a \textit{data augmentation} approach to learn a GMM prior with a randomized direction of the jet. For this we rotated the jet image after alignment by 
-    a random angle. Then again we split each image into patches of size 8x8 pixels. In total we created \todo{insert number} patches and learned a GMM with 64 components. The prior
-    is adapted to the analysis scenario of jet detection, where no prior knowledge on the
-    direction is available.
+    % Alternatively we used a \textit{data augmentation} approach to learn a GMM prior with a randomized direction of the jet. For this we rotated the jet image after alignment by 
+    % a random angle. Then again we split each image into patches of size 8x8 pixels. In total we created \todo{insert number} patches and learned a GMM with 64 components. The prior
+    % is adapted to the analysis scenario of jet detection, where no prior knowledge on the
+    % direction is available.
 
@@
     \subsection{Computational Performance}
-    We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations
-    as well as large images.
+    We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations as well as large images.
 
@@
 
+    To evaluate the reconstruction performance of \jolideco and compare it against other methods we defined a set of test source scenarios.
+They consist of simplified elementary morphological structures resembling those found in astronomical images.
+We have devised four distinct arrangements of combinations of point and extended sources of different shapes.
+The scenarios are:
+
+    \begin{itemize}
+        \item[(A)] {\enquote{\bf Points}:} point sources arranged in a grid with different separations and brightness. 
+        \item[(B)] {\enquote{\bf Asterism}:} a set of four point sources arranged around an extended Gaussian source
+        \item[(C)] {\enquote{\bf Shield}:} disk shaped flat extended source with superposed point sources and linear jet-like features 4 different directions.
+        \item[(D)] \enquote{{\bf Spiral}:} extended thin double-spiral with a flat disk at the center and point sources adjacent to it. 
+    \end{itemize}
+
+    In addition we consider two different instrument scenarios:
+
+    \begin{itemize}
+        \item {\enquote{\bf Chandra}:} an instrument with good angular resolution, but low effective area.
+We assume a Gaussian PSF of sizes $\sigma = 2$ pixels and a reference effective area of \qty[mode=text]{1}{A.U.}.
+        \item {\enquote{\bf XMM}:} an instrument with worse angular resolution, but higher effective area.
+We assume a Gaussian PSF of sizes $\sigma = 6$ pixels and an effective area of \qty[mode=text]{5}{A.U.}.
+    \end{itemize}
+
+    The ground truth and corresponding expected counts for the combination of scenarios are shown in Figure~\ref{fig:scenarios}, and the details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios}.
+
+    \begin{figure*}
+        \label{fig:scenarios}
+        \centering\includegraphics{figures/scenarios.pdf}
+        \caption{Illustration of the expected counts for the different source and instrument scenarios we used to make test datasets.
+The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}).
+For the instrument scenario \chandra we convolved the with a narrow Gausssian shaped PSF of width $\sigma=2$~pix.
+For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix and a five times increased effective are.
+        All images are of size $128{\times}128$.
+The dashed red and magenta boxes depict $32{\times}32$ and $64{\times}64$ regions of interest.
+Note that the boxes are displaced to the lower left corner in Case B, and leftwards in Case D.
+        convolved with a diffuse PSF (Gaussian with $\sigma=6$~pix), \todo{add back boxes if we have time}.
+        }
+        \label{fig:simulated_models_chandra}
+    \end{figure*}
+
+    Constant background levels of $\lambda_{Bkg}= 0.001, 0.01 \textrm{and} 0.1 \textrm{counts/pixel}$.
+
     \begin{table*}[t]
+    \label{tab:scenarios}
       \centering
@@
 
-    \todo{Vinay writes this?}
-    \vlk{yes}
-
-    \vlk{We have devised four distinct arrangements of combinations of point and extended sources of different shapes to test the algorithms.  The arrangements are 
-    \begin{itemize}
-        \item[(A)] {\bf asterism:} A set of four point sources arranged around an extended Gaussian source
-        \item[(B)] {\bf points:} Point sources arranged with different separations
-        \item[(C)] {\bf shield:} Disk shaped flat extended source with superposed point sources and linear jet-like features
-        \item[(D)] {\bf spiral:} Extended thin double-spiral with a flat disk at the center and point sources adjacent to it
-    \end{itemize}
-    The arrangements are shown in Figure~TBD, and the details of the locations and brightness of each component is listed in Table~TBD.}
-
-    \begin{figure*}
-        \centering\includegraphics{figures/scenarios.pdf}
-        \caption{Illustrating the source patterns used to make test datasets.
-The patterns shown are for the {\sl (A)} {\tt asterism}, {\sl (B)} {\tt points}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}), convolved with a sharp PSF (Gaussian with $\sigma=2$~pix).
-All images are of size $128{\times}128$.
-The dashed red and magenta boxes depict $32{\times}32$ and $64{\times}64$ regions of interest.
-Note that the boxes are displaced to the lower left corner in Case B, and leftwards in Case D.
-        convolved with a diffuse PSF (Gaussian with $\sigma=6$~pix), \todo{add back boxes if we have time}.
-        }
-        \label{fig:simulated_models_chandra}
-    \end{figure*}
-
-    We use the test datasets provided by Vinay et al.
-    First we evaluate the performance of the method on a set of simulated observations.
-    For this we assume:
-
-    \begin{itemize}
-        \item An instrument with good angular resolution, but low effective area (e.g. like Chandra)
-        \item An instrument with worse angular resolution, but higher effective area (e.g. like XMM)
-    \end{itemize}
-
-    For both scenarios we assume a Gaussian PSF of sizes $\sigma = 2$ pixels and  $\sigma = 5$.
-    As true flux we consider the following scenarios:
-
-    \begin{itemize}
-        \item Point source with varying distances and brightness
-        \item Disk and point sources of varying brightness
-        \item Spiral and point sources of varying brightness
-    \end{itemize}
-
-    Background levels of $\lambda_{Bkg}= 0.001, 0.01 \textrm{and} 0.1 \textrm{counts/pixel}$.
-
-    Show results of experiments on simulated toy datasets
-
     \subsection{Methods}
@@
 It also uses the standardised patch normalisation as described by Equation~\ref{eq:patch-norm}.
-We use cycle spinning, a stride of 4 pixels and 1000 iterations.
+We use cycle spinning, a stride of 4 pixels and 2000 \textit{training epochs}.
+Given 5 observations this results in 10.000 iterations.
 Which optimizes "to the end" until there is no relevant change in the posterior log-likelihood.
@@
 However in the following we only discuss a subset of the results, which we consider the most relevant.
-All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
+The complete set of results is available at \url{https://jolideco.github.io/jolideco-comparison}.
 
@@
             \caption{
-                Comparison of different deconvolution methods for different selected scenarios, as described in Section~\ref{subsec:test-datasets}.
-The simulation of the data used a fixed background level of, a constant exposure and a Gaussian PSF of \todo{x pixels}, corresponding to the "Chandra" scenario.
-The left column shows the simulated counts data and the second most column from the left the underlying ground truth to compare.
-The other column show the reconstructed flux by the different methods and prior assumptions.
+                Comparison of different deconvolution methods and prior assumptions for different selected source scenarios, as described in Section~\ref{subsec:test-datasets}.
+The simulation of the data for this figure used a fixed background level of $\lambda_{Bkg} = \qty[mode = math]{0.01}{cts/pix}$, a uniform exposure and a Gaussian PSF of width $\sigma_{PSF} = \qty[mode = math]{2}{pix}$, corresponding to the \enquote{Chandra} instrument scenario.
+The leftmost column shows the simulated counts data and the second most column from the left the underlying ground truth to compare.
+The other columns show the reconstructed flux by the different methods and prior assumptions for \jolideco.
+To enhance weak structures the images use an $\arcsinh$ stretching with a scale parameter of $a=0.02$.
+The stretching is the same for all images.
 The methods are described in detail in Section~\ref{subsec:methods}.
@@
     %
-    First we compare the performance of methods on the different source scenarios.
-    Figure \ref{fig:comparison-scenarios} shows the comparison of the methods for a selected subset of scenarios A1, B3, C3 and D4.
+    First we compare the performance of methods and prior assumptions on the different source scenarios.
+Figure \ref{fig:comparison-scenarios} shows the results for the selected subset of scenarios A1, B3, C3 and D4.
 
@@
 The \jolideco method with the patch priors shows the best results both visually as well as measured by the SSI.
-The GLEAM v0.1 patch prior reconstructs the
-    sources almost perfectly, visually indistinguishable from the ground truth.
+The GLEAM v0.1 patch prior reconstructs the sources almost perfectly, visually almost indistinguishable from the ground truth.
 The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a visible extension in the surrounding point sources.
@@
 While again all methods reconstruct the point sources well, the visual differences are large for the weak underlying extended emission.
-The uniform prior with 1000 iterations
+The uniform prior with 1000 iterations decomposes the source into a grid of almost equidistant point sources resembling only the outer boundary of the original source.
+\textit{Pylira} shows a similar tendency but already improves the reconstruction of the extended source by leaving more emission in between the bright emission spots.
+The best results are achieved by the patch priors, which reconstruct a plausible extended source with approximately uniform brightness.
+
+    On the jet like features the patch prior does not show a preferred direction or bias in reconstruction and preserves the linear correlation between the pixels.
 
@@
     it converges to the reference solution for very high signal to noise.
-
-    \par{\textbf{Pylira}}
-    Pylira shows 
-    \begin{itemize}
-        \item Shows good results for point sources
-        \item Slightly improved results on extended source, but still "speckly"
-        \item Pixels loose spatial correlation over larger scales..
-    \end{itemize}
-
-    \par{\textbf{Jolideco, Uniform Prior n=1000:}}
-    The uniform priors show the expected behaviour: decompose into point sources, when "optimized to the end".
-
-    \begin{itemize}
-        \item the uniform priors show the expected behaviour: decompose into point sources, when "optimized to the end".
-        \item yields very good results, if the true underlying source are only point sources
-        \item results are very bad, once extended emission is present. Result is "speckly" with no visible spatial correlation between nearby pixels.
-    \end{itemize}
-
-    \par{\textbf{Jolideco, Patch Prior GLEAM}}
-    \begin{itemize}
-        \item shows best results
-        \item slightly worse results on point sources only
-        \item visually very close to ground truth (!)
-        \item good compromise between sufficient separation of point sources and good reconstruction of extended sources.
-    \end{itemize}
+We find the prior learned from GLEAM data to be a very good compromise between teh ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
 
@@
     %
-    As a second experiment we explored the dependency of the results on background level and signal strength.
+    As a second experiment we explored the dependency of the results on the background level and signal strength.
 Figure~\ref{fig:comparison-signal-noise} shows the results for the \jolideco method with the GLEAM prior in the scenario D1-5.
+The background level was varied between
+
     As expected the reconstruction quality improves with signal strength.
-The method seems to converge to the ground truth for very high signal-to-noise ratio.
-
-    Es expected once the signal strength becomes very large there is no dependency of the result on the background level anymore (scenario D5)
-
+This includes both the variation of the background as well as signal strength.
+\todo{sensitivity scales as signal / sqrt(Bkg)?
+} Visually the method converges to the ground truth for very high signal-to-noise ratio.
+Once the signal strength becomes very large there is no dependency of the result on the background level anymore (especially valid for scenario D5)
+
+    We observe the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3). 
+    \todo{this is somewhat surprising as visually the signal can be seen in the data...at least for D2 and D3}.
     \todo{We should give a single number for the S/N, how to compute? Per source, like spiral ring and point sources...}
-
-    Some observations:
-
-    \begin{itemize}
-        \item 
-        \item there seems to be a "jump" in the reconstruction quality of the point sources. The weakest is much more blurry, but all the others look fine.
-        \item the method "fails" at the highest background level.
-    \end{itemize}
 
@@
 Figure~\ref{fig:comparison-instruments} shows the data as well as flux images reconstructed using \jolideco and the GLEAM v0.1 patch prior.
-We consider the source scenario D1-5 and the instrument scenarios and of \chandra, \xmm and combining both for a single reconstructed image.
-
-    Using the \chandra data alone results in a solid reconstruction at all variations of the D scenario. As expected the reconstruction quality improves for higher signal to noise ratio.
-
-    Using just the data from the \xmm instrument scenario results in lower quality reconstructions.
-However the spiral arm structure is reconstructed at all levels of the signal.
-The spiral arm structure is not really visible from the data by eye, because it is heavily blurred by the limited angular resolution.
+We consider the source scenarios D1-5 and the instrument scenarios \enquote{Chandra} and  \enquote{XMM} as well as the combination of their data to reconstruct a single image.
+
+    Using the data from the \enquote{Chandra} scenario alone results in a good reconstruction at all variations of scenario D.
+As expected the reconstruction quality improves for larger signal to noise ratio.
+
+    Using just the data from the \enquote{XMM} scenario results in lower quality reconstructions, due to the lower angular resolution.
+However we note that the spiral arm structure is reconstructed at all levels of the signal, even when barely visible from the data by eye \todo{check saturation of the color map...}.
+The ring structure is sharpened considerably in all cases.
+The points source left and right to the spiral arm structure cannot be separated as individual point sources.
+This remains for all scenarios D1-5, as the brightness of the point sources remains the same.
+This is an inherent limitation of the method.
+\todo{how far are those apart compared to the PSF?
+Hoes does this compare to the point scenario with XMM?}.
 
     Combining the data results in the best reconstruction quality.
-This confirms the results from \cite{Ingaramo2014}, that combining multiple measurements for deconvolution with RL was "general tool for combining images with complementary strengths".
+The addition of the lower resolution \enquote{XMM} data does not negatively affect the quality of the reconstruction.
+When comparing the D5 scenario we see that the \enquote{Chandra} reconstruction shows speckles in the ring, suggestion the prior cannot account for pixel to pixel correlations in the case of high signal strength.
+This behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the is smoother.
+The joint reconstruction shows the positive qualities of both individual reconstructions.
+This confirms the results from \cite{Ingaramo2014}, where the authors found that combining multiple measurements for deconvolution with RL to be a \textquote{general tool for combining images with complementary strengths}.
 
@@
 The left large image shows the summed counts from 25 observations.
-The right large image  shows the result from the \jolideco de-convolution process.
+The right large image  shows the result from the \jolideco deconvolution process.
 The flux is given as counts relative to the reference observation with ID=1308.
@@
 
-    As a first application example for real data we choose a set of 25 short exposure observations of the SNR \textit{E0102} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
+    As a first application example for real data we choose a set of short exposure observations of the SNR \textit{E0102} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
 In total we chose 25 observations (same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}) taken with with the ACIS instrument and no grating.
@@
 With \jolideco we can handle  PSF for each observation.
-We assume a spatially constant background of \qty[mode = text]{1e-5}{ct/pixels}.
-    We also assumed the exposure to be spatially constant.
-Its absolute value for each observation we expressed as the ratio of observation time with respect to the reference observation.
-As reference we chose the observation id 1308.
-    We reduced the data \textit{ciao} v4.15 and a custom \textit{snakemake} workflow (see Section~\ref{sec:reproducibility}).
-The PSF were simulated for each observation independently using \textit{marx} \todo{reference} and the \textit{simulate\_psf} script.
-The complete list of observation IDs can be found online.
-We selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a bins size of 0.25 "native" bins, corresponding to a bin size of \qty[mode = text]{0.001}{$\deg$/pixel} \todo{How large is the Chandra PSF compared to this?}.
+We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the norm to vary later in the reconstruction process.
+We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation.
+As reference we chose the observation with id 1308.
+
+    We reduced the data using \texttt{ciao} v4.15 and a custom \texttt{snakemake} workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
+The PSF were simulated for each observation independently using the tool \texttt{marx} \todo{reference} and the \texttt{simulate\_psf} script.
+We selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a bins size of 0.25 native bins, corresponding to a bin size of \qty[mode = text]{0.001}{$\deg$/pixel} \todo{How large is the Chandra PSF compared to this?}.
 As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
-We converted the spectral from XSPEC to sherpa script using the helper script \textit{convert\_xspec\_script}.
+We converted the spectral from XSPEC to sherpa script using the helper script \texttt{convert\_xspec\_script}.
+As reported in \cite{Xi2019} the effect of pileup, even for the brightest regions is small (<5\%), so we did not include the effect of pileup in our PSF simulations.
 
@@
 Figure~\ref{fig:example-chandra} shows the final result.
-\jolideco improves both the angular resolution as well as signal to noise ratio of the counts image.
+\jolideco clearly improves both the angular resolution as well as reduces the noise of the counts image.
 
@@
 
-    \todo{Showing residuals does not really make sense here the SNR seems to extend with time...this is clearly visible in the residuals..or ist the the exposure time calibration that changes?
-One could run on the Zoom A individually and the per obs shift might account for the motion with time...}
-
-    \url{https://github.com/jolideco/jolideco-chandra-examples}
+    Checking the residuals per observation (not shown here), we noticed that the assumption of the time independence of the source as well the instrument response is not completely fulfilled in this case.
+We saw the detection efficiency of \chandra changed between the observations as well as sub-structure in the source expands over time.
+Both effects are previously known have been reported e.g.
+in \cite{Xi2019} and \cite{}.
+Despite the clear improvement in spatial resolution the proper motion of structures in the image might limit the quality of the result.
+The full analysis example is available at \url{https://github.com/jolideco/jolideco-chandra-examples}
 
@@
             \caption{
-                The \jolideco method applied to \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
+                Illustration of the result of the \jolideco method applied to \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
 The left image shows the counts above \qty[mode = text]{10}{GeV}.
 The different event classes are stacked into a single image.
-                The image in the center show the flux reconstructed by the \jolideco methods. The image on the right shows the 
-                residuals as compute by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels.
+The image in the center shows the flux reconstructed by the \jolideco method.
+The image on the right shows the residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels.
 More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.
@@
 We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
-For the first part of the data reduction we use the standard \textit{fermitools} \todo{add version and reference}.
-
-    The \textit{fermitools} output an energy dependent counts, exposure and PSF cube.
+For the first part of the data reduction we use the standard \texttt{fermitools} \todo{add version and reference}.
+
+    The \texttt{fermitools} output an energy dependent counts, exposure and PSF cube.
 To further reduce the data to images we use the \textit{Gammapy} package.
 To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \cite{Ajello2017}.
-We first fit the model components to the data, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on \textit{Vela Junior}.
+We first fit the model components to the data using \textit{Gammapy}, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on \textit{Vela Junior}.
 Finally we reduce this model to an image by summing over the energy dimension.
@@
     As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit \textit{Gaussian} distribution.
-
 More details of the example \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
@@
     \section{Paper Reproducibility}
+    \label{sec:reproducibility}
     In order to facilitate reproducibility of our results we provide the source code for the paper and figures at \url{https://github.com/jolideco/jolideco-paper}.
-The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021}, following the instructions in the \texttt{README.md} file in the same repository.
-All data is available on Zenodo \todo{how do we do this exactly...?}
-
-    For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow 
-    available at \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
-
+The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021} and following the instructions in the \texttt{README.md} file in the same repository.
+All data is available for download from Zenodo \todo{how do we do this exactly...?} or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \url{https://github.com/jolideco} \texttt{GitHub} organisation.
+For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow  available at \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
 For the Chandra data reduction we used a custom \texttt{Snakemake} workflow available at \footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
@@
     \section{Summary \& Outlook}
-    In this work we presented a new method for image de-convolution and de-noising in the presence of Poisson noise.
-From multiple observations of the same sky region we reconstructed a single flux image using the approximate MAP estimate of the joint likelihood under patch based GMM prior.
+    In this work we presented a new method for image deconvolution and denoising in the presence of Poisson noise.
+Using multiple observations of the same sky region rthe methods reconstructs a single flux image using the approximate MAP estimate of the joint likelihood under patch based GMM prior.
 We showed that the methods leads to improved results in variety of scenarios.
@@
 
+    The choice of the prior becomes more important at low signal noise ratios.
+The right choice can yield superior reconstruction quality then any other method we have compared to.
+The advantage of the GMM patch prior is its expressiveness and that it is adapted to the data in the optimization process.
+However if the GMM patch prior is learned on unsuited data or data that not diverse enough it can contain a strong bias and there is the danger of hallucinating features.
+Testing of systematic uncertainties therefore becomes crucial.
+
     We consider the \jolideco method as a first step into the territory of \textit{ML inspired} methods for reconstruction of astronomical image data dominated by Poisson noise.
-While we achieved already superior results to any other existing method,
-    the \jolideco methods shows large potential for future extension and improvements.
+While we achieved already superior results to any other existing method, the \jolideco methods shows large potential for future extension and improvements.
 

### 2023-05-04 src/scripts/example-chandra.py
Add one more inset to chandra plot

@@ -86,13 +86,13 @@ filenames_data = path.parent.glob("*/maps/e0102-broadband-*-counts.fits")
 
 npred = Map.read(filename_npred)
 
-aspect_ratio = 1.618
+aspect_ratio = 1.8
 figsize = config.FigureSizeAA(aspect_ratio=aspect_ratio, width_aa="two-column")
 
 fig = plt.figure(figsize=figsize.inch)
 
 wcs = npred.geom.wcs
-height = 0.54
+height = 0.57
 width = height / aspect_ratio
 y_bottom = 0.1
 
@@ -113,12 +113,24 @@ for filename in filenames_data:
 
 print(f"Total counts: {stacked.data.sum()}")
 
-stacked.plot(ax=ax_counts, cmap="viridis", interpolation="None")
+norm_counts = simple_norm(
+    stacked.data,
+    stretch="linear",
+    min_cut=0,
+    max_cut=145,
+)
+stacked.plot(ax=ax_counts, cmap="viridis", interpolation="None", norm=norm_counts)
 add_cbar(ax_counts.images[0], ax_counts, fig, label="Counts")
 
 flux_data = fits.getdata(filename_jolideco, hdu="VELA-JUNIOR")
 flux = Map.from_geom(npred.geom.upsample(2), data=flux_data)
-flux.plot(ax=ax_flux, cmap="viridis", interpolation="gaussian")
+norm_flux = simple_norm(
+    flux.data,
+    stretch="linear",
+    min_cut=0,
+    max_cut=3.5,
+)
+flux.plot(ax=ax_flux, cmap="viridis", interpolation="gaussian", norm=norm_flux)
 add_cbar(ax_flux.images[0], ax_flux, fig, label="Flux / A.U.")
 
 norm_factor = np.pi * SMOOTH_WIDTH**2
@@ -131,13 +143,22 @@ print(f"Mean residuals : {residuals_per_pix.data.mean():.3f}")
 print(f"Sigma residuals: {residuals_per_pix.data.std():.3f}")
 
 
-def draw_zoom(fig, ax, ax_zoom_rect, map_, center, width, title):
+def draw_zoom(
+    fig,
+    ax,
+    ax_zoom_rect,
+    map_,
+    center,
+    width,
+    title,
+    norm=None,
+):
     """Draw zoom box"""
     cutout = map_.cutout(position=center, width=width)
 
     ax_zoom = fig.add_axes(ax_zoom_rect, projection=cutout.geom.wcs)
 
[…]

### 2023-05-05 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \item either we neglect the correlation between overlapping patches
-        \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of "per patch optimization". However optimization on discrete 
+        \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of per patch optimization. However optimization on discrete 
         values is not easily possible in Pytorch. However here is one idea:
@@
         parameter $z$, which interpolates between similar components.
-        \item Another idea is to use "Gumbel Softmax"...
+        \item Another idea is to use Gumbel Softmax...
         \item we also compute the mean of the likelihood for the overlapping parts
@@
     \subsubsection{Patch Normalisation and Dynamic Range}
-    Astronomical images typically show a much higher dynamic range compared to 
-    natural images. This is mostly due to the existence of point sources, which
-    rarely occur in natural images. Astronomical point sources typically relate
-    to compact bright objects, such as active galactic nuclei at high distances,
-    or binary objects and stars at Galactic distances.
+    Astronomical images typically show a much higher dynamic range compared to natural images.
+This is mostly due to the existence of point sources, which rarely occur in natural images.
+Astronomical point sources typically relate to compact bright objects, such as active galactic nuclei at high distances, or binary objects and stars at Galactic distances.
 In addition the visible matter in the universe is sparse such that astronomical images typically show sparse bright emission on a dark background.
 
-    \cite{Zoran2011} used a patch normalisation where the mean of the patch is subtracted.
-This means the same morphological features are present in the GMM at various levels of contrast.
+    To normalise the patches \cite{Zoran2011} proposed to subtract the patch mean before learning the GMM.
+This leads to the GMM modeling the same morphological features at different levels of contrast as different components.
 While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, only at the cost of introducing a lot more components to the GMM, which is unfeasible in practice due to limited availability of training data and computational resources.
-
-    The high dynamic range of astronomical images challenges any deconvolution method.
+For this reason we propose the following modified normalisation for the patches:
+    %
+    \begin{equation}
+        \label{eq:patch-norm}
+        \tilde{\mathbf{x}}_n = \frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n}
+    \end{equation}
+
+    With dividing by the mean of the patch $\Bar{\mathbf{x}}_n$ the structure in the patch becomes independent of the total brightness the patch contains.
+This results in patches being grouped only by their pixel to pixel correlation structure and not by total contrast.
+This corresponds the assumption that the structure in the patch is statistically independent of the total flux contained in the patch, which we consider a valid assumption for astronomical images.
+
+    % The high dynamic range of astronomical images challenges any deconvolution method.
 To recover point sources accurately it is required to keep correlations with neighbouring pixels low, while for extended source the opposite is true.
@@
 
-    \begin{equation}
-        \label{eq:patch-norm}
-        \tilde{\mathbf{x}}_n = f \left(\frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n} \right)
-    \end{equation}
-
-    With a given non-linearity:
-
-    \begin{equation}
-        f(x) = \arcsinh{x / \alpha}
-    \end{equation}
-
-    \todo{The patch normalisation remains to be decided, but it would be advantageous to get rid of the hyper-parameter associated with the total image normalisation}.
-    The GMM patch prior is learned from other images whose pixel intensities
-    have no physical relationship of the intensities of the Poisson data we are
-    dealing with. To overcome this the GMM is learned on normalized images,
-    where the intensity values are constrained between 0 and 1.
-    To evaluate the GMM patch prior on the 
-    model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
-    in the same dynamic range between 0 and 1. Multiple common choices for such a
-    mapping function are shown in Fig.~\ref{fig:image-norms}.
-
-    In practice we are interested in the likelihood of a given structure in a patch and
-    So we subtract the mean value of a given patch. This represents the assumption that
-    the image structure is independent of the total flux contained in the patch.
-
-    % \begin{figure}
-    %     \script{image-norms.py}
-    %     \begin{centering}
-    %         \includegraphics[width=\linewidth]{figures/image-norms.pdf}
-    %         \caption{
-    %             Various image norms with different dynamic behaviour.
-    %         }
-    %         \label{fig:image-norms}
-    %     \end{centering}
-    % \end{figure}
-
-    The choice of the image normalisation allows to adjust the contrast of the image
-    and e.g. enhance low intensity structures, which also enhances the regularising
-    effect of the patch prior.
-
-    \todo{Which normalisation to choose, atan, asinh, log, inverse-cdf?}
-
-    There are arguments for $\arcsinh(\mathbf{x})$, see e.g. \cite{Lupton2004}, which we use.
+    % With a given non-linearity:
+
+    % \begin{equation}
+    %     f(x) = \arcsinh{x / \alpha}
+    % \end{equation}
+
+    % \todo{The patch normalisation remains to be decided, but it would be advantageous to get rid of the hyper-parameter associated with the total image normalisation}.
+    % The GMM patch prior is learned from other images whose pixel intensities
+    % have no physical relationship of the intensities of the Poisson data we are
+    % dealing with. To overcome this the GMM is learned on normalized images,
+    % where the intensity values are constrained between 0 and 1.
+    % To evaluate the GMM patch prior on the 
+    % model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
+    % in the same dynamic range between 0 and 1. Multiple common choices for such a
+    % mapping function are shown in Fig.~\ref{fig:image-norms}.
+
+    % In practice we are interested in the likelihood of a given structure in a patch and
+    % So we subtract the mean value of a given patch. This represents the assumption that
+    % the image structure is independent of the total flux contained in the patch.
+
+    % % \begin{figure}
+    % %     \script{image-norms.py}
+    % %     \begin{centering}
+    % %         \includegraphics[width=\linewidth]{figures/image-norms.pdf}
+    % %         \caption{
+    % %             Various image norms with different dynamic behaviour.
+    % %         }
+    % %         \label{fig:image-norms}
+    % %     \end{centering}
+    % % \end{figure}
+
+    % The choice of the image normalisation allows to adjust the contrast of the image
+    % and e.g. enhance low intensity structures, which also enhances the regularising
+    % effect of the patch prior.
+
+    % \todo{Which normalisation to choose, atan, asinh, log, inverse-cdf?}
+
+    % There are arguments for $\arcsinh(\mathbf{x})$, see e.g. \cite{Lupton2004}, which we use.
 
@@
 This has the advantage of potentially speeding up the computation as well.
-\todo{It is available in the implementation, but a bit "ad hoc", maybe just not mention...}
+\todo{It is available in the implementation, but a bit ad hoc, maybe just not mention...}
     \end{itemize}
@@
     \subsubsection{Cross Validation}
-    Cross validation (CV) is an established method for model selection in statisticd and machine learning to prevent a model from overfitting to the training data.
-To perform CV the available data is slit into a "training" and "validation" dataset.
+    Cross validation (CV) is an established method for model selection in statistics and machine learning to prevent a model from overfitting to the training data.
+To perform CV the available data is slit into a \enquote{training} and \enquote{validation} dataset.
 While optimizing the log-likelihood value is monitored  The use of multiple dataset allows to use cross-validation to prevent overfitting.
-One of the standard techniques in "machine learning"...
+One of the standard techniques in machine learning...
 
@@
 
-    \subsection{Statistical Errors}
+    \subsection{Estimation of Statistical Errors}
+    Estimating the global covariance matrix for image based data is computationally not feasible, because the size of the matrix scales with the squared number of pixels in the image.
+However there are a few ways to estimate the statistical uncertainties associated with the flux image reconstructed by \jolideco.
+We propose three methods for this:
+
     \begin{itemize}
-        \item Bootstrapping observations
-        \item Bootstrapping events
-        \item Hessian diagonal
+    \item The first method we propose is bootstrapping of observations.
+Given that multiple observations of the same region of the sky are available, \jolideco can be run repeatedly on a random subset of those.
+This results in a set of reconstructed images which are sampled from the posterior distribution.
+Depending on the size of the images the associated computational effort can be very large as it requires running \jolideco many times to achieve sufficient statistics.
+
+    \item If only one or few observations are available we propose bootstrapping of the events used to compute the counts image instead.
+This basically corresponds to splitting a single observation into multiple ones splitting the single exposure into multiple time intervals.
+This way one can apply the first proposed method again.
+
+    \item We can also estimate the diagonal of the Hessian. However this is numerically challenging because of the random elements in the method, such as stochastic gradient decent and cycle spinning.
+
     \end{itemize}
+
+    \todo{One could try to estimate a sparse covariance matrix...or apprxoimate it using the GMM covariance...}
 
@@
 
-    In total we extracted \todo{insert number} patches and trained a GMM with 128 components. We used "data augmentation" by introducing a random shift of the sub-pixel position.
+    In total we extracted \todo{insert number} patches and trained a GMM with 128 components. We used data augmentation by introducing a random shift of the sub-pixel position.
 
@@
     \begin{itemize}
-        \item the optimizer sees $\log{\mathbf{x}}$, note this corresponds to an "implicit" prior of the flux being positive...
+        \item the optimizer sees $\log{\mathbf{x}}$, note this corresponds to an implicit prior of the flux being positive...
         \item First run with uniform prior, to get a rough estimate
@@
     \begin{figure*}
-        \label{fig:scenarios}
         \centering\includegraphics{figures/scenarios.pdf}
@@
         }
-        \label{fig:simulated_models_chandra}
+        \label{fig:scenarios}
     \end{figure*}
@@
 We rely on the default prior definition and allow the scale for the background to vary.
-In total we run the the sampling process for 5000 iterations and use 500 iterations as a "burn-in" period to allow the MCMC chain to converge.
+In total we run the the sampling process for 5000 iterations and use 500 iterations as a \endquote{burn-in} period to allow the MCMC chain to converge.
 Then we compute the mean of the posterior distribution ignoring the burn-in period.
@@
 While the optimization procedure is different, we still expect to see similar behaviour for the local correlations of pixels.
-This ad hoc approach of "early stopping" is often used in practice to "regularise" the RL method.
+This ad hoc approach of early stopping is often used in practice to regularise the RL method.
 
@@
 Given 5 observations this results in 10.000 iterations.
-Which optimizes "to the end" until there is no relevant change in the posterior log-likelihood.
+Which optimizes \enquote{to end} until there is no relevant change in the posterior log-likelihood.
 In addition we use and upsampling factor of 2.
@@
 In the lower left of the image the point sources become fainter and move closer, challenging all methods in succeeding to separate those as independent sources.
-The uniform prior optimized "to end" shows excellent results, still separating the sources.
+The uniform prior optimized \endquote{to end} shows excellent results, still separating the sources.
 
@@
 This includes both the variation of the background as well as signal strength.
-\todo{sensitivity scales as signal / sqrt(Bkg)?
+\todo{sensitivity scales as approx signal / sqrt(Bkg)?
 } Visually the method converges to the ground truth for very high signal-to-noise ratio.
@@
     Using just the data from the \enquote{XMM} scenario results in lower quality reconstructions, due to the lower angular resolution.
-However we note that the spiral arm structure is reconstructed at all levels of the signal, even when barely visible from the data by eye \todo{check saturation of the color map...}.
+However we find that the spiral arm structure is reconstructed at all levels of signal strength, even when barely visible from the data by eye \todo{check saturation of the color map...}.
 The ring structure is sharpened considerably in all cases.
@@
 The addition of the lower resolution \enquote{XMM} data does not negatively affect the quality of the reconstruction.
-When comparing the D5 scenario we see that the \enquote{Chandra} reconstruction shows speckles in the ring, suggestion the prior cannot account for pixel to pixel correlations in the case of high signal strength.
-This behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the is smoother.
+When comparing the D5 scenario we see that the \enquote{Chandra} reconstruction shows a very good reconstruction of the spiral structure but still shows speckles in the surrounding ring.
+The latter suggests that the prior is not strong enough to guide the pixel to pixel correlations in the case of high signal strength.
+The strength of the prior could be increased with the $\beta$ parameter, but for this study we did not tweak individual parameters, but just used the default configuration.
+The speckle behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the ring is smoother.
+In this case the correlation between pixels that are further apart is stronger because of the larger correlation PSF.
+However the reconstruction of the spiral structure in the center shows visual artifacts, with the individual arms not completely separated.
 The joint reconstruction shows the positive qualities of both individual reconstructions.
 This confirms the results from \cite{Ingaramo2014}, where the authors found that combining multiple measurements for deconvolution with RL to be a \textquote{general tool for combining images with complementary strengths}.
-
-    \begin{itemize}
-        \item surprising reconstruction quality for XMM with a strong signal
-        \item combining the data results in the best reconstruction
-        \item for a strong signal adding the "XMM" data improves the "Chandra" result for extende sources. It further reduces the "speckliness"
-        \item not understood: reconstruction of point source becomes worse as spiral becomes brighter.
+\todo{not understood: reconstruction of point source becomes worse as spiral becomes brighter.
 Maybe because the strong signal dominates the likelihood function?
-Not sure how to improve this...it is image dynamics...
-        \item confirm results by , the method takes "the" best pout of two different measurements. 
-    \end{itemize}
+Not sure how to improve this...is it image dynamics?}
 
@@
             \caption{
-               The \jolideco method applied to \chandra data of the SNR E0102.
+               The \jolideco method applied to \chandra data of the SNR \textit{1E~0102.2–7219}.
 The left large image shows the summed counts from 25 observations.
@@
 The panels \textit{Zoom A} and \textit{Zoom B} show a zoomed-in version of two example regions in the SNR, marked with the white rectangles in the large images.
+The colormap and scale used in the zoom insets is the same as used for the larger images.
             }
@@
 
-    As a first application example for real data we choose a set of short exposure observations of the SNR \textit{E0102} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
-In total we chose 25 observations (same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}) taken with with the ACIS instrument and no grating.
+    As a first application example for real data we choose a set of short exposure observations of the SNR \textit{1E~0102.2–7219} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
+In total we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with with the ACIS instrument and no grating.
 For \chandra the instrument response varies with the observation offset and energy \todo{reference}.
@@
 
-    For \jolideco we used the GMM prior learned on the JWST image Cas-A and an oversampling factor of 2.
-For each observation we allow the background level and position calibration to vary.
-Figure~\ref{fig:example-chandra} shows the final result.
-\jolideco clearly improves both the angular resolution as well as reduces the noise of the counts image.
-
-    \textit{Zoom A} shows an example for a filamentous structure in more detail.
+    For \jolideco we used the GMM prior learned on the JWST Cas A image.
+As there is a lot of statistics in the image we used and oversampling factor of 2.
+For each observation we allowed the background level and position calibration to vary.
+As reference for the positional shift we used the observation with the ID 1308.
+    Figure~\ref{fig:example-chandra} shows the final result. \jolideco clearly improves both the angular resolution as well as reduces the noise of the counts image.
+
+    \textbf{Zoom A} shows an example for a filamentous structure in more detail.
 \jolideco maintains the extended structure along the filament, while sharpening in the perpendicular direction.
 Looking at the upper right one can also see that weak background emission is suppressed, also improving the contrast of the image.
-\textit{Zoom B} shows a another circular filamentous structure of the SNR.
+
+    \textbf{Zoom B} shows the region around the central compact object of the SNR \cite{Vogt2018}.
+While the emission is barely visible in the counts image it clearly sticks out above the background in the image reconstructed by \jolideco.
+The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
+As shown in Section~\ref{subsec:methods} for scenario A, the apparent size of the points source becomes smaller if the source becomes brighter.
+
+    \textbf{Zoom C} shows a another circular filamentous structure of the SNR.
 In the counts data the structure is barely visible, while the image reconstructed by \jolideco shows a circular structure with a bright emission spot.
@@
     Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
-    \todo{To account for the Poisson statistics it would be more precise to compute a "TS" map, but for an approximate estimation it should  be fine...I have a derivation for this formula }
+    \todo{To account for the Poisson statistics it would be more precise to compute a TS map, but for an approximate estimation it should  be fine...I have a derivation for this formula }
 
@@
 The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021} and following the instructions in the \texttt{README.md} file in the same repository.
-All data is available for download from Zenodo \todo{how do we do this exactly...?} or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \url{https://github.com/jolideco} \texttt{GitHub} organisation.
+All data is available for download from Zenodo \todo{how do we do this exactly...?} or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \jolideco GitHub organisation \footnote{\url{https://github.com/jolideco}}.
 For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow  available at \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
@@
     In this work we presented a new method for image deconvolution and denoising in the presence of Poisson noise.
-Using multiple observations of the same sky region rthe methods reconstructs a single flux image using the approximate MAP estimate of the joint likelihood under patch based GMM prior.
+Using multiple observations of the same sky region the methods reconstructs a single flux image using the approximate MAP estimate of the joint likelihood under a patch based image prior.
 We showed that the methods leads to improved results in variety of scenarios.
@@
 
-    Firstly it is possibly to rely on more general mixture models such as a Student-T or a generalised Gaussian mixture model.
-Those more flexible functional shapes can account for tails in the distributions.
-Improved results on natural images have been reported e.g.
-by \cite{}.
+    The first category of future improvements is related to the prior handling.
+It is possibly to rely on more general mixture models such as a Student-T or a generalised Gaussian mixture model to model the distribution of patches.
+As shown by \cite{VanDenOord2014} those more flexible functional shapes can account for tails in the distributions and lead to improved results on natural images.
+
+    To increase the size of the correlation window of the patch prior, \cite{Papyan2015} proposed to evaluate and combine the prior on multiple scales of the image.
+This is a promising approach to  further improve the reconstruction quality for extended sources with low signal to noise ratio.
 
     To further improve the expressiveness of the prior \cite{Altekrueger2022} used normalising flows to model the distribution of patches in the context of CT image reconstruction.
+
+    Another promising approach to handle prior information for images has been introduced by \citep{Ulyanov2017} with the so called \enquote{Deep Image Prior}.
+They showed that a prior structure for an image can be built into a deep neural network.
+The structure of the network encodes the prior information on correlation between neighbouring pixels and also imposes self similarity on the structures in the image.
+
+    We also plan to extend the method to deal with the spectral dimension of the data as well. We also plan to extend the method to handle multiple source components at the same time.
 
@@
         \item Extend \jolideco to handle multiple source components at the same time.
-        \item one could try deep image priors \citep{Ulyanov2017}
-        \item Extend to use GMM patch prior on multiple scales, see \cite{Papyan2015}
-        \item Exclude point sources either via separate component or "J-invariance"
+        \item Exclude point sources either via separate component or J-invariance
     \end{itemize}

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 The method reconstructs a single flux image from a set of observations by optimizing the \aposteriori joint Poisson likelihood of all observations under a patch based image prior.
-The patch prior is parameterised by a Gaussian Mixture model (GMM) and learned from astronomical images with high signal to noise ratio, such as the James Webb Telescope.
-During the reconstruction process the patch prior adapts  to the structures in the data by finding the most likely GMM component for each patch in the image.
+The patch prior is parameterised by a Gaussian Mixture model (GMM) which we trained on astronomical images with high signal to noise ratio, including data from the  James Webb Telescope as well as the GLEAM radio survey.
+During the reconstruction process the patch prior adapts to the patch structures in the data by finding the most likely GMM component for each patch in the image.
 By applying the method to simulated data we show that both the combination of multiple observations as well as the patch based prior lead to a much improved reconstruction quality in many different source scenarios as well as signal to noise regimes.
 We show also that the method yields superior reconstruction quality to alternative standard methods such as the Richardson-Lucy method.
-We also show that the method can be highly adapted to various real analysis scenarios by learning problem specific GMM prior  such as images of extragalactic or Galactic sources.
+We also the results of the method applied to example data from the \chandra observatory as well as the \fermi.
+In both cases \jolideco improves the angular resolution as well as signal to noise ratio
+        by a factor of 42 \todo{it would be good to summarize the results with a few key numbers...}.
     \end{abstract}
@@
 
-    \newpage
     \subsection{Related Work}
@@
 
-    However in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion when to stop the optimization process.
+    However in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion for when to stop the optimization process.
 Usually the iteration is stopped when the reconstructed image seems plausible to the eye.
-Second, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\textit{speckles}).
+Second, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
 This problem was e.g.
@@
     To address the issue with RL decomposing extended emission structures into groups of point source, multiple additions to the RL method were proposed.
-Most importantly this lead to the introduction of regularised RL methods.
-    such as use of total variation \citep{Dey2006} or sparseness \todo{add reference}.
+Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparseness \todo{add reference}.
+The challenge is due to fundamentally contradicting goals: deconvolution favoring point sources will decompose extend structures, while introducing local correlations will lead to less sharp reconstrcution of point sources.
 
@@
 
-    An alternative approach to solve the problem in the framework of information field theory.
+    \cite{Pumpe2018} and \cite{Selig2015} approached the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
+Deconvolution, Denoising and Decomposition (D3PO) and (D4PO).
+
     Recently, image deconvolution using physical assumptions and decomposition into point and diffuse flux in 3D/4D has gained attention.
-\cite{Pumpe2018} and \cite{Selig2015} proposed priors based on physical assumptions, which have been shown to work well for large-scale emission.
+proposed priors based on physical assumptions, which have been shown to work well for large-scale emission.
 However, the smoothness assumption in these methods can lead to artifacts in the galactic plane.
 
-    The challenge is due to fundamentally contradicting goals: deconvolution favoring point sources will decompose extend structures, while introducing local correlations will lead to
-
-    \cite{Zoran2011} build on very similar assumption for natural images.
-    Instead of assuming a fixed local correlation structures, such as smoothness
-    they proposed to learn the local correlation structure on millions of patches
-    extracted from natural images.
-
-    For this they proposed to split training images from representative
-    data sets into small patches of size 8x8~pixels and fit a 64 dimensional
-    Gaussian Mixture Model (GMM) to the distribution of extracted patches. Each pixel of the patch 
+    Interesting approaches to the problem of deconvolution can of course be found in the field of computer vision.
+For example \cite{Zoran2011} build on very similar assumption of local correlation for natural images.
+Instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
+This approach can be seen as a form of transfer learning.
+For this they proposed to split training images from representative data sets into small patches of size 8x8~pixels and fit a 64 dimensional Gaussian Mixture Model (GMM) to the distribution of extracted patches.
+Each pixel of the patch
     is thereby treated as an independent dimension in the model. In total
     they chose to use $k=200$ Gaussian components.
-
 To use the GMM in reconstruction they introduce the expected patch likelihood (EPLL).
-
 They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
-
-    \cite{Bouman2016} later adapted the patch prior reconstruction to be used
+\cite{Bouman2016} later adapted the patch prior successfully for the reconstruction of radio data from the Event Horizon Telescope (EHT).
 
@@
 In a single layer, linear approximation, the network would need to learn the inverse filter of the PSF, corresponding to the well known \textit{Wiener filter} solution of the problem.
-This requires large convolution kernels or deep network architectures.
-\cite{Li2014} have introduced a baseline architecture for a deep CNN for image deblurring by introducing large kernels under the separability assumption.
-
-    One last important challenge is obtaining uncertainty estimates for the reconstructed image from CNNs.
+This requires large convolution kernels or deep network architectures, which require in turn large amounts of training data.
+This challenge was described early by \cite{Li2014} who introduced a baseline architecture for a deep CNN for image deblurring.
+
+    One last important challenge for deep learning based methods is obtaining uncertainty estimates for the reconstructed image from CNNs.
 In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possible for most network architectures, with the exception of for example normalising flows.
+    This problem could be adresses with Monte Carlo base methods, such as bootstrapping, further increasing the demand on training data and computation ressources.
 
@@
     For each individual observation $j$ the predicted counts can be modelled by \textit{forward folding} the unknown flux image $\mathbf{x}$ through the individual instrument response:
-
+    %
     \begin{equation}
@@
     counts $\boldsymbol{\lambda_j}$ with $N$ pixels is given by:
-
+    %
     \begin{equation}
@@
     \citep{Cash1979} fit statistics:
-
+    %
     \begin{equation}
@@
     By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
-
+    %
     \begin{equation}
@@
     \subsection{A Posteriori Joint Likelihood}
-    When reconstructing images in the context of inverse problems we are operating
-    in a high dimensional parameter space, because each pixel in the image represents
-    an independent parameter in the optimization process. By using prior information
-    we can introduce correlations between the parameters, to reduce the \textit{effective}
-    dimensionality of the problem and guide the optimization process towards unique 
-    and more stable solutions.
+    When reconstructing images in the context of inverse problems we are operating in a high dimensional parameter space, because each pixel in the image represents an independent parameter in the optimization process.
+By using prior information we can introduce correlations between the parameters, to reduce the \textit{effective} dimensionality of the problem and guide the optimization process towards unique and more stable solutions.
 
     Using Bayes rule we can estimate the \aposteriori likelihood under a given prior:
-
+    %
     \begin{equation}
@@
     And use a Maximum A Posteriori (MAP) approach to find an estimate for $\mathbf{x}$.
-    Taking the logarithm of Eq.~\ref{eq:bayes}, replacing the definition of the likelihood
-    $P(\mathbf{D}|\mathbf{x})$ with Eq.~\ref{eq:joint} and dropping the normalisation term $P(\mathbf{D})$
-    which is independent of $\mathbf{x}$, we get the following expression for the log-posterior
-    likelihood $\mathcal{L}$ :
-
+Taking the logarithm of Eq.~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Eq.~\ref{eq:joint} and dropping the normalisation term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we get the following expression for the log-posterior likelihood $\mathcal{L}$ :
+    %
     \begin{equation}
@@
 
-    Where $\mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)$ represents the summed log-likelihood
-    for an individual observation $j$. Additionally the function includes a log-prior
-    term $\mathcal{P}(\mathbf{x})$ and a factor $\beta$ to adjust the weight of the prior with respect to the joint log likelihood term.
-The parameter $\beta$ can be seen as a hyper-parameter, chosen by the user
-    to quantify their belief in the correctness of the chosen prior distribution.
-    \todo{this is somewhat dissatisfying...but in practice very common...see e.g. any kind of regularisation...if there is enough data cross validation could be used to tune this hyper-parameter}.
+    Where $\mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)$ represents the summed log-likelihood for an individual observation $j$.
+Additionally the function includes a log-prior term $\mathcal{P}(\mathbf{x})$ and a factor $\beta$ to adjust the weight of the prior with respect to the joint log likelihood term.
+The parameter $\beta$ can be seen as a hyper-parameter, chosen by the user to quantify their belief in the correctness of the chosen prior distribution.
+\todo{this is somewhat dissatisfying...but in practice very common...see e.g.
+any kind of regularisation...if there is enough data cross validation could be used to tune this hyper-parameter}.
 
@@
 For this reason we adopt the idea of a patch based image prior approach as introduced by \cite{Zoran2011}.
-We use a pre-trained Gaussian Mixture Model (GMM) to evaluate and approximate a patch based prior for the reconstructed image $\mathbf{x}$.
+Given a pre-trained Gaussian Mixture Model (GMM) for the distribution of pixel values in patches, we can evaluate a patch based prior for the reconstructed image $\mathbf{x}$ and approximate the \aposteriori likelihood.
 
     One convenient property of the GMM is the possibility to evaluate its likelihood in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
-
+    %
     \begin{equation}
@@
 
-    Where $\mathcal{N}$ is a Gaussian distribution, $K$ the total number of components, $\boldsymbol{\mu}_k$ the vector of means for a given component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix
-    and $\pi_k$ the weight of the component. The different weights are required to sum to unity such that $\sum_{k=1}^N\pi_k = 1$.
+    Where $\mathcal{N}$ is a Gaussian distribution, $K$ the total number of components, $\boldsymbol{\mu}_k$ the vector of means for a given component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix and $\pi_k$ the weight of the component.
+The different weights are required to sum to unity such that $\sum_{k=1}^N\pi_k = 1$.
 
     From Equation~\ref{eq:gmm} we can also derive the log-likelihood for a specific choice of the component $k$:
-
+    %
     \begin{equation}
@@
     If we split the image into non-overlapping patches, we can find for each noisy patch $\mathbf{x}_n$ the GMM component $\hat{k}_n$, which maximises the log-likelihood of the GMM:
-
+    %
     \begin{equation}
@@
 
-    As the number of components in the GMM is limited we can do this simply by evaluating the likelihood for each of the components and choose the one with
-    the maximum value of the log-likelihood. To finally evaluate the log-likelihood
-    of the total image we can sum up the log-likelihood of the individual patches:
-
+    As the number of components in the GMM is limited we can do this simply by evaluating the likelihood for each of the components and choose the one with the maximum value of the log-likelihood.
+To finally evaluate the log-likelihood of the total image we can sum up the maximum log-likelihood values of the individual patches:
+    %
     \begin{equation}
@@
 This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
+
+    In the case of non-overlapping patches the
 
@@
     with radio astronomy data.
-    They have shown that the reconstructed image only weakly depends on the choice
-    of the reference data on which the the patch prior is learned. They found
-    equivalent results for GMMs learned on natural images and specifically
-    simulated images of black hole ring structures.
-
-    Using half quadratic splitting and the Wiener filter solution, which is not possible
-    in our case. Instead we choose a direct optimization by relying on differentiable
-    programming later.
+They have shown that the reconstructed image only weakly depends on the choice of the reference data on which the the patch prior is learned.
+They found equivalent results for GMMs learned on natural images and specifically simulated images of black hole ring structures.
+
+    Using half quadratic splitting and the Wiener filter solution, which is not possible in our case. Instead we choose a direct optimization by relying on differentiable programming later.
 
@@
     \subsubsection{Cycle Spinning}
-    To avoid artifact due to the choice of the grid of overlapping patches we propose
-    three variations:
+    To avoid artifact due to the choice of the grid of overlapping patches we propose three variations:
 
@@
     Each measured counts image $\mathbf{D_j}$ is associated with systematic errors.
-    This includes e.g. the pointing accuracy of the telescopes: when repeatedly pointed
-    to the same object or when using different types of telescopes for observation, the
-    absolute position of an astronomical object might vary in the image between different
-    observations. The process of correcting for these inaccuracies is called \textit{astrometry} and a standard procedure in for example \chandra data analysis.
-    A second example of systematic errors is the variation of background emission
-    between multiple observations.
-
-    To account for both systematic effects we extend the model for the predicted
-    counts introduced in Eq.~\ref{eq:model}, by a background normalisation factor
-    $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$, which is specific for each observation. This yields the following modified model definition:
-
+This includes e.g.
+the pointing accuracy of the telescopes: when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object might vary in the image between different observations.
+The process of correcting for these inaccuracies is called \textit{astrometry} and a standard procedure in for example \chandra data analysis.
+A second example of systematic errors is the variation of background emission between multiple observations.
+
+    To account for both systematic effects we extend the model for the predicted counts introduced in Eq.~\ref{eq:model}, by a background normalisation factor $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$, which is specific for each observation.
+This yields the following modified model definition:
+    %
     \begin{equation}
@@
 
-    In practice one observation is used as a reference and its corresponding
-    systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during
-    optimization. An example of the effect of the positional shift and background
-    normalisation can be seen in Fig.~\ref{fig:npred-systematics}.
+    In practice one observation is used as a reference and its corresponding systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during optimization.
+An example of the effect of the positional shift and background normalisation can be seen in Fig.~\ref{fig:npred-systematics}.
 
@@
 
-    \todo{One could try to estimate a sparse covariance matrix...or apprxoimate it using the GMM covariance...}
+    \todo{One could try to estimate a sparse covariance matrix...or approximate it using the GMM covariance...}
 
@@
     We implemented the \jolideco method as an independent Python package, based on \texttt{PyTorch} as optimization back-end.
-We tried to define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of image normalisation scales, the choice of GMM models, optimization methods and serialisation formats for the reconstruction results as well as corresponding diagnostic information such as the trace of the posterior and prior likelihood values.
-The package is available at \url{https://github.com/jolideco/jolideco}
+We tried to define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of the patch normalisation, the choice of GMM models, optimization methods and serialisation formats for the reconstruction results as well as corresponding diagnostic information such as the trace of the posterior and prior likelihood values.
+We hope that this simplifies the future improvement and extension of the package.
+The package is available at \url{https://github.com/jolideco/jolideco}.
 
@@
     \subsubsection{JWST Cassiopeia A}
-    The James Webb Space Telescope is the it delivers data a very high resolution and excellent signal to noise ratio. We extracted 2 million patches out of the image...
-    Would be 
-    Of \textit{Cassiopeia A}
-    As a last GM prior we use the promotional image of JWST realeased by...
-    The image is particularly suited becasue of the excellent angular resolution, extrating many patches for the same object
-    as well as the high signal to noise ratio.
-
-    Taken from \url{https://webbtelescope.org/contents/media/images/2023/121/01GWQBBY77MHGFV3M3N63KDCEJ}
+    The James Webb Space Telescope (JWST) is a large, infrared space telescope launched in late 2021.
+It delivers image data a very high spatial resolution as well as excellent signal to noise ratio.
+Both of these properties make JWST data an excellent choice for extracting patches for training a GMM.
+To limit the data reduction effort we relied on a promotional image of the SNR \textit{Cassiopeia A}\footnote{The image was downloaded from \url{https://webbtelescope.org/contents/media/images/2023/121/01GWQBBY77MHGFV3M3N63KDCEJ}}.
+    We first converted the image to gray scale using a perceived brightness model \todo{reference skimage...}.
+Then we split the image into $approx 2$ million patches and learned a GMM with 128 mixture components.
 
@@
 The flux is given as counts relative to the reference observation with ID=1308.
-The panels \textit{Zoom A} and \textit{Zoom B} show a zoomed-in version of two example regions in the SNR, marked with the white rectangles in the large images.
+The panels \textit{Zoom A}, \textit{Zoom B} and \textit{Zoom C} show a zoomed-in version of three example regions in the SNR, marked with the white rectangles in the large images.
 The colormap and scale used in the zoom insets is the same as used for the larger images.
@@
     The \texttt{fermitools} output an energy dependent counts, exposure and PSF cube.
-To further reduce the data to images we use the \textit{Gammapy} package.
+To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Donath2023}.
 To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \cite{Ajello2017}.
@@
 The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021} and following the instructions in the \texttt{README.md} file in the same repository.
-All data is available for download from Zenodo \todo{how do we do this exactly...?} or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \jolideco GitHub organisation \footnote{\url{https://github.com/jolideco}}.
-For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow  available at \footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
-For the Chandra data reduction we used a custom \texttt{Snakemake} workflow available at \footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
+All data is available for download from Zenodo \todo{how do we do this exactly...?} or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \jolideco GitHub organisation\footnote{\url{https://github.com/jolideco}}.
+For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow  available at\footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
+For the Chandra data reduction we used a custom \texttt{Snakemake} workflow available at\footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
 
@@
 
-    To increase the size of the correlation window of the patch prior, \cite{Papyan2015} proposed to evaluate and combine the prior on multiple scales of the image.
+    To increase the size of the correlation window of the patch prior, \cite{Papyan2015} proposed to evaluate and combine the prior on patches extracted at multiple scales of the image.
 This is a promising approach to further improve the reconstruction quality for extended sources with low signal to noise ratio.
 
-    To further improve the expressiveness of the prior \cite{Altekrueger2022} used normalising flows to model the distribution of patches in the context of CT image reconstruction.
+    To further improve the general expressiveness of the prior \cite{Altekrueger2022} used normalising flows (NF) to model the distribution of patches in the context of computer tomography image reconstruction.
+Just like a GMM the NF allows to evaluate its likelihood function and therfore construct an explicit, approximate \aposteriori probability for optimization.
+\todo{However it is also know that NFs struggle with multi-modality...not sure how this affects the propsoed approach...}
 
     Another promising approach to handle prior information for images has been introduced by \citep{Ulyanov2017} with the so called \enquote{Deep Image Prior}.
-They showed that a prior structure for an image can be built into a deep neural network.
-The structure of the network encodes the prior information on correlation between neighbouring pixels and also imposes self similarity on the structures in the image.
+They showed that a prior structure for an image can be built into a deep neural network, where the architecture of the network encodes the prior information on the correlation structure between neighbouring pixels.
+The authors showed, that the deep image prior successfully imposes self similarity on the structures in the image.
+As structures in astronomical images often show sell-similarity this is and interesting approach, that could even be combined with the patch prior.
 

### 2023-05-08 src/scripts/image-norms.py

@@ -1,34 +1,0 @@
-import config
-import matplotlib.pyplot as plt
-import numpy as np
-import paths
-from jolideco.utils.norms import NORMS_REGISTRY
-
-figsize = config.FigureSizeAA(aspect_ratio=1.618)
-
-init_kwargs = {
-    "fixed-max": {"max_value": 10},
-    "asinh": {"alpha": 0.1, "beta": 10},
-    "atan": {},
-}
-
-fig = plt.figure(figsize=figsize.inch)
-ax = fig.add_axes([0.15, 0.2, 0.80, 0.77])
-
-x = np.linspace(0, 15, 100)
-
-
-for name, norm_clas in NORMS_REGISTRY.items():
-    if name not in init_kwargs:
-        continue
-
-    norm_cls = NORMS_REGISTRY[name]
-    norm = norm_cls(**init_kwargs[name])
-    ax.plot(x, norm.evaluate_numpy(x), label=name)
-
-ax.set_xlim(0, 15)
-ax.set_ylim(0, 1.2)
-ax.set_xlabel("Pixel value")
-ax.set_ylabel("Normalised pixel value")
-plt.legend()
-plt.savefig(paths.figures / "image-norms.pdf", facecolor="w", dpi=300)

### 2023-05-08 src/scripts/patches.py

@@ -1,31 +1,52 @@
 import config
 import matplotlib.pyplot as plt
+import numpy as np
 import paths
+from astropy.io import fits
+from astropy.nddata import block_reduce
+from astropy.utils.data import get_pkg_data_filename
+from astropy.visualization import simple_norm
 from matplotlib.patches import Rectangle
 
-figsize = config.FigureSizeAA(aspect_ratio=2)
+random_state = np.random.RandomState(49837)
+filename = get_pkg_data_filename("galactic_center/gc_msx_e.fits")
+
+
+image_size = (128, 68)
+x, y = 10, 40
+cutout = (slice(y, y + image_size[1]), slice(x, x + image_size[0]))
+
+figsize = config.FigureSizeAA(aspect_ratio=image_size[0] / image_size[1])
 
 fig = plt.figure(figsize=figsize.inch)
 ax = fig.add_axes([0, 0, 1, 1])
 
+max_value = 100
+data = block_reduce(fits.getdata(filename)[cutout], 2)
+data = np.clip(max_value * data / data.max(), 0, np.inf)
+data = random_state.poisson(data)
+norm = simple_norm(data, "asinh", asinh_a=0.01, min_cut=0, max_cut=max_value)
+ax.imshow(data, origin="lower", norm=norm, cmap="viridis")
+
 image_size = (64, 32)
 patch_size = (8, 8)
+stride = 6
 
-for x in range(0, 2 * image_size[0], 6):
-    for y in range(0, 2 * image_size[1], 6):
+for x in range(0, image_size[0] - stride, stride):
+    for y in range(0, image_size[1] - stride, stride):
         rectangle = Rectangle(
-            xy=(x, y),
+            xy=(x + 0.5, y + 0.5),
             width=patch_size[0],
             height=patch_size[1],
-            facecolor="tab:blue",
-            edgecolor="None",
+            facecolor="white",
+            edgecolor="none",
             alpha=0.2,
         )
 
         ax.add_patch(rectangle)
 
 rectangle = Rectangle(
-    xy=(12, 12),
+    xy=(12.5, 12.5),
     width=patch_size[0],
     height=patch_size[1],
     facecolor="None",
@@ -34,11 +55,11 @@ rectangle = Rectangle(
 )
 ax.add_patch(rectangle)
 
-ax.text(x=16, y=20.5, s="8 x 8 Patch", color="tab:red", ha="center")
[…]

### 2023-05-08 src/scripts/gmm-eigen-images.py
Add eigen image plot

@@ -1,14 +1,39 @@
 import config
 import matplotlib.pyplot as plt
+import numpy as np
 import paths
 from jolideco.priors import GaussianMixtureModel
+from scipy import linalg
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618)
 
 fig = plt.figure(figsize=figsize.inch)
 
-gmm = GaussianMixtureModel.from_registry("nrao-jets-v0.1")
+gmm = GaussianMixtureModel.from_registry("jwst-cas-a-v0.1")
 
 
-plt.legend()
+gridspec_kw = {
+    "left": 0.01,
+    "right": 0.99,
+    "bottom": 0.005,
+    "top": 0.95,
+}
+
+fig, axes = plt.subplots(
+    nrows=4, ncols=8, figsize=figsize.inch, gridspec_kw=gridspec_kw
+)
+
+
+component = 10
+covariance = gmm.covariances_numpy[component]
+w, v = linalg.eigh(covariance)
+
+idx_sort = np.argsort(w)
+eigen_images = gmm.eigen_images  # v[:, idx_sort]
+
+for idx, ax in enumerate(axes.flat):
+    ax.imshow(eigen_images[idx].reshape((8, 8)))
+    ax.set_axis_off()
+    ax.set_title(f"{idx}", size=8, pad=0.5)
+
 plt.savefig(paths.figures / "gmm-eigen-images.pdf", facecolor="w", dpi=300)

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             \caption{
-                Grid of overlapping patches of size 8x8 pixels. The overlap size was chosen to be 2 pixels.
+                Grid of overlapping quadratic patches of size $8\times8$ pixels on top of an example image of the size $128 \times 68$ pixels.
+The overlap size was chosen to be $2$ pixels, which results in 50 patches in total.
+The patches are shown translucent, such that the light \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter, squares result from four patches overlapping at the their corners.
             }
@@
 This leads to the GMM modeling the same morphological features at different levels of contrast as different components.
-While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, only at the cost of introducing a lot more components to the GMM, which is unfeasible in practice due to limited availability of training data and computational resources.
+While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range.
+Only at the cost of introducing a lot more components to the GMM, which is unfeasible in practice due to limited availability of training data and computational resources.
 For this reason we propose the following modified normalisation for the patches:

### 2023-05-10 src/scripts/gmm-eigen-images.py
Adapt patch plot

@@ -1,4 +1,5 @@
 import config
+import matplotlib.colors as colors
 import matplotlib.pyplot as plt
 import numpy as np
 import paths
@@ -32,7 +33,11 @@ idx_sort = np.argsort(w)
 eigen_images = gmm.eigen_images  # v[:, idx_sort]
 
 for idx, ax in enumerate(axes.flat):
-    ax.imshow(eigen_images[idx].reshape((8, 8)))
+    ax.imshow(
+        eigen_images[idx].reshape((8, 8)),
+        origin="lower",
+        cmap="viridis",
+    )
     ax.set_axis_off()
     ax.set_title(f"{idx}", size=8, pad=0.5)
 

### 2023-05-10 src/scripts/patches.py

@@ -45,6 +45,17 @@ for x in range(0, image_size[0] - stride, stride):
 
         ax.add_patch(rectangle)
 
+        outline = Rectangle(
+            xy=(x + 0.5, y + 0.5),
+            width=patch_size[0],
+            height=patch_size[1],
+            facecolor="none",
+            edgecolor="white",
+            alpha=0.5,
+            lw=0.2,
+        )
+        ax.add_patch(outline)
+
 rectangle = Rectangle(
     xy=(12.5, 12.5),
     width=patch_size[0],

### 2023-05-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    First astronomical x-ray and \gammaray data data is rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
+    Firstly, astronomical x-ray and \gammaray data data is rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
 To circumvent this one could rely on transfer learning and simulated data.
@@
 However this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
+\cite{Sweere2022} used images from
+    the large scale structure simulations with promising results.
 
@@
 on energy as well as offset angle from the pointing direction.
-To cover the whole parameter space of the PSF one would need to train either a network for each of the PSF models, or define a very large network, which would require a very large computational effort.
+To cover the whole parameter space of the PSF one would need to train either a network for each of the PSF models, or define a very large network, which allows to represent the the varying PSF as well.
 
@@
 In a single layer, linear approximation, the network would need to learn the inverse filter of the PSF, corresponding to the well known \textit{Wiener filter} solution of the problem.
-This requires large convolution kernels or deep network architectures, which require in turn large amounts of training data.
+This requires either large convolution kernels or deep network architectures, which require in turn large amounts of training data.
 This challenge was described early by \cite{Li2014} who introduced a baseline architecture for a deep CNN for image deblurring.
@@
 In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possible for most network architectures, with the exception of for example normalising flows.
-    This problem could be adresses with Monte Carlo base methods, such as bootstrapping, further increasing the demand on training data and computation ressources.
+This problem could be addressed with Monte Carlo based methods, such as bootstrapping, which further increases the demand on training data and computational resources.
+For these reasons we decided to choose an approach more close to \enquote{classical} statistical modelling techniques.
+However we will include elements from ML to represent the prior information on images.
 
@@
 
-    To account for the possibility of different datasets having a different number of pixels we divide by $N$ (\todo{Does this need more justification...?}).
+    To account for the possibility of different datasets having a different number of pixels we divide by $N$ (\todo{Does this need more justification...is it reasonable?}).
     By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
@@
 
-    Using Maximum Likelihood Estimation (MLE) we could try to get an estimate $\hat{\mathbf{x}}$ directly,
-    using some optimization procedure. However in general this represents an \textit{ill posed}
-    inverse problem.
+    Using Maximum Likelihood Estimation (MLE) we could try to get an estimate $\hat{\mathbf{x}}$ directly, using some optimization procedure.
+However in general this represents an \textit{ill posed} inverse problem.
 Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}_1})$ look very different from each other and might also look different compared to a given ground truth, if available.
-    Both the convolution operation as well as the level of noise lead
-    to a loss of information in the data which cannot easily be recovered.
-    The likelihood surface shows many local, close-by minima. Depending on the initial estimate for $\mathbf{x}$ and the minimization algorithm the MLE based estimate
-    is likely to only find such a local minimum. This is fundamentally the reason for RL decomposing estimates into point sources, described in the previous section.
+Both the convolution operation as well as the level of noise lead to a loss of information in the data which cannot easily be recovered.
+The likelihood surface shows many local, close-by minima.
+Depending on the initial estimate for $\mathbf{x}$ and the minimization algorithm the MLE based estimate is likely to only find such a local minimum.
+This is fundamentally the reason for RL decomposing estimates into point sources, described in the previous section.
 
@@
 The overlap size was chosen to be $2$ pixels, which results in 50 patches in total.
-The patches are shown translucent, such that the light \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter, squares result from four patches overlapping at the their corners.
+The patches are shown translucent, such that the light \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter squares result from four patches overlapping at the their corners.
             }
@@
 Both of these properties make JWST data an excellent choice for extracting patches for training a GMM.
-To limit the data reduction effort we relied on a promotional image of the SNR \textit{Cassiopeia A}\footnote{The image was downloaded from \url{https://webbtelescope.org/contents/media/images/2023/121/01GWQBBY77MHGFV3M3N63KDCEJ}}.
+To limit the data reduction effort we relied on a promotional image of the SNR \textit{Cassiopeia A}\footnote{We downloaded the full resolution (4k)  PNG image from \url{https://webbtelescope.org/contents/media/images/2023/121/01GWQBBY77MHGFV3M3N63KDCEJ}}.
     We first converted the image to gray scale using a perceived brightness model \todo{reference skimage...}.
@@
             \caption{
-                Eigenimages of the covariance matrices of the 32 components of the GMM learned from the NRAO jets. \todo{Provide other examples...?!?}
+                Weighted sum of Eigenimages of the covariance matrices of the first $32$ components of the GMM learned from the JWST Cas A image.
+The color scale varies between the images, so their contrast is different.
             }
@@
 
-    The ground truth and corresponding expected counts for the combination of scenarios are shown in Figure~\ref{fig:scenarios}, and the details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios}.
+    The ground truth and corresponding expected counts for all combinations of source and instrument scenarios are shown in Figure~\ref{fig:scenarios}.
+The details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios}.
+In addition we also assume a constant background with varying levels of $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
 
@@
     \end{figure*}
-
-    Constant background levels of $\lambda_{Bkg}= 0.001, 0.01 \textrm{and} 0.1 \textrm{counts/pixel}$.
 
@@
 The complete results for the simulations and additional information are available at \url{https://jolideco.github.io/jolideco-comparison}.
-\todo{the background handling does not yet seem right...maybe we should let the background norm free}
             }
@@
 The background level was varied between
+    $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
 
@@
 \todo{sensitivity scales as approx signal / sqrt(Bkg)?
+so what what is the implication?
 } Visually the method converges to the ground truth for very high signal-to-noise ratio.
-Once the signal strength becomes very large there is no dependency of the result on the background level anymore (especially valid for scenario D5)
+Once the signal strength becomes very large there is no dependency of the result on the background level anymore.
+This especially valid for scenario D5
 
@@
             \caption{
-               The \jolideco method applied to \chandra data of the SNR \textit{1E~0102.2–7219}.
+               Result of the \jolideco method applied to \chandra data of the SNR \textit{1E~0102.2–7219}.
 The left large image shows the summed counts from 25 observations.
@@
     As a first application example for real data we choose a set of short exposure observations of the SNR \textit{1E~0102.2–7219} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
-In total we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with with the ACIS instrument and no grating.
-For \chandra the instrument response varies with the observation offset and energy \todo{reference}.
-With \jolideco we can handle  PSF for each observation.
+In total we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS instrument and no grating.
+
+    We reduced the data using \texttt{ciao} v4.15 and a custom \texttt{snakemake} workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
+For the counts image we selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandra.
+This corresponds to a pixel size of \qty[mode = text]{0.001}{$\deg$/pixel} \todo{How large is the Chandra PSF compared to this?}.
+
+    \chandra's instrument response varies with the observation offset and energy \todo{reference}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \todo{reference} and the \texttt{simulate\_psf} script.
+As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
+We converted the spectral from XSPEC to sherpa script using the helper script \texttt{convert\_xspec\_script}.
+As reported in \cite{Xi2019} the effect of pileup, even for the brightest regions is small ($<5\%$), so we did not include the effect of pileup in our PSF simulations.
+
     We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the norm to vary later in the reconstruction process.
@@
 
-    We reduced the data using \texttt{ciao} v4.15 and a custom \texttt{snakemake} workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
-The PSF were simulated for each observation independently using the tool \texttt{marx} \todo{reference} and the \texttt{simulate\_psf} script.
-We selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a bins size of 0.25 native bins, corresponding to a bin size of \qty[mode = text]{0.001}{$\deg$/pixel} \todo{How large is the Chandra PSF compared to this?}.
-As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
-We converted the spectral from XSPEC to sherpa script using the helper script \texttt{convert\_xspec\_script}.
-As reported in \cite{Xi2019} the effect of pileup, even for the brightest regions is small (<5\%), so we did not include the effect of pileup in our PSF simulations.
-
     For \jolideco we used the GMM prior learned on the JWST Cas A image.
@@
 For each observation we allowed the background level and position calibration to vary.
-As reference for the positional shift we used the observation with the ID 1308.
+As reference for the positional shift we also used the observation with the ID 1308.
+
     Figure~\ref{fig:example-chandra} shows the final result. \jolideco clearly improves both the angular resolution as well as reduces the noise of the counts image.
@@
 
-    Checking the residuals per observation (not shown here), we noticed that the assumption of the time independence of the source as well the instrument response is not completely fulfilled in this case.
-We saw the detection efficiency of \chandra changed between the observations as well as sub-structure in the source expands over time.
-Both effects are previously known have been reported e.g.
+    Checking the residual images per observation (not shown here), we noticed that the assumption of the time independence of the source as well the instrument response is not completely fulfilled in this case.
+We saw the detection efficiency of \chandra changed between the observations as well as that sub-structure in the remnant expands over time.
+Both effects are previously known and have been reported e.g.
 in \cite{Xi2019} and \cite{}.

### 2023-05-16 src/scripts/model-illustration.py
Model illustration

@@ -1,0 +1,186 @@
+import config
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+from astropy.convolution import Gaussian2DKernel, convolve_fft
+from astropy.io import fits
+from astropy.utils.data import get_pkg_data_filename
+from astropy.visualization import simple_norm
+from matplotlib import patches
+from matplotlib.transforms import Bbox
+from scipy.special import gamma
+
+random_state = np.random.RandomState(49837)
+
+figsize = config.FigureSizeAA(aspect_ratio=1.9, width_aa="two-column")
+
+fig = plt.figure(figsize=figsize.inch)
+
+image_size = (128, 128)
+
+GRAY = (0.7, 0.7, 0.7)
+
+
+def draw_circular_arrow(ax, x, y, angle_start, radius=0.15, angle=90, **kwargs):
+    kwargs.setdefault("color", GRAY)
+    theta1 = 0
+    theta2 = angle
+
+    if angle_start < 180:
+        width, height = 2 * radius, radius
+        y_head = y + radius
+    else:
+        width, height = radius, 2 * radius
+        y_head = y - radius
+
+    arc = patches.Arc(
+        xy=[x, y],
+        width=width,
+        height=height,
+        angle=angle_start,
+        theta1=theta1,
+        theta2=theta2,
+        linestyle="-",
+        color=kwargs.get("color", "black"),
+        lw=5,
+    )
+    ax.add_patch(arc)
+
+    x_head = x + 0.01
+    ax.scatter(x_head, y_head, marker=">", s=100, color=kwargs.get("color", "black"))
+
+
+def shrink_axis(ax, factor=0.55, shift_x=0, shift_y=0):
+    """Shrink axis by *factor*."""
+    x0, y0, width, height = ax.get_position().bounds
+
+    x0 += (1 - factor) / 2 * width + shift_x
+    y0 += (1 - factor) / 2 * height + shift_y
+    width *= factor
+    height *= factor
+    ax.set_position(Bbox.from_bounds(x0, y0, width, height))
+
+
+def get_flux():
+    """Get flux image from MSX data."""
[…]

### 2023-05-16 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    Using Maximum Likelihood Estimation (MLE) we could try to get an estimate $\hat{\mathbf{x}}$ directly, using some optimization procedure.
+    Using Maximum Likelihood Estimation (MLE) we could try to get an estimate of $\hat{\mathbf{x}}$ directly, using some optimization procedure.
 However in general this represents an \textit{ill posed} inverse problem.
 Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}_1})$ look very different from each other and might also look different compared to a given ground truth, if available.
-Both the convolution operation as well as the level of noise lead to a loss of information in the data which cannot easily be recovered.
+Both the convolution operation as well as the exitence of noise lead to a loss of information in the data which cannot easily be recovered.
 The likelihood surface shows many local, close-by minima.
@@
 This is fundamentally the reason for RL decomposing estimates into point sources, described in the previous section.
-
-    \todo{did you know this sum corresponds to the loop over data sets in machine learning...?}
 
@@
 
-    Where $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch
-    from the image $\mathbf{x}$ to be reconstructed.
+    Where $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed.
 This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
 
-    In the case of non-overlapping patches the
-
-    \begin{itemize}
-        \item the case of non-overlapping patches is rather simple
-        \item for overlapping patches we have to make a few more approximations
-        \item either we neglect the correlation between overlapping patches
-        \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of per patch optimization. However optimization on discrete 
-        values is not easily possible in Pytorch. However here is one idea:
-        group the GMM components by similarity and introduce a single continues
-        parameter $z$, which interpolates between similar components.
-        \item Another idea is to use Gumbel Softmax...
-        \item we also compute the mean of the likelihood for the overlapping parts
-    \end{itemize}
-
-    To use the learned GMM as prior for the reconstruction of another image, the image is split into overlapping patches.
+    \citep{Zoran2011} found that the reconstruction quality could be improved by working with a grid of overlapping patches.
+Such a grid is illustrated in Figure~\ref{fig:patches}.
+However using a grid of overlapping patches makes the interpretation of the prior as likelihood more difficult, because pixels at the corners and edges of patches are counted multiple times.
+For this we introduce a weighting mask when evaluating the likelihood of the GMM.
+This mask weights the pixels of the patch by their overlap with the neighboring patch.
+Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4.
+We keep the process of choosing the most likely component, however we note that in this case we neglected the correlation between neighbouring patches.
+As the choice of the GMM component per patch is discrete a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
+    This would require a continuous representation or interpolation between GMM components.
+
+    % \begin{itemize}
+    %     \item the case of non-overlapping patches is rather simple
+    %     \item for overlapping patches we have to make a few more approximations
+    %     \item either we neglect the correlation between overlapping patches
+    %     \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of per patch optimization. However optimization on discrete 
+    %     values is not easily possible in Pytorch. However here is one idea:
+    %     group the GMM components by similarity and introduce a single continues
+    %     parameter $z$, which interpolates between similar components.
+    %     \item Another idea is to use Gumbel Softmax...
+    %     \item we also compute the mean of the likelihood for the overlapping parts
+    % \end{itemize}
+
+    % To use the learned GMM as prior for the reconstruction of another image, the image is split into overlapping patches.
 For each of the patches the log-likelihood for each of the GMM components is evaluated.
@@
             \caption{
-                Grid of overlapping quadratic patches of size $8\times8$ pixels on top of an example image of the size $128 \times 68$ pixels.
+                Grid of overlapping quadratic patches of size $8\times8$~pixels on top of an example image of the size $128 \times 68$~pixels.
 The overlap size was chosen to be $2$ pixels, which results in 50 patches in total.
-The patches are shown translucent, such that the light \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter squares result from four patches overlapping at the their corners.
+The patches are shown translucent, such that the horizontal and vertical \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter squares result from four patches overlapping at the their corners.
             }
@@
 
-    with radio astronomy data.
+    % with radio astronomy data.
 They have shown that the reconstructed image only weakly depends on the choice of the reference data on which the the patch prior is learned.
@@
 
-    Using half quadratic splitting and the Wiener filter solution, which is not possible in our case. Instead we choose a direct optimization by relying on differentiable programming later.
+    % Using half quadratic splitting and the Wiener filter solution, which is not possible in our case. Instead we choose a direct optimization by relying on differentiable programming later.
 
@@
     \label{ssec:jolideco-gmm-library}
-    On radio data \cite{Bouman2016} found the results to be mostly independent of the choice of data the GMM prior was learned on.
-The strength of the GMM prior is its high \textit{expressiveness}, meaning the prior contains a large variety of patch shapes and adapts to the data in the optimization process.
+    In general the strength of the GMM prior is its high \textit{expressiveness}.
+This means the prior contains a large variety of structural shapes and has a lot of freedom to adapt to the data in the optimization process.
+On radio data \cite{Bouman2016} found their results to be mostly independent of the choice of data the GMM prior was learned on.
 However in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of the data the GMM was learned on.
@@
 More details of how the model was learned are given in the original publication.
+This model uses the subtraction of the mean of the patch for normalisation.
 
@@
     The James Webb Space Telescope (JWST) is a large, infrared space telescope launched in late 2021.
-It delivers image data a very high spatial resolution as well as excellent signal to noise ratio.
+It delivers image data at very high spatial resolution as well as excellent signal to noise ratio.
 Both of these properties make JWST data an excellent choice for extracting patches for training a GMM.
@@
     \subsubsection{Chandra SNRs}
-    \label{sssec:chandra-snrs}. Because of the limited statistics we did not use any oversampling but kept the pixel
-    Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}.
+    \label{sssec:chandra-snrs}.
+Because of the limited statistics we did not use any oversampling but kept the pixel Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}.
 Structures appear on multiple angular scales.
@@
         \item GPU support via \texttt{Pytorch}
-
     \end{itemize}
@@
 We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
-For the first part of the data reduction we use the standard \texttt{fermitools} \todo{add version and reference}.
+For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \cite{}.
 

### 2023-05-17 src/scripts/config.py
Adapt patch plot

@@ -43,6 +43,7 @@ class FigureSizeAA:
     def __init__(self, aspect_ratio=1, width_aa="single-column"):
         self.width = FIGURE_WIDTH_AA[width_aa]
         self.height = self.width / aspect_ratio
+        self.aspect_ratio = aspect_ratio
 
     @property
     def inch(self):

### 2023-05-17 src/scripts/patches.py

@@ -2,10 +2,12 @@ import config
 import matplotlib.pyplot as plt
 import numpy as np
 import paths
+import torch
 from astropy.io import fits
 from astropy.nddata import block_reduce
 from astropy.utils.data import get_pkg_data_filename
 from astropy.visualization import simple_norm
+from jolideco.priors import GaussianMixtureModel
 from matplotlib.patches import Rectangle
 
 random_state = np.random.RandomState(49837)
@@ -16,15 +18,20 @@ image_size = (128, 68)
 x, y = 10, 40
 cutout = (slice(y, y + image_size[1]), slice(x, x + image_size[0]))
 
-figsize = config.FigureSizeAA(aspect_ratio=image_size[0] / image_size[1])
+figsize = config.FigureSizeAA(aspect_ratio=1.2)
 
 fig = plt.figure(figsize=figsize.inch)
-ax = fig.add_axes([0, 0, 1, 1])
 
-max_value = 100
+ratio = image_size[0] / image_size[1]
+width = 1
+height = width / ratio * figsize.aspect_ratio
+ax = fig.add_axes([0, 1 - height, width, height])
+ax.set_axis_off()
+
+max_value = 1
 data = block_reduce(fits.getdata(filename)[cutout], 2)
 data = np.clip(max_value * data / data.max(), 0, np.inf)
-data = random_state.poisson(data)
+# data = random_state.poisson(data)
 norm = simple_norm(data, "asinh", asinh_a=0.01, min_cut=0, max_cut=max_value)
 ax.imshow(data, origin="lower", norm=norm, cmap="viridis")
 
@@ -57,20 +64,55 @@ for x in range(0, image_size[0] - stride, stride):
         ax.add_patch(outline)
 
 rectangle = Rectangle(
-    xy=(12.5, 12.5),
+    xy=(30.5, 12.5),
     width=patch_size[0],
     height=patch_size[1],
     facecolor="None",
     edgecolor="tab:red",
-    lw=1,
+    lw=1.5,
 )
 ax.add_patch(rectangle)
 
-ax.text(x=16.5, y=21.5, s="8 x 8 Patch", color="tab:red", ha="center")
+ax.text(x=34.5, y=21.5, s="8 x 8 Patch", color="tab:red", ha="center")
 
-offset = patch_size[0] // 2
-# ax.set_xlim(offset, image_size[0] - offset - offset // 2)
[…]

### 2023-05-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\begin{figure*}
+        \script{model-illustration.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/model-illustration.pdf}
+            \caption{
+                Illustration of the forward model of the low counts imaging process.
+The flux represents the true unknown flux distribution in the sky.
+The flux is convolved with an image of the PSF, which represents an estimate of the resolution of the imaging instrument.
+The exposure consists of the superposition of multiple independent observations with different observation time and pointing position.
+The exposure weighted flux image is degraded by Poisson noise.
+            }
+            \label{fig:model-illustration}
+        \end{centering}
+    \end{figure*}
     \section{Method}
+
     \subsection{Poisson Joint Likelihood}

### 2023-05-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \label{eq:model}
-        \boldsymbol{\lambda}_j(\mathbf{x}) = \mathrm{PSF}_j \circledast \left(\mathbf{E}_j \cdot (\mathbf{x} + \mathbf{B}_j) \right)
+        \boldsymbol{\lambda}_j(\mathbf{x}) = \mathbf{E}_j \cdot \left(\mathrm{PSF}_j \circledast \mathbf{x}\right) + \mathbf{B}_j
     \end{equation}
@@
     Where the expected counts $\lambda_j$ are given by the convolution of the unknown 
-    flux image $\mathbf{x}$ with the observation specific point spread function $\mathrm{PSF}_j$. Additionally
-    an observation specific image of the exposure $\mathbf{E}_j$ and background emission $\mathbf{B_j}$ can be
-    optionally taken into account.
+    flux image $\mathbf{x}$ with the observation specific point spread function $\mathrm{PSF}_j$.
+Additionally an observation specific image of the exposure $\mathbf{E}_j$ and background emission $\mathbf{B_j}$ can be optionally taken into account.
+A visual representation of the model of the imaging process for a single observation is shown in Figure~\ref{fig:model-illustration}.
 
@@
 
-    As the number of components in the GMM is limited we can do this simply by evaluating the likelihood for each of the components and choose the one with the maximum value of the log-likelihood.
+    As the number of components in the GMM is typically limited to $\mathcal{O}(<10^2)$ we can do this simply by evaluating the likelihood for each of the components and choose the one with the maximum value of the log-likelihood.
 To finally evaluate the log-likelihood of the total image we can sum up the maximum log-likelihood values of the individual patches:
@@
     \begin{equation}
+        \label{eq:prior-total}
         \mathcal{P}(\mathbf{x}, \mathbf{k}) = \sum_{n = 1}^N \mathcal{P}_{GMM}(\hat{k}_n | \mathbf{P}_n \mathbf{x})
@@
     Where $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed.
-This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
+This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$ \todo{isn't this empirical Bayes?
+Should we call it like this?}.
+The bottom row of Figure~\ref{fig:patches} shows an example of a patch and the same patch represented in the \textit{Eigenbasis} of the covariance matrices of its three most likely GMM components.
+\todo{Visually the GMM acts as a denoiser...maybe worth a comment...}
+
+ \begin{figure}
+        \script{patches.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/patches.pdf}
+            \caption{
+                Grid of overlapping quadratic patches of size $8\times8$~pixels on top of an example image of the size $128 \times 68$~pixels.
+The overlap size was chosen to be $2$ pixels, which results in 50 patches in total.
+The patches are shown translucent, such that the horizontal and vertical \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter squares result from four patches overlapping at the their corners.
+The bottom row shows the red example patch $\mathbf{x}_n$ on the left.
+The three other patches show the quantity $\Sigma_{k_{GMM}} \mathbf{x}_n$, which is the result of the patch represented in the \textit{Eigenbasis} of the covariance matrices of the 3 most likely GMM components $k_{GMM} = 105, 77, 17$.
+This example uses the GMM learned from the JWST Cas A image.
+            }
+            \label{fig:patches}
+        \end{centering}
+    \end{figure}
 
@@
 This would require a continuous representation or interpolation between GMM components.
+We propose solutions for this later in the outlook of this manuscript.
 
@@
 
-    \begin{figure}
-        \script{patches.py}
-        \begin{centering}
-            \includegraphics[width=\linewidth]{figures/patches.pdf}
-            \caption{
-                Grid of overlapping quadratic patches of size $8\times8$~pixels on top of an example image of the size $128 \times 68$~pixels.
-The overlap size was chosen to be $2$ pixels, which results in 50 patches in total.
-The patches are shown translucent, such that the horizontal and vertical \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter squares result from four patches overlapping at the their corners.
-            }
-            \label{fig:patches}
-        \end{centering}
-    \end{figure}
-
     % with radio astronomy data.
@@
 
-    \subsubsection{Patch Normalisation and Dynamic Range}
+    \subsubsection{Image Dynamic Range and Patch Normalisation}
     Astronomical images typically show a much higher dynamic range compared to natural images.
@@
 This leads to the GMM modeling the same morphological features at different levels of contrast as different components.
-While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range.
-Only at the cost of introducing a lot more components to the GMM, which is unfeasible in practice due to limited availability of training data and computational resources.
-For this reason we propose the following modified normalisation for the patches:
+While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, because every morphological feature would need to present at many more levels of intensity.
+While this could be handled by introducing a lot more components to the GMM, it seems unfeasible in practice due to the limited availability of training data and computational resources.
+For this reason we propose the following modified normalisation for the patches instead:
     %
@@
 This corresponds the assumption that the structure in the patch is statistically independent of the total flux contained in the patch, which we consider a valid assumption for astronomical images.
+This also generalizes to the prior likelihood of the whole image described by Equation~\ref{eq:prior-total}.
+The value of the prior likelihood becomes independent of the total flux contained in the image.
 
@@
     \end{itemize}
+
+    \todo{This is Bias-Variance trade-off: if all data is used to deconvolve minimizes the statistical error, however the result might be biased... }
 

### 2023-05-19 src/scripts/patches.py
Clean up patches script

@@ -99,16 +99,16 @@ example_patch_torch = torch.from_numpy(example_patch).float()
 patches = example_patch_torch.reshape(1, 64)
 
 patch_mean = float(example_patch.mean())
-normed = gmm.meta.patch_norm(patches)
 
+normed = gmm.meta.patch_norm(patches)
 loglike = gmm.estimate_log_prob(normed)[0, :]
 idx_sort = torch.argsort(loglike, descending=True)
-print(torch.argmax(loglike))
 
 for idx, idx_gmm in enumerate(idx_sort[:3]):
-    prec = gmm.covariances_numpy[idx_gmm]
-    cleaned = np.matmul(normed.numpy(), prec)
-    patch = cleaned + patch_mean
+    covar = gmm.covariances_numpy[idx_gmm]
+    cleaned = np.matmul(normed.numpy(), covar)
+    patch = cleaned * patch_mean + patch_mean
+
     ax_patch = fig.add_axes([0.3 + idx * (width + 0.02), 0.08, width, width])
     ax_patch.imshow(patch.reshape(patch_size), origin="lower", cmap="viridis")
     ax_patch.set_axis_off()

### 2023-09-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 on energy as well as offset angle from the pointing direction.
-To cover the whole parameter space of the PSF one would need to train either a network for each of the PSF models, or define a very large network, which allows to represent the the varying PSF as well.
+To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models.
 
@@
 In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possible for most network architectures, with the exception of for example normalising flows.
-This problem could be addressed with Monte Carlo based methods, such as bootstrapping, which further increases the demand on training data and computational resources.
+This problem could be addressed with Monte Carlo (MC) based methods, such as bootstrapping, which further increases the demand on training data and computational resources.
 For these reasons we decided to choose an approach more close to \enquote{classical} statistical modelling techniques.
@@
 However in general this represents an \textit{ill posed} inverse problem.
-Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}_1})$ look very different from each other and might also look different compared to a given ground truth, if available.
+Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}}_1)$ look very different from each other and might also look different compared to a given ground truth, if available.
 Both the convolution operation as well as the exitence of noise lead to a loss of information in the data which cannot easily be recovered.
@@
     Where $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed.
-This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$ \todo{isn't this empirical Bayes?
-Should we call it like this?}.
+This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
 The bottom row of Figure~\ref{fig:patches} shows an example of a patch and the same patch represented in the \textit{Eigenbasis} of the covariance matrices of its three most likely GMM components.
-\todo{Visually the GMM acts as a denoiser...maybe worth a comment...}
+Visually the representation of the of the patch in the covariance \textit{Eigenbasis} works as a denoising of the patch.
 
@@
 
-    \citep{Zoran2011} found that the reconstruction quality could be improved by working with a grid of overlapping patches.
+    \cite{Zoran2011} found that the reconstruction quality could be improved by working with a grid of overlapping patches.
 Such a grid is illustrated in Figure~\ref{fig:patches}.
@@
 This mask weights the pixels of the patch by their overlap with the neighboring patch.
-Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4.
-We keep the process of choosing the most likely component, however we note that in this case we neglected the correlation between neighbouring patches.
-As the choice of the GMM component per patch is discrete a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
+Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4, when computing the likelihood for a patch as given by  Equation~\ref{eq:gmm}.
+Apart from this we keep the process of choosing the most likely component unmodified.
+However we note that in this case we neglected the correlation between neighbouring patches.
+As the choice of the GMM component per patch is discrete, a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
 This would require a continuous representation or interpolation between GMM components.
-We propose solutions for this later in the outlook of this manuscript.
+We propose ideas to work around this assumption later in the outlook of this manuscript.
 
@@
     \subsubsection{Image Dynamic Range and Patch Normalisation}
+    \label{ssec:patch-norm}
     Astronomical images typically show a much higher dynamic range compared to natural images.
@@
 The value of the prior likelihood becomes independent of the total flux contained in the image.
+The prior just regularizes the structure in the image, while the overall intensities are typically well constrained by the Poisson likelihood term.
 
@@
     Self supervised Poisson loss? J-invariance has been shown to work, Grid Search? Calibration on similar data with ground truth?
+    Ground truth based calibration: record prior vs data likelihood on simulated data...
 
@@
 To handle the serialisation of images to the \textit{FITS} data format and to handle world coordinate systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
-For optimization and internal data handling we use \texttt{PyTorch}.
 
@@
 More details of how the model was learned are given in the original publication.
-This model uses the subtraction of the mean of the patch for normalisation.
+This model relies on subtraction of the mean of the patch for normalisation.
 
@@
 We restricted the choice of data to the Galactic Plane between $b=\pm10\deg$ and $\ell = \pm180\deg$ to avoid a bias towards extra-galactic point sources and represent structures of Galactic sources with rich morphology, such as supernova remnants, pulsar winds etc.
-The data set still includes Galactic as well as extra-galactic point sources in the background.
-There is also physical correlation between e.g.
-the very high energy \gammaray and radio range as their emission is produced by the same electron populations.
-
-    In total we extracted \todo{insert number} patches and trained a GMM with 128 components. We used data augmentation by introducing a random shift of the sub-pixel position.
+The dataset still includes Galactic as well as extra-galactic point sources in the background.
+In total we extracted $\approx 6 \cdot 10^5$ patches and trained a GMM with 128 components.
+We used the patch normalisation described in Section~\ref{ssec:patch-norm}.
 
     \subsubsection{JWST Cassiopeia A}
-    The James Webb Space Telescope (JWST) is a large, infrared space telescope launched in late 2021.
+    As a specific prior for the analysis of SNRs we learned a GMM prior from data of the James Webb Space Telescope (JWST).
+    The JWST is a large, infrared space telescope launched in late 2021.
 It delivers image data at very high spatial resolution as well as excellent signal to noise ratio.
@@
     We first converted the image to gray scale using a perceived brightness model \todo{reference skimage...}.
-Then we split the image into $approx 2$ million patches and learned a GMM with 128 mixture components.
+Then we split the image into $\approx 2$ million patches and learned a GMM with 128 mixture components.
+Again we relied on the patch normalisation described in Section~\ref{ssec:patch-norm}.
+Figure~\ref{fig:gmm-eigen-images} shows the weighted sum of the \textit{Eigenimages} of the covariance matrices of the first 32 components of the GMM.
+The patches show a large variety in morphological shapes, including edges, gradients, bright compact spots and more combinations thereof.
 
@@
 
-    \subsubsection{Chandra SNRs}
-    \label{sssec:chandra-snrs}.
+    % \subsubsection{Chandra SNRs}
+    % \label{sssec:chandra-snrs}.
 Because of the limited statistics we did not use any oversampling but kept the pixel Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}.
@@
         but without success, most likely because the native \texttt{Pytorch} support
-        for parallelisation speeds up the standard GMM quite a bit...
+        for parallelization speeds up the standard GMM quite a bit...
         \item Could use a Neural Net for GMM component selection as proposed in \cite{Rosenbaum15}
@@
     \label{subsec:test-datasets}
-
     To evaluate the reconstruction performance of \jolideco and compare it against other methods we defined a set of test source scenarios.
@@
 The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}).
-For the instrument scenario \chandra we convolved the with a narrow Gausssian shaped PSF of width $\sigma=2$~pix.
+For the instrument scenario \chandra we convolved the with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
 For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix and a five times increased effective are.
-        All images are of size $128{\times}128$.
-The dashed red and magenta boxes depict $32{\times}32$ and $64{\times}64$ regions of interest.
-Note that the boxes are displaced to the lower left corner in Case B, and leftwards in Case D.
-        convolved with a diffuse PSF (Gaussian with $\sigma=6$~pix), \todo{add back boxes if we have time}.
+All images are of size $128{\times}128$ pixels.
         }
@@
         D1-5 & A spiral-arm structure surrounded by point sources and a large ring like feature & 9 \\
-
         \hline
@@
         \item \textbf{Pylira}: first we use the \textit{LIRA} method \citep{Esch2004} via the \textit{Pylira} Python wrapper \citep{Donath2022}.
-We rely on the default prior definition and allow the scale for the background to vary.
+We rely on the default prior definition and keep the background norm fixed.
 In total we run the the sampling process for 5000 iterations and use 500 iterations as a \endquote{burn-in} period to allow the MCMC chain to converge.
@@
 
-    We ran the comparison on the whole parameter grid of methods, source scenarios, background levels and instrument scenarios.
-However in the following we only discuss a subset of the results, which we consider the most relevant.
+    We ran the comparison on all combinations of methods, source scenarios, background levels and instrument scenarios.
+However in the following we only discuss the subset of the results, that we consider the most relevant.
 The complete set of results is available at \url{https://jolideco.github.io/jolideco-comparison}.
@@
     %
-    First we compare the performance of methods and prior assumptions on the different source scenarios.
+    First we compare the performance of methods and different prior assumptions on the different source scenarios.
 Figure \ref{fig:comparison-scenarios} shows the results for the selected subset of scenarios A1, B3, C3 and D4.
@@
     On scenario A1 all methods show acceptable to excellent results for the isolated point sources in the upper right of the image.
-This demonstrates all methods take into account the PSF and background model model correctly.
+This demonstrates all methods take into account the PSF and background models correctly.
 The early stopped uniform prior still shows an extension for those cases, because the optimization process has not finished.
@@
 For the counts image we selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandra.
-This corresponds to a pixel size of \qty[mode = text]{0.001}{$\deg$/pixel} \todo{How large is the Chandra PSF compared to this?}.
-
-    \chandra's instrument response varies with the observation offset and energy \todo{reference}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \todo{reference} and the \texttt{simulate\_psf} script.
+This corresponds to an absolute  pixel size of $\approx$\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx8$ pixels for the $38\%$ containment radius of Chandra's PSF.
+\chandra's instrument response varies with the observation offset and energy \todo{reference}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \citep{Davis2012} and the \texttt{simulate\_psf} script.
 As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
@@
 As reference we chose the observation with id 1308.
-
 For \jolideco we used the GMM prior learned on the JWST Cas A image.
-As there is a lot of statistics in the image we used and oversampling factor of 2.
+As there is a lot of statistics in the image we additonally used an oversampling factor of 2.
 For each observation we allowed the background level and position calibration to vary.
@@
 It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
-For this example we chose again a Galactic source with complex morphology: the supernova remnant \textit{Vela Junior}.
-We use 14 years (from 2008 August 4 to 2023 August 4) of \texttt{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
-To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \texttt{PSF0}, \texttt{PSF1}, \texttt{PSF2} and \texttt{PSF3}, as defined by the \fermi collaboration.
+For this example we chose again a Galactic source with complex morphology: the supernova remnant Vela Junior.
+We use 14 years (from 2008 August 4 to 2023 August 4) of \endquote{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
+To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi collaboration.
 We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
@@
 To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Donath2023}.
-To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \cite{Ajello2017}.
-We first fit the model components to the data using \textit{Gammapy}, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on \textit{Vela Junior}.
+To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \citep{Ajello2017}.
+We first fit the model components to the data using \textit{Gammapy}, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on Vela Junior.
 Finally we reduce this model to an image by summing over the energy dimension.
-To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for \textit{Vela Junior} and integrate over the energy dimension of the cube while weighting with the spectral model.
-
+To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for Vela Junior and integrate over the energy dimension of the cube while weighting with the spectral model.
 We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
 Because of the limited statistics we did not use any oversampling but keep the pixel size of the counts image.
+
     Figure~\ref{fig:example-fermi-lat} shows the data, result and residuals.
@@
 \jolideco clearly improves the noise level as well as angular resolution of the data.
-It reveals morphological details consistent with the HESS measurement \todo{Add HESS image or EROSITA for comparison?
-But this is not an analysis...}
-    The calibration of the predicted counts finds different background model norms and positional shifts in order of \todo{add value} for the different event classes.
+The calibration of the predicted counts finds different background model norms and positional shifts in order of $<1$ pixel for the different event classes.
 This way it corrects for systematic errors in the reconstruction of the position.
-
-     To check the quality of the model we compute a map of approximate residual significance defined by:
+One can see that the reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and / or associated with systematic errors.
+The background estimate could be improved by choosing a larger field of view.
+However this would also require a larger effort of modeling nearby sources, which we avoided here.
+
+    To further check the quality of the model we compute a map of approximate residual significance defined by:
 
@@
     Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
-    \todo{To account for the Poisson statistics it would be more precise to compute a TS map, but for an approximate estimation it should  be fine...I have a derivation for this formula }
-
-    As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit \textit{Gaussian} distribution.
+As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit Gaussian distribution.
 More details of the example \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
@@
     \section{Summary \& Outlook}
-    In this work we presented a new method for image deconvolution and denoising in the presence of Poisson noise.
+    In this work we presented a new method for deconvolution and denoising of images contaminated by Poisson noise.
 Using multiple observations of the same sky region the methods reconstructs a single flux image using the approximate MAP estimate of the joint likelihood under a patch based image prior.
-We showed that the methods leads to improved results in variety of scenarios.
+We showed that the methods leads to improved results compared to existing methods in a variety of morphological, signal to noise and instrument scenarios.
 Especially it leads to much improved results for extended source with a size similar to the PSF.
 In this case it allows to reliably recover features, that are well beyond the angular resolution of the instrument.
-
-    We showed that the approach of joining multiple observations leads improved results and allows to maximize the use of existing observational data.
+We also showed that the approach of joining multiple observations leads to improved reconstruction results.
+Including data with lower angular resolution in the \jolideco reconstruction, improved maintaining the correlation structure of pixels across larger distances, while not affecting the overall sharpness of the result negatively.
 
@@
 
-    We consider the \jolideco method as a first step into the territory of \textit{ML inspired} methods for reconstruction of astronomical image data dominated by Poisson noise.
+    We consider the \jolideco method as a first step into the territory of ML inspired methods for reconstruction of astronomical image data dominated by Poisson noise.
 While we achieved already superior results to any other existing method, the \jolideco methods shows large potential for future extension and improvements.
@@
 It is possibly to rely on more general mixture models such as a Student-T or a generalised Gaussian mixture model to model the distribution of patches.
-As shown by \cite{VanDenOord2014} those more flexible functional shapes can account for tails in the distributions and lead to improved results on natural images.
+As shown by \cite{VanDenOord2014} those more flexible functional shapes can account for tails in the patch distributions and lead to improved results on natural images.
 
@@
     To further improve the general expressiveness of the prior \cite{Altekrueger2022} used normalising flows (NF) to model the distribution of patches in the context of computer tomography image reconstruction.
-Just like a GMM the NF allows to evaluate its likelihood function and therfore construct an explicit, approximate \aposteriori probability for optimization.
-\todo{However it is also know that NFs struggle with multi-modality...not sure how this affects the propsoed approach...}
-
+Just like a GMM the NF allows to evaluate its likelihood function and therefor construct an explicit, approximate \aposteriori probability for optimization.
+\todo{However it is also know that NFs struggle with multi-modality...not sure how this affects the proposed approach...}
     Another promising approach to handle prior information for images has been introduced by \citep{Ulyanov2017} with the so called \enquote{Deep Image Prior}.
@@
 The authors showed, that the deep image prior successfully imposes self similarity on the structures in the image.
-As structures in astronomical images often show sell-similarity this is and interesting approach, that could even be combined with the patch prior.
-
-    We also plan to extend the method to deal with the spectral dimension of the data as well. We also plan to extend the method to handle multiple source components at the same time.
-
-    \begin{itemize}
-        \item Extend \jolideco to handle spectral dimension at the same time.
-        \item Extend \jolideco to handle multiple source components at the same time.
-        \item Exclude point sources either via separate component or J-invariance
-    \end{itemize}
-
-    We statistically combined data from existing telescopes to obtain a new \textit{virtual instrument}, with improved angular resolution and sensitivity.
-We invite the community of x-ray and \gammaray astronomers to use the method an combine data for new scientific discoveries, beyond the current angular resolution of existing instruments.
+As structures in astronomical images often show sell-similarity this is an interesting approach, that could even be combined with the patch prior.
+
+    A second category of improvement is generalizing \jolideco to the energy domain to allow for hyperspectral reconstruction.
+For instruments such as \fermi the instrument response varies strongly with energy, while it also has limited energy resolution.
+This introduces correlations between images in neighbouring energy bands.
+Including the energy domain into the reconstruction will allow for handling these correlations and also open up the use-case of merging \xray data in the spectral domain.
+Allowing for both  and improved angular as well as energy resolution.
+
+    \jolideco already allows for handling an independent background component in the model.
+However we plan to extend the method to handle multiple source components at the same time, just separate by their prior definition.
+As shown by \cite{Selig2015} and \citep{Pumpe2018} this allows in principle to separate extended from e.g.
+point like source components.
+
+    Last we plan to work on improving the error estimates.
+
+    We invite the community of x-ray and \gammaray astronomers to use the \jolideco method to combine data for new scientific discoveries, beyond the current angular resolution of existing instruments.
+We also welcome contributions and feedback to the public \jolideco code and validation repositories.
 

### 2023-09-22 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+    \subsubsection{Image Example}
     As a first application example for real data we choose a set of short exposure observations of the SNR \textit{1E~0102.2–7219} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
@@
 For the counts image we selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandra.
-This corresponds to an absolute  pixel size of $\approx$\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx8$ pixels for the $38\%$ containment radius of Chandra's PSF.
+This corresponds to an absolute  pixel size of $\approx$\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of Chandra's PSF.
 \chandra's instrument response varies with the observation offset and energy \todo{reference}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \citep{Davis2012} and the \texttt{simulate\_psf} script.
@@
 For \jolideco we used the GMM prior learned on the JWST Cas A image.
-As there is a lot of statistics in the image we additonally used an oversampling factor of 2.
+As there is a lot of statistics in the image we additionally used an oversampling factor of 2.
 For each observation we allowed the background level and position calibration to vary.
@@
 The full analysis example is available at \url{https://github.com/jolideco/jolideco-chandra-examples}
+
+    \newpage
+    \subsubsection{Flux Profile}
+    \begin{figure*}
+        \script{chandra-e0102-zoom-a.py}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/chandra-e0102-zoom-a.pdf}
+            \caption{
+               Flux and counts profile of the Zoom A example region. The associated $2\sigma$ error band estimated using the bootstrap method is shown transparent in the background.
+            }
+            \label{fig:chandra-e0102-zoom-a}
+        \end{centering}
+    \end{figure*}
+    To get a more qualitative measurement of the improvement we compute a flux profile on the image reconstructed by \jolideco.
+For this we chose a region perpendicular to the filament shown in Zoom A of Figure~\ref{fig:example-chandra}.
+To estimate the errors we use the bootstrapping method.
+For each individual observation we sample from the event list with replacement.
+For each realization of the set of observation we run \jolideco and compute a flux profile on the reconstructed image.
+This way we obtain a distribution of profiles, which we can use to compute an error band.
+The result is shown in Figure~\ref{fig:chandra-e0102-zoom-a}.
+
+    We find that the error is
+
+    We approximately expect the following relation between the width of the counts profile, the PSF and the flux profile:
+
+    \begin{equation}
+        \sigma_{\mathrm{Flux}} = \sqrt{\sigma_{\mathrm{Counts}}^2 - \sigma_{\mathrm{PSF}} ^2}
+    \end{equation}
+
+    With $\sigma_{\mathrm{PSF}} \approx 0.25 \mathrm{arcsec}$ we obtain ..., which is consistent with the values we measured for the profile.
 
@@
     \subsection{\fermi Event Types}
+    As a second example we apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
+The LAT is a pair conversion \gammaray telescope on board of the Fermi satellite.
+It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
+For this example we chose again a Galactic source with complex morphology: the supernova remnant Vela Junior.
+We use 14 years (from 2008 August 4 to 2023 August 4) of \endquote{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
+To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi collaboration.
+We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
+For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \cite{}.
+
+    The \texttt{fermitools} output an energy dependent counts, exposure and PSF cube.
+To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Donath2023}.
+To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \citep{Ajello2017}.
+We first fit the model components to the data using \textit{Gammapy}, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on Vela Junior.
+Finally we reduce this model to an image by summing over the energy dimension.
+To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for Vela Junior and integrate over the energy dimension of the cube while weighting with the spectral model.
+We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
+Because of the limited statistics we did not use any oversampling but keep the pixel size of the counts image.
+
+    Figure~\ref{fig:example-fermi-lat} shows the data, result and residuals.
+The \fermi data is sparse, with very limited statistics.
+\jolideco clearly improves the noise level as well as angular resolution of the data.
+The calibration of the predicted counts finds different background model norms and positional shifts in order of $<1$ pixel for the different event classes.
+This way it corrects for systematic errors in the reconstruction of the position.
+One can see that the reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and / or associated with systematic errors.
+The background estimate could be improved by choosing a larger field of view.
+However this would also require a larger effort of modeling nearby sources, which we avoided here.
+
+    To further check the quality of the model we compute a map of approximate residual significance defined by:
+
+    \begin{equation}
+        \label{eq:approx-sigma}
+        \sigma \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
+    \end{equation}
+
+    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
+As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit Gaussian distribution.
+More details of the example \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
+
       \begin{figure*}
@@
     \end{figure*}
-    As a second example we apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
-The LAT is a pair conversion \gammaray telescope on board of the Fermi satellite.
-It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
-For this example we chose again a Galactic source with complex morphology: the supernova remnant Vela Junior.
-We use 14 years (from 2008 August 4 to 2023 August 4) of \endquote{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
-To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi collaboration.
-We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
-For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \cite{}.
-
-    The \texttt{fermitools} output an energy dependent counts, exposure and PSF cube.
-To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Donath2023}.
-To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \citep{Ajello2017}.
-We first fit the model components to the data using \textit{Gammapy}, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on Vela Junior.
-Finally we reduce this model to an image by summing over the energy dimension.
-To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for Vela Junior and integrate over the energy dimension of the cube while weighting with the spectral model.
-We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
-Because of the limited statistics we did not use any oversampling but keep the pixel size of the counts image.
-
-    Figure~\ref{fig:example-fermi-lat} shows the data, result and residuals.
-The \fermi data is sparse, with very limited statistics.
-\jolideco clearly improves the noise level as well as angular resolution of the data.
-The calibration of the predicted counts finds different background model norms and positional shifts in order of $<1$ pixel for the different event classes.
-This way it corrects for systematic errors in the reconstruction of the position.
-One can see that the reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and / or associated with systematic errors.
-The background estimate could be improved by choosing a larger field of view.
-However this would also require a larger effort of modeling nearby sources, which we avoided here.
-
-    To further check the quality of the model we compute a map of approximate residual significance defined by:
-
-    \begin{equation}
-        \label{eq:approx-sigma}
-        \sigma \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
-    \end{equation}
-
-    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
-As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit Gaussian distribution.
-More details of the example \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
 

### 2023-09-26 src/scripts/chandra-e0102-zoom-a.py
Update profile plot

@@ -57,21 +57,38 @@ def read_profiles(filenames):
     return profiles
 
 
-def measure_fwhm(d):
+def measure_fwhm(d, spline_smoothing=0.0):
     from scipy.interpolate import UnivariateSpline
 
-    x = d["x_normed"].quantity.to_value("arcsec")
+    x = d["x_normed"].to_value("arcsec")
     y = d["mean"]
 
     # create a spline of x and blue-np.max(blue)/2
     y_half = y - np.max(y) / 2
-    spline = UnivariateSpline(x, y_half, s=0)
+    spline = UnivariateSpline(x, y_half, s=spline_smoothing)
     r1, r2 = spline.roots()  # find the roots
-    return r1, r2, np.max(y) / 2.0
+    fwhm = r2 - r1
+    return fwhm, r1, r2, np.max(y) / 2.0
 
 
-def plot_fwhm(ax, d, color):
-    r1, r2, y_max_half = measure_fwhm(d)
+def normalize_profile(profile, smooth_offset=0):
+    """Normalize profile to integral"""
+    profile_data = profile.profile
+
+    x = profile.x_ref
+
+    smoothed = gaussian_filter(profile_data, smooth_offset)
+    offset = x[np.argmax(smoothed)]
+
+    return {
+        "x_normed": x - offset,
+        "mean": profile_data,
+    }
+
+
+def plot_fwhm(ax, fwhm, y_max_half, color, subscript, va="top"):
+    r1 = -fwhm / 2
+    r2 = fwhm / 2
 
     ax.annotate(
         text="",
@@ -80,12 +97,18 @@ def plot_fwhm(ax, d, color):
         color=color,
         arrowprops=dict(arrowstyle="<->", color=color),
     )
+
+    if va == "top":
+        y = y_max_half * 0.98
+    else:
+        y = y_max_half * 1.01
+
     ax.text(
         (r1 + r2) / 2,
-        y_max_half * 0.98,
-        f"$\lambda_{{fwhm}}$={r2 - r1:.2f}",
+        y,
+        f"$\lambda_{{{subscript}}}$",
         ha="center",
-        va="top",
+        va=va,
         color=color,
     )
 
@@ -94,7 +117,7 @@ def get_mean_and_std(profiles, smooth_offset=0):
[…]

### 2023-09-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We show also that the method yields superior reconstruction quality to alternative standard methods such as the Richardson-Lucy method.
-We also the results of the method applied to example data from the \chandra observatory as well as the \fermi.
-In both cases \jolideco improves the angular resolution as well as signal to noise ratio
-        by a factor of 42 \todo{it would be good to summarize the results with a few key numbers...}.
+We also show the results of the method applied to example data from the \chandra observatory as well as the \fermi.
     \end{abstract}
@@
     To maximise the scientific use of available data it is desirable to correct for the instrumental imprint on the data as well as reduce its noise level.
-The process of improving the resolution of an image in post-processing is often called deblurring or deconvolution, as it aims to invert the effect of the data being degraded by a forward convolution through the point spread function (PSF) of the instrument.
-In general this class of problems is categorised as \textit{inverse problems}.
-If there is prior information available on the shape of the PSF, we typically refer to the process more precisely as unblind deconvolution.
+The process of improving the resolution of an image in post-processing is often called \enquote{deblurring} or \enquote{deconvolution}, as it aims to invert the effect of the data being degraded by a forward convolution through the point spread function (PSF) of the instrument.
+In general this class of problems is categorised as \enquote{inverse problems}.
+If there is prior information available on the shape of the PSF, we typically refer to the process more precisely as \enquote{unblind deconvolution}.
 In case of astronomical observations the PSF can for example be estimated empirically from observation of known point sources, such as distant activate galactic nuclei or a model of the PSF can obtained from simulation of the telescope or instrument.
@@
 Most methods rely fundamentally on modeling the image generating process as a linear process.
-Given a known point spread function a prediction of the discrete measured image can be obtained via \textit{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
+Given a known PSF a prediction of the discrete measured image can be obtained via \enquote{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
 However the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function.
-
-    The standard baseline method for image deconvolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \textit{RL}).
+In the following section we give a short overview over those methods.
+
+    The standard baseline method for image deconvolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \enquote{\textit{RL}}).
+Their method involves the
+
+    involves treating the forward convolution by the PSF in a Bayesian and solving the e
+
     The method involves estimating the original image by iteratively convolving the observed image with the PSF and dividing by the result of convolving the estimated image with the transposed PSF.
@@
 Second, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
-This problem was e.g.
-described and studied by \cite{Reeves1995} and \cite{Fish1995}.
-Lastly the RL method does not provided an associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain to measure the significance of specific features found in the reconstructed image.
+This problem was for example described and studied by \cite{Reeves1995} and \cite{Fish1995}.
+Lastly the RL method only provide a \enquote{point estimate} and no associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain for example to measure the significance of specific features found in the reconstructed image.
 
@@
 
-    To address the issue with RL decomposing extended emission structures into groups of point source, multiple additions to the RL method were proposed.
-Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparseness \todo{add reference}.
-The challenge is due to fundamentally contradicting goals: deconvolution favoring point sources will decompose extend structures, while introducing local correlations will lead to less sharp reconstrcution of point sources.
-
-    Multi-scale LIRA prior has been used in image deconvolution to incorporate error estimates and Bayesian sampling.
-This prior has been used in various studies, including those by \cite{Esch2004} and \cite{Connors2011}.
-However, the prior is ad-hoc and lacks physical information or assumptions, limiting its applicability.
-
     Another approach to image deconvolution is joint likelihood RL, which has been shown to be effective in creating a merged image from multiple images \cite{Ingaramo2014}.
@@
 
-    \cite{Pumpe2018} and \cite{Selig2015} approached the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
+    To address the issue with RL decomposing extended emission structures into groups of point source, multiple additions to the RL method were proposed.
+Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparse representations based on \enquote{wavelets} or \enquote{curvelets} \citep{Starck2003}.
+The challenge is rooted in two fundamentally contradicting goals: a deconvolution process that favors point sources will decompose extend structures present in the image, while introducing local correlations between neighbouring pixels will lead to less sharp reconstruction of point sources.
+
+    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstrction and Analysis} (LIRA) method.
+Their key idea was to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
+Instead of a trying to find a single point estimate for the reconstructed image  they also changed to sampling from the posterior distribution, which allowed them to quantify the associated uncertainties.
+However the prior distribution is based on the generic assumption of smoothness and does not encode any \enquote{real world} or physical information on the structures present in the image.
+
+     \cite{Selig2015} and \cite{Pumpe2018} approached the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
 Deconvolution, Denoising and Decomposition (D3PO) and (D4PO).
@@
 
-    Interesting approaches to the problem of deconvolution can of course be found in the field of computer vision.
+    Other interesting approaches to the problem of deconvolution can of course be found in the field of computer vision.
 For example \cite{Zoran2011} build on very similar assumption of local correlation for natural images.
-Instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
+However instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
 This approach can be seen as a form of transfer learning.
 For this they proposed to split training images from representative data sets into small patches of size 8x8~pixels and fit a 64 dimensional Gaussian Mixture Model (GMM) to the distribution of extracted patches.
-Each pixel of the patch
-    is thereby treated as an independent dimension in the model. In total
-    they chose to use $k=200$ Gaussian components.
+Each pixel of the patch  is thereby treated as an independent dimension in the model.
+In total they chose to use $k=200$ Gaussian components.
 To use the GMM in reconstruction they introduce the expected patch likelihood (EPLL).
@@
     \subsection{Some Remarks on Deep Learning Methods}
-    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the \textit{de facto} standard for deblurring and super-resolution of natural images \todo{reference review?}.
+    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images \todo{reference review?}.
 However their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
@@
     In addition to the challenge of obtaining training data, it is known that the PSF of instruments such as \chandra is highly variable.
-It varies with observation conditions and depends e.g.
-on energy as well as offset angle from the pointing direction.
+It varies with observation conditions and depends for example on energy as well as offset angle from the pointing direction.
 To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models.
@@
         \item Different observations of one instrument or telescope at different times and observation conditions.
-E.g., multiple observations of \chandra of the same astrophysical object with different offset angles and exposure times
-        \item Observations from different telescopes, which operate in the same wavelength range. E.g., a \chandra and \xmm observation of the same region in the sky
+For example, multiple observations of \chandra of the same astrophysical object with different offset angles and exposure times
+        \item Observations from different telescopes, which operate in the same wavelength range. For example, a \chandra and \xmm observation of the same region in the sky
         \item A single observation of one telescope with different data quality categories and different associated instrument response functions, such as event classes for \fermi
@@
 Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}}_1)$ look very different from each other and might also look different compared to a given ground truth, if available.
-Both the convolution operation as well as the exitence of noise lead to a loss of information in the data which cannot easily be recovered.
+Both the convolution operation as well as the existence of noise lead to a loss of information in the data which cannot easily be recovered.
 The likelihood surface shows many local, close-by minima.
@@
     When reconstructing images in the context of inverse problems we are operating in a high dimensional parameter space, because each pixel in the image represents an independent parameter in the optimization process.
-By using prior information we can introduce correlations between the parameters, to reduce the \textit{effective} dimensionality of the problem and guide the optimization process towards unique and more stable solutions.
-
-    Using Bayes rule we can estimate the \aposteriori likelihood under a given prior:
+By using prior information we can introduce correlations between the parameters, to reduce the \enquote{effective dimensionality} of the problem and guide the optimization process towards unique and more stable solutions.
+
+    Using Bayes' rule we can estimate the \aposteriori likelihood under a given prior:
     %
@@
 The parameter $\beta$ can be seen as a hyper-parameter, chosen by the user to quantify their belief in the correctness of the chosen prior distribution.
-\todo{this is somewhat dissatisfying...but in practice very common...see e.g.
-any kind of regularisation...if there is enough data cross validation could be used to tune this hyper-parameter}.
-
+The choice of the parameter is optional and for all experiments we show later it is simply fixed to $\beta=1$.
+
+    \newpage
     \subsection{Patch Based Image Prior}
@@
 This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
-The bottom row of Figure~\ref{fig:patches} shows an example of a patch and the same patch represented in the \textit{Eigenbasis} of the covariance matrices of its three most likely GMM components.
-Visually the representation of the of the patch in the covariance \textit{Eigenbasis} works as a denoising of the patch.
+The bottom row of Figure~\ref{fig:patches} shows an example of a patch and the same patch represented in the \enquote{Eigenbasis} of the covariance matrices of its three most likely GMM components.
+Visually the representation of the of the patch in the Eigenbasis of the covariance results in a denoised version of the patch.
 
@@
 This results in patches being grouped only by their pixel to pixel correlation structure and not by total contrast.
-This corresponds the assumption that the structure in the patch is statistically independent of the total flux contained in the patch, which we consider a valid assumption for astronomical images.
+This corresponds to the assumption that the structure in the patch is statistically independent of the total flux contained in the patch, which we consider a valid assumption for astronomical images.
 This also generalizes to the prior likelihood of the whole image described by Equation~\ref{eq:prior-total}.
@@
     % The choice of the image normalisation allows to adjust the contrast of the image
-    % and e.g. enhance low intensity structures, which also enhances the regularising
+    % and for example enhance low intensity structures, which also enhances the regularising
     % effect of the patch prior.
@@
 
-    % There are arguments for $\arcsinh(\mathbf{x})$, see e.g. \cite{Lupton2004}, which we use.
+    % There are arguments for $\arcsinh(\mathbf{x})$, see for example \cite{Lupton2004}, which we use.
 
     \subsubsection{Cycle Spinning}
-    To avoid artifact due to the choice of the grid of overlapping patches we propose three variations:
-
-    \begin{itemize}
-        \item Cycle spinning by randomly shifting the image by a given number of pixels in x and y direction, e.g. used in \cite{Esch2004}
-        \item Sub pixel cycle spinning, by randomly distributing the brightness of a given pixel to a 4 pixel grid \todo{This is something I came up with to allow for point sources to have sub-pixel positions, but I never showed it actually works...}
-        \item A randomly chosen patch grid, such that each pixel is at least covered once.
-The random grid of patches was proposed by \cite{Parameswaran2018}.
-This has the advantage of potentially speeding up the computation as well.
-\todo{It is available in the implementation, but a bit ad hoc, maybe just not mention...}
-    \end{itemize}
+    The evaluation of the patch prior divides the reconstructed image into a fixed grid of overlapping patches.
+To avoid artifacts in the reconstruction due to the fixed position of the grid, we use the method of \enquote{cycle spinning}.
+Before evaluating the patch prior we randomly shift the image $\mathbf{x}$ by a given number of pixels in x and y direction.
+Were the shift is smaller than half the size of a patch.
+The same method has, for example, been used in \cite{Esch2004}.
+We also experimented with cycle spinning by a sub-pixel amount, mostly for the reconstruction of point sources.
+However we later introduced the possibility to reconstruct an upsampled version of $\mathbf{x}$, which made the sub-pixel cycle-spinning mostly redundant.
+
+    A variation of cycle spinning specifically for the patch prior was proposed by \cite{Parameswaran2018}.
+Instead of a regular grid for the patches they proposed to work with a randomised grid of patches, where the center of each patch was randomly shifted, while ensuring that patches still overlap by at least one pixel.
+In doing so they found they could work with a smaller total number of patches, while retaining the same reconstruction quality.
+This improved the computational performance of the method.
+We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction was slightly faster with the same reconstruction quality.
+However for all results shown later in the manuscript we chose the simple cycle spinning with upsampling.
 
@@
 
-    Cross validation is feasible once sufficient data is available, which is e.g. the 
+    Cross validation is feasible once sufficient data is available, which is for example the 
     case for deep \chandra~observations.
@@
     Each measured counts image $\mathbf{D_j}$ is associated with systematic errors.
-This includes e.g.
-the pointing accuracy of the telescopes: when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object might vary in the image between different observations.
+This includes for example the pointing accuracy of the telescopes: when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object might vary in the image between different observations.
 The process of correcting for these inaccuracies is called \textit{astrometry} and a standard procedure in for example \chandra data analysis.
@@
 Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019} allow for solving these kind of high dimensional modeling problems, by using back-propagation and adapted optimization methods for high dimensional models such as stochastic gradient decent.
+The latter is also applicable in our case, as we work with multiple observations at the same time, where a subset of those represents a \enquote{batch} in terms of ML.
 
     We implemented the \jolideco method as an independent Python package, based on \texttt{PyTorch} as optimization back-end.
-We tried to define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of the patch normalisation, the choice of GMM models, optimization methods and serialisation formats for the reconstruction results as well as corresponding diagnostic information such as the trace of the posterior and prior likelihood values.
-We hope that this simplifies the future improvement and extension of the package.
+We tried to define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of the patch normalisation, the choice of GMM models, optimization methods and serialisation formats for the reconstruction results as well as corresponding diagnostic information, such as the trace of the posterior and prior likelihood values.
+We hope that this simplifies the future improvement and extension of the package as well as the adoption by the astromical community.
 The package is available at \url{https://github.com/jolideco/jolideco}.
@@
     We also use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
-To learn the Gaussian Mixture Models from patches we use the standard implementation provided in the \texttt{Scikit-Learn}~\citep{Skimage2014} package.
+To learn the Gaussian Mixture Models from patches we use the standard implementation provided in the \texttt{Scikit-Learn}~\citep{scikit-learn} package.
 To handle the serialisation of images to the \textit{FITS} data format and to handle world coordinate systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
@@
 To limit the data reduction effort we relied on a promotional image of the SNR \textit{Cassiopeia A}\footnote{We downloaded the full resolution (4k)  PNG image from \url{https://webbtelescope.org/contents/media/images/2023/121/01GWQBBY77MHGFV3M3N63KDCEJ}}.
-    We first converted the image to gray scale using a perceived brightness model \todo{reference skimage...}.
+    We first converted the image to gray scale using a perceived brightness model \citep{scikit-image}.
 Then we split the image into $\approx 2$ million patches and learned a GMM with 128 mixture components.
@@
 In total we extracted \todo{insert number} patches and used those to train a GMM with 32 components.
-The prior is useful in a scenario were the direction of the jet known from e.g.
-previous radio observations.
+The prior is useful in a scenario were the direction of the jet known from for example previous radio observations.
 
@@
     Maximising the \aposteriori likelihood defined Eq.\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
+
     To improve the convergence rate of the optimization process we employ the following optimization strategy: the optimization strategy begins with the optimizer viewing $\log{\mathbf{x}}$, and the first step involves running a rough estimate using a uniform prior.
@@
 In the lower left of the image the point sources become fainter and move closer, challenging all methods in succeeding to separate those as independent sources.
-The uniform prior optimized \endquote{to end} shows excellent results, still separating the sources.
-
-    For scenario B3 all method recover the point sources and the central extend source.
+The uniform prior optimized \endquote{to end} shows good results, still separating the sources.
+All other methods cannot fully resolve weak and close by point sources.
+\jolideco with th e
+
+    For scenario B3 all methods recover the point sources well.
 However large difference can be observed in the reconstruction of the Gaussian shaped extended sources.
-As expected the uniform prior decompose the emission into many point sources, neglecting the spatial correlation between them.
-\textbf{Pylira} shows slightly improved results with the gaps between the bright emission peeks being more filled, however still lacks a convincing result into reconstructing the source as a single object.
+As expected, the uniform prior assumption lets the emission decomose into many point sources, neglecting the spatial correlation between them.
+\textbf{Pylira} shows slightly improved results with the gaps between the bright emission peeks being more filled, however still lacks a convincing result of reconstructing the source as a single object.
 The \jolideco method with the patch priors shows the best results both visually as well as measured by the SSI.
 The GLEAM v0.1 patch prior reconstructs the sources almost perfectly, visually almost indistinguishable from the ground truth.
-The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a visible extension in the surrounding point sources.
+The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a more visible extension in the surrounding point sources.
 
@@
 The best results are achieved by the patch priors, which reconstruct a plausible extended source with approximately uniform brightness.
-
-    On the jet like features the patch prior does not show a preferred direction or bias in reconstruction and preserves the linear correlation between the pixels.
-
-    \jolideco shows excellent performance of a variety of morphological shapes. 
+The jet like features in the same scenario are decomposed into a \enquote{thread} of point sources by the uniform prior and LIRA method.
+The patch prior achieves a much more plausible reconstruction with almost uniform brightness for the linear structures.
+We also note that the patch prior does not show a preferred direction or bias in reconstruction, that is possibly encoded in the training data.
+
+    The last scenario D4 shows a similar result as before: the uniform prior and LIRA decompose the spiral and ring like structure in the image.
+The patch priors reconstruct a visually much more plausible flux image.
+
+    In summary \jolideco shows excellent performance of a variety of morphological shapes.
 it converges to the reference solution for very high signal to noise.
-We find the prior learned from GLEAM data to be a very good compromise between teh ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
+We find the prior learned from GLEAM data to be a very good compromise between the ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
 
@@
     %
-    As a second experiment we explored the dependency of the results on the background level and signal strength.
+    As a second experiment we explore the dependency of the results on the background level and signal strength.
 Figure~\ref{fig:comparison-signal-noise} shows the results for the \jolideco method with the GLEAM prior in the scenario D1-5.
-The background level was varied between
-    $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
-
+The background level varies between $\lambda_{Bkg}= 0.01, 0.1$ and \qty[mode = text]{1}{counts/pixel}.
 As expected the reconstruction quality improves with signal strength.
@@
     We observe the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
-    \todo{this is somewhat surprising as visually the signal can be seen in the data...at least for D2 and D3}.
-    \todo{We should give a single number for the S/N, how to compute? Per source, like spiral ring and point sources...}
 
@@
     Using just the data from the \enquote{XMM} scenario results in lower quality reconstructions, due to the lower angular resolution.
-However we find that the spiral arm structure is reconstructed at all levels of signal strength, even when barely visible from the data by eye \todo{check saturation of the color map...}.
-The ring structure is sharpened considerably in all cases.
-The points source left and right to the spiral arm structure cannot be separated as individual point sources.
-This remains for all scenarios D1-5, as the brightness of the point sources remains the same.
-This is an inherent limitation of the method.
-\todo{how far are those apart compared to the PSF?
-Hoes does this compare to the point scenario with XMM?}.
+However we find that the spiral arm structure is reconstructed at all levels of signal strength, even when barely visible from the data by eye.
+The ring structure is sharpened considerably in all cases as well.
+The near-by point sources left and right to the spiral arm structure cannot be separated as individual point sources, but still appear with improved
+    signal-to-noise ratio. This is an inherent limitation of the method. \todo{how far are those apart compared to the PSF? Hoes does this compare to the point scenario with XMM?}
 
@@
 When comparing the D5 scenario we see that the \enquote{Chandra} reconstruction shows a very good reconstruction of the spiral structure but still shows speckles in the surrounding ring.
-The latter suggests that the prior is not strong enough to guide the pixel to pixel correlations in the case of high signal strength.
+The latter suggests that the prior is not strong enough to maintain the pixel to pixel correlations in the case of high signal strength.
 The strength of the prior could be increased with the $\beta$ parameter, but for this study we did not tweak individual parameters, but just used the default configuration.
@@
 This confirms the results from \cite{Ingaramo2014}, where the authors found that combining multiple measurements for deconvolution with RL to be a \textquote{general tool for combining images with complementary strengths}.
-\todo{not understood: reconstruction of point source becomes worse as spiral becomes brighter.
-Maybe because the strong signal dominates the likelihood function?
-Not sure how to improve this...is it image dynamics?}
 
@@
 For the counts image we selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandra.
-This corresponds to an absolute  pixel size of $\approx$\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of Chandra's PSF.
+This corresponds to an absolute  pixel size of $\approx$~\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of Chandra's PSF.
 \chandra's instrument response varies with the observation offset and energy \todo{reference}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \citep{Davis2012} and the \texttt{simulate\_psf} script.
@@
 As reference for the positional shift we also used the observation with the ID 1308.
-
-    Figure~\ref{fig:example-chandra} shows the final result. \jolideco clearly improves both the angular resolution as well as reduces the noise of the counts image.
+Figure~\ref{fig:example-chandra} shows the final result.
+\jolideco clearly improves both the angular resolution as well as reduces the noise of the counts image.
 
@@
 
-    \textbf{Zoom B} shows the region around the central compact object of the SNR \cite{Vogt2018}.
+    \textbf{Zoom B} shows the region around the central compact object of the SNR \citep{Vogt2018}.
 While the emission is barely visible in the counts image it clearly sticks out above the background in the image reconstructed by \jolideco.
 The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
-As shown in Section~\ref{subsec:methods} for scenario A, the apparent size of the points source becomes smaller if the source becomes brighter.
+As shown in Section~\ref{subsec:methods} for scenario A, the apparent size of the point source becomes smaller if the source becomes brighter.
 
@@
 We saw the detection efficiency of \chandra changed between the observations as well as that sub-structure in the remnant expands over time.
-Both effects are previously known and have been reported e.g.
-in \cite{Xi2019} and \cite{}.
+Both effects are previously known and have been reported for example in \cite{Xi2019} and \cite{}.
 Despite the clear improvement in spatial resolution the proper motion of structures in the image might limit the quality of the result.
-The full analysis example is available at \url{https://github.com/jolideco/jolideco-chandra-examples}
-
-    \newpage
-    \subsubsection{Flux Profile}
+The full analysis example is available at \url{https://github.com/jolideco/jolideco-chandra-examples}.
+
     \begin{figure*}
@@
             \caption{
-               Flux and counts profile of the Zoom A example region. The associated $2\sigma$ error band estimated using the bootstrap method is shown transparent in the background.
+                The left panel shows the flux and counts profile of the region illustrated in the right panel.
+The associated $2\sigma$ error band estimated using the bootstrap method is shown transparent in the background.
             }
@@
     \end{figure*}
-    To get a more qualitative measurement of the improvement we compute a flux profile on the image reconstructed by \jolideco.
+
+    \subsubsection{Flux Profile}
+    To get a more qualitative measurement of the improvement we compute a flux profile on the image of E0102 reconstructed by \jolideco.
 For this we chose a region perpendicular to the filament shown in Zoom A of Figure~\ref{fig:example-chandra}.
@@
 This way we obtain a distribution of profiles, which we can use to compute an error band.
+For comparison we also compute the profiles and associated errors directly on the stacked bootstrapped images of counts.
 The result is shown in Figure~\ref{fig:chandra-e0102-zoom-a}.
 
-    We find that the error is
-
-    We approximately expect the following relation between the width of the counts profile, the PSF and the flux profile:
+    The profile computed from the images reconstructed with \jolideco has a much smaller noise level and the peak is much more pronounced.
+By fitting the profile with a univariate spline and finding its roots we measure the full width half maximum of the curves.
+We find $\sigma=$ and $\sigma=$.
+Assuming that the PSF and the shape of peak of the profile are approximately Gaussian a we expect the following relation between the width of the counts profile, the PSF and the flux profile:
 
@@
 However we plan to extend the method to handle multiple source components at the same time, just separate by their prior definition.
-As shown by \cite{Selig2015} and \citep{Pumpe2018} this allows in principle to separate extended from e.g.
-point like source components.
+As shown by \cite{Selig2015} and \citep{Pumpe2018} this allows in principle to separate extended from for example point like source components.
 

### 2023-09-26 src/scripts/chandra-e0102-zoom-a.py
Update profile plot

@@ -201,11 +201,11 @@ fwhms_counts = np.array(
 )
 
 ax.text(
-    s=f"$\lambda_J={fwhms_counts.mean():.2f}\pm{fwhms_counts.std():.2f}$ arcsec",
-    x=0.8,
+    s=f"$\lambda_C={fwhms_counts.mean():.2f}\pm{fwhms_counts.std():.2f}$ arcsec",
+    x=0.59,
     y=0.8,
     transform=ax.transAxes,
-    ha="center",
+    ha="left",
     va="top",
     color=config.COLORS["viridis-2"],
 )
@@ -234,10 +234,10 @@ fwhms_jolideco = np.array(
 
 ax.text(
     s=f"$\lambda_J={fwhms_jolideco.mean():.2f}\pm{fwhms_jolideco.std():.2f}$ arcsec",
-    x=0.79,
+    x=0.59,
     y=0.9,
     transform=ax.transAxes,
-    ha="center",
+    ha="left",
     va="top",
     color=config.COLORS["viridis-0"],
 )
@@ -259,7 +259,7 @@ ax.set_ylabel("Normalized Flux")
 ax.set_xlabel("Offset / arcsec")
 ax.ticklabel_format(axis="y", style="sci", scilimits=(0, 0))
 ax.set_ylim(0, 1.8e-2)
-ax.set_xlim(-1.6, 1.6)
+ax.set_xlim(-1.4, 1.4)
 ax.legend(loc="upper left", frameon=False, fontsize=9)
 
 plt.savefig(paths.figures / "chandra-e0102-zoom-a.pdf", facecolor="w", dpi=300)

### 2023-09-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             \caption{
-                The left panel shows the flux and counts profile of the region illustrated in the right panel.
-The associated $2\sigma$ error band estimated using the bootstrap method is shown transparent in the background.
+                The left panel shows the deconvolved flux and counts profile of the region illustrated in the right panel.
+The associated $3\sigma$ error band is shown transparent in the background.
+Both profiles are normalized such that they integrate to unity and are aligned such that the position of their peak coincides.
             }

### 2023-10-04 src/scripts/example-chandra.py
Add position measure for PS in Zoom B

@@ -6,6 +6,7 @@ from astropy import units as u
 from astropy.coordinates import SkyCoord
 from astropy.io import fits
 from astropy.visualization import simple_norm
+from gammapy.estimators.utils import find_peaks
 from gammapy.maps import Map
 from regions import RectangleSkyRegion
 
@@ -252,6 +253,14 @@ draw_zoom(
     title="B",
     norm=norm_flux,
 )
+
+cutout_zoom_b = flux.cutout(position=center, width=width)
+
+peaks = find_peaks(cutout_zoom_b, threshold=0.5)
+position = SkyCoord(peaks["ra"], peaks["dec"], unit="deg", frame="icrs")
+
+print(position.to_string("hmsdms"))
+
 
 # inset 3
 center = SkyCoord("16.003d", "-72.035d")

### 2023-10-04 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    The standard baseline method for image deconvolution was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \enquote{\textit{RL}}).
-Their method involves the
-
-    involves treating the forward convolution by the PSF in a Bayesian and solving the e
-
-    The method involves estimating the original image by iteratively convolving the observed image with the PSF and dividing by the result of convolving the estimated image with the transposed PSF.
-The iterations continue until the estimated image converges to a satisfactory solution.
+    The standard baseline method for image deconvolution in the presence of Poisson noise was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \enquote{\textit{RL}}).
+The method involves estimating the reconstructed image by an iterative procedure that converges to a maximum likelihood solution of the problem.
 
@@
 
-    To address the question of when to stop the RL iteration \cite{Reeves1995} proposed to use cross validation.
-The authors of \citep{Bi1994} proposed a bootstrapped based assessment of the significance of reconstructed image as as a stopping rule for RL.
-
-    Another approach to image deconvolution is joint likelihood RL, which has been shown to be effective in creating a merged image from multiple images \cite{Ingaramo2014}.
-In this approach, RL takes the best out of each image and merges them to create a more accurate representation of the object.
-
     To address the issue with RL decomposing extended emission structures into groups of point source, multiple additions to the RL method were proposed.
@@
 
+    An interesting modification of the standard RL method has been proposed by \cite{Ingaramo2014}.
+They showed that RL can be effective in creating a merged image from multiple observations.
+They also observed that RL would take the best visual properties out of an each image and merged them to create a more accurate estimate of the ground truth.
+
     \cite{Selig2015} and \cite{Pumpe2018} approached the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
-Deconvolution, Denoising and Decomposition (D3PO) and (D4PO).
-
-    Recently, image deconvolution using physical assumptions and decomposition into point and diffuse flux in 3D/4D has gained attention.
-proposed priors based on physical assumptions, which have been shown to work well for large-scale emission.
-However, the smoothness assumption in these methods can lead to artifacts in the galactic plane.
+Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they were able to deconvolve an astrophysical observation as well as decomposing it into point-like and diffuse emission components.
+While the method has worked well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it seemed to fail for smaller extended emission structures such as mrophological details of extended sources.
 
@@
 However instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
-This approach can be seen as a form of transfer learning.
-For this they proposed to split training images from representative data sets into small patches of size 8x8~pixels and fit a 64 dimensional Gaussian Mixture Model (GMM) to the distribution of extracted patches.
-Each pixel of the patch  is thereby treated as an independent dimension in the model.
-In total they chose to use $k=200$ Gaussian components.
-To use the GMM in reconstruction they introduce the expected patch likelihood (EPLL).
+For this they proposed to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) modeling the distribution of extracted patches.
+To use the GMM in reconstruction they introduced the concept of expected patch likelihood (EPLL).
 They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
@@
     \subsection{Some Remarks on Deep Learning Methods}
-    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images \todo{reference review?}.
+    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images.
 However their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
@@
 
-    To account for the possibility of different datasets having a different number of pixels we divide by $N$ (\todo{Does this need more justification...is it reasonable?}).
+    To account for the possibility of different datasets having a different number of pixels we divide by $N$.
 By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
@@
 
-    \newpage
     \subsection{Patch Based Image Prior}
@@
 This would require a continuous representation or interpolation between GMM components.
-We propose ideas to work around this assumption later in the outlook of this manuscript.
 
@@
 
-    \subsection{Choice and Tuning of Hyperparameters}
-    \subsubsection{Cross Validation}
-    Cross validation (CV) is an established method for model selection in statistics and machine learning to prevent a model from overfitting to the training data.
+    % \subsection{Choice and Tuning of Hyperparameters}
+    % \subsubsection{Cross Validation}
+    % Cross validation (CV) is an established method for model selection in statistics and machine learning to prevent a model from overfitting to the training data.
 To perform CV the available data is slit into a \enquote{training} and \enquote{validation} dataset.
@@
 
-    Cross validation is feasible once sufficient data is available, which is for example the 
-    case for deep \chandra~observations.
-
-    CV as stopping rule for RL was proposed by \cite{Reeves1995}...
-
-    \subsubsection{Other Approaches}
-
-    Self supervised Poisson loss? J-invariance has been shown to work, Grid Search? Calibration on similar data with ground truth?
-    Ground truth based calibration: record prior vs data likelihood on simulated data...
+    % Cross validation is feasible once sufficient data is available, which is for example the 
+    % case for deep \chandra~observations.
+
+    % CV as stopping rule for RL was proposed by \cite{Reeves1995}...
+
+    % \subsubsection{Other Approaches}
+
+    % Self supervised Poisson loss? J-invariance has been shown to work, Grid Search? Calibration on similar data with ground truth?
+    % Ground truth based calibration: record prior vs data likelihood on simulated data...
 
@@
 
-    % \subsubsection{Chandra SNRs}
-    % \label{sssec:chandra-snrs}.
-Because of the limited statistics we did not use any oversampling but kept the pixel Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}.
+    \subsubsection{Chandra SNRs}
+    \label{sssec:chandra-snrs}.
+Because of the limited statistics we did not use any oversampling but kept the pixel Astrophysical processes forming the morphological structures are typically self-similar.
 Structures appear on multiple angular scales.
@@
         \item Could use a Neural Net for GMM component selection as proposed in \cite{Rosenbaum15}
-        \item GPU support via \texttt{Pytorch}
+        \item GPU support via Pytorch
     \end{itemize}
@@
     \begin{itemize}
-        \item \textbf{Pylira}: first we use the \textit{LIRA} method \citep{Esch2004} via the \textit{Pylira} Python wrapper \citep{Donath2022}.
+        \item \textbf{Pylira}: first we use the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
 We rely on the default prior definition and keep the background norm fixed.
@@
 In the lower left of the image the point sources become fainter and move closer, challenging all methods in succeeding to separate those as independent sources.
-The uniform prior optimized \endquote{to end} shows good results, still separating the sources.
+The uniform prior optimized \enquote{to end} shows good results, still separating the sources.
 All other methods cannot fully resolve weak and close by point sources.
-\jolideco with th e
 
@@
 However large difference can be observed in the reconstruction of the Gaussian shaped extended sources.
-As expected, the uniform prior assumption lets the emission decomose into many point sources, neglecting the spatial correlation between them.
-\textbf{Pylira} shows slightly improved results with the gaps between the bright emission peeks being more filled, however still lacks a convincing result of reconstructing the source as a single object.
+As expected, the uniform prior assumption lets the emission decompose into many point sources, neglecting the spatial correlation between them.
+Pylira shows slightly improved results with the gaps between the bright emission peeks being more filled, however still lacks a convincing result of reconstructing the source as a single object.
 The \jolideco method with the patch priors shows the best results both visually as well as measured by the SSI.
@@
 The uniform prior with 1000 iterations decomposes the source into a grid of almost equidistant point sources resembling only the outer boundary of the original source.
-\textit{Pylira} shows a similar tendency but already improves the reconstruction of the extended source by leaving more emission in between the bright emission spots.
+Pylira shows a similar tendency but already improves the reconstruction of the extended source by leaving more emission in between the bright emission spots.
 The best results are achieved by the patch priors, which reconstruct a plausible extended source with approximately uniform brightness.
@@
     \section{Application Examples}
-    \subsection{Deep \chandra Observation}
-
+    %
     \begin{figure*}
@@
     \end{figure*}
-
+    %
+    \subsection{Deep \chandra Observation}
     \subsubsection{Image Example}
@@
 This corresponds to an absolute  pixel size of $\approx$~\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of Chandra's PSF.
-\chandra's instrument response varies with the observation offset and energy \todo{reference}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \citep{Davis2012} and the \texttt{simulate\_psf} script.
+\chandra's instrument response varies with the observation offset and energy \citep{ChandraPOG2022}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \citep{Davis2012} and the \texttt{simulate\_psf} script.
 As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
@@
 
-    \textbf{Zoom B} shows the region around the central compact object of the SNR \citep{Vogt2018}.
+    \textbf{Zoom B} shows the region around the central compact object of the SNR.
 While the emission is barely visible in the counts image it clearly sticks out above the background in the image reconstructed by \jolideco.
 The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
-As shown in Section~\ref{subsec:methods} for scenario A, the apparent size of the point source becomes smaller if the source becomes brighter.
+We note that, as shown in Section~\ref{subsec:methods} for scenario A, the apparent size of the point source was smaller if the source was brighter.
+We estimated the position of point source by finding the brightest pixel in the map.
+We obtained $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
 
@@
 We saw the detection efficiency of \chandra changed between the observations as well as that sub-structure in the remnant expands over time.
-Both effects are previously known and have been reported for example in \cite{Xi2019} and \cite{}.
+Both effects are previously known and have been reported for example in \cite{Xi2019}.
 Despite the clear improvement in spatial resolution the proper motion of structures in the image might limit the quality of the result.
@@
 By fitting the profile with a univariate spline and finding its roots we measure the full width half maximum of the curves.
-We find $\sigma=$ and $\sigma=$.
+We find $\lambda_J=0.56\pm0.03$ for the \jolideco profile and $\lambda_C=0.63\pm0.09$ for the profile computed on the counts image.
 Assuming that the PSF and the shape of peak of the profile are approximately Gaussian a we expect the following relation between the width of the counts profile, the PSF and the flux profile:
@@
     \begin{equation}
-        \sigma_{\mathrm{Flux}} = \sqrt{\sigma_{\mathrm{Counts}}^2 - \sigma_{\mathrm{PSF}} ^2}
-    \end{equation}
-
-    With $\sigma_{\mathrm{PSF}} \approx 0.25 \mathrm{arcsec}$ we obtain ..., which is consistent with the values we measured for the profile.
+        \lambda_{J} = \sqrt{\lambda_C^2 - \lambda_{\mathrm{PSF}}^2}
+    \end{equation}
+
+    With $\lambda_{\mathrm{PSF}} \approx 0.25 \mathrm{arcsec}$ \footnote{The 38\% containment radius of the Chandra PSF is $\sigma_{39}=2$ native pixels.
+This corresponds to  see e.g.
+\url{https://space.mit.edu/cxc/marx/tests/PSF.html}}
+    we obtain ..., which is consistent with the values we measured for the profile.
+The profile computed from the images reconstructed with \jolideco show both a smaller width of the profile as well as a much smaller error.
 
@@
 
-    The \texttt{fermitools} output an energy dependent counts, exposure and PSF cube.
+    The \texttt{fermitools} produce an energy dependent counts, exposure and PSF cube.
 To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Donath2023}.
@@
 
-    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
-As a check we compute a map of residuals based on the predicted counts, the resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit Gaussian distribution.
+    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma=5$ pixels. The result is shown in the most right panel of Fig.~\ref{fig:example-fermi-lat}. The image
+    shows no systematic effects and a spatially homogeneous distribution of the residual noise.
+The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit Gaussian distribution, as expected for a good model of the emission.
 More details of the example \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
@@
 More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.
-\todo{Move color bar to top and make images larger}
             }

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \begin{figure*}
-        \script{model-illustration.py}
         \begin{centering}
@@
             \label{fig:model-illustration}
+            \script{model-illustration.py}
         \end{centering}
@@
  \begin{figure}
-        \script{patches.py}
         \begin{centering}
@@
             \label{fig:patches}
+            \script{patches.py}
         \end{centering}
@@
     \begin{figure}
-        \script{gmm-eigen-images.py}
         \begin{centering}
@@
             \label{fig:gmm-eigen-images}
+            \script{gmm-eigen-images.py}
         \end{centering}
@@
     \begin{figure*}
-        \centering\includegraphics{figures/scenarios.pdf}
+        \centering\includegraphics{figures/comparison-scenarios.pdf}
         \caption{Illustration of the expected counts for the different source and instrument scenarios we used to make test datasets.
@@
         \label{fig:scenarios}
+        \script{comparison-scenarios.py}
     \end{figure*}
@@
     \begin{figure*}
-        \script{comparison-scenarios.py}
         \begin{centering}
@@
             \label{fig:comparison-scenarios}
+            \script{comparison-scenarios.py}
         \end{centering}
@@
     \begin{figure*}
-        \script{comparison-signal-noise.py}
         \begin{centering}
@@
             \label{fig:comparison-signal-noise}
+            \script{comparison-signal-noise.py}
         \end{centering}
@@
     \begin{figure*}
-        \script{comparison-instruments.py}
         \begin{centering}
@@
             \label{fig:comparison-instruments}
+            \script{comparison-instruments.py}
         \end{centering}
@@
     \begin{figure*}
-        \script{example-chandra.py}
         \begin{centering}
@@
             \label{fig:example-chandra}
+            \script{example-chandra.py}
         \end{centering}
@@
     \begin{figure*}
-        \script{chandra-e0102-zoom-a.py}
         \begin{centering}
@@
             \label{fig:chandra-e0102-zoom-a}
+            \script{chandra-e0102-zoom-a.py}
         \end{centering}
@@
       \begin{figure*}
-        \script{example-fermi-lat.py}
         \begin{centering}
@@
             \label{fig:example-fermi-lat}
+            \script{example-fermi-lat.py}
         \end{centering}
@@
 Just like a GMM the NF allows to evaluate its likelihood function and therefor construct an explicit, approximate \aposteriori probability for optimization.
-\todo{However it is also know that NFs struggle with multi-modality...not sure how this affects the proposed approach...}
     Another promising approach to handle prior information for images has been introduced by \citep{Ulyanov2017} with the so called \enquote{Deep Image Prior}.

### 2023-10-06 src/scripts/scenarios.py
Remove old scenarios.py

@@ -1,117 +1,0 @@
-import config
-import numpy as np
-import paths
-from astropy.io import fits
-from astropy.visualization import simple_norm
-from matplotlib import pyplot as plt
-from matplotlib.gridspec import GridSpec
-
-asinh_a = 0.01
-
-scenario_titles = {
-    "Scenario A": {
-        "name": "point1",
-        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
-    },
-    "Scenario B": {
-        "name": "aster3",
-        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
-    },
-    "Scenario C": {
-        "name": "disk3",
-        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
-    },
-    "Scenario D": {
-        "name": "spiral4",
-        "plot": {"max_cut": 200.0, "asinh_a": asinh_a},
-    },
-}
-
-
-instrument_titles = {
-    "ground truth": "Ground\n  Truth",
-    "chandra": '"Chandra"',
-    "xmm": '"XMM"',
-}
-
-figsize = config.FigureSizeAA(aspect_ratio=1.32, width_aa="two-column")
-
-upsampling_factor = 2
-DATA_SHAPE = (128, 128)
-
-gridspec_kw = {
-    "left": 0.14,
-    "right": 0.98,
-    "bottom": 0.12,
-    "top": 0.95,
-    "wspace": 0.05,
-    "hspace": 0.02,
-}
-
-fig, axes = plt.subplots(
-    nrows=len(instrument_titles),
-    ncols=len(scenario_titles),
-    figsize=figsize.inch,
-    gridspec_kw=gridspec_kw,
-)
-
-
-def add_cbar(im, ax, fig, label=""):
-    """Add cbar to a given axis and figure"""
-    bbox = ax.get_position()
-    loleft = bbox.corners()[0]
-    rect = [loleft[0], loleft[1] - 0.04, bbox.width, 0.02]
-    cax = fig.add_axes(rect)
-    cbar = fig.colorbar(im, cax=cax, orientation="horizontal")
-    cbar.set_label(label, size=9)
-    cbar.set_ticks([0, 10, 100])
-    cax.tick_params(labelsize=9)
-
-
-def read_flux_ref(instrument, scenario):
-    """Reda reference flux"""
-    path = paths.jolideco_repo_comparison / "data"
-
-    if instrument == "ground truth":
[…]

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 For analysis of Galactic sources with complex morphology and typically radially symmetric features such as supernova remnants (SNRs) we learned a prior from images of the bright \chandra SNRs \textit{Cas A} and \textit{G292.0+01.8}.
-In total we extracted \todo{insert number} patches and learned a GMM with 128 components.
+In total we extracted $\approx 10^6$ patches and learned a GMM with 128 components.
 
@@
 The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021} and following the instructions in the \texttt{README.md} file in the same repository.
-All data is available for download from Zenodo \todo{how do we do this exactly...?} or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \jolideco GitHub organisation\footnote{\url{https://github.com/jolideco}}.
+All data is available for download from Zenodo or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \jolideco GitHub organisation\footnote{\url{https://github.com/jolideco}}.
 For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow  available at\footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.

### 2023-10-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 This is for comparison to the original method and the method used on \cite{Bouman2016}.
-We use maximum image norm with the maximum values defined by the ground truth \todo{is this fair?}.
+We use a maximum image norm with the maximum values defined by the ground truth.
+        \footnote{This is not completely fair, as it requires knowledge of the brightest expected pixel in $\mathbf{x}$, however in practice this information could be estimated from the brightest pixel in the data and the shape of the PSF.}
     \end{itemize}
@@
 This includes both the variation of the background as well as signal strength.
-\todo{sensitivity scales as approx signal / sqrt(Bkg)?
-so what what is the implication?
-} Visually the method converges to the ground truth for very high signal-to-noise ratio.
+Visually the method converges to the ground truth for very high signal-to-noise ratio.
 Once the signal strength becomes very large there is no dependency of the result on the background level anymore.

### 2023-10-26 src/scripts/chandra-obs-table.py
Add chandra obs table writing

@@ -1,0 +1,40 @@
+import logging
+from io import StringIO
+
+import paths
+from astropy import units as u
+from astropy.table import Table
+from dateutil import parser
+
+logging.basicConfig(level=logging.INFO)
+
+log = logging.getLogger(__name__)
+OBS_ID_REF = 8365
+
+colnames = ["Obs ID", "Exposure", "Start Date"]
+obs_table = Table(names=colnames, dtype=[int, "f8", "S10"], units=["", "ks", ""])
+
+path = paths.jolideco_repo_chandra_example / "data"
+filenames = sorted(path.glob("*/oif.fits"))
+
+for filename in filenames:
+    obs_id = filename.parent.name
+    table = Table.read(filename)
+    exposure = table.meta["EXPOSURE"] * u.s
+    date = parser.parse(table.meta["DATE-OBS"])
+    row = [obs_id, round(exposure.to_value("ks"), 1), date.strftime("%m/%d/%Y")]
+    obs_table.add_row(row)
+
+
+content_io = StringIO()
+obs_table.write(content_io, format="latex", overwrite=True)
+
+content = content_io.getvalue()
+lines = content.split("\n")
+lines = lines[2:-3]
+content = "\n".join(lines)
+
+filename = paths.output / "chandra-obs-table.tex"
+
+with filename.open("w") as f:
+    f.write(content)

### 2023-10-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\vlk}[1]{{\color{blue} [VLK: #1]}}
-
+\newcommand{\as}[1]{{\color{purple} [AS: #1]}}
 % Begin!
@@
     \author[0000-0000-0000-0000]{David van Dyk}
+    \author[0000-0003-4428-7835]{Douglas Burke}
 
@@
 If there is prior information available on the shape of the PSF, we typically refer to the process more precisely as \enquote{unblind deconvolution}.
-In case of astronomical observations the PSF can for example be estimated empirically from observation of known point sources, such as distant activate galactic nuclei or a model of the PSF can obtained from simulation of the telescope or instrument.
+In case of astronomical observations the PSF can for example be estimated empirically from observation of known point sources, such as distant \as{I would say stars instead of AGN - in optical and even in X-rays telescopes AGN are resolved, so not point sources} activate galactic nuclei or a model of the PSF can obtained from simulation of the telescope or instrument.
+
+\as{You may want to add a short para or just a sentance saying that X-ray and gamma-ray images are the Poisson type images containing low number of counts in each image pixel etc..
+- this is to link to the next subsection which is specific to Poisson noise?}
 
@@
 Given a known PSF a prediction of the discrete measured image can be obtained via \enquote{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
-However the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function.
+However, the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function.
 In the following section we give a short overview over those methods.
@@
 
-    However in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion for when to stop the optimization process.
+    However, in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion for when to stop the optimization process.
 Usually the iteration is stopped when the reconstructed image seems plausible to the eye.
@@
 This problem was for example described and studied by \cite{Reeves1995} and \cite{Fish1995}.
-Lastly the RL method only provide a \enquote{point estimate} and no associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain for example to measure the significance of specific features found in the reconstructed image.
-
-    To address the issue with RL decomposing extended emission structures into groups of point source, multiple additions to the RL method were proposed.
+Lastly, the RL method only provided a \enquote{point estimate} and no associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain, for example, to measure the significance of specific features found in the reconstructed image.
+
+    To address the issue with RL decomposing extended emission structures into groups of point sources, multiple additions to the RL method were proposed.
 Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparse representations based on \enquote{wavelets} or \enquote{curvelets} \citep{Starck2003}.
@@
 
-    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstrction and Analysis} (LIRA) method.
+    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstruction and Analysis} (LIRA) method.
 Their key idea was to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
-Instead of a trying to find a single point estimate for the reconstructed image  they also changed to sampling from the posterior distribution, which allowed them to quantify the associated uncertainties.
-However the prior distribution is based on the generic assumption of smoothness and does not encode any \enquote{real world} or physical information on the structures present in the image.
+Instead of a trying to find a single point estimate for the reconstructed image they also introduced the sampling from the posterior distribution, which allowed them to quantify the associated uncertainties.
+However, the prior distribution is based on the generic assumption of smoothness and does not encode any \enquote{real world} or physical information on the structures present in the image.
 
@@
 They showed that RL can be effective in creating a merged image from multiple observations.
-They also observed that RL would take the best visual properties out of an each image and merged them to create a more accurate estimate of the ground truth.
+They also observed that RL would take the best visual properties out of each image and merged them to create a more accurate estimate of the `ground truth'.
 
@@
 Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they were able to deconvolve an astrophysical observation as well as decomposing it into point-like and diffuse emission components.
-While the method has worked well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it seemed to fail for smaller extended emission structures such as mrophological details of extended sources.
+While the method has worked well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it seemed to fail for smaller extended emission structures such as morphological details of extended sources.
 
@@
 For example \cite{Zoran2011} build on very similar assumption of local correlation for natural images.
-However instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
+However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
 For this they proposed to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) modeling the distribution of extracted patches.
@@
 They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
-\cite{Bouman2016} later adapted the patch prior successfully for the reconstruction of radio data from the Event Horizon Telescope (EHT).
+\cite{Bouman2016} later adapted the patch prior successfully for the reconstruction of sub-millimeter radio data from the Event Horizon Telescope (EHT).
 
@@
     In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images.
-However their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
-For a variety of reasons, which we will outline in the following, this approach is not ideal for astronomical x-ray and \gammaray data.
-
-    Firstly, astronomical x-ray and \gammaray data data is rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
-To circumvent this one could rely on transfer learning and simulated data.
+However, their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
+For a variety of reasons, which we will outline in the following, this approach is not ideal for astronomical \xray and \gammaray data.
+
+    Firstly, astronomical \xray and \gammaray data are rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
+To circumvent this issue one could rely on transfer learning and simulated data.
 For example radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise to generate training data.
-However astronomical images still have a large dynamic range and show a high diversity in morphological structure, which would still require a large amount of training data.
-However this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
-\cite{Sweere2022} used images from
+However, astronomical images still have a large dynamic range and show a high diversity in morphological structure, which would still require a large amount of training data.
+However, this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
+Recently, \cite{Sweere2022} used images from
     the large scale structure simulations with promising results.
@@
     One last important challenge for deep learning based methods is obtaining uncertainty estimates for the reconstructed image from CNNs.
-In the limit of Poisson noise it is desirable to trace the full a-postiori likelihood, which is not possible for most network architectures, with the exception of for example normalising flows.
+In the limit of Poisson noise it is desirable to trace the full a-posteriori likelihood, which is not possible for most network architectures, with the exception of, for example, normalising flows.
 This problem could be addressed with Monte Carlo (MC) based methods, such as bootstrapping, which further increases the demand on training data and computational resources.
-For these reasons we decided to choose an approach more close to \enquote{classical} statistical modelling techniques.
-However we will include elements from ML to represent the prior information on images.
+For these reasons we decided chose a statistical modelling approach to approach the de-convolution problem in the presence of Poisson noise.
+However, we will include elements from ML to represent the prior information on images.
 
@@
     \begin{itemize}
-        \item Different observations of one instrument or telescope at different times and observation conditions.
-For example, multiple observations of \chandra of the same astrophysical object with different offset angles and exposure times
-        \item Observations from different telescopes, which operate in the same wavelength range. For example, a \chandra and \xmm observation of the same region in the sky
-        \item A single observation of one telescope with different data quality categories and different associated instrument response functions, such as event classes for \fermi
+        \item Different observations with one instrument or telescope at different times and observation conditions.
+For example, multiple observations of \chandra of the same astrophysical object with different offset angles and exposure times;
+        \item Observations from different telescopes, which operate in the same wavelength range. For example, a \chandra and \xmm observation of the same region in the sky;
+        \item A single observation with one telescope with different data quality categories and different associated instrument response functions, such as event classes for \fermi.
     \end{itemize}
@@
     Or even an arbitrary combination of the possibilities listed above.
-It could also be the combination of observations in different energy ranges, however in this case the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for the astronomical data we are dealing with.
+It could also be the combination of observations in different energy ranges, however in this case the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for the astronomical data.
 
@@
 
-    By taking the logarithm and dropping the constant terms one can transform the
-    product into a sum over pixels, which is also often called the \textit{Cash}
-    \citep{Cash1979} fit statistics:
+    Where $\mathbf{\lambda_j}$ depends on $\mathbf{x}$ as defined by Equation~\ref{eq:model}.
+By taking the logarithm and dropping the constant terms one can transform the product into a sum over pixels, which is also often called the \textit{Cash} \citep{Cash1979} fit statistics:
     %
@@
 
-    To account for the possibility of different datasets having a different number of pixels we divide by $N$.
+    To account for the possibility of different data sets having a different number of pixels we divide by $N$.
 By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
@@
 
+%\as{in Eq.4 - should there will be $\lambda$ not x in the sum term?, or maybe this is correct, but the formula in 3 is not? I'm confused.}
+
     Using Maximum Likelihood Estimation (MLE) we could try to get an estimate of $\hat{\mathbf{x}}$ directly, using some optimization procedure.
-However in general this represents an \textit{ill posed} inverse problem.
+However, in general this represents an \textit{ill posed} inverse problem.
 Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}}_1)$ look very different from each other and might also look different compared to a given ground truth, if available.
@@
 The size of the corresponding correlation matrix would grow with the number of pixels squared and thus quickly becomes computationally untraceable.
-However astronomical images typically only show local correlations between pixels.
+However, astronomical images typically only show local correlations between pixels.
 This is because the spatial scale of astrophysical processes in an image is always limited by the finite interaction time and the fact that the interaction cannot propagate faster than the speed of light (structure in the CMB might be an exception here).
@@
 
-    One convenient property of the GMM is the possibility to evaluate its likelihood in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
+    One convenient property of the G MM is the possibility to evaluate its likelihood in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
     %
@@
 The bottom row of Figure~\ref{fig:patches} shows an example of a patch and the same patch represented in the \enquote{Eigenbasis} of the covariance matrices of its three most likely GMM components.
-Visually the representation of the of the patch in the Eigenbasis of the covariance results in a denoised version of the patch.
+Visually, the representation of the patch in the Eigenbasis of the covariance results in a denoised version of the patch.
 
@@
 Such a grid is illustrated in Figure~\ref{fig:patches}.
-However using a grid of overlapping patches makes the interpretation of the prior as likelihood more difficult, because pixels at the corners and edges of patches are counted multiple times.
+However, using a grid of overlapping patches makes the interpretation of the prior as likelihood more difficult, because pixels at the corners and edges of patches are counted multiple times.
 For this we introduce a weighting mask when evaluating the likelihood of the GMM.
@@
 Apart from this we keep the process of choosing the most likely component unmodified.
-However we note that in this case we neglected the correlation between neighbouring patches.
+However, we note that in this case we neglected the correlation between neighbouring patches.
 As the choice of the GMM component per patch is discrete, a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
@@
 This leads to the GMM modeling the same morphological features at different levels of contrast as different components.
-While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, because every morphological feature would need to present at many more levels of intensity.
+While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, because every morphological feature would need to be present at many levels of intensity.
 While this could be handled by introducing a lot more components to the GMM, it seems unfeasible in practice due to the limited availability of training data and computational resources.
@@
 We also experimented with cycle spinning by a sub-pixel amount, mostly for the reconstruction of point sources.
-However we later introduced the possibility to reconstruct an upsampled version of $\mathbf{x}$, which made the sub-pixel cycle-spinning mostly redundant.
+However, we later introduced the possibility to reconstruct an upsampled version of $\mathbf{x}$, which made the sub-pixel cycle-spinning mostly redundant.
 
@@
     \subsection{Systematic Errors of Predicted Counts}
-    Each measured counts image $\mathbf{D_j}$ is associated with systematic errors.
+    Each observation $\mathbf{D_j}$ comes with associated systematic errors.
 This includes for example the pointing accuracy of the telescopes: when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object might vary in the image between different observations.
@@
     Estimating the global covariance matrix for image based data is computationally not feasible, because the size of the matrix scales with the squared number of pixels in the image.
-However there are a few ways to estimate the statistical uncertainties associated with the flux image reconstructed by \jolideco.
+However, there are a few ways to estimate the statistical uncertainties associated with the flux image.
 We propose three methods for this:
@@
     \begin{itemize}
-    \item The first method we propose is bootstrapping of observations.
+    \item The first method is bootstrapping of observations.
 Given that multiple observations of the same region of the sky are available, \jolideco can be run repeatedly on a random subset of those.
@@
     \item If only one or few observations are available we propose bootstrapping of the events used to compute the counts image instead.
-This basically corresponds to splitting a single observation into multiple ones splitting the single exposure into multiple time intervals.
+This basically corresponds to splitting a single observation into multiple ones by splitting the single exposure into multiple time intervals.
 This way one can apply the first proposed method again.
@@
     \end{itemize}
+
+\as{There is no mention of stochastic gradient decent in the description of the method above, so this is the first time you talk about it...
+maybe it needs to be included when you describe solving the GMM model?}
 
@@
 On radio data \cite{Bouman2016} found their results to be mostly independent of the choice of data the GMM prior was learned on.
-However in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of the data the GMM was learned on.
+However, in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of the data the GMM was learned on.
 The choice of the prior becomes more important and to avoid introducing a strong bias it should be adapted to the analysis scenario.
@@
 The dataset still includes Galactic as well as extra-galactic point sources in the background.
-In total we extracted $\approx 6 \cdot 10^5$ patches and trained a GMM with 128 components.
+In total we extracted $\approx 6 \times 10^5$ patches and trained a GMM with 128 components.
 We used the patch normalisation described in Section~\ref{ssec:patch-norm}.
@@
     \subsubsection{Chandra SNRs}
-    \label{sssec:chandra-snrs}.
-Because of the limited statistics we did not use any oversampling but kept the pixel Astrophysical processes forming the morphological structures are typically self-similar.
+    \label{sssec:chandra-snrs} Because of the limited statistics we did not use any oversampling but kept the pixel.
+Astrophysical processes forming the morphological structures are typically self-similar.
 Structures appear on multiple angular scales.
@@
 Following this, a full optimization is performed using the patch prior, which can be computationally expensive.
-The optimization algorithm used is ADAM, a stochastic gradient descent method, without decay.
-Finally, there is an optional step of learning rate scheduling, although so far, a fixed step size value of $\mathrm{lr}=10^{-3}$ has been used.
+The optimization algorithm used is ADAM \citep{Kingma2014}, a stochastic gradient descent method, without decay and a fixed step size value of $\mathrm{lr}=10^{-3}$ has been used.
 
@@
     \label{subsec:test-datasets}
-    To evaluate the reconstruction performance of \jolideco and compare it against other methods we defined a set of test source scenarios.
+
+    \vlk{We have devised several test patterns that are designed to exercise and stress test deconvolution algorithms for low counts images.
+The patters consist of both point and extended sources, with strengths characteristic of typical observations, arranged with different spacings between the sources, and include point sources superposed on extended sources, as well as different background levels.
+The goal of the patterns is not to set up or devise a ``perfect'' deconvolution algorithm, but to help assess their relative strengths and limitations.
+The source patterns are described in Appendix~\\ref{sec:appA}.
+
+    We adopt two distinct scenarios, one which mimics \textit{Chandra} observations with a sharp PSF (a Gaussian with $\sigma=2$~pix) and low background (at 0.01, 0.1, and 1 ct~pix$^{-1}$) but lower effective area (nominally with an exposure of 1 unit), and the other which mimics XMM-\textit{Newton} observations with a broader PSF ($\sigma=3$~pix), higher background (at 0.1, 1, and 10 ct~pix$^{-1}$), and higher effective area (imitated with an exposure of 5 units).
+    }
+
+    % To evaluate the reconstruction performance of \jolideco and compare it against other methods we defined a set of test scenarios.
 They consist of simplified elementary morphological structures resembling those found in astronomical images.
@@
 
-    \begin{itemize}
-        \item[(A)] {\enquote{\bf Points}:} point sources arranged in a grid with different separations and brightness. 
-        \item[(B)] {\enquote{\bf Asterism}:} a set of four point sources arranged around an extended Gaussian source
-        \item[(C)] {\enquote{\bf Shield}:} disk shaped flat extended source with superposed point sources and linear jet-like features 4 different directions.
-        \item[(D)] \enquote{{\bf Spiral}:} extended thin double-spiral with a flat disk at the center and point sources adjacent to it. 
-    \end{itemize}
-
-    In addition we consider two different instrument scenarios:
-
-    \begin{itemize}
-        \item {\enquote{\bf Chandra}:} an instrument with good angular resolution, but low effective area.
+    % \begin{itemize}
+    %     \item[(A)] {\enquote{\bf Points}:} point sources arranged in a grid with different separations and brightness. 
+    %     \item[(B)] {\enquote{\bf Asterism}:} a set of four point sources arranged around an extended Gaussian source
+    %     \item[(C)] {\enquote{\bf Shield}:} disk shaped flat extended source with superposed point sources and linear jet-like features 4 different directions.
+    %     \item[(D)] \enquote{{\bf Spiral}:} extended thin double-spiral with a flat disk at the center and point sources adjacent to it. 
+    % \end{itemize}
+
+    % In addition we consider two different instrument scenarios:
+
+    % \begin{itemize}
+    %     \item {\enquote{\bf Chandra}:} an instrument with good angular resolution, but low effective area.
 We assume a Gaussian PSF of sizes $\sigma = 2$ pixels and a reference effective area of \qty[mode=text]{1}{A.U.}.
-        \item {\enquote{\bf XMM}:} an instrument with worse angular resolution, but higher effective area.
+    %     \item {\enquote{\bf XMM}:} an instrument with worse angular resolution, but higher effective area.
 We assume a Gaussian PSF of sizes $\sigma = 6$ pixels and an effective area of \qty[mode=text]{5}{A.U.}.
-    \end{itemize}
+    % \end{itemize}
 
@@
 All images are of size $128{\times}128$ pixels.
+\vlk{Please avoid using "A.U." for anything but Astronomical Units!}
         }
@@
 We rely on the default prior definition and keep the background norm fixed.
-In total we run the the sampling process for 5000 iterations and use 500 iterations as a \endquote{burn-in} period to allow the MCMC chain to converge.
+In total we run the sampling process for 5000 iterations and use the first 500 iterations as a \endquote{burn-in} period to allow the MCMC chain to converge.
 Then we compute the mean of the posterior distribution ignoring the burn-in period.
@@
 We use cycle spinning, a stride of 4 pixels and 2000 \textit{training epochs}.
-Given 5 observations this results in 10.000 iterations.
+Given 5 observations this results in 10,000 iterations.
 Which optimizes \enquote{to end} until there is no relevant change in the posterior log-likelihood.
-In addition we use and upsampling factor of 2.
+In addition we use an upsampling factor of 2.
 
         \item \textbf{Jolideco (Patch, Zoran-Weiss)}: \jolideco with a patch prior from \cite{Zoran2011} and the mean subtracted patch norm.
-This is for comparison to the original method and the method used on \cite{Bouman2016}.
+This is for comparison to the original method and the method used in \cite{Bouman2016}.
 We use a maximum image norm with the maximum values defined by the ground truth.
@@
     We ran the comparison on all combinations of methods, source scenarios, background levels and instrument scenarios.
-However in the following we only discuss the subset of the results, that we consider the most relevant.
+However, in the following we only discuss the subset of the results, that we consider the most relevant.
 The complete set of results is available at \url{https://jolideco.github.io/jolideco-comparison}.
@@
     For scenario B3 all methods recover the point sources well.
-However large difference can be observed in the reconstruction of the Gaussian shaped extended sources.
+However, a large difference can be observed in the reconstruction of the Gaussian shaped extended sources.
 As expected, the uniform prior assumption lets the emission decompose into many point sources, neglecting the spatial correlation between them.
-Pylira shows slightly improved results with the gaps between the bright emission peeks being more filled, however still lacks a convincing result of reconstructing the source as a single object.
+Pylira shows slightly improved results with the gaps between the bright emission peeks being more filled, however, it still lacks a convincing result of reconstructing the source as a single object.
 The \jolideco method with the patch priors shows the best results both visually as well as measured by the SSI.
@@
 While again all methods reconstruct the point sources well, the visual differences are large for the weak underlying extended emission.
-The uniform prior with 1000 iterations decomposes the source into a grid of almost equidistant point sources resembling only the outer boundary of the original source.
+The uniform prior with 1000 iterations decomposes the extended source into a grid of almost equidistant point sources resembling only the outer boundary of the original source.
 Pylira shows a similar tendency but already improves the reconstruction of the extended source by leaving more emission in between the bright emission spots.
 The best results are achieved by the patch priors, which reconstruct a plausible extended source with approximately uniform brightness.
-The jet like features in the same scenario are decomposed into a \enquote{thread} of point sources by the uniform prior and LIRA method.
+The jet like features in the same scenario are decomposed into a \enquote{thread} of point sources by the uniform prior and Pylira method.
 The patch prior achieves a much more plausible reconstruction with almost uniform brightness for the linear structures.
@@
 
-    The last scenario D4 shows a similar result as before: the uniform prior and LIRA decompose the spiral and ring like structure in the image.
+    The last scenario D4 shows a similar result as the previous test: the uniform prior and Pylira decompose the spiral and ring like structure in the image.
 The patch priors reconstruct a visually much more plausible flux image.
@@
     In summary \jolideco shows excellent performance of a variety of morphological shapes.
-it converges to the reference solution for very high signal to noise.
+It converges to the reference solution for a very high signal to noise image.
 We find the prior learned from GLEAM data to be a very good compromise between the ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
@@
 The background level varies between $\lambda_{Bkg}= 0.01, 0.1$ and \qty[mode = text]{1}{counts/pixel}.
-As expected the reconstruction quality improves with signal strength.
-This includes both the variation of the background as well as signal strength.
+As expected, the reconstruction quality improves with higher signal strength and lower background level.
 Visually the method converges to the ground truth for very high signal-to-noise ratio.
@@
     Using the data from the \enquote{Chandra} scenario alone results in a good reconstruction at all variations of scenario D.
-As expected the reconstruction quality improves for larger signal to noise ratio.
-
-    Using just the data from the \enquote{XMM} scenario results in lower quality reconstructions, due to the lower angular resolution.
-However we find that the spiral arm structure is reconstructed at all levels of signal strength, even when barely visible from the data by eye.
+As expected the reconstruction quality improves for higher signal to noise ratio.
+
+    Using only the data from the \enquote{XMM} scenario results in lower quality reconstructions, due to the lower angular resolution.
+However, we find that the spiral arm structure is reconstructed at all levels of signal strength, even when barely visible by eye.
 The ring structure is sharpened considerably in all cases as well.
-The near-by point sources left and right to the spiral arm structure cannot be separated as individual point sources, but still appear with improved
+The near-by point sources left and right to the spiral arm structure cannot be separated into individual point sources, but still appear with improved
     signal-to-noise ratio. This is an inherent limitation of the method. \todo{how far are those apart compared to the PSF? Hoes does this compare to the point scenario with XMM?}
@@
 In this case the correlation between pixels that are further apart is stronger because of the larger correlation PSF.
-However the reconstruction of the spiral structure in the center shows visual artifacts, with the individual arms not completely separated.
+However, the reconstruction of the spiral structure in the center shows visual artifacts, with the individual arms not completely separated.
 The joint reconstruction shows the positive qualities of both individual reconstructions.
@@
     \subsubsection{Image Example}
-    As a first application example for real data we choose a set of short exposure observations of the SNR \textit{1E~0102.2–7219} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
-In total we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS instrument and no grating.
+    First we apply our method to a set of short exposure observations of the SNR \textit{1E~0102.2–7219} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
+In total, we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS instrument and no grating.
+
+    \begin{table}
+        \centering
+        \begin{tabular}{ |c|c|c| } 
+        \input{output/chandra-obs-table.tex}
+        \end{tabular}
+        \label{tab:chandra_obs}
+        \script{chandra-obs-table.py}
+    \end{table}
 
@@
 As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
-We converted the spectral from XSPEC to sherpa script using the helper script \texttt{convert\_xspec\_script}.
+We converted the spectral script from XSPEC to sherpa using the helper script \texttt{convert\_xspec\_script}.
 As reported in \cite{Xi2019} the effect of pileup, even for the brightest regions is small ($<5\%$), so we did not include the effect of pileup in our PSF simulations.
 
-    We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the norm to vary later in the reconstruction process.
+    We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the normalization to vary later in the reconstruction process.
 We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation.
-As reference we chose the observation with id 1308.
+As reference we chose the observation with ID 1308.
 For \jolideco we used the GMM prior learned on the JWST Cas A image.
-As there is a lot of statistics in the image we additionally used an oversampling factor of 2.
+As there is a lot of counts in the image we additionally used an oversampling factor of 2.
 For each observation we allowed the background level and position calibration to vary.
@@
 \jolideco maintains the extended structure along the filament, while sharpening in the perpendicular direction.
-Looking at the upper right one can also see that weak background emission is suppressed, also improving the contrast of the image.
+Looking at the upper right corner one can also see that weak background emission is suppressed, also improving the contrast of the image.
 
@@
 Both profiles are normalized such that they integrate to unity and are aligned such that the position of their peak coincides.
+                \vlk{I notice that you avoid the bright knot to SW.
+Any particular reason why?
+You could legitimately exclude it to avoid pileup effects, but depends on the actual observed count rates.}
             }
@@
 
+    \vlk{We compute the full-width at half-max (FWHM) of each of the profiles, for both the original counts and the deconvolved intensities, and find that the deconvolved profile is narrower.
+For the counts profile, FWHM$_C=0.63 \pm 0.09$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has FWHM$_J=0.56 \pm 0.03$~arcsec.
+Note that the PSF itself has a FWHM$_{{\rm PSF}\approx{0.6}}$~arcsec\footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
+The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}.
+}
     The profile computed from the images reconstructed with \jolideco has a much smaller noise level and the peak is much more pronounced.
@@
     \subsection{\fermi Event Types}
-    As a second example we apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
+     We apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
 The LAT is a pair conversion \gammaray telescope on board of the Fermi satellite.
 It operates in the energy range between \qty[mode = text]{30}{MeV} to  \qty[mode = text]{300}{GeV}.
-For this example we chose again a Galactic source with complex morphology: the supernova remnant Vela Junior.
+For this example we chose  a Galactic source with complex morphology: the supernova remnant Vela Junior.
 We use 14 years (from 2008 August 4 to 2023 August 4) of \endquote{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
@@
     The \texttt{fermitools} produce an energy dependent counts, exposure and PSF cube.
-To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Donath2023}.
+To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Gammapy2023}.
 To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \citep{Ajello2017}.
@@
 \jolideco clearly improves the noise level as well as angular resolution of the data.
-The calibration of the predicted counts finds different background model norms and positional shifts in order of $<1$ pixel for the different event classes.
+The calibration of the predicted counts finds different background model norms and positional shifts of order of $<1$ pixel for the different event classes.
 This way it corrects for systematic errors in the reconstruction of the position.
@@
 
-    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma=5$ pixels. The result is shown in the most right panel of Fig.~\ref{fig:example-fermi-lat}. The image
+    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma=5$ pixels. The result is shown in the right panel of Fig.~\ref{fig:example-fermi-lat}. The image
     shows no systematic effects and a spatially homogeneous distribution of the residual noise.
 The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit Gaussian distribution, as expected for a good model of the emission.
-More details of the example \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
+More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
 
@@
     \bibliography{bib.bib}
+
+    \appendix
+    \section{Source Patterns}
+
+    We have devised elaborate source patterns consisting of point sources and extended sources of different shapes, sizes, orientations, and spacings in order to test deconvolution algorithms for astronomical low counts images.
+There are four distinct patterns, illustrated in Figure~\ref{fig:scenarios}, which we denote (1) {\sl Pointilist}, (2) {\sl Asterism}, (3) {\sl Shield}, and (4) {\sl Spiral}.
+The construction of each pattern is described below.
+All patterns are placed in a $128{\times}128$ pixel image.
+
+    \paragraph{Pointilist} A series of point sources arranged in a grid with increasing horizontal and vertical separations.
+The sources placed along a horizontal row all have the same strength, which increases with $y$-axis locations.
+The source strengths are
+    $$s_{\rm A} = \{10, 20, 30, 50, 80, 130, 210, 340\} \cdot \tau ~{\rm [counts]} $$
+    for
+    $$y = [8, 10, 13, 18, 26, 39, 55, 76]~{\rm pix} \,,$$
+    and $\tau$ denotes an arbitrary scaling factor, set to 1 for \textit{Chandra}-like simulations and to 5 for XMM-like simulations.
+    The $x$-axis locations of the sources for a given $y$ are
+    $$[8, 9, 10, 11, 13, 16, 21, 29, 42, 61, 95] \,.$$
+    Notice that the spatial separations and intensity changes are based on the Fibonacci series, which places them on a cadence that is sub-logarithmic but supra-linear, and thus provides a good trade-off between dynamic range and point density.
+Further note that at the lower left corner of the image, adjacent sources are placed close together, either in the adjoining pixel or separated by one pixel, with low source strengths, posing an almost impossible challenge to deconvolution algorithms.
+In contrast, the upper right corner of the image is sparse, with strong sources well separated.
+
+    \paragraph{Asterism} This pattern is comprised of a diffuse Gaussian source ($\sigma=2$~pix) at the center of the image at pixel location (64,64), and four larger extended sources (Gaussians with $\sigma=4$~pix) with the same number of counts as the central source are set at each of the corners.
+Four point sources with intensities decreasing by a factor $\frac{1}{3}$ are arranged around the central diffuse source to the top, left, right, and bottom.
+Three brightness levels are considered, with counts in all the diffuse sources set at
+    $$\{100, 500, 1000\} \cdot \tau \,,$$
+    where $\tau=1$ for \textit{Chandra}-like and $\tau=5$ for XMM-like simulations.  The diffuse sources are located at
+    $$(x,y)_{{\rm diffuse}} = (22,22), (22,106), (106,106), (106,22) ~{\rm pix} \,,$$
+    and the point sources at
+    $$(x,y)_{{\rm point}} = (64,76), (44,64), (74,64), (64,44) \,,$$
+    with counts
+    $$\{1, \frac{1}{3}, \frac{1}{3^2}, \frac{1}{3^3} \} \times$$
+    those in the diffuse sources respectively.
+The pattern of point sources explores the effects of contamination by large extended sources, and the diffuse sources at the corners help to characterize the edge effects in deconvolutions.
+
+    \paragraph{Shield} A flat disk at image center, with superposed point sources, and jet-like linear extensions radiating to the corners.  The disk has a radius of 20~pix and has brightness set to
+    $$\{0.5, 1, 2\} \cdot \tau ~{\rm counts~pix^{-1}} \,,$$
+    where again $\tau$ represents an arbitrary scaling factor to mimic telescope sensitivity.
+Four point sources are placed at positions displaced at $\{\pm8,\pm8\}$~pix from image center, with intensities at
+    $$\{10, 50, 100, 500\} \cdot \tau ~{\rm counts}$$
+    clockwise starting from lower left respectively.
+Linear sources of horizontal width 3~pix are placed along the $\pm45^o$ lines extending between radial distances from 36~pix to 64~pix from image center, with surface brightnesses
+    $$\{10, 50, 100, 500\} \cdot \tau ~{\rm counts~pix^{-1}} \,,$$
+    matching those of the nearest point sources.
+This pattern simultaneously tests the ability of deconvolution algorithms to distinguish the disk from the background, and the embedded point sources from the disk.
+The linear radiating sources present a different challenge to algorithms which use symmetrical kernels, which usually break such features (often seen in real astronomical images as jets or detector features like streaks or bad CCD columns) into a string of point-like sources.
+
+    \paragraph{Spiral}
+
 \end{document}

### 2023-10-26 src/scripts/chandra-obs-table.py
Add hlines

@@ -1,6 +1,7 @@
 import logging
 from io import StringIO
 
+import numpy as np
 import paths
 from astropy import units as u
 from astropy.table import Table
@@ -11,7 +12,7 @@ logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 OBS_ID_REF = 8365
 
-colnames = ["Obs ID", "Exposure", "Start Date"]
+colnames = ["Obs ID", "Exposure", "Obs Date"]
 obs_table = Table(names=colnames, dtype=[int, "f8", "S10"], units=["", "ks", ""])
 
 path = paths.jolideco_repo_chandra_example / "data"
@@ -26,12 +27,20 @@ for filename in filenames:
     obs_table.add_row(row)
 
 
+# Add reference observation
+obs_table.add_index("Obs ID")
+exposure_ref = obs_table.loc[OBS_ID_REF]["Exposure"]
+obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
+
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)
 
 content = content_io.getvalue()
 lines = content.split("\n")
 lines = lines[2:-3]
+lines.insert(1, "\hline")
+lines.insert(3, "\hline")
+lines.append("\hline")
 content = "\n".join(lines)
 
 filename = paths.output / "chandra-obs-table.tex"

### 2023-10-26 src/scripts/chandra-e0102-zoom-a.py
Replace lambda by w

@@ -201,7 +201,7 @@ fwhms_counts = np.array(
 )
 
 ax.text(
-    s=f"$\lambda_C={fwhms_counts.mean():.2f}\pm{fwhms_counts.std():.2f}$ arcsec",
+    s=f"$w_C={fwhms_counts.mean():.2f}\pm{fwhms_counts.std():.2f}$ arcsec",
     x=0.59,
     y=0.8,
     transform=ax.transAxes,
@@ -233,7 +233,7 @@ fwhms_jolideco = np.array(
 )
 
 ax.text(
-    s=f"$\lambda_J={fwhms_jolideco.mean():.2f}\pm{fwhms_jolideco.std():.2f}$ arcsec",
+    s=f"$w_J={fwhms_jolideco.mean():.2f}\pm{fwhms_jolideco.std():.2f}$ arcsec",
     x=0.59,
     y=0.9,
     transform=ax.transAxes,

### 2023-10-26 src/scripts/chandra-e0102-zoom-a.py
Change to Gauss fit for profile width measurment

@@ -1,3 +1,4 @@
+import logging
 from pathlib import Path
 
 import config
@@ -14,6 +15,11 @@ from gammapy.estimators import ImageProfile
 from gammapy.maps import Map, WcsGeom
 from regions import RectangleSkyRegion
 from scipy.ndimage import gaussian_filter
+from scipy.optimize import curve_fit
+
+logging.basicConfig(level=logging.INFO)
+
+log = logging.getLogger(__name__)
 
 PATH_RESULTS = paths.jolideco_repo_chandra_e0102_zoom_a / "results" / "e0102-zoom-a"
 
@@ -71,6 +77,42 @@ def measure_fwhm(d, spline_smoothing=0.0):
     return fwhm, r1, r2, np.max(y) / 2.0
 
 
+def gauss(x, norm, x0, sigma):
+    """Gaussian function."""
+    return (
+        norm
+        * np.exp(-((x - x0) ** 2) / (2 * sigma**2))
+        / (sigma * np.sqrt(2 * np.pi))
+    )
+
+
+def baseline(x, a, b):
+    """Baseline function."""
+    return a * x + b
+
+
+def model(x, norm, x0, sigma, a, b):
+    """npred function."""
+    return gauss(x, norm, x0, sigma) + baseline(x, a, b)
+
+
+def least_squares(data, model):
+    """Cash statistic"""
+    return ((data - model) ** 2).sum()
+
+
+def measure_fwhm_gauss(d):
+    """Measure FWHM using a Gaussian model."""
+    x = d["x_normed"].to_value("arcsec")
+    y = d["mean"]
+
+    popt, _ = curve_fit(model, x, y, p0=[1, 0, 1, 0, 0])
+
+    sigma = popt[2]
+    fwhm = 2 * np.sqrt(2 * np.log(2)) * sigma
+    return fwhm
+
+
 def normalize_profile(profile, smooth_offset=0):
     """Normalize profile to integral"""
     profile_data = profile.profile
@@ -106,7 +148,7 @@ def plot_fwhm(ax, fwhm, y_max_half, color, subscript, va="top"):
     ax.text(
         (r1 + r2) / 2,
         y,
-        f"$\lambda_{{{subscript}}}$",
+        f"$\omega_{{{subscript}}}$",
         ha="center",
         va=va,
         color=color,
[…]

### 2023-10-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         for parallelization speeds up the standard GMM quite a bit...
-        \item Could use a Neural Net for GMM component selection as proposed in \cite{Rosenbaum15}
         \item GPU support via Pytorch
@@
 
-    \begin{table}
-        \centering
-        \begin{tabular}{ |c|c|c| } 
-        \input{output/chandra-obs-table.tex}
-        \end{tabular}
-        \label{tab:chandra_obs}
-        \script{chandra-obs-table.py}
-    \end{table}
-
     We reduced the data using \texttt{ciao} v4.15 and a custom \texttt{snakemake} workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
@@
 By fitting the profile with a univariate spline and finding its roots we measure the full width half maximum of the curves.
-We find $\lambda_J=0.56\pm0.03$ for the \jolideco profile and $\lambda_C=0.63\pm0.09$ for the profile computed on the counts image.
+We find $w_J=0.56\pm0.03$ for the \jolideco profile and $w_C=0.63\pm0.09$ for the profile computed on the counts image.
 Assuming that the PSF and the shape of peak of the profile are approximately Gaussian a we expect the following relation between the width of the counts profile, the PSF and the flux profile:
@@
     \begin{equation}
-        \lambda_{J} = \sqrt{\lambda_C^2 - \lambda_{\mathrm{PSF}}^2}
-    \end{equation}
-
-    With $\lambda_{\mathrm{PSF}} \approx 0.25 \mathrm{arcsec}$ \footnote{The 38\% containment radius of the Chandra PSF is $\sigma_{39}=2$ native pixels.
-This corresponds to  see e.g.
+        w_{J} = \sqrt{w_C^2 - \w_{\mathrm{PSF}}^2}
+    \end{equation}
+
+    With $w_{\mathrm{PSF}} \approx 0.25 \mathrm{arcsec}$ \footnote{The 38\% containment radius of the Chandra PSF is $\sigma_{39}=2$ native pixels.
+This corresponds to  ee e.g.
 \url{https://space.mit.edu/cxc/marx/tests/PSF.html}}
@@
 To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for Vela Junior and integrate over the energy dimension of the cube while weighting with the spectral model.
+
     We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
 Because of the limited statistics we did not use any oversampling but keep the pixel size of the counts image.
-
-    Figure~\ref{fig:example-fermi-lat} shows the data, result and residuals.
-The \fermi data is sparse, with very limited statistics.
+    Figure~\ref{fig:example-fermi-lat} shows the data, result of the \jolideco method and corresponding residuals.
+The \fermi data is sparse, with very limited number of signal counts.
 \jolideco clearly improves the noise level as well as angular resolution of the data.
-The calibration of the predicted counts finds different background model norms and positional shifts of order of $<1$ pixel for the different event classes.
-This way it corrects for systematic errors in the reconstruction of the position.
+The calibration parameters of the predicted counts converged to different norms for the background model and positional shifts of order of $<1$ pixel for the different event classes.
+This way \jolideco corrects for systematic errors in the reconstruction of the position.
 One can see that the reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and / or associated with systematic errors.
@@
 
-    To further check the quality of the model we compute a map of approximate residual significance defined by:
+    To further check the quality of the reconstructed flux we compute a map of approximate residual significance defined by:
 
@@
     shows no systematic effects and a spatially homogeneous distribution of the residual noise.
-The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a unit Gaussian distribution, as expected for a good model of the emission.
+The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a standard normal distribution, as expected for a good model of the emission.
 More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
@@
     \appendix
-    \section{Source Patterns}
+    \section{Details on Source Patterns}
 
@@
 
+    \section{Chandra Observation Table}
+
+    \begin{table}
+    \centering
+        \begin{tabular}{ c|c|c|c } 
+            \input{output/chandra-obs-table.tex}
+        \end{tabular}
+        \label{tab:chandra_obs}
+        \script{chandra-obs-table.py}
+        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}}
+    \end{table}
+
 \end{document}

### 2023-10-27 src/scripts/comparison-scenarios.py
Use counts rate instead of flux as unit

@@ -148,7 +148,7 @@ for idx, scenario_title in enumerate(scenario_titles):
             )
 
         if jdx == len(method_titles) - 1:
-            add_cbar(im, ax, fig, label="Flux / A.U.")
+            add_cbar(im, ax, fig, label="Count rate / cts s$^{-1}$")
 
 
 plt.savefig(paths.figures / "comparison-scenarios.pdf", dpi=config.DPI)

### 2023-10-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \centering\includegraphics{figures/comparison-scenarios.pdf}
-        \caption{Illustration of the expected counts for the different source and instrument scenarios we used to make test datasets.
+        \caption{Illustration of the expected counts for the different source scenarios we used to make test datasets.
 The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}).
@@
 The \jolideco method with the patch priors shows the best results both visually as well as measured by the SSI.
-The GLEAM v0.1 patch prior reconstructs the sources almost perfectly, visually almost indistinguishable from the ground truth.
+With the GLEAM v0.1 patch prior the reconstruction is almost perfectly, visually almost indistinguishable from the ground truth.
 The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a more visible extension in the surrounding point sources.
@@
     \subsubsection{Flux Profile}
-    To get a more qualitative measurement of the improvement we compute a flux profile on the image of E0102 reconstructed by \jolideco.
+    To get a more quantitative measurement of the improvement in angular resolution we compute a flux profile on the image of E0102 reconstructed by \jolideco.
 For this we chose a region perpendicular to the filament shown in Zoom A of Figure~\ref{fig:example-chandra}.
@@
 
-    \vlk{We compute the full-width at half-max (FWHM) of each of the profiles, for both the original counts and the deconvolved intensities, and find that the deconvolved profile is narrower.
-For the counts profile, FWHM$_C=0.63 \pm 0.09$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has FWHM$_J=0.56 \pm 0.03$~arcsec.
-Note that the PSF itself has a FWHM$_{{\rm PSF}\approx{0.6}}$~arcsec\footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
-The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}.
-}
-    The profile computed from the images reconstructed with \jolideco has a much smaller noise level and the peak is much more pronounced.
-By fitting the profile with a univariate spline and finding its roots we measure the full width half maximum of the curves.
-We find $w_J=0.56\pm0.03$ for the \jolideco profile and $w_C=0.63\pm0.09$ for the profile computed on the counts image.
-Assuming that the PSF and the shape of peak of the profile are approximately Gaussian a we expect the following relation between the width of the counts profile, the PSF and the flux profile:
-
-    \begin{equation}
-        w_{J} = \sqrt{w_C^2 - \w_{\mathrm{PSF}}^2}
-    \end{equation}
-
-    With $w_{\mathrm{PSF}} \approx 0.25 \mathrm{arcsec}$ \footnote{The 38\% containment radius of the Chandra PSF is $\sigma_{39}=2$ native pixels.
-This corresponds to  ee e.g.
-\url{https://space.mit.edu/cxc/marx/tests/PSF.html}}
-    we obtain ..., which is consistent with the values we measured for the profile.
-The profile computed from the images reconstructed with \jolideco show both a smaller width of the profile as well as a much smaller error.
+    We compute the full-width at half-max (FWHM) of each of the profiles, by fitting a Gaussian shape with a linear gradient as baseline 
+    for both the original counts and the deconvolved intensities.
+We find that the deconvolved profile is significantly narrower.
+For the counts profile, $\omega_C=0.77 \pm 0.22$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.52 \pm 0.03$~arcsec.
+
+    Assuming that the PSF and the shape of peak of the profile are approximately Gaussian we expect the following relation between the width of the counts profile, the PSF and the flux profile:
+    %
+    \begin{equation}
+        \omega_{J} = \sqrt{\omega_C^2 - \omega_{\mathrm{PSF}}^2}
+    \end{equation}
+    %
+    With $w_{\mathrm{PSF}} \approx 0.6 \mathrm{arcsec}$ \footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
+The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after de-convolution of $\approx\omega_J=0.48$~arcsec.
+This is roughly consistent with the values we measured for the profile.
 

### 2023-10-27 src/scripts/comparison-scenarios.py
Use single lable for all rows

@@ -62,14 +62,13 @@ fig, axes = plt.subplots(
 )
 
 
-def add_cbar(im, ax, fig, label=""):
+def add_cbar(im, ax, fig):
     """Add cbar to a given axis and figure"""
     bbox = ax.get_position()
     loright = bbox.corners()[-2]
     rect = [loright[0] + 0.005, loright[1], 0.02, bbox.height]
     cax = fig.add_axes(rect)
     cbar = fig.colorbar(im, cax=cax, orientation="vertical")
-    cbar.set_label(label, size=9)
     cbar.set_ticks([0, 10, 100])
     cax.tick_params(labelsize=9)
 
@@ -148,7 +147,17 @@ for idx, scenario_title in enumerate(scenario_titles):
             )
 
         if jdx == len(method_titles) - 1:
-            add_cbar(im, ax, fig, label="Count rate / cts s$^{-1}$")
+            add_cbar(im, ax, fig)
 
+ax.text(
+    x=0.99,
+    y=0.5,
+    s="Count rate / (cts s$^{-1}$)",
+    fontsize=9,
+    ha="center",
+    va="center",
+    transform=fig.transFigure,
+    rotation=90,
+)
 
 plt.savefig(paths.figures / "comparison-scenarios.pdf", dpi=config.DPI)

### 2023-10-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \begin{figure*}
-        \centering\includegraphics{figures/comparison-scenarios.pdf}
+        \centering\includegraphics{figures/scenarios.pdf}
         \caption{Illustration of the expected counts for the different source scenarios we used to make test datasets.
 The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}).
-For the instrument scenario \chandra we convolved the with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
+For the instrument scenario \chandra we convolved the ground truth image with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
 For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix and a five times increased effective are.
 All images are of size $128{\times}128$ pixels.
-\vlk{Please avoid using "A.U." for anything but Astronomical Units!}
         }
         \label{fig:scenarios}
-        \script{comparison-scenarios.py}
+        \script{scenarios.py}
     \end{figure*}

### 2023-11-01 src/scripts/patches.py
Make patch example brighter

@@ -1,3 +1,5 @@
+import logging
+
 import config
 import matplotlib.pyplot as plt
 import numpy as np
@@ -10,9 +12,12 @@ from astropy.visualization import simple_norm
 from jolideco.priors import GaussianMixtureModel
 from matplotlib.patches import Rectangle
 
+log = logging.getLogger(__name__)
+
 random_state = np.random.RandomState(49837)
 filename = get_pkg_data_filename("galactic_center/gc_msx_e.fits")
 
+highlight_color = "red"
 
 image_size = (128, 68)
 x, y = 10, 40
@@ -68,12 +73,12 @@ rectangle = Rectangle(
     width=patch_size[0],
     height=patch_size[1],
     facecolor="None",
-    edgecolor="tab:red",
+    edgecolor=highlight_color,
     lw=1.5,
 )
 ax.add_patch(rectangle)
 
-ax.text(x=34.5, y=21.5, s="8 x 8 Patch", color="tab:red", ha="center")
+ax.text(x=34.5, y=21.5, s="8 x 8 Patch", color=highlight_color, ha="center")
 
 # example_patch = data[13:21, 13:21]
 example_patch = data[13:21, 31:39]
@@ -81,11 +86,11 @@ example_patch = data[13:21, 31:39]
 width = 0.22
 ax_patch = fig.add_axes([0.05, 0.08, width, width])
 ax_patch.imshow(example_patch, origin="lower", norm=norm, cmap="viridis")
-ax_patch.set_title("Example Patch", size=9, y=-0.4, color="tab:red")
+ax_patch.set_title("Example Patch", size=9, y=-0.4, color=highlight_color)
 ax_patch.set_xticks([])
 ax_patch.set_yticks([])
 for spine in ax_patch.spines.values():
-    spine.set_edgecolor("tab:red")
+    spine.set_edgecolor(highlight_color)
     spine.set_linewidth(1.5)
 
 ax_fig = fig.add_axes([0, 0, 1, 1])
@@ -115,4 +120,6 @@ for idx, idx_gmm in enumerate(idx_sort[:3]):
     ax_patch.set_title(f"$k_{{GMM}}$={idx_gmm}", size=9, y=-0.4)
 
 plt.axis("off")
-plt.savefig(paths.figures / "patches.pdf", facecolor="w", dpi=300)
+filename = paths.figures / "patches.pdf"
+log.info(f"Writing {filename}")
+plt.savefig(filename, facecolor="w", dpi=300)

### 2023-11-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\jolideco}{\textit{Jolideco}~}
+\newcommand{\jolideconospace}{\textit{Jolideco}}
 \newcommand{\aposteriori}{a~posteriori~}
@@
 This includes images taken by \xray and \gammaray~telescopes but also medical images obtained with methods such as positron emission tomography or single-photon emission computed tomography.
+This low counts imaging process is illustrated in Figure~\ref{fig:model-illustration}.
 
@@
 If there is prior information available on the shape of the PSF, we typically refer to the process more precisely as \enquote{unblind deconvolution}.
-In case of astronomical observations the PSF can for example be estimated empirically from observation of known point sources, such as distant \as{I would say stars instead of AGN - in optical and even in X-rays telescopes AGN are resolved, so not point sources} activate galactic nuclei or a model of the PSF can obtained from simulation of the telescope or instrument.
-
-\as{You may want to add a short para or just a sentance saying that X-ray and gamma-ray images are the Poisson type images containing low number of counts in each image pixel etc..
-- this is to link to the next subsection which is specific to Poisson noise?}
-
-    \subsection{Related Work}
-    In literature there have been many efforts to solve the unblind deconvolution problem for images affected by Poisson noise.
-Most methods rely fundamentally on modeling the image generating process as a linear process.
-Given a known PSF a prediction of the discrete measured image can be obtained via \enquote{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
-However, the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function.
-In the following section we give a short overview over those methods.
-
-    The standard baseline method for image deconvolution in the presence of Poisson noise was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \enquote{\textit{RL}}).
-The method involves estimating the reconstructed image by an iterative procedure that converges to a maximum likelihood solution of the problem.
-
-    However, in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion for when to stop the optimization process.
-Usually the iteration is stopped when the reconstructed image seems plausible to the eye.
-Second, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
-This problem was for example described and studied by \cite{Reeves1995} and \cite{Fish1995}.
-Lastly, the RL method only provided a \enquote{point estimate} and no associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain, for example, to measure the significance of specific features found in the reconstructed image.
-
-    To address the issue with RL decomposing extended emission structures into groups of point sources, multiple additions to the RL method were proposed.
-Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparse representations based on \enquote{wavelets} or \enquote{curvelets} \citep{Starck2003}.
-The challenge is rooted in two fundamentally contradicting goals: a deconvolution process that favors point sources will decompose extend structures present in the image, while introducing local correlations between neighbouring pixels will lead to less sharp reconstruction of point sources.
-
-    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstruction and Analysis} (LIRA) method.
-Their key idea was to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
-Instead of a trying to find a single point estimate for the reconstructed image they also introduced the sampling from the posterior distribution, which allowed them to quantify the associated uncertainties.
-However, the prior distribution is based on the generic assumption of smoothness and does not encode any \enquote{real world} or physical information on the structures present in the image.
-
-    An interesting modification of the standard RL method has been proposed by \cite{Ingaramo2014}.
-They showed that RL can be effective in creating a merged image from multiple observations.
-They also observed that RL would take the best visual properties out of each image and merged them to create a more accurate estimate of the `ground truth'.
-
-    \cite{Selig2015} and \cite{Pumpe2018} approached the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
-Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they were able to deconvolve an astrophysical observation as well as decomposing it into point-like and diffuse emission components.
-While the method has worked well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it seemed to fail for smaller extended emission structures such as morphological details of extended sources.
-
-    Other interesting approaches to the problem of deconvolution can of course be found in the field of computer vision.
-For example \cite{Zoran2011} build on very similar assumption of local correlation for natural images.
-However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
-For this they proposed to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) modeling the distribution of extracted patches.
-To use the GMM in reconstruction they introduced the concept of expected patch likelihood (EPLL).
-They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
-\cite{Bouman2016} later adapted the patch prior successfully for the reconstruction of sub-millimeter radio data from the Event Horizon Telescope (EHT).
-
-    % \begin{figure*}
-    %     \script{rl_decomposition.py}
-    %     \begin{centering}
-    %         \includegraphics[width=\textwidth]{figures/richardson-lucy-decomposition.pdf}
-    %         \caption{
-    %             Decomposition of the RL algorithm for various number of iterations. \todo{Improve figure}
-    %         }
-    %         \label{fig:rl_decomposition}
-    %     \end{centering}
-    % \end{figure*}
-
-    \subsection{Some Remarks on Deep Learning Methods}
-    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images.
-However, their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
-For a variety of reasons, which we will outline in the following, this approach is not ideal for astronomical \xray and \gammaray data.
-
-    Firstly, astronomical \xray and \gammaray data are rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
-To circumvent this issue one could rely on transfer learning and simulated data.
-For example radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise to generate training data.
-However, astronomical images still have a large dynamic range and show a high diversity in morphological structure, which would still require a large amount of training data.
-However, this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
-Recently, \cite{Sweere2022} used images from
-    the large scale structure simulations with promising results.
-
-    In addition to the challenge of obtaining training data, it is known that the PSF of instruments such as \chandra is highly variable.
-It varies with observation conditions and depends for example on energy as well as offset angle from the pointing direction.
-To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models.
-
-    Some of the challenges of deblurring with CNN are due to the convolutional nature of the networks.
-In a single layer, linear approximation, the network would need to learn the inverse filter of the PSF, corresponding to the well known \textit{Wiener filter} solution of the problem.
-This requires either large convolution kernels or deep network architectures, which require in turn large amounts of training data.
-This challenge was described early by \cite{Li2014} who introduced a baseline architecture for a deep CNN for image deblurring.
-
-    One last important challenge for deep learning based methods is obtaining uncertainty estimates for the reconstructed image from CNNs.
-In the limit of Poisson noise it is desirable to trace the full a-posteriori likelihood, which is not possible for most network architectures, with the exception of, for example, normalising flows.
-This problem could be addressed with Monte Carlo (MC) based methods, such as bootstrapping, which further increases the demand on training data and computational resources.
-For these reasons we decided chose a statistical modelling approach to approach the de-convolution problem in the presence of Poisson noise.
-However, we will include elements from ML to represent the prior information on images.
+In case of astronomical observations the PSF can for example be estimated empirically from observation of known point sources, such as distant stars, or a model of the PSF can be obtained from simulation of the telescope or instrument.
 
@@
     \end{figure*}
+
+%\as{You may want to add a short para or just a sentance saying that X-ray and gamma-ray images are the Poisson type images containing low number of counts in each image pixel etc..
+- this is to link to the next subsection which is specific to Poisson noise?}
+% AD: this is mentioned already...
+
+    \subsection{Related Work}
+    In literature there have been many efforts to solve the unblind deconvolution problem for images affected by Poisson noise.
+Most methods rely fundamentally on modeling the image generating process as a linear process.
+Given a known PSF a prediction of the discrete measured image can be obtained via \enquote{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
+However, the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function.
+In the following section we give a short overview over those methods.
+
+    The standard baseline method for image deconvolution in the presence of Poisson noise was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \enquote{RL}).
+The method involves estimating the reconstructed image by an iterative procedure that converges to a maximum likelihood solution of the problem.
+
+    However, in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion for when to stop the optimization process.
+Usually the iteration is stopped when the reconstructed image seems plausible to the eye.
+Second, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
+This problem was for example described and studied by \cite{Reeves1995} and \cite{Fish1995}.
+Lastly, the RL method only provided a \enquote{point estimate} and no associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain, for example, to measure the significance of specific features found in the reconstructed image.
+
+    To address the issue with RL decomposing extended emission structures into groups of point sources, multiple additions to the RL method were proposed.
+Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparse representations based on \enquote{wavelets} or \enquote{curvelets} \citep{Starck2003}.
+The challenge is rooted in two fundamentally contradicting goals: a deconvolution process that favors point sources will decompose extend structures present in the image, while introducing local correlations between neighbouring pixels will lead to less sharp reconstruction of point sources.
+
+    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstruction and Analysis} (LIRA) method.
+Their key idea was to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
+Instead of a trying to find a single point estimate for the reconstructed image they also introduced the sampling from the posterior distribution, which allowed them to quantify the associated uncertainties.
+However, the prior distribution is based on the generic assumption of smoothness and does not encode any \enquote{real world} or physical information on the structures present in the image.
+
+    An interesting modification of the standard RL method has been proposed by \cite{Ingaramo2014}.
+They showed that RL can be effective in creating a merged image from multiple observations.
+They also observed that RL would take the best visual properties out of each image and merged them to create a more accurate estimate of the `ground truth'.
+
+    \cite{Selig2015} and \cite{Pumpe2018} approached the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
+Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they were able to deconvolve \fermi observations as well as decomposing it into point-like and diffuse emission components.
+While their method has worked well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it showed artifacts for smaller extended emission structures such as morphological details of extended sources in the Galactic Plane.
+
+    Other interesting approaches to the problem of deconvolution can of course be found in the field of computer vision.
+For example \cite{Zoran2011} build on very similar assumption of local correlation for natural images.
+However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
+For this they proposed to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) modeling the distribution of extracted patches.
+To use the GMM in reconstruction they introduced the concept of expected patch likelihood (EPLL).
+They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
+\cite{Bouman2016} later adapted the patch prior successfully for the reconstruction of sub-millimeter radio data from the Event Horizon Telescope (EHT).
+
+    % \begin{figure*}
+    %     \script{rl_decomposition.py}
+    %     \begin{centering}
+    %         \includegraphics[width=\textwidth]{figures/richardson-lucy-decomposition.pdf}
+    %         \caption{
+    %             Decomposition of the RL algorithm for various number of iterations. \todo{Improve figure}
+    %         }
+    %         \label{fig:rl_decomposition}
+    %     \end{centering}
+    % \end{figure*}
+
+    \subsection{Some Remarks on Deep Learning Methods}
+    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images.
+However, their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
+For a variety of reasons, which we will outline in the following, this approach is not ideal for astronomical \xray and \gammaray data.
+
+    Firstly, astronomical \xray and \gammaray data are rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
+To circumvent this issue one could rely on transfer learning and simulated data.
+For example radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise to generate training data.
+However, astronomical images still have a large dynamic range and show a high diversity in morphological structure, which would still require a large amount of training data.
+However, this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
+Recently, \cite{Sweere2022} used images from
+    the large scale structure simulations with promising results.
+
+    In addition to the challenge of obtaining training data, it is known that the PSF of instruments such as \chandra is highly variable.
+It varies with observation conditions and depends for example on energy as well as offset angle from the pointing direction.
+To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models.
+
+    Some of the challenges of deblurring with CNN are due to the convolutional nature of the networks.
+In a single layer, linear approximation, the network would need to learn the inverse filter of the PSF, corresponding to the well known \enquote{Wiener Filter} solution of the problem.
+This requires either large convolution kernels or deep network architectures, which require in turn large amounts of training data.
+This challenge was described early by \cite{Li2014} who introduced a baseline architecture for a deep CNN for image deblurring.
+
+    One last important challenge for deep learning based methods is obtaining uncertainty estimates for the reconstructed image from CNNs.
+In the limit of Poisson noise it is desirable to trace the full a-posteriori likelihood, which is not possible for most network architectures, with the exception of, for example, normalising flows.
+This problem could be addressed with Monte Carlo (MC) based methods, such as bootstrapping, which further increases the demand on training data and computational resources.
+For these reasons we decided chose a statistical modelling approach to approach the de-convolution problem in the presence of Poisson noise.
+However, we will include elements from ML to represent the prior information on images.
+
     \section{Method}
@@
 Most generally we assume our total dataset consists of $J$ individual observations of the same region of the sky, which we jointly model.
-The assumption is that the underlying, unknown \textit{true} emission image, we are interested in, does not change with time.
+The assumption is that the underlying, unknown \enquote{true emission} image, we are interested in, does not change with time.
 Under this assumption these datasets can be for example:
@@
     Or even an arbitrary combination of the possibilities listed above.
-It could also be the combination of observations in different energy ranges, however in this case the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for the astronomical data.
-
-    For each individual observation $j$ the predicted counts can be modelled by \textit{forward folding} the unknown flux image $\mathbf{x}$ through the individual instrument response:
+It could also be the combination of observations in different energy ranges, however in this case the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for astronomical objects.
+
+    For each individual observation $j$ the predicted counts can be modelled by forward folding the unknown flux image $\mathbf{x}$ through the individual instrument response:
     %
@@
     Where $\mathbf{\lambda_j}$ depends on $\mathbf{x}$ as defined by Equation~\ref{eq:model}.
-By taking the logarithm and dropping the constant terms one can transform the product into a sum over pixels, which is also often called the \textit{Cash} \citep{Cash1979} fit statistics:
+By taking the logarithm and dropping the constant terms one can transform the product into a sum over pixels, which is also often called the \enquote{Cash} \citep{Cash1979} fit statistics:
     %
@@
     Using Maximum Likelihood Estimation (MLE) we could try to get an estimate of $\hat{\mathbf{x}}$ directly, using some optimization procedure.
-However, in general this represents an \textit{ill posed} inverse problem.
+However, in general this represents an \enquote{ill posed} inverse problem.
 Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}}_1)$ look very different from each other and might also look different compared to a given ground truth, if available.
@@
 
-    One convenient property of the G MM is the possibility to evaluate its likelihood in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
+    One convenient property of the GMM is the possibility to evaluate its likelihood in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
     %
@@
 The bottom row shows the red example patch $\mathbf{x}_n$ on the left.
-The three other patches show the quantity $\Sigma_{k_{GMM}} \mathbf{x}_n$, which is the result of the patch represented in the \textit{Eigenbasis} of the covariance matrices of the 3 most likely GMM components $k_{GMM} = 105, 77, 17$.
+The three other patches show the quantity $\Sigma_{k_{GMM}} \mathbf{x}_n$, which is the result of the patch represented in the Eigenbasis of the covariance matrices of the 3 most likely GMM components $k_{GMM} = 105, 77, 17$.
 This example uses the GMM learned from the JWST Cas A image.
@@
     Astronomical images typically show a much higher dynamic range compared to natural images.
-This is mostly due to the existence of point sources, which rarely occur in natural images.
-Astronomical point sources typically relate to compact bright objects, such as active galactic nuclei at high distances, or binary objects and stars at Galactic distances.
+    % This is mostly due to the existence of point sources, which rarely occur in natural images.
+Astronomical point sources typically relate to compact bright objects, such as unresolved active galactic nuclei at high distances, or binary objects and stars at Galactic distances.
 In addition the visible matter in the universe is sparse such that astronomical images typically show sparse bright emission on a dark background.
-
     To normalise the patches \cite{Zoran2011} proposed to subtract the patch mean before learning the GMM.
@@
     \label{ssec:jolideco-gmm-library}
-    In general the strength of the GMM prior is its high \textit{expressiveness}.
+    In general the strength of the GMM prior is its high \enquote{expressiveness}.
 This means the prior contains a large variety of structural shapes and has a lot of freedom to adapt to the data in the optimization process.
@@
 The choice of the prior becomes more important and to avoid introducing a strong bias it should be adapted to the analysis scenario.
-For this reason and for purposes of testing we learned and provide a selection of GMMs (a \textit{Library}) to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
+For this reason and for purposes of testing we learned and provide a selection of GMMs (a library) to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
 
@@
 To limit the data reduction effort we relied on a promotional image of the SNR \textit{Cassiopeia A}\footnote{We downloaded the full resolution (4k)  PNG image from \url{https://webbtelescope.org/contents/media/images/2023/121/01GWQBBY77MHGFV3M3N63KDCEJ}}.
-    We first converted the image to gray scale using a perceived brightness model \citep{scikit-image}.
+    We first converted the image to gray scale using a perceived brightness model from the Scikit-Image package \citep{scikit-image}.
 Then we split the image into $\approx 2$ million patches and learned a GMM with 128 mixture components.
@@
 Following this, a full optimization is performed using the patch prior, which can be computationally expensive.
-The optimization algorithm used is ADAM \citep{Kingma2014}, a stochastic gradient descent method, without decay and a fixed step size value of $\mathrm{lr}=10^{-3}$ has been used.
+The optimization algorithm used is ADAM\citep{Kingma2014}, a stochastic gradient descent method, without decay and a fixed step size value of $\mathrm{lr}=10^{-3}$ has been used.
 
@@
 The leftmost column shows the simulated counts data and the second most column from the left the underlying ground truth to compare.
-The other columns show the reconstructed flux by the different methods and prior assumptions for \jolideco.
+The other columns show the reconstructed flux by the different methods and prior assumptions for \jolideconospace.
 To enhance weak structures the images use an $\arcsinh$ stretching with a scale parameter of $a=0.02$.
@@
     \textbf{Zoom B} shows the region around the central compact object of the SNR.
-While the emission is barely visible in the counts image it clearly sticks out above the background in the image reconstructed by \jolideco.
+While the emission is barely visible in the counts image it clearly sticks out above the background in the image reconstructed by \jolideconospace.
 The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
@@
     \subsubsection{Flux Profile}
-    To get a more quantitative measurement of the improvement in angular resolution we compute a flux profile on the image of E0102 reconstructed by \jolideco.
+    To get a more quantitative measurement of the improvement in angular resolution we compute a flux profile on the image of E0102 reconstructed by \jolideconospace.
 For this we chose a region perpendicular to the filament shown in Zoom A of Figure~\ref{fig:example-chandra}.
@@
     %
-    With $w_{\mathrm{PSF}} \approx 0.6 \mathrm{arcsec}$ \footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
-The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after de-convolution of $\approx\omega_J=0.48$~arcsec.
+    With $\omega_{\mathrm{PSF}}\approx0.6$~arcsec\footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
+The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after de-convolution of $\omega_J\approx0.48$~arcsec.
 This is roughly consistent with the values we measured for the profile.
@@
     \subsection{\fermi Event Types}
-     We apply the \jolideco method to data from the Fermi Large Area Telescope (LAT).
+     We apply the \jolideco method to data from the Fermi Large Area Telescope (LAT) \citep{Atwood2009}.
 The LAT is a pair conversion \gammaray telescope on board of the Fermi satellite.
@@
 For this example we chose  a Galactic source with complex morphology: the supernova remnant Vela Junior.
-We use 14 years (from 2008 August 4 to 2023 August 4) of \endquote{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to  \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
-To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi collaboration.
-We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5th of the size of the PSF in the best event class.
-For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \cite{}.
+We use 14 years (from 2008 August 4 to 2023 August 4) of \enquote{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
+To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi \enquote{Pass8} data release\footnote{\url{https://fermi.gsfc.nasa.gov/ssc/data/analysis/documentation/Pass8_usage.html}}.
+We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5 of the size of the PSF in the best event class.
+For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \cite{Fermitools2019}.
 
@@
     $$\{100, 500, 1000\} \cdot \tau \,,$$
-    where $\tau=1$ for \textit{Chandra}-like and $\tau=5$ for XMM-like simulations.  The diffuse sources are located at
+    where $\tau=1$ for \chandra-like and $\tau=5$ for \xmm-like simulations.  The diffuse sources are located at
     $$(x,y)_{{\rm diffuse}} = (22,22), (22,106), (106,106), (106,22) ~{\rm pix} \,,$$

### 2023-11-30 src/scripts/chandra-obs-table.py
Add integrated exposure

@@ -12,8 +12,11 @@ logging.basicConfig(level=logging.INFO)
 log = logging.getLogger(__name__)
 OBS_ID_REF = 8365
 
-colnames = ["Obs ID", "Exposure", "Obs Date"]
-obs_table = Table(names=colnames, dtype=[int, "f8", "S10"], units=["", "ks", ""])
+colnames = ["Obs ID", "Obs Date", "Exposure"]
+units = ["", "", "ks"]
+dtype = [int, "S10", "f8"]
+obs_table = Table(names=colnames, dtype=dtype, units=units)
+
 
 path = paths.jolideco_repo_chandra_example / "data"
 filenames = sorted(path.glob("*/oif.fits"))
@@ -23,7 +26,7 @@ for filename in filenames:
     table = Table.read(filename)
     exposure = table.meta["EXPOSURE"] * u.s
     date = parser.parse(table.meta["DATE-OBS"])
-    row = [obs_id, round(exposure.to_value("ks"), 1), date.strftime("%m/%d/%Y")]
+    row = [obs_id, date.strftime("%m/%d/%Y"), round(exposure.to_value("ks"), 1)]
     obs_table.add_row(row)
 
 
@@ -31,6 +34,10 @@ for filename in filenames:
 obs_table.add_index("Obs ID")
 exposure_ref = obs_table.loc[OBS_ID_REF]["Exposure"]
 obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
+
+
+exposure_cum = np.cumsum(obs_table["Exposure"])
+obs_table["Integrated Exposure"] = exposure / exposure_cum[-1]
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\fermi}{\textit{Fermi}-LAT~}
+\newcommand{\ferminospace}{\textit{Fermi}-LAT}
 \newcommand{\jolideco}{\textit{Jolideco}~}
@@
 \newcommand{\aposteriori}{a~posteriori~}
+\newcommand{\aprioir}{a~priori~}
 \newcommand{\gammaray}{$\gamma$-ray\xspace}
@@
 \newcommand{\as}[1]{{\color{purple} [AS: #1]}}
+\newcommand{\dvd}[1]{{\color{red} [DvD: #1]}}
 % Begin!
@@
     \author[0000-0002-3869-7996]{Vinay Kashyap} 
-    \author[0000-0000-0000-0000]{David van Dyk}
+    \author[0000-0002-0816-331X]{David van Dyk}
     \author[0000-0003-4428-7835]{Douglas Burke}
@@
         We present a new method for Joint Likelihood Deconvolution (Jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
-The method reconstructs a single flux image from a set of observations by optimizing the \aposteriori joint Poisson likelihood of all observations under a patch based image prior.
+The method reconstructs a single flux image from a set of observations and given models for the point spread function (PSF) per observation, by optimizing the the posterior distribution based on th}
+        joint Poisson likelihood of all observations under a patch based image prior.
 The patch prior is parameterised by a Gaussian Mixture model (GMM) which we trained on astronomical images with high signal to noise ratio, including data from the  James Webb Telescope as well as the GLEAM radio survey.
@@
 We show also that the method yields superior reconstruction quality to alternative standard methods such as the Richardson-Lucy method.
-We also show the results of the method applied to example data from the \chandra observatory as well as the \fermi.
+We also show the results of the method applied to example data from the \chandra observatory as well as the \ferminospace.
+By comparing the measured width of a counts based and the corresponding Jolideco flux profile we find the deconvolved width to be consistent with the theoretical expectation derived from the known width of the PSF.
     \end{abstract}
@@
     The resolution of any physical or astronomical imaging process is inherently limited by the instrument or telescope used.
-Furthermore, the quality of the resulting image is affected by background or instrumental measurement noise and non-uniform exposure.
+Furthermore, the quality of the resulting image is affected by background, instrumental measurement noise, and non-uniform exposure.
 This is especially true in the low signal-to-noise regime, where images are affected by Poisson noise.
@@
     \subsection{Related Work}
+    \label{sec:related}
     In literature there have been many efforts to solve the unblind deconvolution problem for images affected by Poisson noise.
@@
 Given a known PSF a prediction of the discrete measured image can be obtained via \enquote{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
-However, the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function.
-In the following section we give a short overview over those methods.
-
-    The standard baseline method for image deconvolution in the presence of Poisson noise was proposed independently by \cite{Richardson1972} and \cite{Lucy1974} (we will further refer to this method as \enquote{RL}).
-The method involves estimating the reconstructed image by an iterative procedure that converges to a maximum likelihood solution of the problem.
-
-    However, in practice the RL method was found to have multiple, partly related limitations: first there is no objective criterion for when to stop the optimization process.
+However, the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function or posterior distribution.
+In the following section we give a short overview over these methods.
+
+    The standard baseline method for image deconvolution in the presence of Poisson noise was proposed independently by \cite{Richardson1972} and \cite{Lucy1974}.
+(We refer to this method as \enquote{RL}.) The method involves estimating the reconstructed image by an iterative procedure that converges to a maximum likelihood solution of the problem.
+
+    However, in practice the RL method was found to have multiple, partly related limitations: first, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
+This problem was for example described and studied by \cite{Reeves1995} and \cite{Fish1995}.
+This means that in practice the RL method is not iterated until it converges, leading to the second limitation: there is no objective criterion for when to stop the optimization process.
 Usually the iteration is stopped when the reconstructed image seems plausible to the eye.
-Second, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
-This problem was for example described and studied by \cite{Reeves1995} and \cite{Fish1995}.
-Lastly, the RL method only provided a \enquote{point estimate} and no associated estimate of the uncertainties of the reconstruction, which is desirable especially in the Poisson domain, for example, to measure the significance of specific features found in the reconstructed image.
+    Lastly, the RL method only provided a \enquote{point estimate} and no associated estimate of the uncertainties of the reconstruction.
+Uncertainties are desirable especially in the Poisson domain, for example, to measure the significance of specific features found in the reconstructed image.
 
@@
 
-    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstruction and Analysis} (LIRA) method.
-Their key idea was to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
-Instead of a trying to find a single point estimate for the reconstructed image they also introduced the sampling from the posterior distribution, which allowed them to quantify the associated uncertainties.
+    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstruction and Analysis} (LIRA\footnote{\dvd{LIRA was referred to as EMC2 in \cite{Esch2004}.}}) method.
+Their key idea is to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
+Instead of a trying to find a single point estimate for the reconstructed image they also sampled from the posterior distribution, which allowed them to quantify the associated uncertainties.
 However, the prior distribution is based on the generic assumption of smoothness and does not encode any \enquote{real world} or physical information on the structures present in the image.
 
-    An interesting modification of the standard RL method has been proposed by \cite{Ingaramo2014}.
-They showed that RL can be effective in creating a merged image from multiple observations.
-They also observed that RL would take the best visual properties out of each image and merged them to create a more accurate estimate of the `ground truth'.
-
-    \cite{Selig2015} and \cite{Pumpe2018} approached the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
-Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they were able to deconvolve \fermi observations as well as decomposing it into point-like and diffuse emission components.
-While their method has worked well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it showed artifacts for smaller extended emission structures such as morphological details of extended sources in the Galactic Plane.
+    An interesting modification of the standard RL method is proposed by \cite{Ingaramo2014}.
+They show that RL can be effective in creating a merged image from multiple observations.
+They also observe that RL would take the best visual properties out of each image and merged them to create a more accurate estimate of the `ground truth'.
+
+    \cite{Selig2015} and \cite{Pumpe2018} approach the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
+Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they are able to deconvolve \fermi observations as well as decomposing it into point-like and diffuse emission components.
+While their method works well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it shows artifacts for smaller extended emission structures such as morphological details of extended sources in the Galactic Plane.
 
@@
 However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
-For this they proposed to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) modeling the distribution of extracted patches.
+For this they propose to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) to model the distribution of extracted patches.
 To use the GMM in reconstruction they introduced the concept of expected patch likelihood (EPLL).
@@
     \subsection{Some Remarks on Deep Learning Methods}
-    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images.
+    In the past decade Machine learning (ML) especially deep convolutional neural networks (CNN) became the standard for deblurring and super-resolution of natural images \citep{Zhang2022}.
 However, their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
@@
 
-    Firstly, astronomical \xray and \gammaray data are rare, expensive to obtain and there is no ground truth, because we can only observe the sky with our given instruments.
+    Firstly, astronomical \xray and \gammaray data are rare, expensive to obtain, and there is no ground truth, because we can only observe the sky with our given instruments.
 To circumvent this issue one could rely on transfer learning and simulated data.
-For example radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise to generate training data.
-However, astronomical images still have a large dynamic range and show a high diversity in morphological structure, which would still require a large amount of training data.
-However, this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
-Recently, \cite{Sweere2022} used images from
-    the large scale structure simulations with promising results.
+For example, radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise to generate training data.
+However, astronomical images still
+    have a large dynamic range and show a high diversity in morphological structure, which would still requires a large amount of training data.
+
+    Nonetheless, this approach has been successfully applied for specific classes of sources, such as images of Galaxies in the Sloan Digital Sky Survey (SDSS) \citep{Schawinski2017} or as a post processing step of results obtained with regularised RL \citep{Akhaury2022}.
+Recently, \cite{Sweere2022} used images from the large scale structure simulations with promising results.
 
     In addition to the challenge of obtaining training data, it is known that the PSF of instruments such as \chandra is highly variable.
-It varies with observation conditions and depends for example on energy as well as offset angle from the pointing direction.
+It varies with observation conditions and depends, for example, on energy as well as offset angle from the pointing direction.
 To cover the whole parameter space of the PSF one would need to train a network for each of the PSF models.
@@
     One last important challenge for deep learning based methods is obtaining uncertainty estimates for the reconstructed image from CNNs.
-In the limit of Poisson noise it is desirable to trace the full a-posteriori likelihood, which is not possible for most network architectures, with the exception of, for example, normalising flows.
+In the limit of Poisson noise it is desirable to trace the full posterior distribution
+    which is not possible for most network architectures, with the exception of, for example, normalising flows.
 This problem could be addressed with Monte Carlo (MC) based methods, such as bootstrapping, which further increases the demand on training data and computational resources.
-For these reasons we decided chose a statistical modelling approach to approach the de-convolution problem in the presence of Poisson noise.
-However, we will include elements from ML to represent the prior information on images.
+For these reasons we take a statistical modelling approach to the deconvolution problem in the presence of Poisson noise.
+We do, however, include elements from ML to represent the prior information on images.
 
@@
 Most generally we assume our total dataset consists of $J$ individual observations of the same region of the sky, which we jointly model.
-The assumption is that the underlying, unknown \enquote{true emission} image, we are interested in, does not change with time.
-Under this assumption these datasets can be for example:
+The assumption is that the underlying, unknown \enquote{true emission} image, we are interested in, does not change over the timescale of the observations.
+Under this assumption the datasets can be for example:
 
@@
 
-    Or even an arbitrary combination of the possibilities listed above.
-It could also be the combination of observations in different energy ranges, however in this case the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for astronomical objects.
+    Any arbitrary combination of the possibilities is also possible.
+    In principle, we can also combine observations in different energy ranges.
+In this case, however, the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for astronomical objects.
 
@@
         \label{eq:model}
-        \boldsymbol{\lambda}_j(\mathbf{x}) = \mathbf{E}_j \cdot \left(\mathrm{PSF}_j \circledast \mathbf{x}\right) + \mathbf{B}_j
-    \end{equation}
-
-    Where the expected counts $\lambda_j$ are given by the convolution of the unknown 
-    flux image $\mathbf{x}$ with the observation specific point spread function $\mathrm{PSF}_j$.
-Additionally an observation specific image of the exposure $\mathbf{E}_j$ and background emission $\mathbf{B_j}$ can be optionally taken into account.
+        \boldsymbol{\lambda}_j(\mathbf{x}) = \mathbf{E}_j \cdot \left(\mathrm{PSF}_j \circledast \mathbf{x}\right) + \mathbf{B}_j,
+    \end{equation}
+    %
+    where the expected counts $\boldsymbol{\lambda_j}$ are given by the convolution of the unknown flux image $\mathbf{x}$ with the observation specific point spread function $\mathrm{PSF}_j$ and an observation specific image of the exposure $\mathbf{E}_j$ and background emission $\mathbf{B_j}$ can be optionally taken into account.
 A visual representation of the model of the imaging process for a single observation is shown in Figure~\ref{fig:model-illustration}.
 
-    Given a single observation $j$ of an unknown flux image
-    $\mathbf{x}$ and assuming the noise in each pixel $i$ in the recorded counts image
-    $\mathbf{D_j}$ follows a Poisson distribution, the likelihood $\mathcal{P}$
-    of obtaining the measured image from a model image of the expected
-    counts $\boldsymbol{\lambda_j}$ with $N$ pixels is given by:
+    Given a single observation $j$ of an unknown flux image $\mathbf{x}$ and assuming the noise in each pixel $i$ in the recorded counts image $\mathbf{D_j}$ follow independent Poisson distributions with expectation $\boldsymbol{\lambda_j}$, the likelihood $\mathcal{P}$
+    of obtaining the measured image with $N$ pixels is given by:
     %
@@
         \label{eq:poisson}
-        P\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - D_{j,i} } \lambda_{i,j} ^ {D_{j,i}}}}{{D_{j,i}!}}
-    \end{equation}
-
-    Where $\mathbf{\lambda_j}$ depends on $\mathbf{x}$ as defined by Equation~\ref{eq:model}.
+        P\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - \lambda_{j,i} } \lambda_{i,j} ^ {D_{j,i}}}}{{D_{j,i}!}},
+    \end{equation}
+    %
+    where $\boldsymbol{\lambda_j}$ depends on $\mathbf{x}$ as defined by Equation~\ref{eq:model}.
 By taking the logarithm and dropping the constant terms one can transform the product into a sum over pixels, which is also often called the \enquote{Cash} \citep{Cash1979} fit statistics:
@@
         \label{eq:cash}
-        \mathcal{C}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \frac{1}{N}\sum_{i=1}^N \lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}
-    \end{equation}
-
-    To account for the possibility of different data sets having a different number of pixels we divide by $N$.
-By summing over all observations we finally get the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
+        \mathcal{C}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \sum_{i=1}^{N_j} \left(\lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}\right),
+    \end{equation}
+    %  
+    By summing over all observations we obtain the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
     %
@@
     \end{equation}
-
-%\as{in Eq.4 - should there will be $\lambda$ not x in the sum term?, or maybe this is correct, but the formula in 3 is not? I'm confused.}
-
-    Using Maximum Likelihood Estimation (MLE) we could try to get an estimate of $\hat{\mathbf{x}}$ directly, using some optimization procedure.
+    %
+    In principle, we could try to obtain the Maximum Likelihood Estimate (MLE) of $\hat{\mathbf{x}}$ directly, using an optimization procedure.
+Indeed, this is the objective of the RL algorithm.
 However, in general this represents an \enquote{ill posed} inverse problem.
-Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}}_1)$ look very different from each other and might also look different compared to a given ground truth, if available.
-Both the convolution operation as well as the existence of noise lead to a loss of information in the data which cannot easily be recovered.
-The likelihood surface shows many local, close-by minima.
-Depending on the initial estimate for $\mathbf{x}$ and the minimization algorithm the MLE based estimate is likely to only find such a local minimum.
-This is fundamentally the reason for RL decomposing estimates into point sources, described in the previous section.
-
-    \subsection{A Posteriori Joint Likelihood}
-    When reconstructing images in the context of inverse problems we are operating in a high dimensional parameter space, because each pixel in the image represents an independent parameter in the optimization process.
-By using prior information we can introduce correlations between the parameters, to reduce the \enquote{effective dimensionality} of the problem and guide the optimization process towards unique and more stable solutions.
-
-    Using Bayes' rule we can estimate the \aposteriori likelihood under a given prior:
+Estimates for $\mathbf{x}$ which have similar likelihood values $\mathcal{L}(\hat{\mathbf{x}}_1)$ may look very different from each other and might also look different compared to a given ground truth, if available.
+Both the convolution operation
+    and the noise lead to a loss of information in the data which cannot easily be recovered.
+The likelihood surface shows many local, close-by maxima.
+Depending on the starting value used for $\mathbf{x}$ and the optimization algorithm the MLE based estimate is likely to only find a local maxima.
+This is fundamentally the reason for RL decomposing estimates into point sources, described in Section~\ref{sec:related}.
+
+    \subsection{A Posteriori Distribution}
+    When reconstructing images in the context of inverse problems we are operating in a high dimensional parameter space, because each pixel in the image represents a parameter in the optimization process.
+By using prior information we can introduce correlations between the parameters, to reduce the \enquote{effective dimensionality} of the problem and guide the optimization process toward unique and more stable solutions.
+
+    Using Bayes' rule we can estimate the \aposteriori likelihood under a given prior distribution, $P(\mathbf{x} )$:
     %
@@
         \label{eq:bayes}
-        P(\mathbf{x}|\textbf{D}) = P(\mathbf{x} ) \frac{P(\textbf{D} |\mathbf{x})}{P(\textbf{D})}
-    \end{equation}
-
-    And use a Maximum A Posteriori (MAP) approach to find an estimate for $\mathbf{x}$.
-Taking the logarithm of Eq.~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Eq.~\ref{eq:joint} and dropping the normalisation term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we get the following expression for the log-posterior likelihood $\mathcal{L}$ :
+        P(\mathbf{x}|\textbf{D}) = P(\mathbf{x} ) \frac{P(\textbf{D} |\mathbf{x})}{P(\textbf{D})}.
+    \end{equation}
+    %
+    The Maximum A Posteriori (MAP) estimate of $\mathbf{x}$ is the value that maximizes Equation~\ref{eq:bayes}.
+    Taking the logarithm of Equation~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Equation~\ref{eq:joint} and dropping the normalisation term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we obtain the following expression for the log-posterior distribution
+    %likelihood 
+    $\mathcal{L}$ :
     %
@@
         \label{eq:total}
-        \mathcal{L}\left(\mathbf{x} | \mathbf{D} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x})
-    \end{equation}
-
-    Where $\mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)$ represents the summed log-likelihood for an individual observation $j$.
-Additionally the function includes a log-prior term $\mathcal{P}(\mathbf{x})$ and a factor $\beta$ to adjust the weight of the prior with respect to the joint log likelihood term.
-The parameter $\beta$ can be seen as a hyper-parameter, chosen by the user to quantify their belief in the correctness of the chosen prior distribution.
-The choice of the parameter is optional and for all experiments we show later it is simply fixed to $\beta=1$.
+        \mathcal{L}\left(\mathbf{x} | \mathbf{D} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x}),
+    \end{equation}
+    %
+    where $\mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)$ represents the summed log-likelihood for an individual observation $j$ and $\mathcal{P}(\mathbf{x})$ represents the log of the prior distribution with the factor $\beta$ adjusting the weight of the prior relative to the joint log likelihood term.
+The parameter $\beta$ can be viewed as a hyper-parameter, chosen by the user to adjust the strength of the prior distribution relative to the likelihood.
+The choice of $\beta$ is optional and for all experiments presented in this paper we just set $\beta=1$.
 
     \subsection{Patch Based Image Prior}
-    In general it is difficult to capture global image statistics in a prior likelihood taking into account all pixel to pixel correlations.
-The size of the corresponding correlation matrix would grow with the number of pixels squared and thus quickly becomes computationally untraceable.
-However, astronomical images typically only show local correlations between pixels.
-This is because the spatial scale of astrophysical processes in an image is always limited by the finite interaction time and the fact that the interaction cannot propagate faster than the speed of light (structure in the CMB might be an exception here).
+    \label{sec:patch-prior}
+    In general it is difficult to capture global image characteristics in a prior distribution taking into account all pixel to pixel correlations.
+The size of the corresponding correlation matrix would grow with the number of pixels squared and thus quickly become computationally untraceable.
+However, astronomical images typically only show exhibit correlations among the pixels.
+This is because the spatial scale of astrophysical processes in an image is always limited by the finite interaction time and the fact that the interaction cannot propagate faster than the speed of light.
 This means on smaller scales astronomical images often contain basic structures such as edges, corners, filaments or periodic patterns formed by local astrophysical processes.
-For this reason we adopt the idea of a patch based image prior approach as introduced by \cite{Zoran2011}.
-Given a pre-trained Gaussian Mixture Model (GMM) for the distribution of pixel values in patches, we can evaluate a patch based prior for the reconstructed image $\mathbf{x}$ and approximate the \aposteriori likelihood.
-
-    One convenient property of the GMM is the possibility to evaluate its likelihood in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
+For this reason we adopt the patch-based image prior distribution introduced by \cite{Zoran2011}.
+
+    A patch is defined as a small, typically square, region of size $N \times N$ pixels, representing a local neighbourhood in a given image.
+Mathematically we can formulate the extraction of such patches as:
+    %
+    \begin{equation}
+        \mathbf{x}_n = \mathbf{P_n x}
+    \end{equation}
+    %
+    Where $\mathbf{P_n}$ represents a neighbourhood matrix to extract the $n$-th patch from the image $\mathbf{x}$.
+When given many of theses patches we can model the distribution of pixels values within the patch using a Gaussian Mixture Model (GMM).
+
+    A convenient property of the GMM is that its probability can be evaluated in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
     %
@@
         \label{eq:gmm}
-        P_{GMM}(\mathbf{x}_n) = \sum_{k=1}^K \pi_k \mathcal{N}(\mathbf{x}_n| \boldsymbol{\mu}_k, \boldsymbol{\Sigma}_k^2)
-    \end{equation}
-
-    Where $\mathcal{N}$ is a Gaussian distribution, $K$ the total number of components, $\boldsymbol{\mu}_k$ the vector of means for a given component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix and $\pi_k$ the weight of the component.
-The different weights are required to sum to unity such that $\sum_{k=1}^N\pi_k = 1$.
-
-    From Equation~\ref{eq:gmm} we can also derive the log-likelihood for a specific choice of the component $k$:
+        P_{\rm GMM}(\mathbf{x}_n) = \sum_{k=1}^K \pi_k \mathcal{N}(\mathbf{x}_n| \boldsymbol{\mu}_k, \boldsymbol{\Sigma}_k^2),
+    \end{equation}
+    %
+    where $\mathcal{N}$ is a Gaussian distribution, $K$ the number of components in the GMM, $\boldsymbol{\mu}_k$ is the mean vector for a component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix, and $\pi_k$ the weight of component $k$.
+The weights are required to sum to unity such that $\sum_{k=1}^K\pi_k = 1$.
+
+    If we knew the relevant component, $k_n$, we could derive the conditional log-prior distribution directly from Equation~\ref{eq:gmm}:
     %
@@
     \begin{split}
-    \mathcal{P}_{GMM}(k| \mathbf{x}_n) = -\frac{1}{2} \left[ \right. d \log(2\pi)
-    + \log(|\boldsymbol \Sigma_{k}|)\\
-    + (\mathbf{x}_n - \boldsymbol{\mu}_{k})^T \Sigma^{-1}_{k}(\mathbf{x}_n - \boldsymbol{\mu}_{k}) \left. \right]
+    \mathcal{P}_{\rm GMM}(\mathbf{x}_n|k_n) = -\frac{1}{2} \left[ \right. d \log(2\pi)
+    + \log(|\boldsymbol \Sigma_{k_n}|)\\
+    + (\mathbf{x}_n - \boldsymbol{\mu}_{k_n})^T \Sigma^{-1}_{k}(\mathbf{x}_n - \boldsymbol{\mu}_{k_n}) \left. \right]
+    \label{eq:cond.log.prior}
     \end{split}
     \end{equation}
-
-    If we split the image into non-overlapping patches, we can find for each noisy patch $\mathbf{x}_n$ the GMM component $\hat{k}_n$, which maximises the log-likelihood of the GMM:
-    %
-    \begin{equation}
-        \hat{k}_n = \underset{k \in \{1, ..., N\} }{\argmax}{\mathcal{P}_{GMM}(k| \mathbf{x}_n)}
+    %
+    If we split the image $\mathbf{x}$ into multiple non-overlapping patches, for each patch $\mathbf{x}_n$, we can find the GMM component $\hat{k}_n$, which maximises the conditional log-prior distribution given in Equation~\ref{eq:cond.log.prior}:
+    %
+    \begin{equation}
+        \hat{k}_n = \underset{k \in \{1, ..., N\} }{\argmax}{\mathcal{P}_{\rm GMM}(\mathbf{x}_n|k)}
     \end{equation}
     \vspace{0.2em}
-
-    As the number of components in the GMM is typically limited to $\mathcal{O}(<10^2)$ we can do this simply by evaluating the likelihood for each of the components and choose the one with the maximum value of the log-likelihood.
-To finally evaluate the log-likelihood of the total image we can sum up the maximum log-likelihood values of the individual patches:
+    %
+    As the number of components in the GMM is typically limited to $\mathcal{O}(10^2)$ we can optimize the conditional log-prior distribution by simply evaluating it for each of the GMM components and choose the one with the maximum value.
+Finally, to evaluate the log-prior of the full image we sum the maximum values of the individual patches:
     %
@@
     \label{eq:prior-total}
-        \mathcal{P}(\mathbf{x}, \mathbf{k}) = \sum_{n = 1}^N \mathcal{P}_{GMM}(\hat{k}_n | \mathbf{P}_n \mathbf{x})
-    \end{equation}
-
-    Where $\mathbf{P}_n$ is a matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed.
-This way the index $k$ that identifies the most likely GMM component per patch, becomes a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
-The bottom row of Figure~\ref{fig:patches} shows an example of a patch and the same patch represented in the \enquote{Eigenbasis} of the covariance matrices of its three most likely GMM components.
+        \mathcal{P}(\mathbf{x}, \hat{\mathbf{k}}) = 
+        %\mathcal{P}(\mathbf{x} | \hat{\mathbf{k}})  + \mathcal{P}(\hat{\mathbf{k}}) =
+        \sum_{n = 1}^N \mathcal{P}_{\rm GMM}(\mathbf{P}_n \mathbf{x} | \hat{k}_n) +
+        \sum_{n = 1}^N \log \pi_{\hat{k}_n},
+    \end{equation}   
+    %
+    where $\mathbf{P}_n$ is again the matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed.
+\dvd{I think the following should be moved toward the begining of this subsection.
+It clarifies the calculations are you doing above:} In this way the index $k$ that identifies the most likely GMM component per patch is treated as a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
+
+    The bottom row of Figure~\ref{fig:patches} shows an example of a patch along with its representation in the \enquote{Eigenbasis} of the covariance matrices of its three most likely GMM components.
 Visually, the representation of the patch in the Eigenbasis of the covariance results in a denoised version of the patch.
@@
 The bottom row shows the red example patch $\mathbf{x}_n$ on the left.
-The three other patches show the quantity $\Sigma_{k_{GMM}} \mathbf{x}_n$, which is the result of the patch represented in the Eigenbasis of the covariance matrices of the 3 most likely GMM components $k_{GMM} = 105, 77, 17$.
+The three other patches show the quantity $\Sigma_{k} \mathbf{x}_n$, which is the result of the patch represented in the Eigenbasis of the covariance matrices of the 3 most likely GMM components $k = 105, 77, 17$.
 This example uses the GMM learned from the JWST Cas A image.
@@
     \cite{Zoran2011} found that the reconstruction quality could be improved by working with a grid of overlapping patches.
-Such a grid is illustrated in Figure~\ref{fig:patches}.
-However, using a grid of overlapping patches makes the interpretation of the prior as likelihood more difficult, because pixels at the corners and edges of patches are counted multiple times.
-For this we introduce a weighting mask when evaluating the likelihood of the GMM.
-This mask weights the pixels of the patch by their overlap with the neighboring patch.
-Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4, when computing the likelihood for a patch as given by  Equation~\ref{eq:gmm}.
-Apart from this we keep the process of choosing the most likely component unmodified.
-However, we note that in this case we neglected the correlation between neighbouring patches.
+This is illustrated in Figure~\ref{fig:patches}.
+However, using a grid of overlapping patches makes the interpretation of the prior distribution more difficult, because pixels at the corners and edges of patches are counted multiple times.
+For this reason we introduce a weighting mask when evaluating the GMM prior distribution.
+    This mask weighs the pixels of the patch by their overlap with neighboring patches.
+Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4, when computing the prior distribution for a patch as given by  Equation~\ref{eq:gmm}.
+Apart from this the process for choosing the most likely GMM prior component remains unmodified.
+However, we note that in this case we neglected the prior dependence between neighbouring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixes and are thus clearly not \aprioir independent.}.
 As the choice of the GMM component per patch is discrete, a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
@@
 While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, because every morphological feature would need to be present at many levels of intensity.
-While this could be handled by introducing a lot more components to the GMM, it seems unfeasible in practice due to the limited availability of training data and computational resources.
-For this reason we propose the following modified normalisation for the patches instead:
+While this could be handled by introducing significantly more components to the GMM, it seems unfeasible in practice due to the limited availability of training data and computational resources.
+For this reason we instead propose a modified normalisation for the patches:
     %
@@
     \end{equation}
-
-    With dividing by the mean of the patch $\Bar{\mathbf{x}}_n$ the structure in the patch becomes independent of the total brightness the patch contains.
-This results in patches being grouped only by their pixel to pixel correlation structure and not by total contrast.
-This corresponds to the assumption that the structure in the patch is statistically independent of the total flux contained in the patch, which we consider a valid assumption for astronomical images.
+    %
+    By dividing by the mean of the patch, $\Bar{\mathbf{x}}_n$, the structure in the patch becomes independent of the total brightness the patch contains.
+This results in patches being grouped only by their pixel to pixel contrast and not by their overall brightness.
+This corresponds to the assumption that the structure in the patch is \aprioir independent of the total flux contained in the patch, which we consider a valid assumption for astronomical images.
 This also generalizes to the prior likelihood of the whole image described by Equation~\ref{eq:prior-total}.
 The value of the prior likelihood becomes independent of the total flux contained in the image.
-The prior just regularizes the structure in the image, while the overall intensities are typically well constrained by the Poisson likelihood term.
+The prior distribution simply regularizes the structure in the image, while the overall intensities are typically well constrained by the Poisson likelihood term.
+Thus we only assume a flat prior patch intensities.
 
@@
     The evaluation of the patch prior divides the reconstructed image into a fixed grid of overlapping patches.
-To avoid artifacts in the reconstruction due to the fixed position of the grid, we use the method of \enquote{cycle spinning}.
-Before evaluating the patch prior we randomly shift the image $\mathbf{x}$ by a given number of pixels in x and y direction.
-Were the shift is smaller than half the size of a patch.
+To avoid artifacts in the reconstruction due to the fixed position of the grid, we use the method of \enquote{cycle spinning} \citep{Coifman1995}.
+Before evaluating the patch prior we shift the image $\mathbf{x}$ by a random number of pixels in both the x and y direction, where the shift is less than or equal to half the size of a patch.
 The same method has, for example, been used in \cite{Esch2004}.
-We also experimented with cycle spinning by a sub-pixel amount, mostly for the reconstruction of point sources.
-However, we later introduced the possibility to reconstruct an upsampled version of $\mathbf{x}$, which made the sub-pixel cycle-spinning mostly redundant.
-
-    A variation of cycle spinning specifically for the patch prior was proposed by \cite{Parameswaran2018}.
-Instead of a regular grid for the patches they proposed to work with a randomised grid of patches, where the center of each patch was randomly shifted, while ensuring that patches still overlap by at least one pixel.
-In doing so they found they could work with a smaller total number of patches, while retaining the same reconstruction quality.
-This improved the computational performance of the method.
-We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction was slightly faster with the same reconstruction quality.
-However for all results shown later in the manuscript we chose the simple cycle spinning with upsampling.
+
+    A variation of cycle spinning specifically for the patch prior is proposed in \cite{Parameswaran2018}.
+Instead of a regular grid for the patches they propose to work with a randomised grid of patches, where the center of each patch is randomly shifted, while ensuring that patches still overlap by at least one pixel.
+In doing so they find that a smaller total number of patches can be used, while retaining the same reconstruction quality.
+This improves the computational performance of the method.
+We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction is slightly faster with the same reconstruction quality.
+However for all results shown later in the manuscript we chose the simple cycle spinning described in the previous section.
 
@@
     \subsection{Systematic Errors of Predicted Counts}
-    Each observation $\mathbf{D_j}$ comes with associated systematic errors.
-This includes for example the pointing accuracy of the telescopes: when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object might vary in the image between different observations.
-The process of correcting for these inaccuracies is called \textit{astrometry} and a standard procedure in for example \chandra data analysis.
+    Each observation $\mathbf{D_j}$ is subject to systematic errors.
+For example, the pointing accuracy of the telescope when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object may vary among the  observations.
+The process of correcting for these inaccuracies is called \textit{astrometry} and is a standard procedure in for example \chandra data analysis.
 A second example of systematic errors is the variation of background emission between multiple observations.
 
-    To account for both systematic effects we extend the model for the predicted counts introduced in Eq.~\ref{eq:model}, by a background normalisation factor $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$, which is specific for each observation.
-This yields the following modified model definition:
+    To account for both systematic effects we extend the model in Equation~\ref{eq:model} for the predicted counts, by a background normalisation factor $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$, which is specific for each observation.
+This yields the following modified model:
     %
@@
         \label{eq:model-npred-calibration}
-        \mathbf{\lambda}_j = \mathrm{PSF}_j \circledast \left(\mathbf{E}_j \cdot (\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j}) + \alpha_j \cdot \mathbf{B}_j) \right)
-    \end{equation}
-
+        \mathbf{\lambda}_j = \mathbf{E}_j \cdot  \left(\mathrm{PSF}_j \circledast \phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})\right) + \alpha_j \cdot \mathbf{B}_j
+    \end{equation}
+    %
     In practice one observation is used as a reference and its corresponding systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during optimization.
@@
     \subsection{Estimation of Statistical Errors}
-    Estimating the global covariance matrix for image based data is computationally not feasible, because the size of the matrix scales with the squared number of pixels in the image.
-However, there are a few ways to estimate the statistical uncertainties associated with the flux image.
-We propose three methods for this:
+    Estimating the global covariance matrix for estimated image is computationally infeasible, because the size of the matrix grows with the squared number of pixels.
+However, there are other ways to estimate the statistical uncertainties associated with the flux image.
+We propose three methods:
 
     \begin{itemize}
-    \item The first method is bootstrapping of observations.
-Given that multiple observations of the same region of the sky are available, \jolideco can be run repeatedly on a random subset of those.
-This results in a set of reconstructed images which are sampled from the posterior distribution.
-Depending on the size of the images the associated computational effort can be very large as it requires running \jolideco many times to achieve sufficient statistics.
-
-    \item If only one or few observations are available we propose bootstrapping of the events used to compute the counts image instead.
-This basically corresponds to splitting a single observation into multiple ones by splitting the single exposure into multiple time intervals.
-This way one can apply the first proposed method again.
-
-    \item We can also estimate the diagonal of the Hessian. However this is numerically challenging because of the random elements in the method, such as stochastic gradient decent and cycle spinning.
-
+    \item \textbf{Bootstrapping Observations}.
+Given that multiple observations of the same region of the sky are available, \jolideco can be run repeatedly on a random subset of images.
+This results in a set of reconstructed images representing a distribution from which we can estimate the errors on $\mathbf{x}$.
+Depending on the size and number of the images the associated computational effort can be very large as it requires running \jolideco many times to sufficiently describe uncertainty in the fitted image.
+
+    \item \textbf{Bootstrapping Events}.
+If only one or few observations are available we propose bootstrapping of the events used to compute the counts image(s).
+This corresponds to splitting a single observation into multiple observations by splitting the single exposure into multiple time intervals.
+This way one can apply the first proposed method.
     \end{itemize}
+
+    We also experimented with computing the diagonal of Hessian of the posterior distribution at the minimum.
+However we found this numerically challenging because of the random elements, such as cycle spinning and SGD in the method.
+Which yields no stable second derivative.
 
@@
 
-    \todo{This is Bias-Variance trade-off: if all data is used to deconvolve minimizes the statistical error, however the result might be biased... }
-
-    \todo{One could try to estimate a sparse covariance matrix...or approximate it using the GMM covariance...}
-
     \section{Implementation}
     \subsection{Jolideco Framework}
-    The goal of the reconstruction process is to optimize the a-posteriori likelihood defined by Equation~\ref{eq:total}.
-Given that each pixel in the reconstructed image represents an independent parameter this represents a high dimensional optimization problem.
-Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019} allow for solving these kind of high dimensional modeling problems, by using back-propagation and adapted optimization methods for high dimensional models such as stochastic gradient decent.
-The latter is also applicable in our case, as we work with multiple observations at the same time, where a subset of those represents a \enquote{batch} in terms of ML.
-
-    We implemented the \jolideco method as an independent Python package, based on \texttt{PyTorch} as optimization back-end.
-We tried to define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of the patch normalisation, the choice of GMM models, optimization methods and serialisation formats for the reconstruction results as well as corresponding diagnostic information, such as the trace of the posterior and prior likelihood values.
-We hope that this simplifies the future improvement and extension of the package as well as the adoption by the astromical community.
-The package is available at \url{https://github.com/jolideco/jolideco}.
-
-    We also use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
+    The goal of the reconstruction process is to optimize the a-posteriori likelihood defined by Equation~\ref{eq:total}. Given that there is a parameter for each pixel in the image,  
+    this is a high dimensional optimization problem.
+Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019} allow for solving high dimensional optimization problems using back-propagation and adapted optimization methods such as stochastic gradient decent (SGD).
+The latter is also applicable in our case, as we work with multiple observations at the same time, where a subset of the observations represents a \enquote{mini batch} in terms of ML.
+
+    We implemented the \jolideco method as an independent Python package, based on \texttt{PyTorch} as the back-end optimizer.
+We define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of the patch normalisation, the choice of GMM models, optimization methods, and serialisation formats for the reconstruction results as well as the corresponding diagnostic information, such as the trace of the posterior and prior likelihood values.
+This will simplify future improvement and extension of the package as well as the adoption of \jolideco by the astronomical community.
+The package is available on the platform GitHub\footnote{\url{https://github.com/jolideco/jolideco}}.
+
+    We use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
 To learn the Gaussian Mixture Models from patches we use the standard implementation provided in the \texttt{Scikit-Learn}~\citep{scikit-learn} package.
@@
 
-    \subsection{Jolideco GMM Library}
+    \subsection{Learning GMMs}
     \label{ssec:jolideco-gmm-library}
+    The patch based image prior described in Section~\ref{sec:patch-prior} requires pre-trained GMMs.
+We train the GMM by choosing a set of reference images, splitting them into patches of size $8\times8$ pixels and learning a GMM with $N$-components from the whole distribution of patches.
+
     In general the strength of the GMM prior is its high \enquote{expressiveness}.
-This means the prior contains a large variety of structural shapes and has a lot of freedom to adapt to the data in the optimization process.
-On radio data \cite{Bouman2016} found their results to be mostly independent of the choice of data the GMM prior was learned on.
+This means the prior distribution contains a large variety of structural shapes and has freedom to adapt to the data in the optimization process by choosing the most likely GMM component for each patch in the image.
+With radio data \cite{Bouman2016} found their results to be mostly independent of the choice of data the GMM prior was learned on.
+
     However, in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of the data the GMM was learned on.
-The choice of the prior becomes more important and to avoid introducing a strong bias it should be adapted to the analysis scenario.
-For this reason and for purposes of testing we learned and provide a selection of GMMs (a library) to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
+Simply because the prior distribution is more influential when the data is less informative.
+Thus, the prior should be adapted to the particular analysis scenario in order to avoid bias.
+For this reason and for purposes of testing we learned and provide a selection of GMMs to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
 
     \subsubsection{Zoran \& Weiss}
-    As baseline reference we use the original GMM provided by \cite{Zoran2011}.
-The model was learned from the Berkeley image database \citep{Martin2001} which contains natural images and images of every day scenes and objects.
-The model was learned by splitting the training images into patches of size 8x8 pixels.
-This resulted in a training set of $2 \cdot 10^{6}$ patches, which were used to fit a GMM with 200 components.
+    As a baseline reference we use the original trained GMM provided by \cite{Zoran2011}.
+It was trained from the Berkeley image database \citep{Martin2001} which contains natural images and images of every day scenes and objects.
+
+    The training images were split into patches of size 8x8 pixels, resulting in a training set of $2 \cdot 10^{6}$ patches which were used to fit a GMM with 200 components.The training patches were mean subtracted before the GMM was fit.
 The model is provided by the authors as part of the source code for download\footnote{\url{https://people.csail.mit.edu/danielzoran/epllcode.zip}}.
-More details of how the model was learned are given in the original publication.
-This model relies on subtraction of the mean of the patch for normalisation.
+More details of how the model was trained are given in the original publication.
 
@@
     \subsubsection{Chandra SNRs}
-    \label{sssec:chandra-snrs} Because of the limited statistics we did not use any oversampling but kept the pixel.
+    \label{sssec:chandra-snrs}
+    To demonstrate the flexibility in the selection of data to train the GMM, we also chose a selection of high signal-to-noise images from the \chandra catalog of of Supernova remnants.
+
+    Because of the limited statistics we did not use any oversampling but kept the pixel.
 Astrophysical processes forming the morphological structures are typically self-similar.
@@
 
-    \subsection{Computational Performance}
-    We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations as well as large images.
-
-    \begin{itemize}
-        \item Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
-        \item We tried the binary search tree as proposed in \cite{Parameswaran2018},
-        but without success, most likely because the native \texttt{Pytorch} support
-        for parallelization speeds up the standard GMM quite a bit...
-        \item GPU support via Pytorch
-    \end{itemize}
-
     \subsection{Optimization Strategy}
-    Maximising the \aposteriori likelihood defined Eq.\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
+    Maximising the \aposteriori likelihood defined Equation~\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
 
     To improve the convergence rate of the optimization process we employ the following optimization strategy: the optimization strategy begins with the optimizer viewing $\log{\mathbf{x}}$, and the first step involves running a rough estimate using a uniform prior.
-This step is optional, but if chosen, the next step involves optimizing the parameters associated with the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
+This step is optional, but if chosen, the next step involves optimizing the parameters associated with the systematic error described in Equation~\ref{eq:model-npred-calibration}.
 Following this, a full optimization is performed using the patch prior, which can be computationally expensive.
@@
         \item First run with uniform prior, to get a rough estimate
-        \item (optional) Then optimize the parameters associated to the systematic error described in Eq.~\ref{eq:model-npred-calibration}.
+        \item (optional) Then optimize the parameters associated to the systematic error described in Equation~\ref{eq:model-npred-calibration}.
         \item Then we go for a full optimization using the patch prior, which can be computationally costly
@@
     \label{subsec:test-datasets}
-
-    \vlk{We have devised several test patterns that are designed to exercise and stress test deconvolution algorithms for low counts images.
-The patters consist of both point and extended sources, with strengths characteristic of typical observations, arranged with different spacings between the sources, and include point sources superposed on extended sources, as well as different background levels.
-The goal of the patterns is not to set up or devise a ``perfect'' deconvolution algorithm, but to help assess their relative strengths and limitations.
-The source patterns are described in Appendix~\\ref{sec:appA}.
-
-    We adopt two distinct scenarios, one which mimics \textit{Chandra} observations with a sharp PSF (a Gaussian with $\sigma=2$~pix) and low background (at 0.01, 0.1, and 1 ct~pix$^{-1}$) but lower effective area (nominally with an exposure of 1 unit), and the other which mimics XMM-\textit{Newton} observations with a broader PSF ($\sigma=3$~pix), higher background (at 0.1, 1, and 10 ct~pix$^{-1}$), and higher effective area (imitated with an exposure of 5 units).
-    }
+    We have designed multiple test scenarios to challenge the several deconvolution algorithms listed in Section~\ref{subsec:methods} and to evaluate and compare their performance.
+The test scenarios consist of mixtures of point and extended sources, with typical morphological characteristics of astrophysical sources.
+We arranged the sources in different spatial patterns and with different spacings between them.
+We include point sources superposed on extended sources \dvd{in four arrangements labelled A--D in the first row of Figure~\ref{fig:scenarios}.} Each spatial arrangement is crossed with several signal-to-noise ratios (obtained with a constant background),
+    %is as well as different 
+    %levels of constant background emission,
+    \dvd{denoted 1--X.
+The resulting scenarios are denoted by concatenating the two labels, e.g., A3 or C1, see Appendix~\ref{sec:app:A} for details.}  The goal of these experiments is not to set up or devise a \enquote{perfect} deconvolution algorithm, but to help assess their relative strengths and limitations.
+
+    In addition we adopt two distinct instrument scenarios: one which mimics \textit{Chandra} observations with a sharp PSF (a Gaussian with $\sigma=2$~pix) and low background (at 0.01, 0.1, and 1 ct~pix$^{-1}$) but lower effective area (nominally with an exposure of 1 unit), and the other which mimics XMM-\textit{Newton} observations with a broader PSF ($\sigma=3$~pix), higher background (at 0.1, 1, and 10 ct~pix$^{-1}$), and higher effective area (imitated with an exposure of 5 units).
 
@@
 The details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios}.
-In addition we also assume a constant background with varying levels of $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
+    %In addition we also 
+    We assume a constant background with varying levels of $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
 
@@
         \centering\includegraphics{figures/scenarios.pdf}
-        \caption{Illustration of the expected counts for the different source scenarios we used to make test datasets.
+        \caption{Illustration of the expected counts for the different source scenarios we used to generate test datasets.
 The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}).
-For the instrument scenario \chandra we convolved the ground truth image with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
-For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix and a five times increased effective are.
+For the instrument scenario \chandra we convolve the ground truth image with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
+For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix \dvd{same as \chandra?} and an effective area that is five times larger than that of \chandra.
 All images are of size $128{\times}128$ pixels.
@@
 
-    \begin{table*}[t]
-    \label{tab:scenarios}
-      \centering
-      \begin{tabular}{l|cr}
-        \hline
-        Scenario & Description & Parameters \\
-        \hline
-        A1 & A grid of point sources & x, y \\
-        B1-3 & Extended Gaussian shaped source surrounded by point sources & $\sigma$ \\
-        C1-3 & Point Sources on top of a disk shaped source, jet like line features & $r_{\mathrm{Disk}}$ \\
-        D1-5 & A spiral-arm structure surrounded by point sources and a large ring like feature & 9 \\
-        \hline
-      \end{tabular}
-      \caption{Source scenarios, \todo{maybe we find a good structure for the table...would list the actual flux values per component}}
-      \label{tab:1}
-    \end{table*}
-
     \subsection{Methods}
     \label{subsec:methods}
-    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we use the following methods:
-
-    \begin{itemize}
-        \item \textbf{Pylira}: first we use the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
+    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we compare the following methods:
+
+    \begin{enumerate}
+
+        \item[\bf M1.] \textbf{Pylira}: we implement the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
 We rely on the default prior definition and keep the background norm fixed.
-In total we run the sampling process for 5000 iterations and use the first 500 iterations as a \endquote{burn-in} period to allow the MCMC chain to converge.
-Then we compute the mean of the posterior distribution ignoring the burn-in period.
-
-        \item \textbf{Jolideco (Uniform, n=10)}: second we use \jolideco with a uniform prior and 10 iterations.
-This setup we consider as a baseline method reference similar to RL.
-While the optimization procedure is different, we still expect to see similar behaviour for the local correlations of pixels.
-This ad hoc approach of early stopping is often used in practice to regularise the RL method.
-
-        \item \textbf{Jolideco (Uniform, n=1000)}: again we use \jolideco with a uniform prior but running for 1000 iterations.
-Sames as above except without early stopping.
+In total we run the MCMC sampler for 5000 iterations and discard the first 500 iterations as a \enquote{burn-in} period to allow the MCMC chain to converge.
+We compute the mean of the posterior distribution ignoring the burn-in period.
+
+        \item[\bf M2.] \textbf{Jolideco (Uniform, n=10)}: we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, \dvd{running the optimizer for} 10 iterations.
+We consider this as a baseline method reference similar to RL.
+While the optimization procedure is different, we expect similar behaviour for the local correlations of pixels.
+This ad hoc approach of early stopping is often used in practice to regularise the RL output.
+
+        \item[\bf M3.] \textbf{Jolideco (Uniform, n=1000)}:  we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, but running \dvd{the optimzier} for 1000 iterations.
+This is the same as above but without early stopping.
 This gives rise to the issue of RL decomposing extended emission into point sources.
 
-        \item \textbf{Jolideco (Patch, GLEAM v0.1)}: \jolideco with a patch prior learned on GLEAM data, described in Section~\ref{sssec:gleam-radio-data}.
-It also uses the standardised patch normalisation as described by Equation~\ref{eq:patch-norm}.
-We use cycle spinning, a stride of 4 pixels and 2000 \textit{training epochs}.
-Given 5 observations this results in 10,000 iterations.
-Which optimizes \enquote{to end} until there is no relevant change in the posterior log-likelihood.
-In addition we use an upsampling factor of 2.
-
-        \item \textbf{Jolideco (Patch, Zoran-Weiss)}: \jolideco with a patch prior from \cite{Zoran2011} and the mean subtracted patch norm.
-This is for comparison to the original method and the method used in \cite{Bouman2016}.
+        \item[\bf M4.] \textbf{Jolideco (Patch, GLEAM v0.1)}: we use \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalisation described by Equation~\ref{eq:patch-norm}.
+We use cycle spinning and 2000 \enquote{training epochs}.
+Where one training epoch corresponds to a full iteration over all observations.
+By visualizing the value of the log-posterior we verified
+
+        \dvd{are ``stride'' and ``training epochs'' defined somewhere?} Given 5 observations this results in \dvd{a total of} 10,000 iterations.
+\dvd{What does the following mean?
+Is this a convergence criterion?
+But you just said you run for a fixed number of iterations.} Which optimizes \enquote{to end} until there is no relevant change in the posterior log-likelihood.
+In addition we use an upsampling \dvd{define?} factor of 2.
+
+        \item[\bf M5.] \textbf{Jolideco (Patch, Zoran-Weiss)}: we use \jolideco with the patch prior of \cite{Zoran2011} and the mean subtracted patch norm \dvd{is this the same as ``the patch normalisation described by Equation~\ref{eq:patch-norm}''?
+Best to use the same language for clarity.}.
+This is for comparison to the original \dvd{be more specific} method and the method used in \cite{Bouman2016}.
 We use a maximum image norm with the maximum values defined by the ground truth.
-        \footnote{This is not completely fair, as it requires knowledge of the brightest expected pixel in $\mathbf{x}$, however in practice this information could be estimated from the brightest pixel in the data and the shape of the PSF.}
-    \end{itemize}
-
-    We ran the comparison on all combinations of methods, source scenarios, background levels and instrument scenarios.
-However, in the following we only discuss the subset of the results, that we consider the most relevant.
+\dvd{Is this the convergence criterion?
+Do you describe what this means somewhere?}\footnote{This is not completely fair, as it requires knowledge of the brightest expected pixel in $\mathbf{x}$.
+In practice this could be estimated from the brightest pixel in the data and the shape of the PSF.}
+    \end{enumerate}
+
+    We ran the comparison on all combinations of methods, source scenarios, background levels, and instrument scenarios.
+Here we only discuss the subset of the results, that we consider the most relevant.
 The complete set of results is available at \url{https://jolideco.github.io/jolideco-comparison}.
@@
             \caption{
-                Comparison of different deconvolution methods and prior assumptions for different selected source scenarios, as described in Section~\ref{subsec:test-datasets}.
-The simulation of the data for this figure used a fixed background level of $\lambda_{Bkg} = \qty[mode = math]{0.01}{cts/pix}$, a uniform exposure and a Gaussian PSF of width $\sigma_{PSF} = \qty[mode = math]{2}{pix}$, corresponding to the \enquote{Chandra} instrument scenario.
-The leftmost column shows the simulated counts data and the second most column from the left the underlying ground truth to compare.
-The other columns show the reconstructed flux by the different methods and prior assumptions for \jolideconospace.
+                Comparison of the different deconvolution methods and prior assumptions for selected source scenarios, as described in Section~\ref{subsec:test-datasets}.
+The simulations \dvd{depicted} %of the data for this figure
+                used a fixed background level of $\lambda_{Bkg} = \qty[mode = math]{0.01}{cts/pix}$, a uniform exposure, and a Gaussian PSF of width $\sigma_{PSF} = \qty[mode = math]{2}{pix}$, corresponding to the \enquote{Chandra} instrument scenario.
+The leftmost column shows the simulated counts and the second column %from the left
+                shows the underlying ground truth.% to compare. 
+                The remaining columns show the reconstructed flux for each method and prior assumptions for \jolideconospace.
 To enhance weak structures the images use an $\arcsinh$ stretching with a scale parameter of $a=0.02$.
@@
     %
-    First we compare the performance of methods and different prior assumptions on the different source scenarios.
-Figure \ref{fig:comparison-scenarios} shows the results for the selected subset of scenarios A1, B3, C3 and D4.
-
-    On scenario A1 all methods show acceptable to excellent results for the isolated point sources in the upper right of the image.
+    First we compare the performance of the five methods (and their differing prior assumptions) on the different source scenarios.
+Figure \ref{fig:comparison-scenarios} shows the results for the selected subset of scenarios, i.e., on A1, B3, C3 and D4.
+\dvd{What do the numbers refer to?}
+
+    On scenario A1 all methods provide acceptable to excellent results for the isolated point sources in the upper right of the image.
 This demonstrates all methods take into account the PSF and background models correctly.
-The early stopped uniform prior still shows an extension for those cases, because the optimization process has not finished.
-Optimizing for 1000 iterations clearly improves the result and shows almost perfect point sources corresponding to the size of approximately one pixel.
-The \jolideco method with the Zoran-Weiss patch prior results in less sharp images, because the prior has been learned on natural images of landscapes and every day objects and scenes, which do not include point sources.
-The \jolideco method with the prior learned from GLEAM data, which also includes point sources, shows much improved results.
-However not as sharp as the results obtained with the uniform prior.
-In the lower left of the image the point sources become fainter and move closer, challenging all methods in succeeding to separate those as independent sources.
-The uniform prior optimized \enquote{to end} shows good results, still separating the sources.
-All other methods cannot fully resolve weak and close by point sources.
+The early stopped uniform prior of M2 shows an extension for these cases, because the optimization process has not finished.
+M3, which optimizes for 1000 iterations, clearly improves the result and shows almost perfect point sources corresponding to the size of approximately one pixel.
+The \jolideco method with the Zoran-Weiss  patch prior (M4) results in less sharp images, because the prior has been learned on natural images of landscapes and every day objects and scenes, which \dvd{typically} do not include point sources.
+The \jolideco method with the prior learned from GLEAM data (M5), which also includes point sources, shows much improved results \dvd{relative to M4 but is}
+    %However 
+    not as sharp as the results obtained with the uniform prior (M3).
+In the lower left of the image the point sources are fainter and closer together, challenging all methods.% in succeeding to separate them into separate sources.
+    The uniform prior optimized \enquote{to end} (M3) shows good results, separating the sources well. All other methods, however, cannot fully resolve these weak and closely situated point sources.
 
     For scenario B3 all methods recover the point sources well.
-However, a large difference can be observed in the reconstruction of the Gaussian shaped extended sources.
-As expected, the uniform prior assumption lets the emission decompose into many point sources, neglecting the spatial correlation between them.
-Pylira shows slightly improved results with the gaps between the bright emission peeks being more filled, however, it still lacks a convincing result of reconstructing the source as a single object.
-The \jolideco method with the patch priors shows the best results both visually as well as measured by the SSI.
-With the GLEAM v0.1 patch prior the reconstruction is almost perfectly, visually almost indistinguishable from the ground truth.
+There is, however, a large difference  in the reconstruction of the Gaussian shaped extended sources.
+As expected, the uniform prior assumption lets the emission decompose into many point sources, neglecting the spatial correlations among them.
+Pylira shows slightly improved results with the gaps between the bright emission peeks being more filled, however, it still lacks a convincing result of reconstructing the source into a single object.
+The \jolideco method with the patch priors shows the best results both visually and as measured by the SSI.
+With the GLEAM v0.1 patch prior the reconstruction is almost perfect, visually almost indistinguishable from the ground truth.
 The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a more visible extension in the surrounding point sources.
 
-    Scenario C3 challenges the methods to reconstruct a weak extended source under four brighter point sources.
-While again all methods reconstruct the point sources well, the visual differences are large for the weak underlying extended emission.
+    The weak extended source with four embedded brighter point sources of Scenario C3 is challenging for all the methods.
+While the methods again reconstruct the point sources well, the visual differences are large for the weak underlying extended emission.
 The uniform prior with 1000 iterations decomposes the extended source into a grid of almost equidistant point sources resembling only the outer boundary of the original source.
-Pylira shows a similar tendency but already improves the reconstruction of the extended source by leaving more emission in between the bright emission spots.
+Pylira shows a similar tendency but improves the reconstruction of the extended source by leaving more emission in between the bright emission spots.
 The best results are achieved by the patch priors, which reconstruct a plausible extended source with approximately uniform brightness.
-The jet like features in the same scenario are decomposed into a \enquote{thread} of point sources by the uniform prior and Pylira method.
+The jet like features %in the same scenario
+    are decomposed into a \enquote{thread} of point sources by the uniform prior and Pylira method.
 The patch prior achieves a much more plausible reconstruction with almost uniform brightness for the linear structures.
-We also note that the patch prior does not show a preferred direction or bias in reconstruction, that is possibly encoded in the training data.
-
-    The last scenario D4 shows a similar result as the previous test: the uniform prior and Pylira decompose the spiral and ring like structure in the image.
+We also note that the patch prior does not show a preferred direction or bias in reconstruction, that could be possibly encoded in the training data.
+\dvd{Do you want to say something about the point soures?}
+
+    The last scenario D4 shows a similar result as the previous test: the uniform prior and Pylira decompose the spiral and ring like structure of the image into points.
 The patch priors reconstruct a visually much more plausible flux image.
 
-    In summary \jolideco shows excellent performance of a variety of morphological shapes.
-It converges to the reference solution for a very high signal to noise image.
-We find the prior learned from GLEAM data to be a very good compromise between the ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
+    In summary \jolideco shows excellent performance on a variety of morphological shapes.
+It converges to the reference solution for very high signal to noise images.
+We find the prior learned from the GLEAM data to be a very good compromise between the ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
 
@@
             \caption{
-                Comparison of the \jolideco method with the GLEAM v0.1 prior for different background levels and signal strength represented by scenario D1-5.
-The images are grouped by background levels with each column group showing the counts data in the left column and the reconstruction in the right column.
-The rows show the scenarios D1-5 as described in Section~\ref{subsec:test-datasets}.
+                Comparison of \jolideco with the GLEAM v0.1 prior for different background levels and signal strength, as represented by scenario D1-D5.
+The images are grouped by background level with each pair of columns showing the counts data in the left column and the reconstruction in the right column.
+The rows show the scenarios D1-D5 as described in Section~\ref{subsec:test-datasets}.
 The background levels correspond to \qty[mode = text]{0.001}{cts / pixel}, \qty[mode = text]{0.01}{cts / pixel} and \qty[mode = text]{0.1}{cts / pixel}.
@@
     As a second experiment we explore the dependency of the results on the background level and signal strength.
-Figure~\ref{fig:comparison-signal-noise} shows the results for the \jolideco method with the GLEAM prior in the scenario D1-5.
+Figure~\ref{fig:comparison-signal-noise} shows the results for the \jolideco method with the GLEAM prior in Scenario D1-D5.
 The background level varies between $\lambda_{Bkg}= 0.01, 0.1$ and \qty[mode = text]{1}{counts/pixel}.
@@
 Visually the method converges to the ground truth for very high signal-to-noise ratio.
-Once the signal strength becomes very large there is no dependency of the result on the background level anymore.
-This especially valid for scenario D5
-
-    We observe the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
+Indeed with very high signal strength there is no dependency of the result on the background level, particularly in %This especially valid for
+    Scenario~D5. On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
 
@@
             \caption{
-                Comparison of the \jolideco method with the GLEAM v0.1 prior for the different instrument scenarios.
-The images are grouped by instrument scenario with each column group showing the counts data in the left column and the reconstruction in the right column.
-The rows show the scenarios D1-5 as described in Section\ref{subsec:test-datasets}.
+                Comparison of \jolideco with the GLEAM v0.1 prior for the different instrument scenarios.
+The images are grouped by instrument scenario with each pair of columns showing the counts data in the left column and the reconstruction in the right column.
+The rows show the scenarios D1-D5 as described in Section\ref{subsec:test-datasets}.
                 All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
@@
     %
-    Finally we compare the results from the \jolideco method for the different instrument scenarios.
+    Finally we compare \jolideco results  for the different instrument scenarios.
 Figure~\ref{fig:comparison-instruments} shows the data as well as flux images reconstructed using \jolideco and the GLEAM v0.1 patch prior.
-We consider the source scenarios D1-5 and the instrument scenarios \enquote{Chandra} and \enquote{XMM} as well as the combination of their data to reconstruct a single image.
-
-    Using the data from the \enquote{Chandra} scenario alone results in a good reconstruction at all variations of scenario D.
+We consider source Scenarios~D1-D5 and the  \enquote{Chandra} and \enquote{XMM} instrument scenarios as well as using a combination of their data to reconstruct a single image.
+
+    Using the data from the \enquote{Chandra} scenario alone results in a good reconstruction in all variations of scenario D.
 As expected the reconstruction quality improves for higher signal to noise ratio.
@@
 The ring structure is sharpened considerably in all cases as well.
-The near-by point sources left and right to the spiral arm structure cannot be separated into individual point sources, but still appear with improved
-    signal-to-noise ratio. This is an inherent limitation of the method. \todo{how far are those apart compared to the PSF? Hoes does this compare to the point scenario with XMM?}
+The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but still appear with improved
+    signal-to-noise ratio.
+This is an inherent limitation of the method.
+\dvd{Limitation of the method or of the data?} \todo{how far are those apart compared to the PSF?
+Hoes does this compare to the point scenario with XMM?}
 
     Combining the data results in the best reconstruction quality.
-The addition of the lower resolution \enquote{XMM} data does not negatively affect the quality of the reconstruction.
+The addition of the lower resolution \enquote{XMM} data does not negatively affect the quality of the overall reconstruction.
 When comparing the D5 scenario we see that the \enquote{Chandra} reconstruction shows a very good reconstruction of the spiral structure but still shows speckles in the surrounding ring.
 The latter suggests that the prior is not strong enough to maintain the pixel to pixel correlations in the case of high signal strength.
-The strength of the prior could be increased with the $\beta$ parameter, but for this study we did not tweak individual parameters, but just used the default configuration.
-The speckle behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the ring is smoother.
+The strength of the prior could be increased with the $\beta$ parameter, but for this study we did not tweak individual parameters, but instead used the default configuration.
+The specklely behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the ring is smoother.
 In this case the correlation between pixels that are further apart is stronger because of the larger correlation PSF.
@@
             \caption{
-               Result of the \jolideco method applied to \chandra data of the SNR \textit{1E~0102.2–7219}.
-The left large image shows the summed counts from 25 observations.
-The right large image  shows the result from the \jolideco deconvolution process.
-The flux is given as counts relative to the reference observation with ID=1308.
+               \jolideco result \dvd{for}
+               %of the \jolideco method applied to 
+               \chandra \dvd{observations of} %data of the 
+               SNR \textit{1E~0102.2–7219}. The \dvd{bottom} left %large 
+               image shows the summed counts from 25 observations. The bottom right image  shows the %result from 
+               the \jolideco deconvolution. %process. 
+               The flux is given as counts relative to \dvd{obsID}
+               %the reference observation with ID=
+               1308.
 The panels \textit{Zoom A}, \textit{Zoom B} and \textit{Zoom C} show a zoomed-in version of three example regions in the SNR, marked with the white rectangles in the large images.
@@
     \subsubsection{Image Example}
-    First we apply our method to a set of short exposure observations of the SNR \textit{1E~0102.2–7219} by the \chandra telescope and combine them into a single deep observation using \jolideco and the patch prior learned from JWST data.
-In total, we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS instrument and no grating.
+    First we apply \jolideco} to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data.
+In total, we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS-S instrument and no grating.
 
     We reduced the data using \texttt{ciao} v4.15 and a custom \texttt{snakemake} workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
-For the counts image we selected the energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandra.
+For the counts image we selected an energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandra.
 This corresponds to an absolute  pixel size of $\approx$~\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of Chandra's PSF.
-\chandra's instrument response varies with the observation offset and energy \citep{ChandraPOG2022}, so we simulated the PSF for each observation independently using the tool \texttt{marx} \citep{Davis2012} and the \texttt{simulate\_psf} script.
-As reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
+\chandra's instrument response varies with the observation offset and energy \citep{ChandraPOG2022}, so we simulated the PSF for each observation independently using the \texttt{marx} tool \citep{Davis2012} and the \texttt{simulate\_psf} script.
+As a reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
 We converted the spectral script from XSPEC to sherpa using the helper script \texttt{convert\_xspec\_script}.
@@
 We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation.
-As reference we chose the observation with ID 1308.
-For \jolideco we used the GMM prior learned on the JWST Cas A image.
-As there is a lot of counts in the image we additionally used an oversampling factor of 2.
-For each observation we allowed the background level and position calibration to vary.
-As reference for the positional shift we also used the observation with the ID 1308.
-Figure~\ref{fig:example-chandra} shows the final result.
-\jolideco clearly improves both the angular resolution as well as reduces the noise of the counts image.
-
-    \textbf{Zoom A} shows an example for a filamentous structure in more detail.
+As reference we chose the %observation with
+    \dvd{obsID} 1308. For \jolideco we use the GMM prior learned on the JWST Cas A image. As there are many counts in the image we additionally use an oversampling factor of 2. %For each observation 
+    We allow the background level and position calibration to vary \dvd{among the observations}. As a reference for the positional shift we also use \dvd{obsID} %the observation with the ID 
+    1308. Figure~\ref{fig:example-chandra} shows the final result. \jolideco clearly both improves the angular resolution and reduces the noise of the counts image.
+
+    \textbf{Zoom A} of \dvd{Figure~\ref{fig:example-chandra}} details an example for a filament structure.
 \jolideco maintains the extended structure along the filament, while sharpening in the perpendicular direction.
@@
 
-    \textbf{Zoom B} shows the region around the central compact object of the SNR.
-While the emission is barely visible in the counts image it clearly sticks out above the background in the image reconstructed by \jolideconospace.
+    \textbf{Zoom B} shows the region around the central compact object of the SNR. While the emission is barely visible in the counts image it is clearly \dvd{evident}
+    %sticks 
+    out above the background in the \dvd{\jolideco reconstruction.} %image reconstructed by \jolideconospace. 
     The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
-We note that, as shown in Section~\ref{subsec:methods} for scenario A, the apparent size of the point source was smaller if the source was brighter.
-We estimated the position of point source by finding the brightest pixel in the map.
-We obtained $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
-
-    \textbf{Zoom C} shows a another circular filamentous structure of the SNR.
-In the counts data the structure is barely visible, while the image reconstructed by \jolideco shows a circular structure with a bright emission spot.
-
-    Checking the residual images per observation (not shown here), we noticed that the assumption of the time independence of the source as well the instrument response is not completely fulfilled in this case.
-We saw the detection efficiency of \chandra changed between the observations as well as that sub-structure in the remnant expands over time.
+We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the apparent size of the point source \dvd{may be} %is
+    smaller if the source is brighter.
+\dvd{What does it mean for a point source to be smaller?} We estimate the position of point source by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
+
+    \textbf{Zoom C} shows a circular filament structure of the SNR. In the counts data the structure is barely visible, while the \jolideco reconstruction % by \jolideco 
+    shows a circular structure with a bright emission spot.
+
+    Checking the residual images per observation (not shown here), we notice that the assumption of time independence of the source and the instrument response is not completely fulfilled in this case.
+%We saw
+    The detection efficiency of \chandra changed 
+    \dvd{and the sub-structure in the remnant expanded over the time of} %between
+    the observations 
+    %and the sub-structure in the remnant expands over time. 
     Both effects are previously known and have been reported for example in \cite{Xi2019}.
@@
     \subsubsection{Flux Profile}
-    To get a more quantitative measurement of the improvement in angular resolution we compute a flux profile on the image of E0102 reconstructed by \jolideconospace.
-For this we chose a region perpendicular to the filament shown in Zoom A of Figure~\ref{fig:example-chandra}.
-To estimate the errors we use the bootstrapping method.
-For each individual observation we sample from the event list with replacement.
-For each realization of the set of observation we run \jolideco and compute a flux profile on the reconstructed image.
-This way we obtain a distribution of profiles, which we can use to compute an error band.
-For comparison we also compute the profiles and associated errors directly on the stacked bootstrapped images of counts.
+    To \dvd{quantify} %get a more quantitative measurement of 
+    the improvement in angular resolution \dvd{relative to what?} we compute a flux profile on the \dvd{\jolideco reconstruction} %image 
+    of E0102. %reconstructed by \jolideconospace. 
+    We chose a region perpendicular to the filament shown in Zoom~A of Figure~\ref{fig:example-chandra}.
+\dvd{We compute errors via the bootstrap, with resampled data obtained by sampling the event lists with replacement for each individual observation.}
+    %To estimate the errors we use the bootstrapping method. For each individual observation we sample from the event list with replacement. 
+    For each \dvd{resampled data set}, %realization of the set of observation 
+    we run \jolideco and compute a flux profile on the reconstructed image.
+In this way we obtain a distribution of profiles, which we can use to compute an error band.
+For comparison we also compute the profiles and associated errors directly on the stacked bootstrapped counts \dvd{(without processing or fitting)}.
 The result is shown in Figure~\ref{fig:chandra-e0102-zoom-a}.
 
-    We compute the full-width at half-max (FWHM) of each of the profiles, by fitting a Gaussian shape with a linear gradient as baseline 
-    for both the original counts and the deconvolved intensities.
+    We compute the full-width at half-max (FWHM) of each of the profiles, by fitting a Gaussian shape with a linear gradient as a baseline 
+    for both the original counts and the \jolideconospace-deconvolved intensities.
 We find that the deconvolved profile is significantly narrower.
-For the counts profile, $\omega_C=0.77 \pm 0.22$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.52 \pm 0.03$~arcsec.
-
-    Assuming that the PSF and the shape of peak of the profile are approximately Gaussian we expect the following relation between the width of the counts profile, the PSF and the flux profile:
+For the counts profile, $\omega_C=0.77 \pm 0.22$~arcsec, \dvd{I don't think you have defined $\omega_C$.} where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.52 \pm 0.03$~arcsec.
+\dvd{You say how you compute the error bar.
+How do you compute the central value?
+From the full original data of by averaging the bootstrap values?}
+
+    Assuming that the PSF and the shape of %peak of the 
+    profile are approximately Gaussian we expect %the following relation between 
+    the width of the counts profile, the PSF, and \dvd{the \jolideconospace-reconstructed profile to be related as} %the flux profile:
     %
@@
     With $\omega_{\mathrm{PSF}}\approx0.6$~arcsec\footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
-The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after de-convolution of $\omega_J\approx0.48$~arcsec.
+The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after deconvolution of $\omega_J\approx0.48$~arcsec.
 This is roughly consistent with the values we measured for the profile.
@@
     \subsection{\fermi Event Types}
-     We apply the \jolideco method to data from the Fermi Large Area Telescope (LAT) \citep{Atwood2009}.
+
+     We apply \jolideco  to data from the Fermi Large Area Telescope (LAT) \citep{Atwood2009}.
 The LAT is a pair conversion \gammaray telescope on board of the Fermi satellite.
@@
 We use 14 years (from 2008 August 4 to 2023 August 4) of \enquote{P8R3\_SOURCE} photons with reconstructed energy in the range of \qty[mode = text]{10}{GeV} to \qty[mode = text]{2}{TeV} and applied a zenith angle cut of \ang{105}.
-To preserve as much information as possible on the angular resolution of the instrument we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi \enquote{Pass8} data release\footnote{\url{https://fermi.gsfc.nasa.gov/ssc/data/analysis/documentation/Pass8_usage.html}}.
+This is consistent with the data selection range in \cite{Ackermann2017}.
+To preserve as much information as possible on the angular resolution of the instrument, we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi \enquote{Pass8} data release\footnote{\url{https://fermi.gsfc.nasa.gov/ssc/data/analysis/documentation/Pass8_usage.html}}.
 We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5 of the size of the PSF in the best event class.
-For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \cite{Fermitools2019}.
+For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \citep{Fermitools2019}.
 
@@
 Finally we reduce this model to an image by summing over the energy dimension.
-To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for Vela Junior and integrate over the energy dimension of the cube while weighting with the spectral model.
+To compute the exposure and PSF image we assume a power law with index $\Gamma=1.77$ \citep{Ajello2017} as a spectral model for Vela Junior and integrate over the energy dimension of the cube weighting according to this spectral model.
 
     We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
-Because of the limited statistics we did not use any oversampling but keep the pixel size of the counts image.
-    Figure~\ref{fig:example-fermi-lat} shows the data, result of the \jolideco method and corresponding residuals.
-The \fermi data is sparse, with very limited number of signal counts.
+Because of the limited statistics we do not oversampling but keep the pixel size of the counts image.
+    Figure~\ref{fig:example-fermi-lat} shows the data,  the \jolideco results, and corresponding residuals. The \fermi data is sparse, with %very 
+    limited %number of 
+    signal counts.
 \jolideco clearly improves the noise level as well as angular resolution of the data.
-The calibration parameters of the predicted counts converged to different norms for the background model and positional shifts of order of $<1$ pixel for the different event classes.
-This way \jolideco corrects for systematic errors in the reconstruction of the position.
-One can see that the reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and / or associated with systematic errors.
-The background estimate could be improved by choosing a larger field of view.
+\dvd{I don't think we can improve the noise of the data.
+I guess you mean the \jolideco-reconstruction is cleaner than the data?} The calibration parameters of the predicted counts converged to different norms for the background model and positional shifts of order of $<1$ pixel for the different event classes.
+In this way \jolideco corrects for systematic errors in the reconstruction of the position.
+One can see that the reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and/or associated with systematic errors.
+The background estimate could be improved by choosing a larger region of interest.
 However this would also require a larger effort of modeling nearby sources, which we avoided here.
 
-    To further check the quality of the reconstructed flux we compute a map of approximate residual significance defined by:
+    To further check the quality of the reconstructed flux we compute a map of approximate residual significance \dvd{I would call these standardized residuals} defined by:
 
@@
 The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a standard normal distribution, as expected for a good model of the emission.
+    \dvd{Say something about the correlation among the standardized residuals?}
     More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
@@
             \caption{
-                Illustration of the result of the \jolideco method applied to \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
+                Illustration of \dvd{\jolideco} result %of the \jolideco method applied to 
+                \dvd{for the} \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
 The left image shows the counts above \qty[mode = text]{10}{GeV}.
-The different event classes are stacked into a single image.
+The different event classes are stacked into a single image \vlk{with bin size $0.02$~degrees}.
 The image in the center shows the flux reconstructed by the \jolideco method.
-The image on the right shows the residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels.
+The image on the right shows the \dvd{standardized} residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels \vlk{$\approx 0.1$~degrees, similar to the size of the PSF}.
 More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.
@@
     \label{sec:reproducibility}
+
+        \dvd{I am here.}
+
     In order to facilitate reproducibility of our results we provide the source code for the paper and figures at \url{https://github.com/jolideco/jolideco-paper}.
@@
 
-    A second category of improvement is generalizing \jolideco to the energy domain to allow for hyperspectral reconstruction.
+    A second category of improvement is generalizing \jolideco to the energy domain to allow for hyperspectral image reconstruction.
 For instruments such as \fermi the instrument response varies strongly with energy, while it also has limited energy resolution.
@@
 
-    Last we plan to work on improving the error estimates.
-
-    We invite the community of x-ray and \gammaray astronomers to use the \jolideco method to combine data for new scientific discoveries, beyond the current angular resolution of existing instruments.
+    A last category of improvement is getting error estimates for the reconstruction.
+For this study we relied on bootstrapping.
+However because we have a full estimate of the \aposteriori likelihood, we can build an approximation of the covariance matrix for example by using a block-wise representation.
+Alternatively we can also change to sampling from the \aposteriori distribution.
+
+    Finally we would like to invite the community of x-ray and \gammaray astronomers to use the \jolideco method to combine data for new scientific discoveries, beyond the current angular resolution of existing instruments.
 We also welcome contributions and feedback to the public \jolideco code and validation repositories.
@@
     \section{Details on Source Patterns}
+
+    % \begin{table*}[t]
+    % \label{tab:scenarios}
+    %   \centering
+    %   \begin{tabular}{l|cr}
+    %     \hline
+    %     Scenario & Description & Parameters \\
+    %     \hline
+    %     A1 & A grid of point sources & x, y \\
+    %     B1-3 & Extended Gaussian shaped source surrounded by point sources & $\sigma$ \\
+    %     C1-3 & Point Sources on top of a disk shaped source, jet like line features & $r_{\mathrm{Disk}}$ \\
+    %     D1-D5 & A spiral-arm structure surrounded by point sources and a large ring like feature & 9 \\
+    %     \hline
+    %   \end{tabular}
+    %   \caption{Source scenarios, \todo{maybe we find a good structure for the table...would list the actual flux values per component}}
+    %   \label{tab:1}
+    % \end{table*}
+
+    \label{sec:app:A}
 
@@
 
+    \subsection{Computational Performance}
+    We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations as well as large images.
+
+    \begin{itemize}
+        \item Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
+        \item We tried the binary search tree as proposed in \cite{Parameswaran2018},
+        but without success, most likely because the native \texttt{Pytorch} support
+        for parallelization speeds up the standard GMM quite a bit...
+        \item GPU support via Pytorch
+    \end{itemize}
+
     \section{Chandra Observation Table}

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \subsubsection{Image Example}
-    First we apply \jolideco} to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data.
+    First we apply \jolideco to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data.
 In total, we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS-S instrument and no grating.

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \begin{abstract}
-        We present a new method for Joint Likelihood Deconvolution (Jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
-The method reconstructs a single flux image from a set of observations and given models for the point spread function (PSF) per observation, by optimizing the the posterior distribution based on th}
-        joint Poisson likelihood of all observations under a patch based image prior.
+        We present a new method for Joint Likelihood Deconvolution (\jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
+The method reconstructs a single flux image from a set of observations and given models for the point spread function (PSF) per observation, by optimizing the the posterior distribution based on the joint Poisson likelihood of all observations under a patch based image prior.
 The patch prior is parameterised by a Gaussian Mixture model (GMM) which we trained on astronomical images with high signal to noise ratio, including data from the  James Webb Telescope as well as the GLEAM radio survey.
@@
 We also show the results of the method applied to example data from the \chandra observatory as well as the \ferminospace.
-By comparing the measured width of a counts based and the corresponding Jolideco flux profile we find the deconvolved width to be consistent with the theoretical expectation derived from the known width of the PSF.
+By comparing the measured width of a counts based and the corresponding \jolideco flux profile we find the deconvolved width to be consistent with the theoretical expectation derived from the known width of the PSF.
     \end{abstract}
@@
     \section{Implementation}
-    \subsection{Jolideco Framework}
+    \subsection{\jolideco Framework}
     The goal of the reconstruction process is to optimize the a-posteriori likelihood defined by Equation~\ref{eq:total}. Given that there is a parameter for each pixel in the image,  
@@
 
-        \item[\bf M2.] \textbf{Jolideco (Uniform, n=10)}: we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, \dvd{running the optimizer for} 10 iterations.
+        \item[\bf M2.] \textbf{\jolideco (Uniform, n=10)}: we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, \dvd{running the optimizer for} 10 iterations.
 We consider this as a baseline method reference similar to RL.
@@
 
-        \item[\bf M3.] \textbf{Jolideco (Uniform, n=1000)}:  we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, but running \dvd{the optimzier} for 1000 iterations.
+        \item[\bf M3.] \textbf{\jolideco (Uniform, n=1000)}:  we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, but running \dvd{the optimzier} for 1000 iterations.
 This is the same as above but without early stopping.
@@
 
-        \item[\bf M4.] \textbf{Jolideco (Patch, GLEAM v0.1)}: we use \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalisation described by Equation~\ref{eq:patch-norm}.
+        \item[\bf M4.] \textbf{\jolideco (Patch, GLEAM v0.1)}: we use \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalisation described by Equation~\ref{eq:patch-norm}.
 We use cycle spinning and 2000 \enquote{training epochs}.
@@
 
-        \item[\bf M5.] \textbf{Jolideco (Patch, Zoran-Weiss)}: we use \jolideco with the patch prior of \cite{Zoran2011} and the mean subtracted patch norm \dvd{is this the same as ``the patch normalisation described by Equation~\ref{eq:patch-norm}''?
+        \item[\bf M5.] \textbf{\jolideco (Patch, Zoran-Weiss)}: we use \jolideco with the patch prior of \cite{Zoran2011} and the mean subtracted patch norm \dvd{is this the same as ``the patch normalisation described by Equation~\ref{eq:patch-norm}''?
 Best to use the same language for clarity.}.

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation.
-As reference we chose the %observation with
-    \dvd{obsID} 1308. For \jolideco we use the GMM prior learned on the JWST Cas A image. As there are many counts in the image we additionally use an oversampling factor of 2. %For each observation 
-    We allow the background level and position calibration to vary \dvd{among the observations}. As a reference for the positional shift we also use \dvd{obsID} %the observation with the ID 
-    1308. Figure~\ref{fig:example-chandra} shows the final result. \jolideco clearly both improves the angular resolution and reduces the noise of the counts image.
+As reference we chose the %
+    obsID 1308.
+For \jolideco we use the GMM prior learned on the JWST Cas A image.
+As there are many counts in the image we additionally use an oversampling factor of 2.
+We allow the background level and position calibration to vary among the observations.
+As a reference for the positional shift we also use \dvd{obsID} 1308.
+Figure~\ref{fig:example-chandra} shows the final result.
+\jolideco clearly both improves the angular resolution and reduces the noise of the counts image.
 
@@
     \centering
-        \begin{tabular}{ c|c|c|c } 
+        \begin{tabular}{ c|c|c|c|c } 
             \input{output/chandra-obs-table.tex}

### 2023-11-30 src/scripts/chandra-obs-table.py

@@ -37,7 +37,7 @@ obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
 
 
 exposure_cum = np.cumsum(obs_table["Exposure"])
-obs_table["Integrated Exposure"] = exposure / exposure_cum[-1]
+obs_table["Integrated Exposure"] = exposure_cum / exposure_cum[-1]
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             \caption{
-               \jolideco result \dvd{for}
-               %of the \jolideco method applied to 
-               \chandra \dvd{observations of} %data of the 
-               SNR \textit{1E~0102.2–7219}. The \dvd{bottom} left %large 
-               image shows the summed counts from 25 observations. The bottom right image  shows the %result from 
-               the \jolideco deconvolution. %process. 
-               The flux is given as counts relative to \dvd{obsID}
-               %the reference observation with ID=
-               1308.
+               \jolideco result for \chandra observations of SNR \textit{1E~0102.2–7219}.
+The bottom left image shows the summed counts from 25 observations.
+The bottom right image  shows the the \jolideco deconvolution.
+The flux is given as a counts rate relative to obsID 1308.
 The panels \textit{Zoom A}, \textit{Zoom B} and \textit{Zoom C} show a zoomed-in version of three example regions in the SNR, marked with the white rectangles in the large images.

### 2023-11-30 src/scripts/chandra-obs-table.py

@@ -37,7 +37,7 @@ obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
 
 
 exposure_cum = np.cumsum(obs_table["Exposure"])
-obs_table["Integrated Exposure"] = exposure_cum / exposure_cum[-1]
+obs_table["Integrated Exposure"] = np.round(exposure_cum / exposure_cum[-1], 2)
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2023-11-30 src/scripts/chandra-obs-table.py
Add integrated exposure to table

@@ -37,7 +37,9 @@ obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
 
 
 exposure_cum = np.cumsum(obs_table["Exposure"])
-obs_table["Integrated Exposure"] = np.round(exposure_cum / exposure_cum[-1], 2)
+obs_table["Integrated Fractional Exposure"] = np.round(
+    exposure_cum / exposure_cum[-1], 2
+)
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2023-12-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} as the \enquote{Low Counts Image Reconstruction and Analysis} (LIRA\footnote{\dvd{LIRA was referred to as EMC2 in \cite{Esch2004}.}}) method.
+    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} with the EMC2 and LIRA methods.
 Their key idea is to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
@@
 They show that RL can be effective in creating a merged image from multiple observations.
-They also observe that RL would take the best visual properties out of each image and merged them to create a more accurate estimate of the `ground truth'.
+They also observe that RL would take the best visual properties out of each image and merged them to result in a reconstruction closer to the \enquote{ground truth}.
 
@@
     In practice one observation is used as a reference and its corresponding systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during optimization.
-An example of the effect of the positional shift and background normalisation can be seen in Fig.~\ref{fig:npred-systematics}.
+An example of the effect of the positional shift and background normalisation can be seen in Figure~\ref{fig:npred-systematics}.
 
@@
 For the instrument scenario \chandra we convolve the ground truth image with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
-For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=2$~pix \dvd{same as \chandra?} and an effective area that is five times larger than that of \chandra.
+For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=6$~pix and an effective area that is five times larger than that of \chandra.
 All images are of size $128{\times}128$ pixels.
@@
 
-        \item[\bf M2.] \textbf{\jolideco (Uniform, n=10)}: we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, \dvd{running the optimizer for} 10 iterations.
+        \item[\bf M2.] \textbf{\jolideco (Uniform, n=10)}: we use \jolideco with a uniform prior on $\mathbf{x}$ and running the optimizer for 10 iterations.
 We consider this as a baseline method reference similar to RL.
@@
 
-        \item[\bf M3.] \textbf{\jolideco (Uniform, n=1000)}:  we use \jolideco with a uniform prior \dvd{on $\mathbf{x}$}, but running \dvd{the optimzier} for 1000 iterations.
+        \item[\bf M3.] \textbf{\jolideco (Uniform, n=1000)}:  we use \jolideco with a uniform prior on $\mathbf{x}$, but running the optimzier for 1000 iterations.
 This is the same as above but without early stopping.
@@
                 Comparison of the different deconvolution methods and prior assumptions for selected source scenarios, as described in Section~\ref{subsec:test-datasets}.
-The simulations \dvd{depicted} %of the data for this figure
-                used a fixed background level of $\lambda_{Bkg} = \qty[mode = math]{0.01}{cts/pix}$, a uniform exposure, and a Gaussian PSF of width $\sigma_{PSF} = \qty[mode = math]{2}{pix}$, corresponding to the \enquote{Chandra} instrument scenario.
-The leftmost column shows the simulated counts and the second column %from the left
-                shows the underlying ground truth.% to compare. 
+The simulations depicted used a fixed background level of $\lambda_{Bkg} = \qty[mode = math]{0.01}{cts/pix}$, a uniform exposure, and a Gaussian PSF of width $\sigma_{PSF} = \qty[mode = math]{2}{pix}$, corresponding to the \enquote{Chandra} instrument scenario.
+The leftmost column shows the simulated counts and the second column shows the underlying ground truth.
 The remaining columns show the reconstructed flux for each method and prior assumptions for \jolideconospace.
@@
 M3, which optimizes for 1000 iterations, clearly improves the result and shows almost perfect point sources corresponding to the size of approximately one pixel.
-The \jolideco method with the Zoran-Weiss  patch prior (M4) results in less sharp images, because the prior has been learned on natural images of landscapes and every day objects and scenes, which \dvd{typically} do not include point sources.
-The \jolideco method with the prior learned from GLEAM data (M5), which also includes point sources, shows much improved results \dvd{relative to M4 but is}
-    %However 
-    not as sharp as the results obtained with the uniform prior (M3).
-In the lower left of the image the point sources are fainter and closer together, challenging all methods.% in succeeding to separate them into separate sources.
-    The uniform prior optimized \enquote{to end} (M3) shows good results, separating the sources well. All other methods, however, cannot fully resolve these weak and closely situated point sources.
+The \jolideco method with the Zoran-Weiss  patch prior (M4) results in less sharp images, because the prior has been learned on natural images of landscapes and every day objects and scenes, which typically do not include point sources.
+The \jolideco method with the prior learned from GLEAM data (M5), which also includes point sources, shows much improved results relative to M4 but is not as sharp as the results obtained with the uniform prior (M3).
+In the lower left of the image the point sources are fainter and closer together, challenging all methods.
+The uniform prior optimized \enquote{to end} (M3) shows good results, separating the sources well.
+All other methods, however, cannot fully resolve these weak and closely situated point sources.
 
@@
 The best results are achieved by the patch priors, which reconstruct a plausible extended source with approximately uniform brightness.
-The jet like features %in the same scenario
-    are decomposed into a \enquote{thread} of point sources by the uniform prior and Pylira method.
+The jet like features are decomposed into a \enquote{thread} of point sources by the uniform prior and Pylira method.
 The patch prior achieves a much more plausible reconstruction with almost uniform brightness for the linear structures.
@@
 Visually the method converges to the ground truth for very high signal-to-noise ratio.
-Indeed with very high signal strength there is no dependency of the result on the background level, particularly in %This especially valid for
-    Scenario~D5. On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
+Indeed with very high signal strength there is no dependency of the result on the background level, particularly in Scenario~D5.
+On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
 
@@
 The ring structure is sharpened considerably in all cases as well.
-The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but still appear with improved
-    signal-to-noise ratio.
+The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but still appear with improved signal-to-noise ratio.
 This is an inherent limitation of the method.
-\dvd{Limitation of the method or of the data?} \todo{how far are those apart compared to the PSF?
-Hoes does this compare to the point scenario with XMM?}
+\dvd{Limitation of the method or of the data?}
 
@@
 The strength of the prior could be increased with the $\beta$ parameter, but for this study we did not tweak individual parameters, but instead used the default configuration.
-The specklely behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the ring is smoother.
+The speckly behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the ring is smoother.
 In this case the correlation between pixels that are further apart is stronger because of the larger correlation PSF.
@@
     \subsection{Deep \chandra Observation}
+    \label{sec:chandra-example}
     \subsubsection{Image Example}
@@
 We allow the background level and position calibration to vary among the observations.
-As a reference for the positional shift we also use \dvd{obsID} 1308.
+As a reference for the positional shift we also use obsID 1308.
 Figure~\ref{fig:example-chandra} shows the final result.
@@
 
-    \textbf{Zoom A} of \dvd{Figure~\ref{fig:example-chandra}} details an example for a filament structure.
+    \textbf{Zoom A} of Figure~\ref{fig:example-chandra} details an example for a filament structure.
 \jolideco maintains the extended structure along the filament, while sharpening in the perpendicular direction.
@@
 
-    \textbf{Zoom B} shows the region around the central compact object of the SNR. While the emission is barely visible in the counts image it is clearly \dvd{evident}
-    %sticks 
-    out above the background in the \dvd{\jolideco reconstruction.} %image reconstructed by \jolideconospace. 
+    \textbf{Zoom B} shows the region around the central compact object of the SNR. While the emission is barely visible in the counts image it is clearly evident
+    out above the background in the \jolideco reconstruction.
 The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
-We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the apparent size of the point source \dvd{may be} %is
-    smaller if the source is brighter.
-\dvd{What does it mean for a point source to be smaller?} We estimate the position of point source by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
-
-    \textbf{Zoom C} shows a circular filament structure of the SNR. In the counts data the structure is barely visible, while the \jolideco reconstruction % by \jolideco 
-    shows a circular structure with a bright emission spot.
+We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.
+We estimate the position of point source by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
+
+    \textbf{Zoom C} shows a circular filament structure of the SNR.
+In the counts data the structure is barely visible, while the \jolideco reconstruction shows a distinct circular structure with a bright emission spot.
 
     Checking the residual images per observation (not shown here), we notice that the assumption of time independence of the source and the instrument response is not completely fulfilled in this case.
-%We saw
-    The detection efficiency of \chandra changed 
-    \dvd{and the sub-structure in the remnant expanded over the time of} %between
-    the observations 
-    %and the sub-structure in the remnant expands over time. 
+The detection efficiency of \chandra changed and the sub-structure in the remnant expanded over the time of the observations.
 Both effects are previously known and have been reported for example in \cite{Xi2019}.
@@
 Both profiles are normalized such that they integrate to unity and are aligned such that the position of their peak coincides.
-                \vlk{I notice that you avoid the bright knot to SW.
+                %\vlk{it is not being actively avoided -- the knot shows up after deconvolution.
+But if referee asks, can say it also avoids pileup issues} \vlk{I notice that you avoid the bright knot to SW.
 Any particular reason why?
@@
     \subsubsection{Flux Profile}
-    To \dvd{quantify} %get a more quantitative measurement of 
-    the improvement in angular resolution \dvd{relative to what?} we compute a flux profile on the \dvd{\jolideco reconstruction} %image 
-    of E0102. %reconstructed by \jolideconospace. 
+    To quantify the improvement in angular resolution of the reconstructed image over the data we compute a flux profile on the \jolideco reconstruction of E0102.
 We chose a region perpendicular to the filament shown in Zoom~A of Figure~\ref{fig:example-chandra}.
-\dvd{We compute errors via the bootstrap, with resampled data obtained by sampling the event lists with replacement for each individual observation.}
-    %To estimate the errors we use the bootstrapping method. For each individual observation we sample from the event list with replacement. 
-    For each \dvd{resampled data set}, %realization of the set of observation 
-    we run \jolideco and compute a flux profile on the reconstructed image.
+We compute errors via the bootstrap, with resampled data obtained by sampling the event lists with replacement for each individual observation.
+For each resampled data set we run \jolideco and compute a flux profile on the reconstructed image.
 In this way we obtain a distribution of profiles, which we can use to compute an error band.
-For comparison we also compute the profiles and associated errors directly on the stacked bootstrapped counts \dvd{(without processing or fitting)}.
+For comparison we also compute the profiles and associated errors directly on the stacked bootstrapped counts (without processing or fitting).
 The result is shown in Figure~\ref{fig:chandra-e0102-zoom-a}.
 
-    We compute the full-width at half-max (FWHM) of each of the profiles, by fitting a Gaussian shape with a linear gradient as a baseline 
-    for both the original counts and the \jolideconospace-deconvolved intensities.
+    We compute the full-width at half-max (FWHM) $\omega$ of each of the profiles, by fitting a Gaussian shape with a linear gradient as a baseline for both the original counts and the \jolideconospace-deconvolved intensities.
+In both cases we compute the mean of $\omega$.
 We find that the deconvolved profile is significantly narrower.
-For the counts profile, $\omega_C=0.77 \pm 0.22$~arcsec, \dvd{I don't think you have defined $\omega_C$.} where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.52 \pm 0.03$~arcsec.
-\dvd{You say how you compute the error bar.
-How do you compute the central value?
-From the full original data of by averaging the bootstrap values?}
-
-    Assuming that the PSF and the shape of %peak of the 
-    profile are approximately Gaussian we expect %the following relation between 
-    the width of the counts profile, the PSF, and \dvd{the \jolideconospace-reconstructed profile to be related as} %the flux profile:
+For the counts profile, $\omega_C=0.77 \pm 0.22$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.52 \pm 0.03$~arcsec.
+
+    Assuming that the PSF and the shape of profile are approximately Gaussian we expect
+    the width of the counts profile, the PSF, and the \jolideconospace-reconstructed profile to be related as:
     %
@@
 Because of the limited statistics we do not oversampling but keep the pixel size of the counts image.
-    Figure~\ref{fig:example-fermi-lat} shows the data,  the \jolideco results, and corresponding residuals. The \fermi data is sparse, with %very 
-    limited %number of 
-    signal counts.
-\jolideco clearly improves the noise level as well as angular resolution of the data.
-\dvd{I don't think we can improve the noise of the data.
-I guess you mean the \jolideco-reconstruction is cleaner than the data?} The calibration parameters of the predicted counts converged to different norms for the background model and positional shifts of order of $<1$ pixel for the different event classes.
+Figure~\ref{fig:example-fermi-lat} shows the data,  the \jolideco results, and corresponding residuals.
+The \fermi data is sparse, with limited signal counts.
+\jolideco clearly improves the noise level as well as angular resolution compared to the data.
+The calibration parameters of the predicted counts converged to different norms for the background model and positional shifts of order of $<1$ pixel for the different event classes.
 In this way \jolideco corrects for systematic errors in the reconstruction of the position.
@@
 
-    To further check the quality of the reconstructed flux we compute a map of approximate residual significance \dvd{I would call these standardized residuals} defined by:
+    To further check the quality of the reconstructed flux we compute a map of standardized residuals defined by:
 
@@
         \label{eq:approx-sigma}
-        \sigma \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
-    \end{equation}
-
-    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma=5$ pixels. The result is shown in the right panel of Fig.~\ref{fig:example-fermi-lat}. The image
-    shows no systematic effects and a spatially homogeneous distribution of the residual noise.
+        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
+    \end{equation}
+
+    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma_{\mathrm{smooth}}=5$ pixels.
+The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.
+The image shows no systematic effects and a spatially homogeneous distribution of the residual noise.
 The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a standard normal distribution, as expected for a good model of the emission.
-    \dvd{Say something about the correlation among the standardized residuals?}
 More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
@@
             \caption{
-                Illustration of \dvd{\jolideco} result %of the \jolideco method applied to 
-                \dvd{for the} \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
+                Illustration of the \jolideco result for the \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
 The left image shows the counts above \qty[mode = text]{10}{GeV}.
-The different event classes are stacked into a single image \vlk{with bin size $0.02$~degrees}.
+The different event classes are stacked into a single image with bin size $0.02$~degrees.
 The image in the center shows the flux reconstructed by the \jolideco method.
-The image on the right shows the \dvd{standardized} residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels \vlk{$\approx 0.1$~degrees, similar to the size of the PSF}.
+The image on the right shows the standardized residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels $\approx 0.1$~degrees, similar to the size of the PSF.
 More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.

### 2024-01-08 src/scripts/example-chandra.py
Adapt zoom cutout

@@ -129,7 +129,7 @@ norm_flux = simple_norm(
     flux.data,
     stretch="linear",
     min_cut=0,
-    max_cut=3.5,
+    max_cut=2.0,
 )
 flux.plot(ax=ax_flux, cmap="viridis", interpolation="gaussian", norm=norm_flux)
 add_cbar(ax_flux.images[0], ax_flux, fig, label="Flux / A.U.")
@@ -256,7 +256,7 @@ draw_zoom(
 
 cutout_zoom_b = flux.cutout(position=center, width=width)
 
-peaks = find_peaks(cutout_zoom_b, threshold=0.4)
+peaks = find_peaks(cutout_zoom_b, threshold=0.2)
 position = SkyCoord(peaks["ra"], peaks["dec"], unit="deg", frame="icrs")
 
 print(position.to_string("hmsdms"))

### 2024-01-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+    \newpage
     \subsection{Patch Based Image Prior}
@@
 The size of the corresponding correlation matrix would grow with the number of pixels squared and thus quickly become computationally untraceable.
-However, astronomical images typically only show exhibit correlations among the pixels.
+However, astronomical images typically only exhibit local correlations among the pixels.
 This is because the spatial scale of astrophysical processes in an image is always limited by the finite interaction time and the fact that the interaction cannot propagate faster than the speed of light.
@@
 When given many of theses patches we can model the distribution of pixels values within the patch using a Gaussian Mixture Model (GMM).
+The GMM has the property of being a universal function approximator and thus can model arbitrary distributions.
+For now we assume that we have a pre-trained GMM which encodes the patch distribution of some reference image we have chosen.
+During the actual image reconstruction we then try to identify the most likely GMM component per patch and treat as a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
 
@@
     where $\mathbf{P}_n$ is again the matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed.
-\dvd{I think the following should be moved toward the begining of this subsection.
-It clarifies the calculations are you doing above:} In this way the index $k$ that identifies the most likely GMM component per patch is treated as a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
 
@@
 The prior distribution simply regularizes the structure in the image, while the overall intensities are typically well constrained by the Poisson likelihood term.
-Thus we only assume a flat prior patch intensities.
+Thus we only assume a uniform prior for the patch intensities.
 
@@
 We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction is slightly faster with the same reconstruction quality.
-However for all results shown later in the manuscript we chose the simple cycle spinning described in the previous section.
+However for all results shown later in the manuscript we chose the simple cycle spinning described in the previous section, because it is the simpler method.
 
@@
     \section{Summary \& Outlook}
-    In this work we presented a new method for deconvolution and denoising of images contaminated by Poisson noise.
+    In this article we presented a new method for deconvolution and denoising of images contaminated by Poisson noise.
 Using multiple observations of the same sky region the methods reconstructs a single flux image using the approximate MAP estimate of the joint likelihood under a patch based image prior.

### 2024-01-08 src/scripts/chandra-obs-table.py
Read config file for obs ids

@@ -3,6 +3,7 @@ from io import StringIO
 
 import numpy as np
 import paths
+import yaml
 from astropy import units as u
 from astropy.table import Table
 from dateutil import parser
@@ -10,7 +11,7 @@ from dateutil import parser
 logging.basicConfig(level=logging.INFO)
 
 log = logging.getLogger(__name__)
-OBS_ID_REF = 8365
+
 
 colnames = ["Obs ID", "Obs Date", "Exposure"]
 units = ["", "", "ks"]
@@ -19,10 +20,15 @@ obs_table = Table(names=colnames, dtype=dtype, units=units)
 
 
 path = paths.jolideco_repo_chandra_example / "data"
-filenames = sorted(path.glob("*/oif.fits"))
 
-for filename in filenames:
-    obs_id = filename.parent.name
+with (path.parent / "config/config-e0102.yaml").open("r") as fh:
+    config = yaml.safe_load(fh)
+
+obs_ids = config["chandra-data"]["obs_ids"]
+OBS_ID_REF = config["chandra-data"]["obs_id_ref"]
+
+for obs_id in obs_ids:
+    filename = path / f"{obs_id}" / "oif.fits"
     table = Table.read(filename)
     exposure = table.meta["EXPOSURE"] * u.s
     date = parser.parse(table.meta["DATE-OBS"])

### 2024-01-22 src/scripts/chandra-obs-table.py
Add fractional exposure to table

@@ -42,10 +42,8 @@ exposure_ref = obs_table.loc[OBS_ID_REF]["Exposure"]
 obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
 
 
-exposure_cum = np.cumsum(obs_table["Exposure"])
-obs_table["Integrated Fractional Exposure"] = np.round(
-    exposure_cum / exposure_cum[-1], 2
-)
+exposure_total = np.sum(obs_table["Exposure"])
+obs_table["Frac. Exposure"] = np.round(obs_table["Exposure"] / exposure_total, 2)
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2024-01-22 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    An interesting modification of the standard RL method is proposed by \cite{Ingaramo2014}.
-They show that RL can be effective in creating a merged image from multiple observations.
-They also observe that RL would take the best visual properties out of each image and merged them to result in a reconstruction closer to the \enquote{ground truth}.
+    An interesting modification of the standard RL method has been proposed by \cite{Ingaramo2014}.
+They show that RL could be effective in creating a merged image from multiple observations.
+They also observed that RL would take the best visual properties out of each image and merged them to result in a reconstruction closer to the \enquote{ground truth}.
 
@@
 We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction is slightly faster with the same reconstruction quality.
-However for all results shown later in the manuscript we chose the simple cycle spinning described in the previous section, because it is the simpler method.
+However for all results shown later in the manuscript we chose the simpler cycle spinning described in the previous section.
 
@@
 We arranged the sources in different spatial patterns and with different spacings between them.
-We include point sources superposed on extended sources \dvd{in four arrangements labelled A--D in the first row of Figure~\ref{fig:scenarios}.} Each spatial arrangement is crossed with several signal-to-noise ratios (obtained with a constant background),
-    %is as well as different 
-    %levels of constant background emission,
-    \dvd{denoted 1--X.
-The resulting scenarios are denoted by concatenating the two labels, e.g., A3 or C1, see Appendix~\ref{sec:app:A} for details.}  The goal of these experiments is not to set up or devise a \enquote{perfect} deconvolution algorithm, but to help assess their relative strengths and limitations.
+We include point sources superposed on extended sources in four arrangements labelled A--D in the first row of Figure~\ref{fig:scenarios}.
+Each spatial arrangement is crossed with several signal-to-noise ratios (obtained with a constant background),
+    denoted \texttt{XN}.
+The resulting scenarios are denoted by concatenating the two labels, e.g., A3 or C1, see Appendix~\ref{sec:app:A} for details.
+The goal of these experiments is not to set up or devise a \enquote{perfect} deconvolution algorithm, but to help assess their relative strengths and limitations.
 
@@
 The details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios}.
-    %In addition we also 
     We assume a constant background with varying levels of $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
@@
 
-        \item[\bf M1.] \textbf{Pylira}: we implement the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
+        \item[\bf M1.]: we implement the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
 We rely on the default prior definition and keep the background norm fixed.
@@
     %
-    First we compare the performance of the five methods (and their differing prior assumptions) on the different source scenarios.
+    First we compare the performance of the five methods and their differing prior assumptions on the different source scenarios.
 Figure \ref{fig:comparison-scenarios} shows the results for the selected subset of scenarios, i.e., on A1, B3, C3 and D4.
-\dvd{What do the numbers refer to?}
 
@@
     First we apply \jolideco to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data.
-In total, we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS-S instrument and no grating.
+In total, we chose 25 observations taken with  the ACIS-S instrument and no grating.
+We chose newer data, taken after 2006, to limit the effect of pile up.
 
@@
 We converted the spectral script from XSPEC to sherpa using the helper script \texttt{convert\_xspec\_script}.
-As reported in \cite{Xi2019} the effect of pileup, even for the brightest regions is small ($<5\%$), so we did not include the effect of pileup in our PSF simulations.
 
@@
 
-    \textbf{Zoom B} shows the region around the central compact object of the SNR. While the emission is barely visible in the counts image it is clearly evident
-    out above the background in the \jolideco reconstruction.
+    \textbf{Zoom B} shows the region around the central compact object of the SNR.
+While the emission is barely visible in the counts image it is clearly evident out above the background in the \jolideco reconstruction.
 The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
@@
 For each resampled data set we run \jolideco and compute a flux profile on the reconstructed image.
-In this way we obtain a distribution of profiles, which we can use to compute an error band.
+In this way we obtain a distribution of profiles, which we use to compute an error band.
 For comparison we also compute the profiles and associated errors directly on the stacked bootstrapped counts (without processing or fitting).
@@
 We find that the deconvolved profile is significantly narrower.
-For the counts profile, $\omega_C=0.77 \pm 0.22$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.52 \pm 0.03$~arcsec.
-
-    Assuming that the PSF and the shape of profile are approximately Gaussian we expect
-    the width of the counts profile, the PSF, and the \jolideconospace-reconstructed profile to be related as:
+For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.
+
+    Assuming that the PSF and the shape of profile are approximately Gaussian we expect the width of the counts profile, the PSF, and the \jolideconospace-reconstructed profile to be related as:
     %
@@
     With $\omega_{\mathrm{PSF}}\approx0.6$~arcsec\footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
-The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after deconvolution of $\omega_J\approx0.48$~arcsec.
+The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after deconvolution of $\omega_J\approx0.5$~arcsec.
 This is roughly consistent with the values we measured for the profile.
@@
     \subsection{\fermi Event Types}
-
-     We apply \jolideco  to data from the Fermi Large Area Telescope (LAT) \citep{Atwood2009}.
+     As a second application example, we apply \jolideco  to data from the Fermi Large Area Telescope (LAT) \citep{Atwood2009}.
 The LAT is a pair conversion \gammaray telescope on board of the Fermi satellite.
@@
 
-    The choice of the prior becomes more important at low signal noise ratios.
+    % The choice of the prior becomes more important at low signal noise ratios.
 The right choice can yield superior reconstruction quality then any other method we have compared to.

### 2024-01-22 src/scripts/chandra-obs-table.py

@@ -41,9 +41,9 @@ obs_table.add_index("Obs ID")
 exposure_ref = obs_table.loc[OBS_ID_REF]["Exposure"]
 obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
 
-
 exposure_total = np.sum(obs_table["Exposure"])
-obs_table["Frac. Exposure"] = np.round(obs_table["Exposure"] / exposure_total, 2)
+obs_table["Frac. Exposure"] = np.round(100 * obs_table["Exposure"] / exposure_total, 1)
+obs_table["Frac. Exposure"].format = ".1%"
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2024-01-22 src/scripts/chandra-obs-table.py
[showyourwork] overleaf sync

@@ -43,7 +43,7 @@ obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
 
 exposure_total = np.sum(obs_table["Exposure"])
 obs_table["Frac. Exposure"] = np.round(100 * obs_table["Exposure"] / exposure_total, 1)
-obs_table["Frac. Exposure"].format = ".1%"
+obs_table["Frac. Exposure"].unit = "%"
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2024-01-22 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \script{chandra-obs-table.py}
-        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}}
+        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}.
+The relative exposure columns list the exposure for each observation expressed as the ratio with the exposure of the reference observation with obs ID 8365.
+The }
     \end{table}

### 2024-01-22 src/scripts/chandra-obs-table.py

@@ -42,8 +42,10 @@ exposure_ref = obs_table.loc[OBS_ID_REF]["Exposure"]
 obs_table["Rel. Exposure"] = np.round(obs_table["Exposure"] / exposure_ref, 1)
 
 exposure_total = np.sum(obs_table["Exposure"])
-obs_table["Frac. Exposure"] = np.round(100 * obs_table["Exposure"] / exposure_total, 1)
-obs_table["Frac. Exposure"].unit = "%"
+obs_table["Frac. Exposure Total"] = np.round(
+    100 * obs_table["Exposure"] / exposure_total, 1
+)
+obs_table["Frac. Exposure Total"].unit = "%"
 
 content_io = StringIO()
 obs_table.write(content_io, format="latex", overwrite=True)

### 2024-01-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4, when computing the prior distribution for a patch as given by  Equation~\ref{eq:gmm}.
-Apart from this the process for choosing the most likely GMM prior component remains unmodified.
+
+    Apart from this, the process for choosing the most likely GMM prior component remains unmodified.
 However, we note that in this case we neglected the prior dependence between neighbouring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixes and are thus clearly not \aprioir independent.}.
@@
 
-    We also experimented with computing the diagonal of Hessian of the posterior distribution at the minimum.
-However we found this numerically challenging because of the random elements, such as cycle spinning and SGD in the method.
-Which yields no stable second derivative.
-
-\as{There is no mention of stochastic gradient decent in the description of the method above, so this is the first time you talk about it...
-maybe it needs to be included when you describe solving the GMM model?}
+    We also experimented with computing the diagonal of Hessian of the posterior distribution at the minimum. However we found this numerically challenging because of random the cycle spinning.
 
@@
     this is a high dimensional optimization problem.
-Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019} allow for solving high dimensional optimization problems using back-propagation and adapted optimization methods such as stochastic gradient decent (SGD).
+Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019} allow for solving high dimensional optimization problems using back-propagation.
+They also offer a variety of optimization methods such as stochastic gradient decent (SGD).
 The latter is also applicable in our case, as we work with multiple observations at the same time, where a subset of the observations represents a \enquote{mini batch} in terms of ML.
@@
 The relative exposure columns list the exposure for each observation expressed as the ratio with the exposure of the reference observation with obs ID 8365.
-The }
+The fractional exposure column, gives the exposure of each observation as a fraction of the total exposure.}
     \end{table}
 
+    \section{Fermi-LAT Example Without Calibration}
+     \begin{figure*}
+        \begin{centering}
+            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
+            \caption{
+                Illustration of the \jolideco result for the \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
+The left image shows the counts above \qty[mode = text]{10}{GeV}.
+The different event classes are stacked into a single image with bin size $0.02$~degrees.
+The image in the center shows the flux reconstructed by the \jolideco method.
+The image on the right shows the standardized residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels $\approx 0.1$~degrees, similar to the size of the PSF.
+More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.
+            }
+            \label{fig:example-fermi-lat-non-calibrated}
+            \script{example-fermi-lat-non-calibrated.py}
+        \end{centering}
+    \end{figure*}
 \end{document}

### 2024-01-23 src/scripts/example-fermi-lat-non-calibrated.py

@@ -132,4 +132,4 @@ add_cbar(
 # ticks = np.round(norm.inverse(np.linspace(0, 1, 10)), 1)
 # plt.colorbar(ax_npred.images[-1], cax=ax_cbar, ticks=ticks)
 
-plt.savefig(paths.figures / "example-fermi-lat.pdf", dpi=config.DPI)
+plt.savefig(paths.figures / "example-fermi-lat-non-calibrated.pdf", dpi=config.DPI)

### 2024-01-25 src/scripts/example-fermi-lat-non-calibrated.py
Update Fermi-LAT non calibrated plot

@@ -3,9 +3,9 @@ import matplotlib.pyplot as plt
 import numpy as np
 import paths
 from astropy import units as u
-from astropy.io import fits
 from astropy.visualization import simple_norm
 from gammapy.maps import Map
+from matplotlib.gridspec import GridSpec
 
 SMOOTH_WIDTH = 5
 FONT_SIZE = 8
@@ -13,7 +13,7 @@ FONT_SIZE = 8
 plt.rcParams.update({"font.size": FONT_SIZE})
 
 
-def format_axes(ax, hide_yaxis=False):
+def format_axes(ax, hide_yaxis=False, hide_xaxis=False):
     """Format axes for a map plot"""
     lon = ax.coords["glon"]
     lat = ax.coords["glat"]
@@ -33,6 +33,10 @@ def format_axes(ax, hide_yaxis=False):
     if hide_yaxis:
         lat.set_axislabel("")
         lat.set_ticklabel_visible(False)
+
+    if hide_xaxis:
+        lon.set_axislabel("")
+        lon.set_ticklabel_visible(False)
 
 
 def add_cbar(im, ax, fig, label=""):
@@ -55,81 +59,50 @@ path = (
     / "results/vela-junior-above-10GeV-data/jolideco"
 )
 
-filename_jolideco = path / "vela-junior-above-10GeV-data-result-jolideco.fits"
-filenames_data = (path / "input").glob("*.fits")
-filename_npred = path / "vela-junior-above-10GeV-data-npred.fits"
 
-npred = Map.read(filename_npred)
+filenames = path.glob("vela-junior-above-10GeV-residual-psf*.fits")
+filename_calibrated = path.glob("vela-junior-above-10GeV-residual-calibrated-psf*.fits")
 
-aspect_ratio = 3.8
+
+aspect_ratio = 2.0
 figsize = config.FigureSizeAA(aspect_ratio=aspect_ratio, width_aa="two-column")
 
 fig = plt.figure(figsize=figsize.inch)
 
-wcs = npred.geom.wcs
-height = 0.75
-width = height / aspect_ratio
-y_bottom = 0.22
-
-ax_counts = fig.add_axes([0.08, y_bottom, width, height], projection=wcs)
-format_axes(ax_counts)
-
-ax_flux = fig.add_axes([0.37, y_bottom, width, height], projection=wcs)
-format_axes(ax_flux, hide_yaxis=True)
-
[…]

### 2024-01-25 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 In the counts data the structure is barely visible, while the \jolideco reconstruction shows a distinct circular structure with a bright emission spot.
+This demonstrates the ability of \jolideco to reconstruct sub PSF scale structures with astrophysical relevance.
 
@@
 The source strengths are
-    $$s_{\rm A} = \{10, 20, 30, 50, 80, 130, 210, 340\} \cdot \tau ~{\rm [counts]} $$
+    $$s_{\rm A} = \{10, 20, 30, 50, 80, 130, 210, 340\} \cdot \tau ~\textrm{counts} $$
     for
-    $$y = [8, 10, 13, 18, 26, 39, 55, 76]~{\rm pix} \,,$$
+    $$y = [8, 10, 13, 18, 26, 39, 55, 76]~\textrm{pix} \,,$$
     and $\tau$ denotes an arbitrary scaling factor, set to 1 for \textit{Chandra}-like simulations and to 5 for XMM-like simulations.
     The $x$-axis locations of the sources for a given $y$ are
-    $$[8, 9, 10, 11, 13, 16, 21, 29, 42, 61, 95] \,.$$
+    $$[8, 9, 10, 11, 13, 16, 21, 29, 42, 61, 95]~\textrm{pix} \,.$$
     Notice that the spatial separations and intensity changes are based on the Fibonacci series, which places them on a cadence that is sub-logarithmic but supra-linear, and thus provides a good trade-off between dynamic range and point density.
@@
 Three brightness levels are considered, with counts in all the diffuse sources set at
-    $$\{100, 500, 1000\} \cdot \tau \,,$$
+    $$\{100, 500, 1000\} \cdot \tau ~\textrm{counts~pix}^{-1}\,,$$
     where $\tau=1$ for \chandra-like and $\tau=5$ for \xmm-like simulations.  The diffuse sources are located at
-    $$(x,y)_{{\rm diffuse}} = (22,22), (22,106), (106,106), (106,22) ~{\rm pix} \,,$$
+    $$(x,y)_{{\rm diffuse}} = (22,22), (22,106), (106,106), (106,22) ~\textrm{pix} \,,$$
     and the point sources at
-    $$(x,y)_{{\rm point}} = (64,76), (44,64), (74,64), (64,44) \,,$$
+    $$(x,y)_{{\rm point}} = (64,76), (44,64), (74,64), (64,44) ~\textrm{pix}\,,$$
     with counts
@@
     \paragraph{Shield} A flat disk at image center, with superposed point sources, and jet-like linear extensions radiating to the corners.  The disk has a radius of 20~pix and has brightness set to
-    $$\{0.5, 1, 2\} \cdot \tau ~{\rm counts~pix^{-1}} \,,$$
+    $$\{0.5, 1, 2\} \cdot \tau ~\textrm{counts~pix}^{-1} \,,$$
     where again $\tau$ represents an arbitrary scaling factor to mimic telescope sensitivity.
 Four point sources are placed at positions displaced at $\{\pm8,\pm8\}$~pix from image center, with intensities at
-    $$\{10, 50, 100, 500\} \cdot \tau ~{\rm counts}$$
+    $$\{10, 50, 100, 500\} \cdot \tau ~~\textrm{counts}$$
     clockwise starting from lower left respectively.
 Linear sources of horizontal width 3~pix are placed along the $\pm45^o$ lines extending between radial distances from 36~pix to 64~pix from image center, with surface brightnesses
-    $$\{10, 50, 100, 500\} \cdot \tau ~{\rm counts~pix^{-1}} \,,$$
+    $$\{10, 50, 100, 500\} \cdot \tau ~\textrm{counts~pix}^{-1} \,,$$
     matching those of the nearest point sources.
@@
 
-    \paragraph{Spiral}
+    \paragraph{Spiral} This has 4 major components: First, a double spiral structure, centered at $(-10, 0)$~pix, covering 500$^o$~deg with a maximum radial extent of 24~pixels and a width of 3~pixels; second, a disk of radius 4, also centered at $(-10, 0)$~pix; third, two vertical rows of point sources located at x-axis positions of 40~pixels and 88~pix, and y-axis locations of $\{\pm7,\pm21\}$~pix; and fourth, an annulus that encloses all these elements, also centered at $(-10, 0)$~pix, and with inner radius 52~pix and outer radius 54~pix.
+    The point sources have intensities of $\{25, 50, 100, 200\}$~counts increasing with vertical height, and the spiral, disk, and annulus have surface brightnesses of $$\{0.5, 1, 2, 10, 1000\} \cdot \tau ~\textrm{counts}$$.
+This configuration tests the recovery of closely located diffuse structures (close spiral arms), field-of-view edge effects (annulus that approaches close to the left edge of the image), and the visibility of point sources close to diffuse structures.
+The case with the surface brightness of 1000~counts~pix$^{-1}$ tests the asymptotic limit of the high counts case.
 
@@
         \begin{centering}
-            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
+            \includegraphics[width=\linewidth]{figures/example-fermi-lat-non-calibrated.pdf}
             \caption{

### 2024-02-15 src/scripts/metrics-table.py
Fix metrics table script

@@ -1,0 +1,100 @@
+import logging
+from io import StringIO
+
+import paths
+import yaml
+from astropy.table import Table
+
+log = logging.getLogger(__name__)
+
+
+METRICS = ["MSE", "NMI", "SSI", "NRMSE"]
+SCENARIOS = {"point1": "A1", "aster3": "B3", "disk3": "C3", "spiral4": "D4"}
+
+
+method_titles = {
+    # "gt": "Ground Truth",
+    "jolideco-uniform-prior=n=10": "Jolideco\n(Uni, n=10)",
+    "jolideco-uniform-prior=n=1000": "Jolideco\n(Unif., n=1000)",
+    "pylira": "Pylira",
+    "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
+    "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
+}
+
+
+def get_metrics(path):
+    with open(path) as f:
+        metrics = yaml.safe_load(f)
+
+    return metrics
+
+
+def get_parameters(filename):
+    parts = filename.parts
+    return {
+        "Method": parts[-2],
+        "Bkg. Level": parts[-4],
+        "Scenario": parts[-5],
+        "Instrument": parts[-3],
+    }
+
+
+colnames = [
+    "Method",
+    "Bkg. Level",
+    "Scenario",
+    "Instrument",
+]
+names = colnames + METRICS
+
+dtypes = ["S20"] * len(colnames) + ["f8"] * len(METRICS)
+
+table = Table(names=names, dtype=dtypes)
+
+filenames = paths.jolideco_repo_comparison.glob("results/*/bg*/*/*/metrics.yaml")
+
+
+for filename in filenames:
+    data = get_metrics(filename)
+    data.update(get_parameters(filename))
+    table.add_row(data)
+
+
+selection = (table["Instrument"] == "chandra") & (table["Bkg. Level"] == "bg1")
+table = table[selection]
+
+
+table_metrics = Table(
+    names=["Scenario"] + list(method_titles.keys()),
+    dtype=["S2"] + ["S10"] * len(method_titles),
+)
+
+for scenario in SCENARIOS:
+    data = table[table["Scenario"] == scenario]
+
+    values = {}
+    for method in method_titles:
+        selection = data["Method"] == method
+        v = [float(data[selection][name]) for name in ["SSI", "NRMSE"]]
[…]

### 2024-02-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\chandra}{\textit{Chandra}~}
+\newcommand{\chandranospace}{\textit{Chandra}}
 \newcommand{\xmm}{\textit{XMM}~}
@@
 % Title
-    \title{Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise}
+    \title{%Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise}
+    Jolideco: A Simultaneous Deconvolution of Multiple Images in the Presence of Poisson Noise}
 
@@
     \begin{abstract}
-        We present a new method for Joint Likelihood Deconvolution (\jolideco) of a set of astronomical observations of the same sky region in the presence of Poisson noise.
-The method reconstructs a single flux image from a set of observations and given models for the point spread function (PSF) per observation, by optimizing the the posterior distribution based on the joint Poisson likelihood of all observations under a patch based image prior.
-The patch prior is parameterised by a Gaussian Mixture model (GMM) which we trained on astronomical images with high signal to noise ratio, including data from the  James Webb Telescope as well as the GLEAM radio survey.
-During the reconstruction process the patch prior adapts to the patch structures in the data by finding the most likely GMM component for each patch in the image.
-By applying the method to simulated data we show that both the combination of multiple observations as well as the patch based prior lead to a much improved reconstruction quality in many different source scenarios as well as signal to noise regimes.
-We show also that the method yields superior reconstruction quality to alternative standard methods such as the Richardson-Lucy method.
-We also show the results of the method applied to example data from the \chandra observatory as well as the \ferminospace.
+
+        We present a new method for JOint LIkelihood DECOnvolution (\jolideconospace) of a set of astronomical observations of the same sky region in the presence of Poisson noise. 
+        The observations may be obtained from different missions with  different resolution, and different point spread functions. 
+        \jolideco reconstructs a single flux image 
+        %from the set of observations 
+        %and given models for the point spread function (PSF) per observation, 
+        by optimizing the posterior distribution based on the joint Poisson likelihood of all observations under a patch-based image prior.
+The patch prior is parameterised via a Gaussian Mixture model which we train on high-signal-to-noise astronomical images, including data from the  James Webb Telescope and the GLEAM radio survey.
+This prior favors correlation structures among the reconstructed pixel intensities that are characteristic of those observed in the astronomical images used to train the prior, but is not informative for the mean or scale of the reconstruction.
+By applying the method to simulated data we show that the combination of multiple observations and the patch-based prior leads to much improved reconstruction quality in many different source scenarios and signal to noise regimes.
+We demonstrate that \jolideco yields superior reconstruction quality relative to alternative standard methods such as the Richardson-Lucy method.
+We illustrate the results of \jolideco\ applied to example data from the \chandra observatory and the \ferminospace.
 By comparing the measured width of a counts based and the corresponding \jolideco flux profile we find the deconvolved width to be consistent with the theoretical expectation derived from the known width of the PSF.
@@
     \label{sec:related}
-    In literature there have been many efforts to solve the unblind deconvolution problem for images affected by Poisson noise.
-Most methods rely fundamentally on modeling the image generating process as a linear process.
-Given a known PSF a prediction of the discrete measured image can be obtained via \enquote{forward folding} and be compared against an observation assuming Poisson statistics per pixel.
+    In the literature there have been many efforts to solve the unblind deconvolution problem for images affected by Poisson noise.
+Most methods rely fundamentally on modeling image generating as a linear process.
+Given a known PSF a prediction of the discrete measured image can be obtained via \enquote{forward folding} and be compared against an observation assuming Poisson statistics in each pixel.
 However, the methods differ in their additional prior or regularisation assumptions as well as their approach to optimization or sampling of the underlying likelihood function or posterior distribution.
@@
 
-    However, in practice the RL method was found to have multiple, partly related limitations: first, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
-This problem was for example described and studied by \cite{Reeves1995} and \cite{Fish1995}.
-This means that in practice the RL method is not iterated until it converges, leading to the second limitation: there is no objective criterion for when to stop the optimization process.
+    However, in practice the RL method has multiple, partly related limitations: first, when the number of iterations is too high, the method shows a tendency to decompose regions of constant brightness into a set of bright emission peaks (\enquote{speckles}).
+This problem was described and studied, for example,  by \cite{Reeves1995} and \cite{Fish1995}.
+This means that in practice the RL method is not iterated until it converges, leading to the second limitation: there is no objective criterion for stopping the optimization process.
 Usually the iteration is stopped when the reconstructed image seems plausible to the eye.
@@
 
-    To address the issue with RL decomposing extended emission structures into groups of point sources, multiple additions to the RL method were proposed.
+    To address the issue with RL decomposing extended emission structures into groups of point sources, multiple additions to the RL method  have been proposed.
 Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparse representations based on \enquote{wavelets} or \enquote{curvelets} \citep{Starck2003}.
@@
 
-    One possible approach to overcome this challenge has been proposed by \cite{Esch2004} and \cite{Connors2011} with the EMC2 and LIRA methods.
+    One possible approach to overcome this challenge is proposed by \cite{Esch2004} and \cite{Connors2011} with the EMC2 and LIRA methods.
 Their key idea is to introduce a prior assumption that favors smoothness on multiple spatial scales of the image.
@@
 
-    An interesting modification of the standard RL method has been proposed by \cite{Ingaramo2014}.
+    An interesting modification of the standard RL method is proposed by \cite{Ingaramo2014}.
 They show that RL could be effective in creating a merged image from multiple observations.
@@
     \cite{Selig2015} and \cite{Pumpe2018} approach the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
-Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they are able to deconvolve \fermi observations as well as decomposing it into point-like and diffuse emission components.
+Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they are able to deconvolve \fermi observations
+    into a mixture of point-like and diffuse emission components.
 While their method works well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it shows artifacts for smaller extended emission structures such as morphological details of extended sources in the Galactic Plane.
@@
 For example \cite{Zoran2011} build on very similar assumption of local correlation for natural images.
-However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian with a correlation size, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
-For this they propose to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) to model the distribution of extracted patches.
-To use the GMM in reconstruction they introduced the concept of expected patch likelihood (EPLL).
-They showed that the patch based GMM prior led to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
+However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian kernel with a given bandwidth determining the correlation scale,
+    %with a correlation size, 
+    they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
+For this they propose to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) %to model
+    for the distribution of extracted patches.
+To use the GMM in reconstruction they introduce the concept of expected patch likelihood (EPLL).
+They show that the patch-based GMM prior leads to much improved image reconstructions for multiple inverse problems such as denoising, deblurring and inpainting.
 \cite{Bouman2016} later adapted the patch prior successfully for the reconstruction of sub-millimeter radio data from the Event Horizon Telescope (EHT).
@@
 However, their success relies on the availability of massive sets of training data with typically low noise and corresponding ground truth to perform supervised learning.
-For a variety of reasons, which we will outline in the following, this approach is not ideal for astronomical \xray and \gammaray data.
+For a variety of reasons, which we outline in the following, this approach is not ideal for astronomical \xray and \gammaray data.
 
@@
 To circumvent this issue one could rely on transfer learning and simulated data.
-For example, radio or optical images could be forward folded with a known PSF model and be degraded with Poisson noise to generate training data.
-However, astronomical images still
-    have a large dynamic range and show a high diversity in morphological structure, which would still requires a large amount of training data.
+For example, radio or optical images could be forward folded with a known PSF and degraded with Poisson noise to generate training data.
+Astronomical images, however, have a large dynamic range and show a high diversity in morphological structure, which would requires a large amount of training data.
 
@@
 
-    Some of the challenges of deblurring with CNN are due to the convolutional nature of the networks.
+    Some of the challenges of deblurring with CNNs are due to the convolutional nature of the networks.
 In a single layer, linear approximation, the network would need to learn the inverse filter of the PSF, corresponding to the well known \enquote{Wiener Filter} solution of the problem.
-This requires either large convolution kernels or deep network architectures, which require in turn large amounts of training data.
-This challenge was described early by \cite{Li2014} who introduced a baseline architecture for a deep CNN for image deblurring.
+This requires either large convolution kernels or deep network architectures, which in turn require large amounts of training data.
+This challenge was described early on by \cite{Li2014} who introduced a baseline architecture for a deep CNN for image deblurring.
 
@@
     Any arbitrary combination of the possibilities is also possible.
-    In principle, we can also combine observations in different energy ranges.
+    In principle, we can combine observations in different energy ranges.
 In this case, however, the assumption of the morphology not changing with energy would apply, which is rarely fulfilled for astronomical objects.
@@
 
-    Given a single observation $j$ of an unknown flux image $\mathbf{x}$ and assuming the noise in each pixel $i$ in the recorded counts image $\mathbf{D_j}$ follow independent Poisson distributions with expectation $\boldsymbol{\lambda_j}$, the likelihood $\mathcal{P}$
-    of obtaining the measured image with $N$ pixels is given by:
+    Given a single observation $j$ of an unknown flux image $\mathbf{x}$ and assuming the noise in each pixel $i$ in the recorded counts image $\mathbf{D}_j$ follow independent Poisson distributions with expectation $\boldsymbol{\lambda}_j$, the likelihood $P$ of obtaining the measured image with $N$ pixels is given by:
     %
@@
         \label{eq:poisson}
-        P\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \prod_{i=1}^N \frac{{e^{ - \lambda_{j,i} } \lambda_{i,j} ^ {D_{j,i}}}}{{D_{j,i}!}},
-    \end{equation}
-    %
-    where $\boldsymbol{\lambda_j}$ depends on $\mathbf{x}$ as defined by Equation~\ref{eq:model}.
-By taking the logarithm and dropping the constant terms one can transform the product into a sum over pixels, which is also often called the \enquote{Cash} \citep{Cash1979} fit statistics:
+        P\left( \mathbf{D}_j | \boldsymbol{\lambda}_j \right) = \prod_{i=1}^N \frac{{e^{ - \lambda_{j,i} } \lambda_{i,j} ^ {D_{j,i}}}}{{D_{j,i}!}},
+    \end{equation}
+    %
+    where $\boldsymbol{\lambda}_j$ depends on $\mathbf{x}$ as defined by Equation~\ref{eq:model}.
+By taking the logarithm, multiplying by $-1$, and dropping the constant terms one can transform the product into a sum over pixels, which is also often called the \enquote{Cash} \citep{Cash1979} fit statistics:
     %
@@
         \label{eq:cash}
-        \mathcal{C}\left( \mathbf{D_j} | \boldsymbol{\lambda_j} \right) = \sum_{i=1}^{N_j} \left(\lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}\right),
+        \mathcal{C}\left( \mathbf{D}_j | \boldsymbol{\lambda}_j \right) = \sum_{i=1}^{N_j} \left(\lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}\right),
     \end{equation}
@@
         \label{eq:joint}
-        \mathcal{L}\left( \mathbf{D} | \mathbf{x} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)
-    \end{equation}
-    %
-    In principle, we could try to obtain the Maximum Likelihood Estimate (MLE) of $\hat{\mathbf{x}}$ directly, using an optimization procedure.
+        \mathcal{L}\left( \mathbf{D} | \mathbf{x} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right)
+    \end{equation}
+    %
+    In principle, we could obtain the Maximum Likelihood Estimate (MLE), $\hat{\mathbf{x}}$ of ${\mathbf{x}}$, by directly optimizing Equation~\ref{eq:joint}.
 Indeed, this is the objective of the RL algorithm.
@@
 The likelihood surface shows many local, close-by maxima.
-Depending on the starting value used for $\mathbf{x}$ and the optimization algorithm the MLE based estimate is likely to only find a local maxima.
+Depending on the starting value used for $\mathbf{x}$ and the optimization algorithm the computed MLE is likely to be a local maxima.
 This is fundamentally the reason for RL decomposing estimates into point sources, described in Section~\ref{sec:related}.
@@
     When reconstructing images in the context of inverse problems we are operating in a high dimensional parameter space, because each pixel in the image represents a parameter in the optimization process.
-By using prior information we can introduce correlations between the parameters, to reduce the \enquote{effective dimensionality} of the problem and guide the optimization process toward unique and more stable solutions.
-
-    Using Bayes' rule we can estimate the \aposteriori likelihood under a given prior distribution, $P(\mathbf{x} )$:
+By using prior information we can introduce correlations among the parameters, to reduce the \enquote{effective dimensionality} of the problem and guide the optimization process toward unique and more stable solutions.
+
+    Using Bayes' rule we can express the \aposteriori likelihood under a given prior distribution, $P(\mathbf{x} )$:
     %
@@
     Taking the logarithm of Equation~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Equation~\ref{eq:joint} and dropping the normalisation term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we obtain the following expression for the log-posterior distribution
-    %likelihood 
-    $\mathcal{L}$ :
+    $\mathcal{L}$:
     %
@@
     %
-    where $\mathcal{C}\left( \mathbf{D_j} | \mathbf{x} \right)$ represents the summed log-likelihood for an individual observation $j$ and $\mathcal{P}(\mathbf{x})$ represents the log of the prior distribution with the factor $\beta$ adjusting the weight of the prior relative to the joint log likelihood term.
+    where $\mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right)$ represents the summed log-likelihood for an individual observation $j$ and $\mathcal{P}(\mathbf{x})$ represents the log of the prior distribution with the factor $\beta$ adjusting the weight of the prior relative to the joint log likelihood term.
 The parameter $\beta$ can be viewed as a hyper-parameter, chosen by the user to adjust the strength of the prior distribution relative to the likelihood.
-The choice of $\beta$ is optional and for all experiments presented in this paper we just set $\beta=1$.
-
-    \newpage
-    \subsection{Patch Based Image Prior}
+The choice of $\beta$ is optional and for all experiments presented in this paper we set $\beta=1$.
+
+    %\newpage
+    \subsection{patch-based Image Prior}
     \label{sec:patch-prior}
     In general it is difficult to capture global image characteristics in a prior distribution taking into account all pixel to pixel correlations.
-The size of the corresponding correlation matrix would grow with the number of pixels squared and thus quickly become computationally untraceable.
+The size of the corresponding correlation matrix would grow with the squre of the number of pixels  and thus quickly become computationally untraceable.
 However, astronomical images typically only exhibit local correlations among the pixels.
@@
 
-    A patch is defined as a small, typically square, region of size $N \times N$ pixels, representing a local neighbourhood in a given image.
+    A patch is defined as a small, typically square, region of size $N_p \times N_p$ pixels, representing a local neighbourhood in a given image.
 Mathematically we can formulate the extraction of such patches as:
@@
     \begin{equation}
-        \mathbf{x}_n = \mathbf{P_n x}
-    \end{equation}
-    %
-    Where $\mathbf{P_n}$ represents a neighbourhood matrix to extract the $n$-th patch from the image $\mathbf{x}$.
-When given many of theses patches we can model the distribution of pixels values within the patch using a Gaussian Mixture Model (GMM).
-The GMM has the property of being a universal function approximator and thus can model arbitrary distributions.
+        \mathbf{x}_n = \mathbf{P}_n \mathbf{x}
+    \end{equation}
+    %
+    Where $\mathbf{P}_n$ represents a neighbourhood matrix to extract the $n$-th patch from the image $\mathbf{x}$ and where $\mathbf{x}_n$ is the vector of length $N_p^2$ representing the \enquote{flattened} image patch.
+By obtaining a large number of patches we can model the distribution of pixels values within the patches using a Gaussian Mixture Model (GMM).
+The GMM is a universal function approximator and thus can model arbitrary distributions.
 For now we assume that we have a pre-trained GMM which encodes the patch distribution of some reference image we have chosen.
-During the actual image reconstruction we then try to identify the most likely GMM component per patch and treat as a discrete hyper-parameter in the model that is optimized along with the image $\mathbf{x}$.
-
-    A convenient property of the GMM is that its probability can be evaluated in closed form. For a given single patch $\mathbf{x}_n$ it is given by:
+During the actual image reconstruction we aim to identify the most likely GMM component per patch, treating this as a discrete hyper-parameter
+    that is optimized along with the image $\mathbf{x}$.
+
+    A convenient property of the GMM is that its probability density can be evaluated in closed form. For a given single patch $\mathbf{x}_n$,
     %
@@
     %
-    where $\mathcal{N}$ is a Gaussian distribution, $K$ the number of components in the GMM, $\boldsymbol{\mu}_k$ is the mean vector for a component $k$, $\boldsymbol{\Sigma}_k$ the corresponding covariance matrix, and $\pi_k$ the weight of component $k$.
-The weights are required to sum to unity such that $\sum_{k=1}^K\pi_k = 1$.
-
-    If we knew the relevant component, $k_n$, we could derive the conditional log-prior distribution directly from Equation~\ref{eq:gmm}:
+
+    If we knew the relevant component, $k_n$, for patch $\mathbf{x}_n$ we could derive the conditional log-prior distribution directly from Equation~\ref{eq:gmm}:
     %
@@
     + \log(|\boldsymbol \Sigma_{k_n}|)\\
-    + (\mathbf{x}_n - \boldsymbol{\mu}_{k_n})^T \Sigma^{-1}_{k}(\mathbf{x}_n - \boldsymbol{\mu}_{k_n}) \left. \right]
+    + (\mathbf{x}_n - \boldsymbol{\mu}_{k_n})^T \Sigma^{-1}_{k}(\mathbf{x}_n - \boldsymbol{\mu}_{k_n}) \left. \right].
     \label{eq:cond.log.prior}
@@
     \begin{equation}
-        \hat{k}_n = \underset{k \in \{1, ..., N\} }{\argmax}{\mathcal{P}_{\rm GMM}(\mathbf{x}_n|k)}
+        \hat{k}_n = \underset{k \in \{1, ..., K\} }{\argmax}{\mathcal{P}_{\rm GMM}(\mathbf{x}_n|k)}
+        \label{eq:khat}
     \end{equation}
@@
     As the number of components in the GMM is typically limited to $\mathcal{O}(10^2)$ we can optimize the conditional log-prior distribution by simply evaluating it for each of the GMM components and choose the one with the maximum value.
-Finally, to evaluate the log-prior of the full image we sum the maximum values of the individual patches:
+Finally, to evaluate the (optimizied) log-prior of the full image we sum the maximum values of the individual patches:
     %
@@
 Visually, the representation of the patch in the Eigenbasis of the covariance results in a denoised version of the patch.
+\dvd{Can we discuss this briefly?}
 
@@
 
-    \cite{Zoran2011} found that the reconstruction quality could be improved by working with a grid of overlapping patches.
+    \cite{Zoran2011} found that the reconstruction quality can be improved by working with a grid of overlapping patches.
 This is illustrated in Figure~\ref{fig:patches}.
@@
 For this reason we introduce a weighting mask when evaluating the GMM prior distribution.
-    This mask weighs the pixels of the patch by their overlap with neighboring patches.
-Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4, when computing the prior distribution for a patch as given by  Equation~\ref{eq:gmm}.
+This mask weighs the pixels of each patch by their overlap with neighboring patches.
+Overlapping edges are assigned a weight of 1/2, while overlapping corners are assigned a weight of 1/4, when computing the log prior distribution for a patch as given by Equation~\ref{eq:cond.log.prior}.
 
     Apart from this, the process for choosing the most likely GMM prior component remains unmodified.
-However, we note that in this case we neglected the prior dependence between neighbouring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixes and are thus clearly not \aprioir independent.}.
+However, we note that we neglected the prior dependence between neighbouring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixes and are thus clearly not \aprioir independent.}.
 As the choice of the GMM component per patch is discrete, a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
@@
 This corresponds to the assumption that the structure in the patch is \aprioir independent of the total flux contained in the patch, which we consider a valid assumption for astronomical images.
-This also generalizes to the prior likelihood of the whole image described by Equation~\ref{eq:prior-total}.
-The value of the prior likelihood becomes independent of the total flux contained in the image.
-The prior distribution simply regularizes the structure in the image, while the overall intensities are typically well constrained by the Poisson likelihood term.
-Thus we only assume a uniform prior for the patch intensities.
+This also generalizes to the prior distribution of the whole image described by Equation~\ref{eq:prior-total}.
+The value of the prior distribution is independent of the total flux of the image.
+The prior distribution simply regularizes the structure in the image, while the overall intensities are typically well constrained by data as quantified by the Poisson likelihood term.
+Thus we simply assume a uniform prior distribution for the patch intensities.
+Algorithmically, we replace $\mathbf{x}_n$ with $\tilde{\mathbf{x}}_n$ when evaluating Equations~\ref{eq:gmm} \ref{eq:khat} and transform $\mathbf{P}_n\mathbf{x}$ via Equation~\ref{eq:patch-norm} when evaluating Equation~\ref{eq:prior-total}.
 
@@
 To recover point sources accurately it is required to keep correlations with neighbouring pixels low, while for extended source the opposite is true.
-Ideally those contradicting requirements can be handled with a single flexible prior assumption, which adapts to the data, such as the patch based GMM prior introduced in the previous section.
+Ideally those contradicting requirements can be handled with a single flexible prior assumption, which adapts to the data, such as the patch-based GMM prior introduced in the previous section.
 
@@
 To avoid artifacts in the reconstruction due to the fixed position of the grid, we use the method of \enquote{cycle spinning} \citep{Coifman1995}.
-Before evaluating the patch prior we shift the image $\mathbf{x}$ by a random number of pixels in both the x and y direction, where the shift is less than or equal to half the size of a patch.
+Before evaluating the patch prior at each iteration of our optimizer, we shift the image $\mathbf{x}$ by a random number of pixels in both the x and y direction, where the shift is less than or equal to half the size of a patch.
 The same method has, for example, been used in \cite{Esch2004}.
@@
     A variation of cycle spinning specifically for the patch prior is proposed in \cite{Parameswaran2018}.
-Instead of a regular grid for the patches they propose to work with a randomised grid of patches, where the center of each patch is randomly shifted, while ensuring that patches still overlap by at least one pixel.
+Instead of a regular grid for the patches they propose to work with a randomised grid of patches, where the center of each patch is randomly shifted, while ensuring that patches overlap by at least one pixel.
 In doing so they find that a smaller total number of patches can be used, while retaining the same reconstruction quality.
@@
 We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction is slightly faster with the same reconstruction quality.
-However for all results shown later in the manuscript we chose the simpler cycle spinning described in the previous section.
+However for all results shown later in the manuscript we chose the simpler cycle spinning described in the previous paragraph.
 
@@
     \subsection{Systematic Errors of Predicted Counts}
-    Each observation $\mathbf{D_j}$ is subject to systematic errors.
+    Each observation $\mathbf{D}_j$ is subject to systematic errors.
 For example, the pointing accuracy of the telescope when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object may vary among the  observations.
@@
     In practice one observation is used as a reference and its corresponding systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during optimization.
-An example of the effect of the positional shift and background normalisation can be seen in Figure~\ref{fig:npred-systematics}.
+An example of the effect of the positional shift and background normalisation can be seen in Figure~\ref{fig:example-fermi-lat-non-calibrated}.
 
@@
 However, there are other ways to estimate the statistical uncertainties associated with the flux image.
-We propose three methods:
+We propose two methods:
 
@@
     \item \textbf{Bootstrapping Events}.
-If only one or few observations are available we propose bootstrapping of the events used to compute the counts image(s).
+If only one or a small number of observations are available we propose bootstrapping of the events used to compute the counts image(s).
 This corresponds to splitting a single observation into multiple observations by splitting the single exposure into multiple time intervals.
@@
 
-    We also experimented with computing the diagonal of Hessian of the posterior distribution at the minimum. However we found this numerically challenging because of random the cycle spinning.
+    We also experimented with computing the diagonal of the Hessian of the posterior distribution evaluated at the MAP estimate.
+However we found this numerically challenging because of random the cycle spinning.
 
@@
     \subsection{\jolideco Framework}
-    The goal of the reconstruction process is to optimize the a-posteriori likelihood defined by Equation~\ref{eq:total}. Given that there is a parameter for each pixel in the image,  
-    this is a high dimensional optimization problem.
-Differentiable programming frameworks such as \texttt{PyTorch}~\citep{Pytorch2019} allow for solving high dimensional optimization problems using back-propagation.
+    The goal of the reconstruction process is to optimize the a-posteriori likelihood defined by Equation~\ref{eq:total}.
+Given that there is a parameter for each pixel in the image, this is a high dimensional optimization problem.
+Differentiable programming frameworks such as PyTorch~\citep{Pytorch2019} allow for solving high dimensional optimization problems using back-propagation.
 They also offer a variety of optimization methods such as stochastic gradient decent (SGD).
@@
 
-    We implemented the \jolideco method as an independent Python package, based on \texttt{PyTorch} as the back-end optimizer.
-We define a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as choice of the patch normalisation, the choice of GMM models, optimization methods, and serialisation formats for the reconstruction results as well as the corresponding diagnostic information, such as the trace of the posterior and prior likelihood values.
+    We implemented the \jolideco method as an independent Python package, based on PyTorch as the computational back-end.
+We defined a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as the choice of the patch normalisation, the choice of GMM, optimization methods, and serialisation formats for the reconstruction results as well as the corresponding diagnostic information, such as the trace of the posterior and prior likelihood values.
 This will simplify future improvement and extension of the package as well as the adoption of \jolideco by the astronomical community.
@@
 
-    We use \texttt{Numpy}~\citep{Numpy2020} for handling data arrays and \texttt{Matplotlib}~\citep{Hunter2007} for plotting.
-To learn the Gaussian Mixture Models from patches we use the standard implementation provided in the \texttt{Scikit-Learn}~\citep{scikit-learn} package.
-To handle the serialisation of images to the \textit{FITS} data format and to handle world coordinate systems (WCS) we use \texttt{Astropy}~\citep{Astropy2018}.
+    We use Numpy~\citep{Numpy2020} for handling data arrays and Matplotlib~\citep{Hunter2007} for plotting.
+To learn the GMM from patches we use the standard implementation provided in the Scikit-Learn~\citep{scikit-learn} package.
+To handle the serialisation of images to the FITS data format and to handle world coordinate systems (WCS) we use Astropy~\citep{Astropy2018}.
 
@@
     \label{ssec:jolideco-gmm-library}
-    The patch based image prior described in Section~\ref{sec:patch-prior} requires pre-trained GMMs.
-We train the GMM by choosing a set of reference images, splitting them into patches of size $8\times8$ pixels and learning a GMM with $N$-components from the whole distribution of patches.
-
+    The patch-based image prior described in Section~\ref{sec:patch-prior} requires a pre-trained GMM.
+We train the GMM by choosing a set of reference images, splitting them into patches of size $8\times8$ pixels and learning a GMM with $K$ components from the whole distribution of patches.
 In general the strength of the GMM prior is its high \enquote{expressiveness}.
 This means the prior distribution contains a large variety of structural shapes and has freedom to adapt to the data in the optimization process by choosing the most likely GMM component for each patch in the image.
-With radio data \cite{Bouman2016} found their results to be mostly independent of the choice of data the GMM prior was learned on.
-
-    However, in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of the data the GMM was learned on.
-Simply because the prior distribution is more influential when the data is less informative.
-Thus, the prior should be adapted to the particular analysis scenario in order to avoid bias.
+With radio data, \cite{Bouman2016} found their results to be mostly independent of the choice of data the GMM prior was learned on.
+
+    However, in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of prior, simply because the prior distribution is more influential when the data is less informative.
+Thus, there is the potential for the choice of GMM training data to be influential on results and the prior should be adapted to the particular analysis scenario in order to avoid bias.
 For this reason and for purposes of testing we learned and provide a selection of GMMs to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
@@
 
-    The training images were split into patches of size 8x8 pixels, resulting in a training set of $2 \cdot 10^{6}$ patches which were used to fit a GMM with 200 components.The training patches were mean subtracted before the GMM was fit.
+    The training images were split into patches of size $8\times8$ pixels, resulting in a training set of $2 \cdot 10^{6}$ patches which were used to fit a GMM with 200 components.
+The training patches were mean subtracted before the GMM was fit.
 The model is provided by the authors as part of the source code for download\footnote{\url{https://people.csail.mit.edu/danielzoran/epllcode.zip}}.
-More details of how the model was trained are given in the original publication.
+More details of how the model was trained are given in \citet{Zoran2011}.
 
@@
     \label{sssec:gleam-radio-data}
-    As an alternative we consider a prior learned from astronomical radio data.
-For this we relied on high signal to noise radio data from the \textit{GLEAM} survey \cite{HurleyWalker2022}.
+    As an alternative we consider a GMM prior learned from astronomical radio data.
+For this we relied on high signal to noise radio data from the \textit{GLEAM} survey \citep{HurleyWalker2022}.
 We downloaded the data using the Gleam VO Client\footnote{\url{https://github.com/ICRAR/gleamvo-client}}.
-We restricted the choice of data to the Galactic Plane between $b=\pm10\deg$ and $\ell = \pm180\deg$ to avoid a bias towards extra-galactic point sources and represent structures of Galactic sources with rich morphology, such as supernova remnants, pulsar winds etc.
-The dataset still includes Galactic as well as extra-galactic point sources in the background.
+We restricted the choice of data to the Galactic Plane between $b=\pm10\deg$ and $\ell = \pm180\deg$ to avoid a bias towards extra-galactic point sources and to represent structures of Galactic sources with rich morphology, such as supernova remnants, pulsar winds etc.
+The dataset includes Galactic as well as extra-galactic point sources in the background.
 In total we extracted $\approx 6 \times 10^5$ patches and trained a GMM with 128 components.
@@
 The JWST is a large, infrared space telescope launched in late 2021.
-It delivers image data at very high spatial resolution as well as excellent signal to noise ratio.
+It delivers image data at very high spatial resolution with an excellent signal to noise ratio.
 Both of these properties make JWST data an excellent choice for extracting patches for training a GMM.
@@
 We first converted the image to gray scale using a perceived brightness model from the Scikit-Image package \citep{scikit-image}.
-Then we split the image into $\approx 2$ million patches and learned a GMM with 128 mixture components.
+Then we split the image into $\approx 2$ million $8\times 8$ patches and learned a GMM with 128 mixture components.
 Again we relied on the patch normalisation described in Section~\ref{ssec:patch-norm}.
@@
     \label{sssec:chandra-snrs}
-    To demonstrate the flexibility in the selection of data to train the GMM, we also chose a selection of high signal-to-noise images from the \chandra catalog of of Supernova remnants.
-
-    Because of the limited statistics we did not use any oversampling but kept the pixel.
-Astrophysical processes forming the morphological structures are typically self-similar.
-Structures appear on multiple angular scales.
-This means the prior could even be learned from the data itself if sufficiently free of noise.
-For analysis of Galactic sources with complex morphology and typically radially symmetric features such as supernova remnants (SNRs) we learned a prior from images of the bright \chandra SNRs \textit{Cas A} and \textit{G292.0+01.8}.
-In total we extracted $\approx 10^6$ patches and learned a GMM with 128 components.
+    To demonstrate the flexibility in the selection of data to train the GMM, we also chose higher signal-to-noise images from the \chandra catalog of supernova remnants (SNRs).
+We learned a GMM prior from images of the bright \chandra SNRs \textit{Cas A} and \textit{G292.0+01.8}.
+In total we extracted $\approx 0.5$ million $8\times 8$ patches from each of the images and learned a GMM with 128 components.
 
     \subsection{Optimization Strategy}
-    Maximising the \aposteriori likelihood defined Equation~\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
-
-    To improve the convergence rate of the optimization process we employ the following optimization strategy: the optimization strategy begins with the optimizer viewing $\log{\mathbf{x}}$, and the first step involves running a rough estimate using a uniform prior.
-This step is optional, but if chosen, the next step involves optimizing the parameters associated with the systematic error described in Equation~\ref{eq:model-npred-calibration}.
-Following this, a full optimization is performed using the patch prior, which can be computationally expensive.
-The optimization algorithm used is ADAM\citep{Kingma2014}, a stochastic gradient descent method, without decay and a fixed step size value of $\mathrm{lr}=10^{-3}$ has been used.
-
-    In practice we employ the following optimization strategy:
+    \label{sec:opt-strategy}
+    Maximising the \aposteriori likelihood defined by Equation~\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
+We found the convergence greatly improved when the optimizer operates on $\log{\mathbf{x}}$.
+This is to be expected, as the brightness in pixels of astronomical can span multiple orders of magnitudes.
+We used the ADAM algorithm \citep{Kingma2014}, a stochastic gradient descent method, without decay and a fixed learning rate of $\mathrm{lr}=10^{-3}$.
+To further improve the rate of convergence of the optimization process we applied the following strategy:
+
     \begin{itemize}
-        \item the optimizer sees $\log{\mathbf{x}}$, note this corresponds to an implicit prior of the flux being positive...
-        \item First run with uniform prior, to get a rough estimate
-        \item (optional) Then optimize the parameters associated to the systematic error described in Equation~\ref{eq:model-npred-calibration}.
-        \item Then we go for a full optimization using the patch prior, which can be computationally costly
-        \item we use ADAM (stochastic gradient decent), without decay
-        \item  (optional) learning rate scheduling? So far just a fixed step size value of $1e-3$
+        \item[1.] We start from a random image where each pixel was drawn from a normal distribution with the mean corresponding to the total mean of the flux in the image and a standard deviation of 10\% of the mean.
+We first estimate $\mathbf{x}$ by using a uniform prior and early stopping after a 50 iterations.
+This corresponds approximately to a reconstruction obtained with the RL algorithm.
+        \item[2.] We freeze the image parameters and optimize the parameters associated with the systematic error described in Equation~\ref{eq:model-npred-calibration}.
+        \item[3.] Finally we optimize both the image $\mathbf{x}$ and the parameters associated with systematic error simultaneously until convergence.
+Convergence is verified visually by inspecting the time series of the log posterior distribution evaluated at the iterates or the models parameters.
+We adjust the number of epochs (number of passes through the whole set of observations) such that the curve had flattened out for the last few hundred iterations.
     \end{itemize}
@@
 We include point sources superposed on extended sources in four arrangements labelled A--D in the first row of Figure~\ref{fig:scenarios}.
-Each spatial arrangement is crossed with several signal-to-noise ratios (obtained with a constant background),
-    denoted \texttt{XN}.
+Each spatial arrangement is crossed with several signal-to-noise ratios (obtained with a constant background).
 The resulting scenarios are denoted by concatenating the two labels, e.g., A3 or C1, see Appendix~\ref{sec:app:A} for details.
-The goal of these experiments is not to set up or devise a \enquote{perfect} deconvolution algorithm, but to help assess their relative strengths and limitations.
+The goal of the experiments is not to set up or devise a \enquote{perfect} deconvolution algorithm, but to help assess their relative strengths and limitations.
 
@@
     The ground truth and corresponding expected counts for all combinations of source and instrument scenarios are shown in Figure~\ref{fig:scenarios}.
-The details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios}.
+The details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios} \dvd{I think this table is missing}.
 We assume a constant background with varying levels of $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
@@
         \caption{Illustration of the expected counts for the different source scenarios we used to generate test datasets.
-The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:testmodels}).
-For the instrument scenario \chandra we convolve the ground truth image with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
-For the scenario \xmm we used a Gaussian shaped PSF with a width of $\sigma=6$~pix and an effective area that is five times larger than that of \chandra.
+The source patterns shown are for the {\sl (A)}  {\tt points}, {\sl (B) {\tt asterism}}, {\sl (C)} {\tt shield}, and {\sl (D)} {\tt spiral} cases (see Section~\ref{sec:app:A}.
+For the \chandra instrument scenario we convolve the ground truth image with a narrow Gaussian shaped PSF of width $\sigma=2$~pix.
+For the \xmm scenario we used a Gaussian shaped PSF with a width of $\sigma=6$~pix and an effective area that is five times larger than that of \chandranospace.
 All images are of size $128{\times}128$ pixels.
@@
     \label{subsec:methods}
-    We compare the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we compare the following methods:
+    We compared the performance of \jolideco with different prior assumptions and against the \textit{LIRA} method introduced by \cite{Esch2004}. More specifically we compared the following methods:
 
@@
 
-        \item[\bf M1.]: we implement the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
-We rely on the default prior definition and keep the background norm fixed.
-In total we run the MCMC sampler for 5000 iterations and discard the first 500 iterations as a \enquote{burn-in} period to allow the MCMC chain to converge.
-We compute the mean of the posterior distribution ignoring the burn-in period.
-
-        \item[\bf M2.] \textbf{\jolideco (Uniform, n=10)}: we use \jolideco with a uniform prior on $\mathbf{x}$ and running the optimizer for 10 iterations.
+        \item[\bf M1.] \textbf{Pylira}: we used the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
+We relied on the default prior definition and kept the background norm fixed.
+In total we ran the MCMC sampler for 5000 iterations and discarded the first 500 iterations as a \enquote{burn-in} period to allow the MCMC chain to converge.
+We computed the mean of the posterior distribution ignoring the burn-in period.
+
+        \item[\bf M2.] \textbf{\jolideco (Uniform, n=10)}: we used \jolideco with a uniform prior on $\mathbf{x}$ and ran the optimizer for 10 iterations.
 We consider this as a baseline method reference similar to RL.
@@
 
-        \item[\bf M3.] \textbf{\jolideco (Uniform, n=1000)}:  we use \jolideco with a uniform prior on $\mathbf{x}$, but running the optimzier for 1000 iterations.
+        \item[\bf M3.] \textbf{\jolideco (Uniform, n=1000)}:  we used \jolideco with a uniform prior on $\mathbf{x}$, but running the optimizer for 1000 iterations.
 This is the same as above but without early stopping.
@@
 
-        \item[\bf M4.] \textbf{\jolideco (Patch, GLEAM v0.1)}: we use \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalisation described by Equation~\ref{eq:patch-norm}.
-We use cycle spinning and 2000 \enquote{training epochs}.
-Where one training epoch corresponds to a full iteration over all observations.
-By visualizing the value of the log-posterior we verified
-
-        \dvd{are ``stride'' and ``training epochs'' defined somewhere?} Given 5 observations this results in \dvd{a total of} 10,000 iterations.
-\dvd{What does the following mean?
-Is this a convergence criterion?
-But you just said you run for a fixed number of iterations.} Which optimizes \enquote{to end} until there is no relevant change in the posterior log-likelihood.
-In addition we use an upsampling \dvd{define?} factor of 2.
-
-        \item[\bf M5.] \textbf{\jolideco (Patch, Zoran-Weiss)}: we use \jolideco with the patch prior of \cite{Zoran2011} and the mean subtracted patch norm \dvd{is this the same as ``the patch normalisation described by Equation~\ref{eq:patch-norm}''?
-Best to use the same language for clarity.}.
-This is for comparison to the original \dvd{be more specific} method and the method used in \cite{Bouman2016}.
-We use a maximum image norm with the maximum values defined by the ground truth.
-\dvd{Is this the convergence criterion?
-Do you describe what this means somewhere?}\footnote{This is not completely fair, as it requires knowledge of the brightest expected pixel in $\mathbf{x}$.
-In practice this could be estimated from the brightest pixel in the data and the shape of the PSF.}
+        \item[\bf M4.] \textbf{\jolideco (Patch, GLEAM v0.1)}: we used \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalisation described by Equation~\ref{eq:patch-norm}.
+We used the optimization strategy described in Section~\ref{sec:opt-strategy} with 2000 epochs.
+
+        \item[\bf M5.] \textbf{\jolideco (Patch, Zoran-Weiss)}: we used \jolideco with the patch prior provided by \cite{Zoran2011}.
+To be consistent with how the GMM was learned we only subtracted the mean of the patch and skipped the division by the mean we introduced in Equation~\ref{eq:patch-norm}.
+To make the prior applicable to astronomical images, we re-scaled the image to the range $0 > \mathbf{x}_i > 1$ by dividing them by the maximum value defined by the ground truth\footnote{This is not completely fair, as it requires knowledge of the brightest expected pixel in $\mathbf{x}$.
+In practice this could be estimated from the brightest pixel in the data and the shape of the PSF.}.
     \end{enumerate}
@@
     We ran the comparison on all combinations of methods, source scenarios, background levels, and instrument scenarios.
-Here we only discuss the subset of the results, that we consider the most relevant.
+Here we only discuss the subset of the results that we consider the most relevant.
 The complete set of results is available at \url{https://jolideco.github.io/jolideco-comparison}.
@@
     First we compare the performance of the five methods and their differing prior assumptions on the different source scenarios.
-Figure \ref{fig:comparison-scenarios} shows the results for the selected subset of scenarios, i.e., on A1, B3, C3 and D4.
-
-    On scenario A1 all methods provide acceptable to excellent results for the isolated point sources in the upper right of the image.
+Figure \ref{fig:comparison-scenarios} shows the results for a selected subset of scenarios, i.e., on A1, B3, C3 and D4.
+
+    ]
+    \begin{table}
+    \centering
+        \begin{tabular}{ c|c|c|c|c } 
+            \input{output/metrics-table.tex}
+        \end{tabular}
+        \label{tab:metrics}
+        \script{metrics-table.py}
+        \caption{Image metrics for the difference source scenarios and methods.}
+    \end{table}
+
+    For scenario A1 all methods provide acceptable to excellent results for the isolated point sources in the upper right of the image.
 This demonstrates all methods take into account the PSF and background models correctly.
-The early stopped uniform prior of M2 shows an extension for these cases, because the optimization process has not finished.
+The exception is method M2 (\jolideconospace, uniform prior, stopped early)
+    %shows an extension for these cases, 
+    because its optimization process has not finished.
 M3, which optimizes for 1000 iterations, clearly improves the result and shows almost perfect point sources corresponding to the size of approximately one pixel.
@@
 As expected, the uniform prior assumption lets the emission decompose into many point sources, neglecting the spatial correlations among them.
-Pylira shows slightly improved results with the gaps between the bright emission peeks being more filled, however, it still lacks a convincing result of reconstructing the source into a single object.
-The \jolideco method with the patch priors shows the best results both visually and as measured by the SSI.
+Pylira shows slightly improved results with the gaps between the bright emission peeks being more filled.
+However, Pylira lacks a convincing result of reconstructing the source into a single object.
+The \jolideco method with the patch priors shows the best results both visually and as measured by the SSI \dvd{define SSI}.
 With the GLEAM v0.1 patch prior the reconstruction is almost perfect, visually almost indistinguishable from the ground truth.
@@
 The best results are achieved by the patch priors, which reconstruct a plausible extended source with approximately uniform brightness.
-The jet like features are decomposed into a \enquote{thread} of point sources by the uniform prior and Pylira method.
+The jet like features are decomposed into a \enquote{trail} of point sources by the uniform prior and Pylira method.
 The patch prior achieves a much more plausible reconstruction with almost uniform brightness for the linear structures.
 We also note that the patch prior does not show a preferred direction or bias in reconstruction, that could be possibly encoded in the training data.
-\dvd{Do you want to say something about the point soures?}
 
     The last scenario D4 shows a similar result as the previous test: the uniform prior and Pylira decompose the spiral and ring like structure of the image into points.
-The patch priors reconstruct a visually much more plausible flux image.
-
-    In summary \jolideco shows excellent performance on a variety of morphological shapes.
-It converges to the reference solution for very high signal to noise images.
+The patch priors reconstruct a visually more plausible flux image, much closer to the ground truth.
+
+    In summary, \jolideco shows excellent performance on a variety of morphological shapes.
 We find the prior learned from the GLEAM data to be a very good compromise between the ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
@@
 The rows show the scenarios D1-D5 as described in Section~\ref{subsec:test-datasets}.
-The background levels correspond to \qty[mode = text]{0.001}{cts / pixel}, \qty[mode = text]{0.01}{cts / pixel} and \qty[mode = text]{0.1}{cts / pixel}.
+Each pair of columns corresponds to a  background level,  \qty[mode = text]{0.001}{cts / pixel}, \qty[mode = text]{0.01}{cts / pixel} and \qty[mode = text]{0.1}{cts / pixel}.
 The complete results for the simulations and additional information are available at \url{https://jolideco.github.io/jolideco-comparison}.
@@
 Indeed with very high signal strength there is no dependency of the result on the background level, particularly in Scenario~D5.
-On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
+\dvd{The point sources seem very weak in D5.
+Is this a plotting issue?} On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
 
@@
     %
-    Finally we compare \jolideco results  for the different instrument scenarios.
+    Finally we compare \jolideco results  for the two instrument scenarios.
 Figure~\ref{fig:comparison-instruments} shows the data as well as flux images reconstructed using \jolideco and the GLEAM v0.1 patch prior.
@@
 The ring structure is sharpened considerably in all cases as well.
-The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but still appear with improved signal-to-noise ratio.
-This is an inherent limitation of the method.
-\dvd{Limitation of the method or of the data?}
+The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but appear with a higher signal-to-noise ratio \dvd{can you reference the scenario you are referring to?}.
+This a similar situation as in the A1 point source scenario, when sources are to close by.
 
@@
 The addition of the lower resolution \enquote{XMM} data does not negatively affect the quality of the overall reconstruction.
-When comparing the D5 scenario we see that the \enquote{Chandra} reconstruction shows a very good reconstruction of the spiral structure but still shows speckles in the surrounding ring.
-The latter suggests that the prior is not strong enough to maintain the pixel to pixel correlations in the case of high signal strength.
-The strength of the prior could be increased with the $\beta$ parameter, but for this study we did not tweak individual parameters, but instead used the default configuration.
+When comparing Scenario~D5 we see that the \enquote{Chandra} reconstruction shows a very good reconstruction of the spiral structure but shows speckles in the surrounding ring.
+The latter suggests that the GMM prior is not strong enough to maintain the pixel to pixel correlations in the case of high signal strength.
+The strength of the prior could be increased with the $\beta$ parameter, but for this study we use the default settings and do not tweak individual parameters.
 The speckly behaviour is not observed in the \enquote{XMM} case, where the reconstruction of the ring is smoother.
@@
     \subsubsection{Image Example}
-    First we apply \jolideco to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data.
+    We apply \jolideco to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data.
 In total, we chose 25 observations taken with  the ACIS-S instrument and no grating.
 We chose newer data, taken after 2006, to limit the effect of pile up.
-
-    We reduced the data using \texttt{ciao} v4.15 and a custom \texttt{snakemake} workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
-For the counts image we selected an energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandra.
-This corresponds to an absolute  pixel size of $\approx$~\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of Chandra's PSF.
-\chandra's instrument response varies with the observation offset and energy \citep{ChandraPOG2022}, so we simulated the PSF for each observation independently using the \texttt{marx} tool \citep{Davis2012} and the \texttt{simulate\_psf} script.
+    The list of selected observations including their exposure duration is shown in Table~\ref{tab:chandra_obs} of Appendix~\ref{sec:chandra-table}.
+
+    We reduced the data using Ciao v4.15 and a custom Snakemake workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
+For the counts image we selected an energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandranospace.
+This corresponds to an absolute  pixel size of $\approx$~\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of \chandranospace's PSF.
+\chandranospace's instrument response varies with the observation offset and energy \citep{ChandraPOG2022}, so we simulated the PSF for each observation independently using the \texttt{marx} tool \citep{Davis2012} and the \texttt{simulate\_psf} script.
 As a reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
@@
 
-    We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the normalization to vary later in the reconstruction process.
-We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation.
-As reference we chose the %
-    obsID 1308.
+    We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the normalization to vary in the reconstruction process.
+We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation, namely obsID 8365.
 For \jolideco we use the GMM prior learned on the JWST Cas A image.
-As there are many counts in the image we additionally use an oversampling factor of 2.
-We allow the background level and position calibration to vary among the observations.
-As a reference for the positional shift we also use obsID 1308.
+As there are many counts in the image we additionally use an oversampling factor of 2, meaning the image $\mathbf{x}$ is computed on a finer grid and downsampled after convolution with the PSF to the same grid as the counts data.
+The patch prior is also evaluated on the finer grid.
+
+    We allow the background level and position calibration (cf., Equation~\ref{eq:model-npred-calibration}) to vary among the observations.
+As a reference for the positional shift we also use obsID 8365.
 Figure~\ref{fig:example-chandra} shows the final result.
@@
 
-    \textbf{Zoom A} of Figure~\ref{fig:example-chandra} details an example for a filament structure.
+    \textbf{Zoom A} of Figure~\ref{fig:example-chandra} details an example of a filament structure.
 \jolideco maintains the extended structure along the filament, while sharpening in the perpendicular direction.
-Looking at the upper right corner one can also see that weak background emission is suppressed, also improving the contrast of the image.
+Looking at the upper right corner one can also see that weak background emission is suppressed, improving the contrast of the image.
 
     \textbf{Zoom B} shows the region around the central compact object of the SNR.
-While the emission is barely visible in the counts image it is clearly evident out above the background in the \jolideco reconstruction.
+While the emission is barely visible in the counts image it is clearly evident above the background in the \jolideco reconstruction.
 The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
 We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.
-We estimate the position of point source by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
+We estimate the position of the point source by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}, which
+
+    \dvd{Table 6 of the Long paper cite Vogt et al.
+(2018) for the location.
+Can we say just a bit about how they estimated the location?
+Were we able to find a point source with a general purpose algorithm (\jolideconospace) that they only found when looking specifically for the point source?
+Our general non-parametric method reproduced their science based model?}
 
     \textbf{Zoom C} shows a circular filament structure of the SNR.
-In the counts data the structure is barely visible, while the \jolideco reconstruction shows a distinct circular structure with a bright emission spot.
+In the counts data the structure is barely visible, while the \jolideco reconstruction shows a distinct circular structure with a locus of bright emission.
 This demonstrates the ability of \jolideco to reconstruct sub PSF scale structures with astrophysical relevance.
@@
 Both profiles are normalized such that they integrate to unity and are aligned such that the position of their peak coincides.
-                %\vlk{it is not being actively avoided -- the knot shows up after deconvolution.
-But if referee asks, can say it also avoids pileup issues} \vlk{I notice that you avoid the bright knot to SW.
-Any particular reason why?
-You could legitimately exclude it to avoid pileup effects, but depends on the actual observed count rates.}
+                \dvd{I must not understand what you are doing here.
+Why is the \jolideco result so smooth?
+Isn't this based on the bootstrap?
+There should be MC error.
+Also what is the $3\sigma$ error band?
+The histogram of the bootstrap resampled values represents the uncertainty.}
             }
@@
     To quantify the improvement in angular resolution of the reconstructed image over the data we compute a flux profile on the \jolideco reconstruction of E0102.
-We chose a region perpendicular to the filament shown in Zoom~A of Figure~\ref{fig:example-chandra}.
+We chose a region perpendicular to the filament shown in Zoom~A of Figure~\ref{fig:example-chandra} of the size $128\times128$ pixels.
 We compute errors via the bootstrap, with resampled data obtained by sampling the event lists with replacement for each individual observation.
 For each resampled data set we run \jolideco and compute a flux profile on the reconstructed image.
+In total we sample 100 different realizations.
+Where each reconstruction runs for about 10 min.
+on a standard M1 CPU.
 In this way we obtain a distribution of profiles, which we use to compute an error band.
@@
 
-    We compute the full-width at half-max (FWHM) $\omega$ of each of the profiles, by fitting a Gaussian shape with a linear gradient as a baseline for both the original counts and the \jolideconospace-deconvolved intensities.
+    We compute the full-width at half-max (FWHM), $\omega$, of the profiles for each bootstrapped data set, by fitting a Gaussian shape with a linear gradient as a baseline for both the original counts and the \jolideconospace-deconvolved intensities.
 In both cases we compute the mean of $\omega$.
 We find that the deconvolved profile is significantly narrower.
-For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.
+For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations of $\ometa$ over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.
 
@@
     \subsection{\fermi Event Types}
+    \label{sec:fermi-lat-example}
      As a second application example, we apply \jolideco  to data from the Fermi Large Area Telescope (LAT) \citep{Atwood2009}.
@@
 To preserve as much information as possible on the angular resolution of the instrument, we split the data into the four event types \enquote{PSF0}, \enquote{PSF1}, \enquote{PSF2} and \enquote{PSF3}, as defined by the \fermi \enquote{Pass8} data release\footnote{\url{https://fermi.gsfc.nasa.gov/ssc/data/analysis/documentation/Pass8_usage.html}}.
+Where PSF0 represents the subset of data with the worst and PSF3 the best angular resolution.
+Instead of different observations, the joint likelihood is computed accross those different event types.
+
      We chose a pixel size of \qty[mode = text]{0.02}{$\deg$}, which corresponds to approximately 1/5 of the size of the PSF in the best event class.
-For the first part of the data reduction we use the standard \texttt{fermitools v2.2.0} \citep{Fermitools2019}.
-
-    The \texttt{fermitools} produce an energy dependent counts, exposure and PSF cube.
-To further reduce the data to images we use the \textit{Gammapy} package v1.0 \citep{GammapyZenodov1.0.1, Gammapy2023}.
+For the first part of the data reduction we use the standard \enquote{Fermitools} v2.2.0 \citep{Fermitools2019}.
+
+    The Fermitools produce energy dependent counts, exposure and PSF cubes.
+To further reduce the data to images we use the Gammapy package v1.0 \citep{GammapyZenodov1.0.1, Gammapy2023}.
 To compute an image of the expected background emission we rely on the latest Galactic diffuse emission model \texttt{gll\_iem\_v07.fits} and also include nearby sources from the 3FHL catalog \citep{Ajello2017}.
-We first fit the model components to the data using \textit{Gammapy}, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on Vela Junior.
+We first fit the norm and spectral indices of all the 3FHL sources and the background model to the data using Gammapy, excluding a circular region of radius \qty[mode = text]{1.02}{$\deg$} centered on Vela Junior.
 Finally we reduce this model to an image by summing over the energy dimension.
@@
     We chose the GMM patch prior learned from \chandra SNRs described in the Section~\ref{sssec:chandra-snrs}.
-Because of the limited statistics we do not oversampling but keep the pixel size of the counts image.
+Because of the limited statistics we do not use oversampling but keep the pixel size of the counts image.
 Figure~\ref{fig:example-fermi-lat} shows the data,  the \jolideco results, and corresponding residuals.
@@
 \jolideco clearly improves the noise level as well as angular resolution compared to the data.
-The calibration parameters of the predicted counts converged to different norms for the background model and positional shifts of order of $<1$ pixel for the different event classes.
+The calibration parameters of the predicted counts converged to different norms for the background model and positional shifts of order of $<1$ pixel for the different event types.
 In this way \jolideco corrects for systematic errors in the reconstruction of the position.
-One can see that the reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and/or associated with systematic errors.
+The reconstruction includes background emission around Vela Junior, indicating that the Galactic diffuse background model is either underestimated in brightness and/or associated with systematic errors.
 The background estimate could be improved by choosing a larger region of interest.
@@
         \label{eq:approx-sigma}
-        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
-    \end{equation}
-
-    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma_{\mathrm{smooth}}=5$ pixels.
-The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.
+        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}.
+    \end{equation}
+where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma_{\mathrm{smooth}}=5$ pixels.
+\dvd{I don't understand this notation.
+Do you mean that you apply kernal density estimation to the data and their predicted values under the model, using a Gaussian kernel wtith $\simgam=5$?}  The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.
 The image shows no systematic effects and a spatially homogeneous distribution of the residual noise.
 The resulting distribution of residual significances per pixel is centered at $\mu=-0.001$ with a width of $\sigma=0.991$, indicating a close agreement with a standard normal distribution, as expected for a good model of the emission.
+In Figure~\ref{fig:example-fermi-lat-non-calibrated} we also show the residuals per PSF class with and without the correction defined by Equation~\ref{eq:model-npred-calibration}.
 More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
@@
 
-    \dvd{I am here.}
-
-    In order to facilitate reproducibility of our results we provide the source code for the paper and figures at \url{https://github.com/jolideco/jolideco-paper}.
-The paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021} and following the instructions in the \texttt{README.md} file in the same repository.
-All data is available for download from Zenodo or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided under the \jolideco GitHub organisation\footnote{\url{https://github.com/jolideco}}.
-For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow  available at\footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
-For the Chandra data reduction we used a custom \texttt{Snakemake} workflow available at\footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
+    In order to facilitate reproducibility, we provide the source code for the numerical results
+    and figures presented in this article at \url{https://github.com/jolideco/jolideco-paper}.
+The results in this paper can be reproduced using using the tool \texttt{Showyourwork} \citep{Luger2021} and following the instructions in the \texttt{README.md} file in the same repository.
+All data are available for download from Zenodo or can be reproduced using the custom  \texttt{Snakemake} workflows and repositories provided on the \jolideco GitHub page\footnote{\url{https://github.com/jolideco}}.
+For the Fermi-LAT data reduction we used a custom \texttt{Snakemake} workflow, also  available on GitHub\footnote{\url{https://github.com/adonath/snakemake-workflow-fermi-lat}}.
+For the Chandra data reduction we used a custom \texttt{Snakemake} workflow that is also available on GitHub\footnote{\url{https://github.com/adonath/snakemake-workflow-chandra}}.
 
@@
     In this article we presented a new method for deconvolution and denoising of images contaminated by Poisson noise.
-Using multiple observations of the same sky region the methods reconstructs a single flux image using the approximate MAP estimate of the joint likelihood under a patch based image prior.
-We showed that the methods leads to improved results compared to existing methods in a variety of morphological, signal to noise and instrument scenarios.
-Especially it leads to much improved results for extended source with a size similar to the PSF.
-In this case it allows to reliably recover features, that are well beyond the angular resolution of the instrument.
-We also showed that the approach of joining multiple observations leads to improved reconstruction results.
-Including data with lower angular resolution in the \jolideco reconstruction, improved maintaining the correlation structure of pixels across larger distances, while not affecting the overall sharpness of the result negatively.
+Using multiple observations of the same sky region the methods reconstructs a single flux image using the a MAP estimate that the joint posterior distribution under a patch-based image prior.
+We show that the method leads to improved results compared to existing methods in a variety of morphological, signal to noise, and instrument scenarios.
+Improvement is especially pronounced for extended sources of a size similar to the PSF.
+In this case, \jolideco can reliably recover features that are well beyond the angular resolution of the instrument.
+We also show that the approach of jointly analyzing multiple observations leads to improved reconstruction results.
+Including data with lower angular resolution in the \jolideco reconstruction improves the fitted correlation structure among pixels across larger distances, while not negatively affecting the overall sharpness of the reconstruction.
 
@@
 
-    We consider the \jolideco method as a first step into the territory of ML inspired methods for reconstruction of astronomical image data dominated by Poisson noise.
-While we achieved already superior results to any other existing method, the \jolideco methods shows large potential for future extension and improvements.
+    We believe \jolideco is the first step of a larger project building ML-inspired methods for the reconstruction of astronomical images that are dominated by Poisson noise.
+While \jolideco has already achieved results that are superior to any other existing method, it still has significant potential for future extension and improvements.
 
     The first category of future improvements is related to the prior handling.
-It is possibly to rely on more general mixture models such as a Student-T or a generalised Gaussian mixture model to model the distribution of patches.
-As shown by \cite{VanDenOord2014} those more flexible functional shapes can account for tails in the patch distributions and lead to improved results on natural images.
-
-    To increase the size of the correlation window of the patch prior, \cite{Papyan2015} proposed to evaluate and combine the prior on patches extracted at multiple scales of the image.
-This is a promising approach to further improve the reconstruction quality for extended sources with low signal to noise ratio.
-
-    To further improve the general expressiveness of the prior \cite{Altekrueger2022} used normalising flows (NF) to model the distribution of patches in the context of computer tomography image reconstruction.
-Just like a GMM the NF allows to evaluate its likelihood function and therefor construct an explicit, approximate \aposteriori probability for optimization.
-    Another promising approach to handle prior information for images has been introduced by \citep{Ulyanov2017} with the so called \enquote{Deep Image Prior}.
-They showed that a prior structure for an image can be built into a deep neural network, where the architecture of the network encodes the prior information on the correlation structure between neighbouring pixels.
-The authors showed, that the deep image prior successfully imposes self similarity on the structures in the image.
-As structures in astronomical images often show sell-similarity this is an interesting approach, that could even be combined with the patch prior.
-
-    A second category of improvement is generalizing \jolideco to the energy domain to allow for hyperspectral image reconstruction.
-For instruments such as \fermi the instrument response varies strongly with energy, while it also has limited energy resolution.
-This introduces correlations between images in neighbouring energy bands.
-Including the energy domain into the reconstruction will allow for handling these correlations and also open up the use-case of merging \xray data in the spectral domain.
-Allowing for both  and improved angular as well as energy resolution.
-
-    \jolideco already allows for handling an independent background component in the model.
-However we plan to extend the method to handle multiple source components at the same time, just separate by their prior definition.
-As shown by \cite{Selig2015} and \citep{Pumpe2018} this allows in principle to separate extended from for example point like source components.
-
-    A last category of improvement is getting error estimates for the reconstruction.
-For this study we relied on bootstrapping.
-However because we have a full estimate of the \aposteriori likelihood, we can build an approximation of the covariance matrix for example by using a block-wise representation.
-Alternatively we can also change to sampling from the \aposteriori distribution.
-
-    Finally we would like to invite the community of x-ray and \gammaray astronomers to use the \jolideco method to combine data for new scientific discoveries, beyond the current angular resolution of existing instruments.
+For example, more general mixture models such as the Student-t or a generalised Gaussian mixture model can be used to model the distribution of patches.
+\citet{VanDenOord2014} shows that these more flexible models can account for the tails of the patch distribution and lead to improved results on natural images.
+We expect these improvements to transfer to astronomical images.
+
+    To allow the patch-based prior distribution to capture correlations at larger scales,
+    \cite{Papyan2015} proposed to combine patches extracted at multiple scales of the image when training the GMM.
+This is a promising approach to further improve the reconstruction quality for extended sources with low signal to noise ratios.
+
+    Working in the context of computer tomographic image reconstruction, \cite{Altekrueger2022} used normalising flows (NF) in their formulation of the patch prior in order to further improve the general expressiveness of the prior.
+As with a GMM, we can evaluate the NF-based prior distribution and thus construct an explicit posterior distribution for optimization and computation of the MAP estimate.
+\citet{Ulyanov2017} introduced another promising prior distribution, known as the \enquote{Deep Image Prior} and showed that prior structure for an image can be built into a deep neural network as an \enquote{inductive bias}, where the architecture of the network encodes the prior information on the correlation structure among neighbouring pixels.
+The authors showed, that the deep image prior successfully imposes self similarity on structures in the image.
+As structures in astronomical images often show sell-similarity this is an interesting approach, that in principle could be combined with the patch prior.
+
+    A second category of improvement to \jolideco is generalizing it to jointly model the energy and spatial domains, thus enabling hyperspectral image reconstruction.
+Instruments such as \fermi combine instrument responses that vary strongly with energy along with a limited overall energy resolution.
+This configuration introduces correlations between images in neighbouring energy bands.
+Accounting for energy data in the reconstruction would allow us to handle these correlations and also open up the possibility of merging multiple \xray datasets in the joint spectral/spatial domain,  thus improving both  angular and energy resolution.
+
+    \jolideco can already handle an independent background component.
+However we plan to extend \jolideco to enable it to handle multiple source components at the same time.
+This allows us in principle, as shown by \cite{Selig2015} and \citet{Pumpe2018} to separate extended sources from point-like sources, based on different prior assumptions on the spatial correlation and distribution of pixels for each model component.
+
+    A last category of improvement to \jolideco is computing principled error estimates for the reconstruction.
+In this paper, we use bootstrap methods.
+Since we can compute the full posterior distribution, however, we could build an approximation to the covariance matrix of the MAP estimate, for example, by using a low-rank or sparse representation.
+    Alternatively we can use MCMC to obtain a sampling from the full posterior distribution, enabling us to explore the distribution and quantify  uncertainty both in the parameters and functions of the parameters constructed to represent structures in the image.
+
+    Finally we invite the community of X-ray and \gammaray astronomers to use  \jolideco to combine datasets and make new scientific discoveries, beyond what is possible with the angular resolution of existing instruments.
 We also welcome contributions and feedback to the public \jolideco code and validation repositories.
@@
     with counts
-    $$\{1, \frac{1}{3}, \frac{1}{3^2}, \frac{1}{3^3} \} \times$$
+    $$\left\{1, \frac{1}{3}, \frac{1}{3^2}, \frac{1}{3^3} \right\} \times$$
     those in the diffuse sources respectively.
@@
 The case with the surface brightness of 1000~counts~pix$^{-1}$ tests the asymptotic limit of the high counts case.
-
-    \subsection{Computational Performance}
-    We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations as well as large images.
-
-    \begin{itemize}
-        \item Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
-        \item We tried the binary search tree as proposed in \cite{Parameswaran2018},
-        but without success, most likely because the native \texttt{Pytorch} support
-        for parallelization speeds up the standard GMM quite a bit...
-        \item GPU support via Pytorch
-    \end{itemize}
+\vlk{ALSO MAKE A NOTE OF POINT SOURCE INTENSITY CONTRAST CF.
+SHARP PSFs}
+
+    % \subsection{Computational Performance}
+    % We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations as well as large images.
+
+    % \begin{itemize}
+    %     \item Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
+    %     \item We tried the binary search tree as proposed in \cite{Parameswaran2018},
+    %     but without success, most likely because the native \texttt{Pytorch} support
+    %     for parallelization speeds up the standard GMM quite a bit...
+    %     \item GPU support via Pytorch
+    % \end{itemize}
 
     \section{Chandra Observation Table}
-
+    \label{sec:chandra-table}
+    ]
     \begin{table}
@@
 
-    \section{Fermi-LAT Example Without Calibration}
+    \section{Fermi-LAT Example Residuals With and Without Calibration}
      \begin{figure*}
@@
             \caption{
-                Illustration of the \jolideco result for the \fermi data of the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}.
-The left image shows the counts above \qty[mode = text]{10}{GeV}.
-The different event classes are stacked into a single image with bin size $0.02$~degrees.
-The image in the center shows the flux reconstructed by the \jolideco method.
-The image on the right shows the standardized residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels $\approx 0.1$~degrees, similar to the size of the PSF.
+                Illustration of the residuals of the \fermi analysis example from Section~\ref{sec:fermi-lat-example}.
+All images show the standardized residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels $\approx 0.1$~degrees, similar to the size of the PSF.
+The upper row shows the result without calibration, the lower row shoes the result with the calibration applied, according to Equation~\ref{eq:model-npred-calibration}.
+The columns represent the four different PSF event classes of \fermi.
 More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.

### 2024-02-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \centering
-        \begin{tabular}{ c|c|c|c|c } 
+        \begin{tabular}{ c|c|c|c|c|c } 
             \input{output/metrics-table.tex}
@@
 We find that the deconvolved profile is significantly narrower.
-For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations of $\ometa$ over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.
+For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations of $\omega$ over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.
 

### 2024-02-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \dvd{I don't understand this notation.
-Do you mean that you apply kernal density estimation to the data and their predicted values under the model, using a Gaussian kernel wtith $\simgam=5$?}  The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.
+Do you mean that you apply kernal density estimation to the data and their predicted values under the model, using a Gaussian kernel with $\sigma=5$?}  The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.
 The image shows no systematic effects and a spatially homogeneous distribution of the residual noise.

### 2024-02-15 src/scripts/metrics-table.py

@@ -65,7 +65,7 @@ table = table[selection]
 
 
 table_metrics = Table(
-    names=["Scenario"] + list(method_titles.keys()),
+    names=["Scenario"] + list(method_titles.values()),
     dtype=["S2"] + ["S10"] * len(method_titles),
 )
 
@@ -73,10 +73,10 @@ for scenario in SCENARIOS:
     data = table[table["Scenario"] == scenario]
 
     values = {}
-    for method in method_titles:
+    for method, title in method_titles.items():
         selection = data["Method"] == method
         v = [float(data[selection][name]) for name in ["SSI", "NRMSE"]]
-        values[method] = f"{v[0]:.2f} / {v[1]:.2f}"
+        values[title] = f"{v[0]:.2f} / {v[1]:.2f}"
 
     values["Scenario"] = SCENARIOS[scenario]
     table_metrics.add_row(values)
@@ -89,7 +89,6 @@ content = content_io.getvalue()
 lines = content.split("\n")
 lines = lines[2:-3]
 lines.insert(1, "\hline")
-lines.insert(3, "\hline")
 lines.append("\hline")
 content = "\n".join(lines)
 

### 2024-02-15 src/scripts/comparison-signal-noise.py
Fix metrics table format

@@ -5,7 +5,6 @@ import paths
 from astropy.io import fits
 from astropy.visualization import simple_norm
 from matplotlib import pyplot as plt
-from matplotlib.gridspec import GridSpec
 
 scenario_titles = {
     "D1": {

### 2024-02-15 src/scripts/metrics-table.py

@@ -14,11 +14,11 @@ SCENARIOS = {"point1": "A1", "aster3": "B3", "disk3": "C3", "spiral4": "D4"}
 
 method_titles = {
     # "gt": "Ground Truth",
-    "jolideco-uniform-prior=n=10": "Jolideco\n(Uni, n=10)",
-    "jolideco-uniform-prior=n=1000": "Jolideco\n(Unif., n=1000)",
-    "pylira": "Pylira",
-    "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
-    "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
+    "jolideco-uniform-prior=n=10": r"\thead{Jolideco\\(Uni, n=10)}",
+    "jolideco-uniform-prior=n=1000": r"\thead{Jolideco\\(Unif., n=1000)}",
+    "pylira": r"Pylira",
+    "jolideco-patch-prior-zoran-weiss": r"\thead{Jolideco\\(Zoran-Weiss)}",
+    "jolideco-patch-prior-gleam-v0.1": r"\thead{Jolideco\\(GLEAM v0.1)}",
 }
 
 
@@ -88,7 +88,7 @@ table_metrics.write(content_io, format="latex", overwrite=True)
 content = content_io.getvalue()
 lines = content.split("\n")
 lines = lines[2:-3]
-lines.insert(1, "\hline")
+# lines.insert(1, "\hline")
 lines.append("\hline")
 content = "\n".join(lines)
 

### 2024-02-15 src/scripts/metrics-table.py
Fix metrics table format

@@ -88,7 +88,7 @@ table_metrics.write(content_io, format="latex", overwrite=True)
 content = content_io.getvalue()
 lines = content.split("\n")
 lines = lines[2:-3]
-# lines.insert(1, "\hline")
+lines.insert(1, "\hline")
 lines.append("\hline")
 content = "\n".join(lines)
 

### 2024-02-15 src/scripts/metrics-table.py
Fix metrics table format

@@ -14,11 +14,11 @@ SCENARIOS = {"point1": "A1", "aster3": "B3", "disk3": "C3", "spiral4": "D4"}
 
 method_titles = {
     # "gt": "Ground Truth",
-    "jolideco-uniform-prior=n=10": r"\thead{Jolideco\\(Uni, n=10)}",
-    "jolideco-uniform-prior=n=1000": r"\thead{Jolideco\\(Unif., n=1000)}",
+    "jolideco-uniform-prior=n=10": r"\thead[c]{Jolideco\\(Uni, n=10)}",
+    "jolideco-uniform-prior=n=1000": r"\thead[c]{Jolideco\\(Unif., n=1000)}",
     "pylira": r"Pylira",
-    "jolideco-patch-prior-zoran-weiss": r"\thead{Jolideco\\(Zoran-Weiss)}",
-    "jolideco-patch-prior-gleam-v0.1": r"\thead{Jolideco\\(GLEAM v0.1)}",
+    "jolideco-patch-prior-zoran-weiss": r"\thead[c]{Jolideco\\(Zoran-Weiss)}",
+    "jolideco-patch-prior-gleam-v0.1": r"\thead[c]{Jolideco\\(GLEAM v0.1)}",
 }
 
 

### 2024-02-15 src/scripts/comparison-scenarios.py
Fix uni abbrevation

@@ -34,7 +34,7 @@ method_titles = {
     "data": "Data",
     "gt": "Ground Truth",
     "jolideco-uniform-prior=n=10": "Jolideco\n(Uni, n=10)",
-    "jolideco-uniform-prior=n=1000": "Jolideco\n(Unif., n=1000)",
+    "jolideco-uniform-prior=n=1000": "Jolideco\n(Uni., n=1000)",
     "pylira": "Pylira",
     "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
     "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",

### 2024-02-15 src/scripts/metrics-table.py

@@ -15,7 +15,7 @@ SCENARIOS = {"point1": "A1", "aster3": "B3", "disk3": "C3", "spiral4": "D4"}
 method_titles = {
     # "gt": "Ground Truth",
     "jolideco-uniform-prior=n=10": r"\thead[c]{Jolideco\\(Uni, n=10)}",
-    "jolideco-uniform-prior=n=1000": r"\thead[c]{Jolideco\\(Unif., n=1000)}",
+    "jolideco-uniform-prior=n=1000": r"\thead[c]{Jolideco\\(Uni., n=1000)}",
     "pylira": r"Pylira",
     "jolideco-patch-prior-zoran-weiss": r"\thead[c]{Jolideco\\(Zoran-Weiss)}",
     "jolideco-patch-prior-gleam-v0.1": r"\thead[c]{Jolideco\\(GLEAM v0.1)}",

### 2024-02-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amssymb}
+\usepackage{makecell}
 \let\tablenum\relaxgit 
@@
 \DeclareMathOperator{\arcsinh}{arcsinh}
+
+%\renewcommand\theadalign{bc}
+
 \newcommand{\chandra}{\textit{Chandra}~}
@@
     ]
-    \begin{table}
+    \begin{table*}
     \centering
@@
         \script{metrics-table.py}
-        \caption{Image metrics for the difference source scenarios and methods.}
-    \end{table}
+        \caption{Image metrics for the difference source scenarios and methods shown in Figure~\ref{fig:comparison-scenarios}.
+The first number in a cell shows the structural similarity index (the closer to one the better ) and the second number shows the normalized root mean square (the lower the better).}
+    \end{table*}
 

### 2024-02-16 src/scripts/comparison-signal-noise.py
Adabt color scale for S/N comparison

@@ -13,19 +13,19 @@ scenario_titles = {
     },
     "D2": {
         "name": "spiral2",
-        "plot": {"max_cut": 30.0, "asinh_a": 0.02},
+        "plot": {"max_cut": 30.0, "asinh_a": 0.001},
     },
     "D3": {
         "name": "spiral3",
-        "plot": {"max_cut": 30.0, "asinh_a": 0.02},
+        "plot": {"max_cut": 30.0, "asinh_a": 0.001},
     },
     "D4": {
         "name": "spiral4",
-        "plot": {"max_cut": 100.0, "asinh_a": 0.02},
+        "plot": {"max_cut": 100.0, "asinh_a": 0.005},
     },
     "D5": {
         "name": "spiral5",
-        "plot": {"max_cut": 5000.0, "asinh_a": 0.02},
+        "plot": {"max_cut": 5000.0, "asinh_a": 0.00002},
     },
 }
 
@@ -125,7 +125,7 @@ for idx, scenario_title in enumerate(scenario_titles):
         else:
             data = read_flux(scenario, bg, instrument)
 
-        norm_kwargs["max_cut"] = np.percentile(data, 99.9)
+        # norm_kwargs["max_cut"] = np.percentile(data, 99.9)
         norm = simple_norm(data, stretch="asinh", min_cut=0, **norm_kwargs)
         ax = axes[idx, jdx]
         ax.imshow(data, cmap="viridis", origin="lower", norm=norm)

### 2024-02-16 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     First we compare the performance of the five methods and their differing prior assumptions on the different source scenarios.
-Figure \ref{fig:comparison-scenarios} shows the results for a selected subset of scenarios, i.e., on A1, B3, C3 and D4.
-
-    ]
-    \begin{table*}
-    \centering
-        \begin{tabular}{ c|c|c|c|c|c } 
-            \input{output/metrics-table.tex}
-        \end{tabular}
-        \label{tab:metrics}
-        \script{metrics-table.py}
-        \caption{Image metrics for the difference source scenarios and methods shown in Figure~\ref{fig:comparison-scenarios}.
-The first number in a cell shows the structural similarity index (the closer to one the better ) and the second number shows the normalized root mean square (the lower the better).}
-    \end{table*}
+Figure~\ref{fig:comparison-scenarios} shows the results for a selected subset of scenarios A1, B3, C3 and D4.
+For quantitative comparison we list the corresponding values of the structural similarity index (SSI, \cite{Wang2004}) and the normalized root mean-squared error (NRMSE) in Table~\ref{tab:metrics}.
 
@@
 However, Pylira lacks a convincing result of reconstructing the source into a single object.
-The \jolideco method with the patch priors shows the best results both visually and as measured by the SSI \dvd{define SSI}.
-With the GLEAM v0.1 patch prior the reconstruction is almost perfect, visually almost indistinguishable from the ground truth.
+The \jolideco method with the patch priors shows the best results both visually and as measured by the SSI With the GLEAM v0.1 patch prior the reconstruction is almost perfect, visually almost indistinguishable from the ground truth.
 The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a more visible extension in the surrounding point sources.
-
+    %
+    \begin{table*}
+    \centering
+        \begin{tabular}{ c|c|c|c|c|c } 
+            \input{output/metrics-table.tex}
+        \end{tabular}
+        \label{tab:metrics}
+        \script{metrics-table.py}
+        \caption{Image metrics for the difference source scenarios and methods shown in Figure~\ref{fig:comparison-scenarios}.
+The first number in a cell shows the structural similarity index (SSI, the closer to unity, the better) and the second number shows the normalized root mean square (NRMSE, the lower the better).}
+    \end{table*}
+    %
     The weak extended source with four embedded brighter point sources of Scenario C3 is challenging for all the methods.

### 2024-02-21 src/scripts/gmm-eigen-images.py
Adapt eigen image figure

@@ -6,7 +6,10 @@ import paths
 from jolideco.priors import GaussianMixtureModel
 from scipy import linalg
 
-figsize = config.FigureSizeAA(aspect_ratio=1.618)
+COMPONENT_IDX = [105, 77, 17]
+
+
+figsize = config.FigureSizeAA(aspect_ratio=2.4)
 
 fig = plt.figure(figsize=figsize.inch)
 
@@ -14,31 +17,59 @@ gmm = GaussianMixtureModel.from_registry("jwst-cas-a-v0.1")
 
 
 gridspec_kw = {
-    "left": 0.01,
-    "right": 0.99,
+    "left": 0.23,
+    "right": 0.9,
     "bottom": 0.005,
-    "top": 0.95,
+    "top": 0.8,
 }
 
 fig, axes = plt.subplots(
-    nrows=4, ncols=8, figsize=figsize.inch, gridspec_kw=gridspec_kw
+    nrows=3, ncols=6, figsize=figsize.inch, gridspec_kw=gridspec_kw
 )
 
 
 component = 10
-covariance = gmm.covariances_numpy[component]
-w, v = linalg.eigh(covariance)
 
-idx_sort = np.argsort(w)
-eigen_images = gmm.eigen_images  # v[:, idx_sort]
 
-for idx, ax in enumerate(axes.flat):
-    ax.imshow(
-        eigen_images[idx].reshape((8, 8)),
-        origin="lower",
-        cmap="viridis",
+for row, gmm_idx in enumerate(COMPONENT_IDX):
+    covariance = gmm.covariances_numpy[gmm_idx]
+    w, v = linalg.eigh(covariance)
+    idx_sort = np.argsort(w)[::-1]
+    eigen_images = v[:, idx_sort].T
+
+    axes[row, 0].text(
+        x=-18,
+        y=3.5,
+        s=f"$k_{{GMM}}$={gmm_idx}",
+        color="black",
+        ha="left",
+        va="center",
     )
-    ax.set_axis_off()
-    ax.set_title(f"{idx}", size=8, pad=0.5)
+
+    axes[row, -1].text(
+        x=12,
+        y=3.5,
+        s="...",
+        color="black",
+        ha="right",
+        va="center",
+    )
+
+    for col in range(0, 6):
+        ax = axes[row, col]
+
+        if row == 0:
+            ax.set_title(
+                f"{col+1}",
+                color="black",
+            )
+
+        ax.imshow(
[…]

### 2024-02-21 src/scripts/patches.py

@@ -11,6 +11,7 @@ from astropy.utils.data import get_pkg_data_filename
 from astropy.visualization import simple_norm
 from jolideco.priors import GaussianMixtureModel
 from matplotlib.patches import Rectangle
+from scipy import linalg
 
 log = logging.getLogger(__name__)
 
@@ -101,17 +102,28 @@ gmm = GaussianMixtureModel.from_registry("jwst-cas-a-v0.1")
 
 example_patch_torch = torch.from_numpy(example_patch).float()
 
-patches = example_patch_torch.reshape(1, 64)
+example_patch_torch_flat = example_patch_torch.reshape(1, 64)
 
 patch_mean = float(example_patch.mean())
 
-normed = gmm.meta.patch_norm(patches)
+normed = gmm.meta.patch_norm(example_patch_torch_flat)
 loglike = gmm.estimate_log_prob(normed)[0, :]
 idx_sort = torch.argsort(loglike, descending=True)
 
+eigenvals_max = 5
+
 for idx, idx_gmm in enumerate(idx_sort[:3]):
-    covar = gmm.covariances_numpy[idx_gmm]
-    cleaned = np.matmul(normed.numpy(), covar)
+    w, v = linalg.eigh(gmm.covariances_numpy[idx_gmm])
+
+    idx_sort = np.argsort(w)[::-1]
+    v = v[:, idx_sort]
+    basis = v[:, :eigenvals_max]
+
+    weights = np.matmul(basis.T, normed.numpy().T)
+    cleaned = np.matmul(basis, weights)
+
+    # covar = gmm.covariances_numpy[idx_gmm]
+    # cleaned = np.matmul(normed.numpy(), covar)
     patch = cleaned * patch_mean + patch_mean
 
     ax_patch = fig.add_axes([0.3 + idx * (width + 0.02), 0.08, width, width])

### 2024-02-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-    \title{%Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise}
-    Jolideco: A Simultaneous Deconvolution of Multiple Images in the Presence of Poisson Noise}
+    \title{Joint Deconvolution of Astronomical Images in the Presence of Poisson Noise}
+    %Jolideco: A Simultaneous Deconvolution of Multiple Images in the Presence of Poisson Noise}
 
@@
     \author[0000-0003-4568-7005]{Axel Donath}
+    \affil{Center for Astrophysics $|$ Harvard \& Smithsonian \\ Cambridge MA 02138 USA}
     \author[0000-0002-0905-7375]{Aneta Siemiginowska}
-    \author[0000-0002-3869-7996]{Vinay Kashyap} 
-    \author[0000-0002-0816-331X]{David van Dyk}
+    \affil{Center for Astrophysics $|$ Harvard \& Smithsonian \\ Cambridge MA 02138 USA}
+    \author[0000-0002-3869-7996]{Vinay L.\ Kashyap} 
+    \affil{Center for Astrophysics $|$ Harvard \& Smithsonian \\ Cambridge MA 02138 USA}
+    \author[0000-0002-0816-331X]{David A.\ van Dyk}
+    \affil{Department of Mathematics, Imperial College London \\ London SW7 2AZ UK}
     \author[0000-0003-4428-7835]{Douglas Burke}
+    \affil{Center for Astrophysics $|$ Harvard \& Smithsonian \\ Cambridge MA 02138 USA}
 
@@
 
-        We present a new method for JOint LIkelihood DECOnvolution (\jolideconospace) of a set of astronomical observations of the same sky region in the presence of Poisson noise. 
-        The observations may be obtained from different missions with  different resolution, and different point spread functions. 
+        We present a new method for joint likelihood deconvolution (\jolideconospace) of a set of astronomical observations of the same sky region in the presence of Poisson noise. 
+        The observations may be obtained from different instruments
+         with  different resolution, and different point spread functions. 
         \jolideco reconstructs a single flux image 
@@
 The patch prior is parameterised via a Gaussian Mixture model which we train on high-signal-to-noise astronomical images, including data from the  James Webb Telescope and the GLEAM radio survey.
-This prior favors correlation structures among the reconstructed pixel intensities that are characteristic of those observed in the astronomical images used to train the prior, but is not informative for the mean or scale of the reconstruction.
+This prior favors correlation structures among the reconstructed pixel intensities that are characteristic of those observed in the %astronomical
+        training images. 
+        % used to train the prior. 
+        It is, however, not informative for the mean or scale of the reconstruction.
 By applying the method to simulated data we show that the combination of multiple observations and the patch-based prior leads to much improved reconstruction quality in many different source scenarios and signal to noise regimes.
@@
             \caption{
-                Weighted sum of Eigenimages of the covariance matrices of the first $32$ components of the GMM learned from the JWST Cas A image.
+                Sum of Eigenimages weighted by their corresponding Eigenvalue of the covariance matrices of the first $32$ components of the GMM learned from the JWST Cas A image.
 The color scale varies between the images, so their contrast is different.
@@
     The ground truth and corresponding expected counts for all combinations of source and instrument scenarios are shown in Figure~\ref{fig:scenarios}.
-The details of the locations and brightness of each component is listed in Table~\ref{tab:scenarios} \dvd{I think this table is missing}.
-We assume a constant background with varying levels of $\lambda_{Bkg}= 0.001, 0.01$ and \qty[mode = text]{0.1}{counts/pixel}.
 
@@
 Figure~\ref{fig:comparison-scenarios} shows the results for a selected subset of scenarios A1, B3, C3 and D4.
-For quantitative comparison we list the corresponding values of the structural similarity index (SSI, \cite{Wang2004}) and the normalized root mean-squared error (NRMSE) in Table~\ref{tab:metrics}.
+For quantitative comparison we list the corresponding values of the structural similarity index (SSI, \cite{Wang2004}) and the normalized root mean-squared error (NRMSE)\footnote{We use the definition of $NRMSE = \frac{||\mathbf{x}_{GT} - \mathbf{x}||}{||\mathbf{x}_{GT}||}$, where $||$ is the Frobenius norm.} in Table~\ref{tab:metrics}.
 
@@
 Indeed with very high signal strength there is no dependency of the result on the background level, particularly in Scenario~D5.
-\dvd{The point sources seem very weak in D5.
-Is this a plotting issue?} On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
+On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
 
@@
 
-    Using only the data from the \enquote{XMM} scenario results in lower quality reconstructions, due to the lower angular resolution.
+    Using only the data from the \enquote{XMM} scenario results in lower quality reconstructions, due to the lower angular resolution of the data.
 However, we find that the spiral arm structure is reconstructed at all levels of signal strength, even when barely visible by eye.
 The ring structure is sharpened considerably in all cases as well.
-The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but appear with a higher signal-to-noise ratio \dvd{can you reference the scenario you are referring to?}.
-This a similar situation as in the A1 point source scenario, when sources are to close by.
+The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but remain blurred along the direction of their neighbours.
+This a similar situation as in the lower left of the image in the A1 point source scenario, when sources are to close by.
 
@@
 
-    \textbf{Zoom B} shows the region around the central compact object of the SNR.
+    \textbf{Zoom B} shows the region around the putative central compact object of the SNR (\cite{Vogt2018}, \cite{Hebbar2020}, but \cite{Long2020}).
 While the emission is barely visible in the counts image it is clearly evident above the background in the \jolideco reconstruction.
-The remaining visible extension in the point source is encoded in the JWST patch prior, which also shows a finite extension for point sources.
-We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.
-We estimate the position of the point source by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}, which
-
-    \dvd{Table 6 of the Long paper cite Vogt et al.
-(2018) for the location.
-Can we say just a bit about how they estimated the location?
-Were we able to find a point source with a general purpose algorithm (\jolideconospace) that they only found when looking specifically for the point source?
-Our general non-parametric method reproduced their science based model?}
+The reconstruction leaves a visible extension in the point-like source.
+However, at this level of analysis and signal to noise, both scenarios remain plausible: a real intrinsic extension of the feature, as well as a remaining reconstructed extension in a real point source because of low signal to noise\footnote{We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.}
+
+    To draw stronger scientific conclusions a dedicated analysis of the region, including a simulation of the false detection ratio of point sources would be needed.
+We estimate the position of the feature by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
+It shows the reconstruction of absolute feature positions with \jolideco is consistent with past literature.
 
@@
                 The left panel shows the deconvolved flux and counts profile of the region illustrated in the right panel.
-The associated $3\sigma$ error band is shown transparent in the background.
+The thick solid and dashed lines represent the mean of 100 bootstrapped observations.
+The counts profile is summed (stacked) across all observations, while the \jolideco profile is computed from a single joint reconstruction of all observations.
+The associated $3\sigma$ error band is shown transparent in the background, for both profiles.
 Both profiles are normalized such that they integrate to unity and are aligned such that the position of their peak coincides.
-                \dvd{I must not understand what you are doing here.
-Why is the \jolideco result so smooth?
-Isn't this based on the bootstrap?
-There should be MC error.
-Also what is the $3\sigma$ error band?
-The histogram of the bootstrap resampled values represents the uncertainty.}
             }
@@
 We compute errors via the bootstrap, with resampled data obtained by sampling the event lists with replacement for each individual observation.
-For each resampled data set we run \jolideco and compute a flux profile on the reconstructed image.
-In total we sample 100 different realizations.
-Where each reconstruction runs for about 10 min.
+For each resampled data set we run \jolideco and compute a binned flux profile on the reconstructed image.
+In total we sample 100 different realizations, where each reconstruction runs for about 10 min.
 on a standard M1 CPU.
-In this way we obtain a distribution of profiles, which we use to compute an error band.
-For comparison we also compute the profiles and associated errors directly on the stacked bootstrapped counts (without processing or fitting).
+In this way we obtain a set of profiles, which we use to compute the mean and error per bin of the profile.
+For comparison we also compute the profiles and associated errors directly on the bootstrapped counts summed across all observatoions (without processing or fitting).
 The result is shown in Figure~\ref{fig:chandra-e0102-zoom-a}.
@@
 Where PSF0 represents the subset of data with the worst and PSF3 the best angular resolution.
-Instead of different observations, the joint likelihood is computed accross those different event types.
+Instead of different observations, the joint likelihood is computed across those different event types.
 
@@
         \label{eq:approx-sigma}
-        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}.
-    \end{equation}
-where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel with $\sigma_{\mathrm{smooth}}=5$ pixels.
-\dvd{I don't understand this notation.
-Do you mean that you apply kernal density estimation to the data and their predicted values under the model, using a Gaussian kernel with $\sigma=5$?}  The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.
+        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{1}{\sqrt{\pi \sigma^2}}\frac{(N_{\mathrm{Data}} - N_{\mathrm{Pred}}) \circledast g_{\sigma}} {\sqrt{N_{\mathrm{Pred}}\circledast g_{\sigma}}}.
+    \end{equation}
+
+    where $g_{\sigma}$ is a Gaussian smoothing kernel of width $\sigma=5$ pixels.
+The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.
 The image shows no systematic effects and a spatially homogeneous distribution of the residual noise.
@@
 The case with the surface brightness of 1000~counts~pix$^{-1}$ tests the asymptotic limit of the high counts case.
-\vlk{ALSO MAKE A NOTE OF POINT SOURCE INTENSITY CONTRAST CF.
-SHARP PSFs}
+
+    \vlk{ALSO MAKE A NOTE OF POINT SOURCE INTENSITY CONTRAST CF. SHARP PSFs}
 

### 2024-02-21 src/scripts/patches.py
Cut off eigenvalues at 6

@@ -110,7 +110,7 @@ normed = gmm.meta.patch_norm(example_patch_torch_flat)
 loglike = gmm.estimate_log_prob(normed)[0, :]
 idx_sort = torch.argsort(loglike, descending=True)
 
-eigenvals_max = 5
+eigenvals_max = 6
 
 for idx, idx_gmm in enumerate(idx_sort[:3]):
     w, v = linalg.eigh(gmm.covariances_numpy[idx_gmm])

### 2024-02-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             \caption{
-                Sum of Eigenimages weighted by their corresponding Eigenvalue of the covariance matrices of the first $32$ components of the GMM learned from the JWST Cas A image.
+                Example Eigenimages of the covariance matrices of the GMM learned from the JWST Cas A image.
+The figure shows the first six Eigenvectors, reshaped as images, of the GMM components $\{105, 77, 17\}$ (same as Figure~\ref{fig:patches}), in descending order of the value of their corresponding Eigenvalue.
 The color scale varies between the images, so their contrast is different.

### 2024-02-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 The bottom row shows the red example patch $\mathbf{x}_n$ on the left.
-The three other patches show the quantity $\Sigma_{k} \mathbf{x}_n$, which is the result of the patch represented in the Eigenbasis of the covariance matrices of the 3 most likely GMM components $k = 105, 77, 17$.
+The three other patches show the example patch represented by a linear combination of the six largest Eigenvectors of the covariance matrices of the 3 most likely GMM components $k = 105, 77, 17$.
 This example uses the GMM learned from the JWST Cas A image.

### 2024-02-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         We present a new method for joint likelihood deconvolution (\jolideconospace) of a set of astronomical observations of the same sky region in the presence of Poisson noise. 
-        The observations may be obtained from different instruments
-         with  different resolution, and different point spread functions. 
-        \jolideco reconstructs a single flux image 
-        %from the set of observations 
-        %and given models for the point spread function (PSF) per observation, 
-        by optimizing the posterior distribution based on the joint Poisson likelihood of all observations under a patch-based image prior.
+        The observations may be obtained from different instruments with  different resolution, and different point spread functions.
+\jolideco reconstructs a single flux image by optimizing the posterior distribution based on the joint Poisson likelihood of all observations under a patch-based image prior.
 The patch prior is parameterised via a Gaussian Mixture model which we train on high-signal-to-noise astronomical images, including data from the  James Webb Telescope and the GLEAM radio survey.
@@
 Visually, the representation of the patch in the Eigenbasis of the covariance results in a denoised version of the patch.
-\dvd{Can we discuss this briefly?}
 

### 2024-03-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Define document class
-\documentclass[twocolumn]{aastex631}
-
-% Filler text
+\documentclass[twocolumn, lineno]{aastex631}
+
 \usepackage{blindtext}
@@
 \DeclareMathOperator{\arcsinh}{arcsinh}
-
-%\renewcommand\theadalign{bc}
 
@@
 \newcommand{\dvd}[1]{{\color{red} [DvD: #1]}}
-% Begin!
+
 \begin{document}
@@
     \title{Joint Deconvolution of Astronomical Images in the Presence of Poisson Noise}
-    %Jolideco: A Simultaneous Deconvolution of Multiple Images in the Presence of Poisson Noise}
 
@@
 
-% Abstract with filler text
     \begin{abstract}
@@
 The patch prior is parameterised via a Gaussian Mixture model which we train on high-signal-to-noise astronomical images, including data from the  James Webb Telescope and the GLEAM radio survey.
-This prior favors correlation structures among the reconstructed pixel intensities that are characteristic of those observed in the %astronomical
-        training images. 
-        % used to train the prior. 
+This prior favors correlation structures among the reconstructed pixel intensities that are characteristic of those observed in the training images.
 It is, however, not informative for the mean or scale of the reconstruction.
 By applying the method to simulated data we show that the combination of multiple observations and the patch-based prior leads to much improved reconstruction quality in many different source scenarios and signal to noise regimes.
-We demonstrate that \jolideco yields superior reconstruction quality relative to alternative standard methods such as the Richardson-Lucy method.
-We illustrate the results of \jolideco\ applied to example data from the \chandra observatory and the \ferminospace.
-By comparing the measured width of a counts based and the corresponding \jolideco flux profile we find the deconvolved width to be consistent with the theoretical expectation derived from the known width of the PSF.
+We demonstrate that with the patch prior \jolideco yields superior reconstruction quality relative to alternative standard methods such as the Richardson-Lucy method.
+We illustrate the results of \jolideco\ applied to example data from the \chandra X-ray Observatory and the \ferminospace\ Gamma-ray Space Telescope.
+By comparing the measured width of a counts based and the corresponding \jolideco flux profile of an X-ray filament in SNR {\it 1E 0102.2-7219} we find the deconvolved width of $0.58\pm 0.02$ arcsec to be consistent with the theoretical expectation derived from the known width of the PSF.
     \end{abstract}
-
-    % Main body with filler text
 
@@
 This includes images taken by \xray and \gammaray~telescopes but also medical images obtained with methods such as positron emission tomography or single-photon emission computed tomography.
-This low counts imaging process is illustrated in Figure~\ref{fig:model-illustration}.
+This low-count imaging process is illustrated in Figure~\ref{fig:model-illustration}.
 
@@
             \caption{
-                Illustration of the forward model of the low counts imaging process.
+                Illustration of the forward model of the low-count imaging process.
 The flux represents the true unknown flux distribution in the sky.
@@
 
-%\as{You may want to add a short para or just a sentance saying that X-ray and gamma-ray images are the Poisson type images containing low number of counts in each image pixel etc..
-- this is to link to the next subsection which is specific to Poisson noise?}
-% AD: this is mentioned already...
-
     \subsection{Related Work}
@@
 For example \cite{Zoran2011} build on very similar assumption of local correlation for natural images.
-However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian kernel with a given bandwidth determining the correlation scale,
-    %with a correlation size, 
-    they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
-For this they propose to split training images from representative data sets into small patches and learn a  Gaussian Mixture Model (GMM) %to model
-    for the distribution of extracted patches.
+However, instead of assuming a fixed local correlation structure, such as smoothness defined by a Gaussian kernel with a given bandwidth determining the correlation scale, they proposed to learn the local correlation structure on millions of patches extracted from a set of reference images.
+For this they propose to split training images from representative datasets into small patches and learn a  Gaussian Mixture Model (GMM) for the distribution of extracted patches.
 To use the GMM in reconstruction they introduce the concept of expected patch likelihood (EPLL).
@@
 \cite{Bouman2016} later adapted the patch prior successfully for the reconstruction of sub-millimeter radio data from the Event Horizon Telescope (EHT).
-
-    % \begin{figure*}
-    %     \script{rl_decomposition.py}
-    %     \begin{centering}
-    %         \includegraphics[width=\textwidth]{figures/richardson-lucy-decomposition.pdf}
-    %         \caption{
-    %             Decomposition of the RL algorithm for various number of iterations. \todo{Improve figure}
-    %         }
-    %         \label{fig:rl_decomposition}
-    %     \end{centering}
-    % \end{figure*}
 
@@
     \subsection{Poisson Joint Likelihood}
-    Our goal is to recover an image $\mathbf{x}$ from a set of multiple low counts observations.
+    Our goal is to recover an image $\mathbf{x}$ from a set of multiple low-count observations.
 Most generally we assume our total dataset consists of $J$ individual observations of the same region of the sky, which we jointly model.
@@
     The Maximum A Posteriori (MAP) estimate of $\mathbf{x}$ is the value that maximizes Equation~\ref{eq:bayes}.
-    Taking the logarithm of Equation~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Equation~\ref{eq:joint} and dropping the normalisation term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we obtain the following expression for the log-posterior distribution
+    Taking the logarithm of Equation~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Equation~\ref{eq:joint} and dropping the normalization term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we obtain the following expression for the log-posterior distribution
     $\mathcal{L}$:
@@
     %\newpage
-    \subsection{patch-based Image Prior}
+    \subsection{Patch-based Image Prior}
     \label{sec:patch-prior}
@@
     \begin{equation}
-        \mathbf{x}_n = \mathbf{P}_n \mathbf{x}
-    \end{equation}
-    %
-    Where $\mathbf{P}_n$ represents a neighbourhood matrix to extract the $n$-th patch from the image $\mathbf{x}$ and where $\mathbf{x}_n$ is the vector of length $N_p^2$ representing the \enquote{flattened} image patch.
-By obtaining a large number of patches we can model the distribution of pixels values within the patches using a Gaussian Mixture Model (GMM).
+        \mathbf{x}_n = \mathbf{P}_n \mathbf{x},
+    \end{equation}
+    %
+    where $\mathbf{P}_n$ represents a neighbourhood matrix to extract the $n$-th patch from the image $\mathbf{x}$ and where $\mathbf{x}_n$ is the vector of length $N_p^2$ representing the \enquote{flattened} image patch.
+By obtaining a large number of patches we can model the distribution of pixel intensities within the patches using a Gaussian Mixture Model (GMM).
 The GMM is a universal function approximator and thus can model arbitrary distributions.
 For now we assume that we have a pre-trained GMM which encodes the patch distribution of some reference image we have chosen.
-During the actual image reconstruction we aim to identify the most likely GMM component per patch, treating this as a discrete hyper-parameter
-    that is optimized along with the image $\mathbf{x}$.
+During the actual image reconstruction we aim to identify the most likely GMM component per patch, treating this as a discrete nuisance-parameter that is optimized along with the image $\mathbf{x}$.
 
@@
 
+    Where $\mathcal{N}$ is the Gaussian normal distribution.
 If we knew the relevant component, $k_n$, for patch $\mathbf{x}_n$ we could derive the conditional log-prior distribution directly from Equation~\ref{eq:gmm}:
@@
     As the number of components in the GMM is typically limited to $\mathcal{O}(10^2)$ we can optimize the conditional log-prior distribution by simply evaluating it for each of the GMM components and choose the one with the maximum value.
-Finally, to evaluate the (optimizied) log-prior of the full image we sum the maximum values of the individual patches:
+Finally, to evaluate the (optimized) log-prior of the full image we sum the maximum values of the individual patches:
     %
@@
     Apart from this, the process for choosing the most likely GMM prior component remains unmodified.
-However, we note that we neglected the prior dependence between neighbouring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixes and are thus clearly not \aprioir independent.}.
+However, we note that we neglected the prior dependence between neighbouring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixels and are thus clearly not \aprioir independent.}.
 As the choice of the GMM component per patch is discrete, a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
@@
 
-    % \begin{itemize}
-    %     \item the case of non-overlapping patches is rather simple
-    %     \item for overlapping patches we have to make a few more approximations
-    %     \item either we neglect the correlation between overlapping patches
-    %     \item or we have to optimize the array of $\mathbf{k}$ at the same time, instead of per patch optimization. However optimization on discrete 
-    %     values is not easily possible in Pytorch. However here is one idea:
-    %     group the GMM components by similarity and introduce a single continues
-    %     parameter $z$, which interpolates between similar components.
-    %     \item Another idea is to use Gumbel Softmax...
-    %     \item we also compute the mean of the likelihood for the overlapping parts
-    % \end{itemize}
-
-    % To use the learned GMM as prior for the reconstruction of another image, the image is split into overlapping patches.
-For each of the patches the log-likelihood for each of the GMM components is evaluated.
-The resulting grid of overlapping patches is illustrated in Figure~\ref{fig:patches}.
-
-    % with radio astronomy data.
-They have shown that the reconstructed image only weakly depends on the choice of the reference data on which the the patch prior is learned.
-They found equivalent results for GMMs learned on natural images and specifically simulated images of black hole ring structures.
-
-    % Using half quadratic splitting and the Wiener filter solution, which is not possible in our case. Instead we choose a direct optimization by relying on differentiable programming later.
-
-    \subsubsection{Image Dynamic Range and Patch Normalisation}
+    \subsubsection{Image Dynamic Range and Patch Normalization}
     \label{ssec:patch-norm}
     Astronomical images typically show a much higher dynamic range compared to natural images.
-    % This is mostly due to the existence of point sources, which rarely occur in natural images.
-Astronomical point sources typically relate to compact bright objects, such as unresolved active galactic nuclei at high distances, or binary objects and stars at Galactic distances.
-In addition the visible matter in the universe is sparse such that astronomical images typically show sparse bright emission on a dark background.
-    To normalise the patches \cite{Zoran2011} proposed to subtract the patch mean before learning the GMM.
+To normalize the patches \cite{Zoran2011} proposed to subtract the patch mean before learning the GMM.
 This leads to the GMM modeling the same morphological features at different levels of contrast as different components.
@@
 While this could be handled by introducing significantly more components to the GMM, it seems unfeasible in practice due to the limited availability of training data and computational resources.
-For this reason we instead propose a modified normalisation for the patches:
+For this reason we instead propose a modified normalization for the patches:
     %
@@
 Thus we simply assume a uniform prior distribution for the patch intensities.
-Algorithmically, we replace $\mathbf{x}_n$ with $\tilde{\mathbf{x}}_n$ when evaluating Equations~\ref{eq:gmm} \ref{eq:khat} and transform $\mathbf{P}_n\mathbf{x}$ via Equation~\ref{eq:patch-norm} when evaluating Equation~\ref{eq:prior-total}.
-
-    % The high dynamic range of astronomical images challenges any deconvolution method.
-To recover point sources accurately it is required to keep correlations with neighbouring pixels low, while for extended source the opposite is true.
-Ideally those contradicting requirements can be handled with a single flexible prior assumption, which adapts to the data, such as the patch-based GMM prior introduced in the previous section.
-
-    % With a given non-linearity:
-
-    % \begin{equation}
-    %     f(x) = \arcsinh{x / \alpha}
-    % \end{equation}
-
-    % \todo{The patch normalisation remains to be decided, but it would be advantageous to get rid of the hyper-parameter associated with the total image normalisation}.
-    % The GMM patch prior is learned from other images whose pixel intensities
-    % have no physical relationship of the intensities of the Poisson data we are
-    % dealing with. To overcome this the GMM is learned on normalized images,
-    % where the intensity values are constrained between 0 and 1.
-    % To evaluate the GMM patch prior on the 
-    % model image $\mathbf{x}$ the pixel values of $\mathbf{x}$  need to be mapped 
-    % in the same dynamic range between 0 and 1. Multiple common choices for such a
-    % mapping function are shown in Fig.~\ref{fig:image-norms}.
-
-    % In practice we are interested in the likelihood of a given structure in a patch and
-    % So we subtract the mean value of a given patch. This represents the assumption that
-    % the image structure is independent of the total flux contained in the patch.
-
-    % % \begin{figure}
-    % %     \script{image-norms.py}
-    % %     \begin{centering}
-    % %         \includegraphics[width=\linewidth]{figures/image-norms.pdf}
-    % %         \caption{
-    % %             Various image norms with different dynamic behaviour.
-    % %         }
-    % %         \label{fig:image-norms}
-    % %     \end{centering}
-    % % \end{figure}
-
-    % The choice of the image normalisation allows to adjust the contrast of the image
-    % and for example enhance low intensity structures, which also enhances the regularising
-    % effect of the patch prior.
-
-    % \todo{Which normalisation to choose, atan, asinh, log, inverse-cdf?}
-
-    % There are arguments for $\arcsinh(\mathbf{x})$, see for example \cite{Lupton2004}, which we use.
+Algorithmically, we replace $\mathbf{x}_n$ with $\tilde{\mathbf{x}}_n$ when evaluating Equations~\ref{eq:gmm} and \ref{eq:khat} and transform $\mathbf{P}_n\mathbf{x}$ via Equation~\ref{eq:patch-norm} when evaluating Equation~\ref{eq:prior-total}.
 
@@
 
-    % \subsection{Choice and Tuning of Hyperparameters}
-    % \subsubsection{Cross Validation}
-    % Cross validation (CV) is an established method for model selection in statistics and machine learning to prevent a model from overfitting to the training data.
-To perform CV the available data is slit into a \enquote{training} and \enquote{validation} dataset.
-While optimizing the log-likelihood value is monitored  The use of multiple dataset allows to use cross-validation to prevent overfitting.
-One of the standard techniques in machine learning...
-
-    % Cross validation is feasible once sufficient data is available, which is for example the 
-    % case for deep \chandra~observations.
-
-    % CV as stopping rule for RL was proposed by \cite{Reeves1995}...
-
-    % \subsubsection{Other Approaches}
-
-    % Self supervised Poisson loss? J-invariance has been shown to work, Grid Search? Calibration on similar data with ground truth?
-    % Ground truth based calibration: record prior vs data likelihood on simulated data...
-
     \subsection{Systematic Errors of Predicted Counts}
     Each observation $\mathbf{D}_j$ is subject to systematic errors.
-For example, the pointing accuracy of the telescope when repeatedly pointed to the same object or when using different types of telescopes for observation, the absolute position of an astronomical object may vary among the  observations.
+For example, the pointing accuracy of the telescope when repeatedly pointed to the same object or when using different types of telescopes for observation, the reconstructed position of an astronomical object may vary among the observations.
 The process of correcting for these inaccuracies is called \textit{astrometry} and is a standard procedure in for example \chandra data analysis.
@@
 
-    To account for both systematic effects we extend the model in Equation~\ref{eq:model} for the predicted counts, by a background normalisation factor $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$, which is specific for each observation.
+    To account for both systematic effects we extend the model in Equation~\ref{eq:model} for the predicted counts, by a background normalization factor $\alpha_j$ and a linear shift in position $\phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})$, which is specific for each observation.
 This yields the following modified model:
@@
     In practice one observation is used as a reference and its corresponding systematic shifts in position $\delta_{x,j}, \delta_{y,j}$ are frozen during optimization.
-An example of the effect of the positional shift and background normalisation can be seen in Figure~\ref{fig:example-fermi-lat-non-calibrated}.
+An example of the effect of the positional shift and background normalization can be seen in Figure~\ref{fig:example-fermi-lat-non-calibrated}.
 
@@
     We also experimented with computing the diagonal of the Hessian of the posterior distribution evaluated at the MAP estimate.
-However we found this numerically challenging because of random the cycle spinning.
+However we found this numerically challenging because of the random cycle spinning.
 
@@
     We implemented the \jolideco method as an independent Python package, based on PyTorch as the computational back-end.
-We defined a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as the choice of the patch normalisation, the choice of GMM, optimization methods, and serialisation formats for the reconstruction results as well as the corresponding diagnostic information, such as the trace of the posterior and prior likelihood values.
+We defined a modular, object oriented code structure, to allow parts of the algorithm to be flexible and interchangeable, such as the choice of the patch normalization, the choice of GMM, optimization methods, and serialisation formats for the reconstruction results as well as the corresponding diagnostic information, such as the trace of the posterior and prior likelihood values.
 This will simplify future improvement and extension of the package as well as the adoption of \jolideco by the astronomical community.
@@
 This means the prior distribution contains a large variety of structural shapes and has freedom to adapt to the data in the optimization process by choosing the most likely GMM component for each patch in the image.
-With radio data, \cite{Bouman2016} found their results to be mostly independent of the choice of data the GMM prior was learned on.
+With radio data, \cite{Bouman2016} found their results to be mostly independent of the choice of data used for learning the GMM prior.
 
@@
 In total we extracted $\approx 6 \times 10^5$ patches and trained a GMM with 128 components.
-We used the patch normalisation described in Section~\ref{ssec:patch-norm}.
+We used the patch normalization described in Section~\ref{ssec:patch-norm}.
 
@@
 Then we split the image into $\approx 2$ million $8\times 8$ patches and learned a GMM with 128 mixture components.
-Again we relied on the patch normalisation described in Section~\ref{ssec:patch-norm}.
-Figure~\ref{fig:gmm-eigen-images} shows the weighted sum of the \textit{Eigenimages} of the covariance matrices of the first 32 components of the GMM.
+Again we relied on the patch normalization described in Section~\ref{ssec:patch-norm}.
+Figure~\ref{fig:gmm-eigen-images} shows the principal Eigenimages of the covariance matrices of three example components of the GMM.
 The patches show a large variety in morphological shapes, including edges, gradients, bright compact spots and more combinations thereof.
-
-    % \subsubsection{NRAO Jets, Jets, Jets}
-    % \todo{Include the jet prior or not?}
-    % For the specific application of jet detection and analysis in extract galactic data we learned a GMM patch prior from radio jet images.
-It represents the prior knowledge of both the morphology and preferred direction of the jet.
-As reference data we chose
-    % a PR image released under the name \textit{Jets, jets jets}  by the NRAO collaboration containing ~150 example jets from their data\footnote{\url{https://public.nrao.edu/gallery/quicklook-samples/}}.
-
-    % We first split the compiled image into 150 individual examples.
-For each image we ran a blob detection algorithm and line fit to find the preferred direction of the jet.
-Using this information we aligned all images to the same horizontal reference direction of the jet split all images into patches of size 8x8 pixels.
-In total we extracted \todo{insert number} patches and used those to train a GMM with 32 components.
-The prior is useful in a scenario were the direction of the jet known from for example previous radio observations.
-
-    % Alternatively we used a \textit{data augmentation} approach to learn a GMM prior with a randomized direction of the jet. For this we rotated the jet image after alignment by 
-    % a random angle. Then again we split each image into patches of size 8x8 pixels. In total we created \todo{insert number} patches and learned a GMM with 64 components. The prior
-    % is adapted to the analysis scenario of jet detection, where no prior knowledge on the
-    % direction is available.
 
@@
         \item[1.] We start from a random image where each pixel was drawn from a normal distribution with the mean corresponding to the total mean of the flux in the image and a standard deviation of 10\% of the mean.
-We first estimate $\mathbf{x}$ by using a uniform prior and early stopping after a 50 iterations.
-This corresponds approximately to a reconstruction obtained with the RL algorithm.
+We first estimate $\mathbf{x}$ by using a uniform prior and early stopping after 50 iterations.
+This corresponds approximately to a reconstruction obtained with the standard RL algorithm.
         \item[2.] We freeze the image parameters and optimize the parameters associated with the systematic error described in Equation~\ref{eq:model-npred-calibration}.
-        \item[3.] Finally we optimize both the image $\mathbf{x}$ and the parameters associated with systematic error simultaneously until convergence.
+        \item[3.] Finally we simultaneously optimize
+        the image $\mathbf{x}$, the GMM component indicators for each patch, $k_n$ and the parameters associated with systematic error simultaneously until convergence.
 Convergence is verified visually by inspecting the time series of the log posterior distribution evaluated at the iterates or the models parameters.
@@
 We arranged the sources in different spatial patterns and with different spacings between them.
-We include point sources superposed on extended sources in four arrangements labelled A--D in the first row of Figure~\ref{fig:scenarios}.
-Each spatial arrangement is crossed with several signal-to-noise ratios (obtained with a constant background).
+We include combinations of point and extended sources, sometimes superposed, in four arrangements (labeled A--D in Figure~\ref{fig:scenarios}).
+Each arrangement is considered at several signal-to-noise ratios (obtained with a constant background and numbered in order of increasing signal).
 The resulting scenarios are denoted by concatenating the two labels, e.g., A3 or C1, see Appendix~\ref{sec:app:A} for details.
-The goal of the experiments is not to set up or devise a \enquote{perfect} deconvolution algorithm, but to help assess their relative strengths and limitations.
+The goal of the experiments is not to set up or devise a \enquote{perfect} deconvolution algorithm, but to help assess their relative strengths and limitations,
+    and assess the situations where they fail.
 
@@
 
-    % To evaluate the reconstruction performance of \jolideco and compare it against other methods we defined a set of test scenarios.
-They consist of simplified elementary morphological structures resembling those found in astronomical images.
-We have devised four distinct arrangements of combinations of point and extended sources of different shapes.
-The scenarios are:
-
-    % \begin{itemize}
-    %     \item[(A)] {\enquote{\bf Points}:} point sources arranged in a grid with different separations and brightness. 
-    %     \item[(B)] {\enquote{\bf Asterism}:} a set of four point sources arranged around an extended Gaussian source
-    %     \item[(C)] {\enquote{\bf Shield}:} disk shaped flat extended source with superposed point sources and linear jet-like features 4 different directions.
-    %     \item[(D)] \enquote{{\bf Spiral}:} extended thin double-spiral with a flat disk at the center and point sources adjacent to it. 
-    % \end{itemize}
-
-    % In addition we consider two different instrument scenarios:
-
-    % \begin{itemize}
-    %     \item {\enquote{\bf Chandra}:} an instrument with good angular resolution, but low effective area.
-We assume a Gaussian PSF of sizes $\sigma = 2$ pixels and a reference effective area of \qty[mode=text]{1}{A.U.}.
-    %     \item {\enquote{\bf XMM}:} an instrument with worse angular resolution, but higher effective area.
-We assume a Gaussian PSF of sizes $\sigma = 6$ pixels and an effective area of \qty[mode=text]{5}{A.U.}.
-    % \end{itemize}
-
-    The ground truth and corresponding expected counts for all combinations of source and instrument scenarios are shown in Figure~\ref{fig:scenarios}.
+    The ground truth and corresponding expected counts for several exemplar combinations of source and instrument scenarios are shown in Figure~\ref{fig:scenarios}.
 
@@
 
-        \item[\bf M4.] \textbf{\jolideco (Patch, GLEAM v0.1)}: we used \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalisation described by Equation~\ref{eq:patch-norm}.
+        \item[\bf M4.] \textbf{\jolideco (Patch, GLEAM v0.1)}: we used \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalization described by Equation~\ref{eq:patch-norm}.
 We used the optimization strategy described in Section~\ref{sec:opt-strategy} with 2000 epochs.
@@
 However, Pylira lacks a convincing result of reconstructing the source into a single object.
-The \jolideco method with the patch priors shows the best results both visually and as measured by the SSI With the GLEAM v0.1 patch prior the reconstruction is almost perfect, visually almost indistinguishable from the ground truth.
+The \jolideco method with the patch priors shows the best results both visually and as measured by SSI, see Table~\ref{tab:metrics}.
+With the GLEAM v0.1 patch prior the reconstruction is almost perfect, visually almost indistinguishable from the ground truth.
 The Zoran \& Weiss prior also shows good reconstruction of the extended sources, but less smooth and leaving a more visible extension in the surrounding point sources.
@@
         \script{metrics-table.py}
-        \caption{Image metrics for the difference source scenarios and methods shown in Figure~\ref{fig:comparison-scenarios}.
+        \caption{Image metrics for the different source scenarios and methods shown in Figure~\ref{fig:comparison-scenarios}.
 The first number in a cell shows the structural similarity index (SSI, the closer to unity, the better) and the second number shows the normalized root mean square (NRMSE, the lower the better).}
@@
 
-    In summary, \jolideco shows excellent performance on a variety of morphological shapes.
+    In summary, \jolideco with the patch priors shows excellent performance on a variety of morphological shapes.
 We find the prior learned from the GLEAM data to be a very good compromise between the ability to separate nearby point sources and the ability to reconstruct the spatial correlation of extended sources.
@@
 Indeed with very high signal strength there is no dependency of the result on the background level, particularly in Scenario~D5.
-On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-3).
+On the other hand, the method struggles to reconstruct a useful signal in the case of very high background (scenarios D1-D3).
 
@@
             \caption{
-               \jolideco result for \chandra observations of SNR \textit{1E~0102.2–7219}.
+               \jolideco result with the JWST patch prior for \chandra observations of SNR \textit{1E~0102.2–7219}.
 The bottom left image shows the summed counts from 25 observations.
@@
     \subsubsection{Image Example}
-    We apply \jolideco to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data.
+    We apply \jolideco to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and reconstruct a single long-exposure image using the patch prior learned from JWST data.
 In total, we chose 25 observations taken with  the ACIS-S instrument and no grating.
-We chose newer data, taken after 2006, to limit the effect of pile up.
+We chose the data taken after 2006 when the contamination layer results in lower pileup.
 The list of selected observations including their exposure duration is shown in Table~\ref{tab:chandra_obs} of Appendix~\ref{sec:chandra-table}.
 
-    We reduced the data using Ciao v4.15 and a custom Snakemake workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
-For the counts image we selected an energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandranospace.
+    We reduced the data using CIAO v4.15 \citep{Fruscione2006} and a custom Snakemake workflow (see also Section~\ref{sec:reproducibility} on reproducibility).
+For the counts image we selected an energy range from \qty[mode = text]{0.5}{keV} to  \qty[mode = text]{7}{keV} and a pixel size of $0.25$ of the native pixel size of \chandranospace ACIS detector.
 This corresponds to an absolute  pixel size of $\approx$~\qty[mode = text]{0.125}{$\arcsec$/pixel} or a sampling of $\approx2$ pixels for the $38\%$ containment radius of \chandranospace's PSF.
@@
 As a reference spectrum for the PSF simulation we assumed the model derived by \cite{Plucinsky2017}.
-We converted the spectral script from XSPEC to sherpa using the helper script \texttt{convert\_xspec\_script}.
+We converted the spectral script from XSPEC to {\it Sherpa} using the helper script \texttt{convert\_xspec\_script}.
 
@@
 We estimate the position of the feature by finding the brightest pixel in the map, obtaining $\alpha_{J2000}=01^h04^m02.75^s$ and $\delta_{J2000}=-72^d02^m00.19^s$ which is consistent with the value reported by \cite{Long2020}.
-It shows the reconstruction of absolute feature positions with \jolideco is consistent with past literature.
+This demonstrates an absolute feature position that was reconstructed with \jolideco that is consistent with the existing literature.
 
@@
 Both effects are previously known and have been reported for example in \cite{Xi2019}.
-Despite the clear improvement in spatial resolution the proper motion of structures in the image might limit the quality of the result.
+Despite the clear improvement in spatial resolution, systematic issues such as the proper-motion of structures and calibration uncertainties, might limit the quality of the result.
 The full analysis example is available at \url{https://github.com/jolideco/jolideco-chandra-examples}.
@@
                 The left panel shows the deconvolved flux and counts profile of the region illustrated in the right panel.
-The thick solid and dashed lines represent the mean of 100 bootstrapped observations.
-The counts profile is summed (stacked) across all observations, while the \jolideco profile is computed from a single joint reconstruction of all observations.
-The associated $3\sigma$ error band is shown transparent in the background, for both profiles.
+The thick solid and dashed lines represent the mean across the 100 bootstrap-resampled datasets.
+The counts profile for each bootstrapped dataset is summed (stacked) across the 25 observations per dataset, while the \jolideco profile is computed from a single joint reconstruction based on all 25 observations.
+The variability across the 100 bootstrapped datasets is represented by the $3\sigma$ error bands, shown transparent in the background for both profiles.
 Both profiles are normalized such that they integrate to unity and are aligned such that the position of their peak coincides.
@@
     \subsubsection{Flux Profile}
-    To quantify the improvement in angular resolution of the reconstructed image over the data we compute a flux profile on the \jolideco reconstruction of E0102.
+    To quantify the improvement in angular resolution of the reconstructed image over the raw data we compute a flux profile on the \jolideco (with the JWST patch prior) reconstruction of E0102.
 We chose a region perpendicular to the filament shown in Zoom~A of Figure~\ref{fig:example-chandra} of the size $128\times128$ pixels.
 We compute errors via the bootstrap, with resampled data obtained by sampling the event lists with replacement for each individual observation.
-For each resampled data set we run \jolideco and compute a binned flux profile on the reconstructed image.
-In total we sample 100 different realizations, where each reconstruction runs for about 10 min.
-on a standard M1 CPU.
+For each resampled dataset (composed of 25 observations) we run \jolideco and compute a binned flux profile on the reconstructed image.
+In total we sample 100 different realizations, where each reconstruction runs for about 10 minutes on a standard M1 CPU.
 In this way we obtain a set of profiles, which we use to compute the mean and error per bin of the profile.
-For comparison we also compute the profiles and associated errors directly on the bootstrapped counts summed across all observatoions (without processing or fitting).
+For comparison we also compute the profiles and associated errors directly on the bootstrapped counts summed across the 25 observations (without processing or fitting).
 The result is shown in Figure~\ref{fig:chandra-e0102-zoom-a}.
 
-    We compute the full-width at half-max (FWHM), $\omega$, of the profiles for each bootstrapped data set, by fitting a Gaussian shape with a linear gradient as a baseline for both the original counts and the \jolideconospace-deconvolved intensities.
-In both cases we compute the mean of $\omega$.
-We find that the deconvolved profile is significantly narrower.
-For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations of $\omega$ over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.
-
-    Assuming that the PSF and the shape of profile are approximately Gaussian we expect the width of the counts profile, the PSF, and the \jolideconospace-reconstructed profile to be related as:
-    %
-    \begin{equation}
-        \omega_{J} = \sqrt{\omega_C^2 - \omega_{\mathrm{PSF}}^2}
-    \end{equation}
-    %
-    With $\omega_{\mathrm{PSF}}\approx0.6$~arcsec\footnote{See projected radial profiles of the on-axis PSF at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}.
-The 1$\sigma$ radius is $\approx$0.26~arcsec (corresponding to 39\% enclosed counts in 2-D), suggesting that FWHM$_{{\rm PSF}}\approx{2.355{\cdot}0.26=0.62}$~arcsec.}, we expect a FWHM after deconvolution of $\omega_J\approx0.5$~arcsec.
-This is roughly consistent with the values we measured for the profile.
-
-    % \subsection{Combined \xmm and \chandra Observation}
-    % As a second application example we combine data from \chandra and \xmm.
-    % \url{https://github.com/jolideco/jolideco-chandra-nustar-examples}
-
-    % \begin{figure*}
-    %     \script{example-xmm-chandra.py}
-    %     \begin{centering}
-    %         \includegraphics[width=\linewidth]{figures/example-xmm-chandra.pdf}
-    %         \caption{
-    %             Chandra Example
-    %         }
-    %         \label{fig:example-xmm-chandra}
-    %     \end{centering}
-    % \end{figure*}
+    For each bootstrapped dataset, we then compute the full-width at half-max (FWHM) of the profiles by fitting a Gaussian shape with a linear gradient as a baseline, for both the counts profile ($\omega_C=0.78{\pm}0.02$~arcsec) and the \jolideconospace-deconvolved intensities ($\omega_J=0.58{\pm}0.02$~\arcsec), where the uncertainty is represented by the standard deviations in the bootstrap sample.
+Note that a significant narrowing of the cross-sectional profile is seen.
+The width of the filament however is definitively $>0''$, suggesting that it is resolved in the \jolideconospace\ reconstruction.\footnote{The projected radial profiles of the on-axis \chandra\ PSF (see the \chandra/MARX raytrace assessment at \url{https://space.mit.edu/cxc/marx/tests/PSF.html}) show that the 39\% enclosed counts fraction radius is $\approx$0.26~arcsec.
+Approximating the PSF as a 2D Gaussian, this corresponds to a $1\sigma$ radius, and a FWHM $\omega_{\textrm{PSF}}{\approx}0.62$~arcsec.
+Since the observed profile is expected to result from a convolution of the PSF with the true profile, we expect
+    $$\omega_C^2 = \omega_{\textrm{PSF}}^2+\omega_J^2 \,.$$  
+    A true filament width of $\gtrsim$0.5~arcsec is thus necessary to match the measured $\omega_C$.
+That the estimated $\omega_J$ is larger by $\approx$0.1~arcsec can be attributed to presence of several systematic confounding factors, such as the PSF being heavier tailed than a Gaussian, and the intrinsic profile of the filament not being Gaussian.}
 
@@
     In this article we presented a new method for deconvolution and denoising of images contaminated by Poisson noise.
-Using multiple observations of the same sky region the methods reconstructs a single flux image using the a MAP estimate that the joint posterior distribution under a patch-based image prior.
+Using multiple observations of the same sky region the method reconstructs a single flux image using the MAP estimate of the joint posterior distribution under a patch-based image prior.
 We show that the method leads to improved results compared to existing methods in a variety of morphological, signal to noise, and instrument scenarios.
@@
 
-    % The choice of the prior becomes more important at low signal noise ratios.
-The right choice can yield superior reconstruction quality then any other method we have compared to.
-The advantage of the GMM patch prior is its expressiveness and that it is adapted to the data in the optimization process.
-However if the GMM patch prior is learned on unsuited data or data that not diverse enough it can contain a strong bias and there is the danger of hallucinating features.
-Testing of systematic uncertainties therefore becomes crucial.
-
-    We believe \jolideco is the first step of a larger project building ML-inspired methods for the reconstruction of astronomical images that are dominated by Poisson noise.
+    We imagine that \jolideco is the first step of a larger project building ML-inspired methods for the reconstruction of astronomical images that are dominated by Poisson noise.
 While \jolideco has already achieved results that are superior to any other existing method, it still has significant potential for future extension and improvements.
@@
 
-    Aneta Siemiginowska, Vinay Kashyap, and Doug Burke further acknowledge support from NASA
+    Aneta Siemiginowska, Vinay Kashyap, and Douglas Burke further acknowledge support from NASA
     contract to the Chandra X-ray Center NAS8-03060.
@@
 
+    This research has made use of data obtained from the Chandra Data Archive and software provided by the Chandra X-ray Center (CXC) in the application packages CIAO \citep{Fruscione2006} and {\it Sherpa} \citep{Freeman2001,Burke2022}.
+
     \newpage
@@
     \appendix
-    \section{Details on Source Patterns}
-
-    % \begin{table*}[t]
-    % \label{tab:scenarios}
-    %   \centering
-    %   \begin{tabular}{l|cr}
-    %     \hline
-    %     Scenario & Description & Parameters \\
-    %     \hline
-    %     A1 & A grid of point sources & x, y \\
-    %     B1-3 & Extended Gaussian shaped source surrounded by point sources & $\sigma$ \\
-    %     C1-3 & Point Sources on top of a disk shaped source, jet like line features & $r_{\mathrm{Disk}}$ \\
-    %     D1-D5 & A spiral-arm structure surrounded by point sources and a large ring like feature & 9 \\
-    %     \hline
-    %   \end{tabular}
-    %   \caption{Source scenarios, \todo{maybe we find a good structure for the table...would list the actual flux values per component}}
-    %   \label{tab:1}
-    % \end{table*}
+    \section{Details on Source Patterns Used in Numerical Experiments}
 
@@
 
-    We have devised elaborate source patterns consisting of point sources and extended sources of different shapes, sizes, orientations, and spacings in order to test deconvolution algorithms for astronomical low counts images.
+    We have devised a series of elaborate simulation scenarios  consisting of point sources and extended sources of different shapes, sizes, orientations, and spacings in order to test deconvolution algorithms for astronomical low-count images.
 There are four distinct patterns, illustrated in Figure~\ref{fig:scenarios}, which we denote (1) {\sl Pointilist}, (2) {\sl Asterism}, (3) {\sl Shield}, and (4) {\sl Spiral}.
@@
 
-    \paragraph{Pointilist} A series of point sources arranged in a grid with increasing horizontal and vertical separations.
+    \subsection{Scenario A1: ``Pointilist"}
+    The first scenario conisists of a series of point sources arranged in a grid with increasing horizontal and vertical separations.
 The sources placed along a horizontal row all have the same strength, which increases with $y$-axis locations.
@@
     $$y = [8, 10, 13, 18, 26, 39, 55, 76]~\textrm{pix} \,,$$
-    and $\tau$ denotes an arbitrary scaling factor, set to 1 for \textit{Chandra}-like simulations and to 5 for XMM-like simulations.
+    where $\tau$ denotes an arbitrary scaling factor, set to 1 for \textit{Chandra}-like simulations and to 5 for XMM-like simulations.
     The $x$-axis locations of the sources for a given $y$ are
-    $$[8, 9, 10, 11, 13, 16, 21, 29, 42, 61, 95]~\textrm{pix} \,.$$
-    Notice that the spatial separations and intensity changes are based on the Fibonacci series, which places them on a cadence that is sub-logarithmic but supra-linear, and thus provides a good trade-off between dynamic range and point density.
-Further note that at the lower left corner of the image, adjacent sources are placed close together, either in the adjoining pixel or separated by one pixel, with low source strengths, posing an almost impossible challenge to deconvolution algorithms.
-In contrast, the upper right corner of the image is sparse, with strong sources well separated.
-
-    \paragraph{Asterism} This pattern is comprised of a diffuse Gaussian source ($\sigma=2$~pix) at the center of the image at pixel location (64,64), and four larger extended sources (Gaussians with $\sigma=4$~pix) with the same number of counts as the central source are set at each of the corners.
-Four point sources with intensities decreasing by a factor $\frac{1}{3}$ are arranged around the central diffuse source to the top, left, right, and bottom.
-Three brightness levels are considered, with counts in all the diffuse sources set at
-    $$\{100, 500, 1000\} \cdot \tau ~\textrm{counts~pix}^{-1}\,,$$
-    where $\tau=1$ for \chandra-like and $\tau=5$ for \xmm-like simulations.  The diffuse sources are located at
-    $$(x,y)_{{\rm diffuse}} = (22,22), (22,106), (106,106), (106,22) ~\textrm{pix} \,,$$
+    $$x=[8, 9, 10, 11, 13, 16, 21, 29, 42, 61, 95]~\textrm{pix} \,.$$
+    The spatial separation and intensity changes are based on the Fibonacci series, which places them on a cadence that is sub-logarithmic but supra-linear, and thus provides a good trade-off between dynamic range and point density.
+Notice that at the lower left corner of the image, adjacent sources are placed closer together, either in the adjoining pixel or separated by one pixel, with low source strengths, posing an almost impossible challenge to deconvolution algorithms.
+In contrast, the upper right corner of the image is sparse, with strong well separated sources.
+
+    \subsection{Scenario B1-B3: ``Asterism"}
+    The pattern for these scenarios includes a diffuse Gaussian source ($\sigma=2$~pix) at the center of the image with pixel location (64,64).
+Four larger extended sources (Gaussians with $\sigma=4$~pix) with the same number of counts as the central source are set at each of the corners.
+Four point sources with intensities decreasing by a factor $1/3$ are arranged around the central diffuse source to the top, left, right, and bottom.
+The three signal-to-noise ratios (indicated by the scenario number) are determined by the counts in the diffuse sources, all of which are set to one of the values in $$\{B1, B2, B3\} := \{100, 500, 1000\} \cdot \tau ~\textrm{counts}/\textrm{pix}\,,$$ where $\tau=1$ for \chandra-like and $\tau=5$ for \xmm-like simulations, as above.
+The diffuse sources are located at
+    $$(x,y)_{{\rm diffuse}} = \{(22,22), (22,106), (106,106), (106,22)\} ~\textrm{pix} \,,$$
     and the point sources at
-    $$(x,y)_{{\rm point}} = (64,76), (44,64), (74,64), (64,44) ~\textrm{pix}\,,$$
+    $$(x,y)_{{\rm point}} = \{(64,76), (44,64), (74,64), (64,44)\} ~\textrm{pix}\,,$$
     with counts
@@
     those in the diffuse sources respectively.
-The pattern of point sources explores the effects of contamination by large extended sources, and the diffuse sources at the corners help to characterize the edge effects in deconvolutions.
-
-    \paragraph{Shield} A flat disk at image center, with superposed point sources, and jet-like linear extensions radiating to the corners.  The disk has a radius of 20~pix and has brightness set to
-    $$\{0.5, 1, 2\} \cdot \tau ~\textrm{counts~pix}^{-1} \,,$$
+The pattern of point sources explores the effects of contamination by large extended sources, while the diffuse sources at the corners help to characterize the edge effects in deconvolutions.
+
+    \subsection{Scenario C1-C3: ``Shield"}
+    These scenarios consists of a flat disk at the image center, with superposed point sources, and a jet-like linear extensions radiating to the corners.
+The disk has a radius of 20~pix.
+The overall signal-to-noise ratio of each of the three scenarios is determined by the disc's brightness, which is set to one of the values in
+    $$\{C1, C2, C3\} := \{0.5, 1, 2\} \cdot \tau ~\textrm{counts~pix}^{-1} \,,$$
     where again $\tau$ represents an arbitrary scaling factor to mimic telescope sensitivity.
-Four point sources are placed at positions displaced at $\{\pm8,\pm8\}$~pix from image center, with intensities at
+Four point sources are placed at positions displaced at $\{\pm8,\pm8\}$~pix from image center, with intensities set to
     $$\{10, 50, 100, 500\} \cdot \tau ~~\textrm{counts}$$
-    clockwise starting from lower left respectively.
-Linear sources of horizontal width 3~pix are placed along the $\pm45^o$ lines extending between radial distances from 36~pix to 64~pix from image center, with surface brightnesses
+    clockwise starting from the lower left, respectively.
+Linear sources, each with a horizontal width of 3~pix, are placed along the $\pm45^o$ lines extending from radial distances of 36~pix to 64~pix from the image center, with surface brightnesses of
     $$\{10, 50, 100, 500\} \cdot \tau ~\textrm{counts~pix}^{-1} \,,$$
@@
 This pattern simultaneously tests the ability of deconvolution algorithms to distinguish the disk from the background, and the embedded point sources from the disk.
-The linear radiating sources present a different challenge to algorithms which use symmetrical kernels, which usually break such features (often seen in real astronomical images as jets or detector features like streaks or bad CCD columns) into a string of point-like sources.
-
-    \paragraph{Spiral} This has 4 major components: First, a double spiral structure, centered at $(-10, 0)$~pix, covering 500$^o$~deg with a maximum radial extent of 24~pixels and a width of 3~pixels; second, a disk of radius 4, also centered at $(-10, 0)$~pix; third, two vertical rows of point sources located at x-axis positions of 40~pixels and 88~pix, and y-axis locations of $\{\pm7,\pm21\}$~pix; and fourth, an annulus that encloses all these elements, also centered at $(-10, 0)$~pix, and with inner radius 52~pix and outer radius 54~pix.
-    The point sources have intensities of $\{25, 50, 100, 200\}$~counts increasing with vertical height, and the spiral, disk, and annulus have surface brightnesses of $$\{0.5, 1, 2, 10, 1000\} \cdot \tau ~\textrm{counts}$$.
+The linear radiating sources present a different difficult challenge to algorithms which use symmetrical kernels, which usually break such features into a string of point-like sources.
+(We emphasize that such features are often seen in real astronomical images as jets or detector features like streaks or bad CCD columns.)
+
+    \subsection{Scenario D1-D5: ``Spiral"}
+    These scenarios have 4 major components.
+First is a double spiral structure, centered at $(-10, 0)$~pix, covering 500$^o$~deg, and with a maximum radial extent of 24~pixels and a width of 3~pixels.
+Second is a disk of radius 4, centered at $(-10, 0)$~pix.
+Third are two vertical rows of point sources located at x-axis positions of 40~pixels and 88~pix, with y-axis locations spanning $\{\pm7,\pm21\}$~pix.
+Fourth is an annulus that encloses all these elements; it is also centered at $(-10, 0)$~pix, with inner radius 52~pix and outer radius 54~pix.
+    The point sources have intensities of $\{25, 50, 100, 200\}$~counts increasing with vertical height.
+The overall signal-to-noise ratio of the scenarios is determined by the surface brightnesses of the spiral, disk, and annulus, which are set to one of the values in
+    $$\{D1, D2, D3, D4, D5 \} := \{0.5, 1, 2, 10, 1000\} \cdot \tau ~\textrm{counts}.$$  
     This configuration tests the recovery of closely located diffuse structures (close spiral arms), field-of-view edge effects (annulus that approaches close to the left edge of the image), and the visibility of point sources close to diffuse structures.
 The case with the surface brightness of 1000~counts~pix$^{-1}$ tests the asymptotic limit of the high counts case.
-
-    \vlk{ALSO MAKE A NOTE OF POINT SOURCE INTENSITY CONTRAST CF. SHARP PSFs}
-
-    % \subsection{Computational Performance}
-    % We conduct as series of performance benchmarks (see Appendix?) to asses the scalability of the method to a large number of observations as well as large images.
-
-    % \begin{itemize}
-    %     \item Results are available in \url{https://github.com/jolideco/jolideco-benchmarks}
-    %     \item We tried the binary search tree as proposed in \cite{Parameswaran2018},
-    %     but without success, most likely because the native \texttt{Pytorch} support
-    %     for parallelization speeds up the standard GMM quite a bit...
-    %     \item GPU support via Pytorch
-    % \end{itemize}
-
-    \section{Chandra Observation Table}
+Since only the diffuse emission components have the enhanced brightness, this scenario also demonstrates the benefits of a sharp PSF; broad PSFs contaminate the diffuse emission around the point sources which results in a significantly higher difficulty in recovering faint sources.
+
+    \section{Additional Tables and Figures}    
+    In this section we present an additional figure (Figure~\ref{fig:example-fermi-lat-non-calibrated} illustrating the deconvolution of \fermi data of \textit{RX J0852.0-4622}) and table (Table~\ref{tab:chandra_obs} describing the characteristics of the analyzed dataset).
+
     \label{sec:chandra-table}
-    ]
     \begin{table}
     \centering
-        \begin{tabular}{ c|c|c|c|c } 
+        %\begin{tabular}{ c|c|c|c|c }
+        \begin{tabular}{ c c c c c }
             \input{output/chandra-obs-table.tex}
@@
         \script{chandra-obs-table.py}
-        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}.
+        \caption{Observation list and details from the \chandra \textit{1E~0102.2–7219} example analysis in Section~\ref{sec:chandra-example}.
 The relative exposure columns list the exposure for each observation expressed as the ratio with the exposure of the reference observation with obs ID 8365.
@@
 
-    \section{Fermi-LAT Example Residuals With and Without Calibration}
      \begin{figure*}
@@
             \caption{
-                Illustration of the residuals of the \fermi analysis example from Section~\ref{sec:fermi-lat-example}.
+                Illustration of the residuals of the \fermi analysis example of \textit{RX J0852.0-4622} from Section~\ref{sec:fermi-lat-example}.
 All images show the standardized residuals as computed by Equation~\ref{eq:approx-sigma} and smoothed with a \textit{Gaussian} kernel of width 5~pixels $\approx 0.1$~degrees, similar to the size of the PSF.
-The upper row shows the result without calibration, the lower row shoes the result with the calibration applied, according to Equation~\ref{eq:model-npred-calibration}.
+The upper row shows the result without calibration, the lower row shows the result with the calibration applied, according to Equation~\ref{eq:model-npred-calibration}.
 The columns represent the four different PSF event classes of \fermi.
+The color scale is shown in the right panel.
 More information on this analysis example can be found on \url{https://github.com/jolideco/jolideco-fermi-examples}.

### 2024-03-12 src/scripts/example-fermi-lat.py
Fix fermi lat example filename

@@ -57,7 +57,7 @@ path = (
 
 filename_jolideco = path / "vela-junior-above-10GeV-data-result-jolideco.fits"
 filenames_data = (path / "input").glob("*.fits")
-filename_npred = path / "vela-junior-above-10GeV-data-npred-calibrated.fits"
+filename_npred = path / "vela-junior-above-10GeV-data-npred.fits"
 
 npred = Map.read(filename_npred)
 

### 2024-05-24 src/scripts/comparison-scenarios.py
Add method identifiers to Fig 5

@@ -33,11 +33,11 @@ instrument = "chandra"
 method_titles = {
     "data": "Data",
     "gt": "Ground Truth",
-    "jolideco-uniform-prior=n=10": "Jolideco\n(Uni, n=10)",
-    "jolideco-uniform-prior=n=1000": "Jolideco\n(Uni., n=1000)",
-    "pylira": "Pylira",
-    "jolideco-patch-prior-zoran-weiss": "Jolideco\n(Zoran-Weiss)",
-    "jolideco-patch-prior-gleam-v0.1": "Jolideco\n(GLEAM v0.1)",
+    "jolideco-uniform-prior=n=10": "M1: Jolideco\n(Uni, n=10)",
+    "jolideco-uniform-prior=n=1000": "M2: Jolideco\n(Uni., n=1000)",
+    "pylira": "M3: Pylira",
+    "jolideco-patch-prior-zoran-weiss": "M4: Jolideco\n(Zoran-Weiss)",
+    "jolideco-patch-prior-gleam-v0.1": "M5: Jolideco\n(GLEAM v0.1)",
 }
 
 figsize = config.FigureSizeAA(aspect_ratio=1.618, width_aa="two-column")

### 2024-05-24 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Define document class
-\documentclass[twocolumn, lineno]{aastex631}
+\documentclass[twocolumn, linenumbers]{aastex631}
 
@@
     \affil{Center for Astrophysics $|$ Harvard \& Smithsonian \\ Cambridge MA 02138 USA}
+    \correspondingauthor{Axel Donath}
+    \email{axel.donath@cfa.harvard.edu}
 
@@
 
-    \cite{Selig2015} and \cite{Pumpe2018} approach the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
+    \cite{Selig2015A} and \cite{Pumpe2018} approach the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
 Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they are able to deconvolve \fermi observations
     into a mixture of point-like and diffuse emission components.
-While their method works well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it shows artifacts for smaller extended emission structures such as morphological details of extended sources in the Galactic Plane.
+While their method works well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it showed artifacts around the Galactic Plane, when applied to gamma-ray data from the Fermi-LAT \cite{Selig2015B}.
 
@@
     where $\mathbf{P}_n$ represents a neighbourhood matrix to extract the $n$-th patch from the image $\mathbf{x}$ and where $\mathbf{x}_n$ is the vector of length $N_p^2$ representing the \enquote{flattened} image patch.
-By obtaining a large number of patches we can model the distribution of pixel intensities within the patches using a Gaussian Mixture Model (GMM).
+By obtaining a large number of patches we can model the distribution of pixel intensities within the patches using a Gaussian Mixture Model (GMM) \citep{McLachlan2004}.
 The GMM is a universal function approximator and thus can model arbitrary distributions.
@@
 
-    Where $\mathcal{N}$ is the Gaussian normal distribution.
+    Where $\mathcal{N}$ is a multivariate Gaussian normal distribution.
+The distribution is parameterized by the vector $\mathbf{\mu_k}$, which a dimension equivalent to the number of pixels in a patch and represents the mean of each Gaussian component.
+The pairwise correlation between pixels is represented by the corresponding covariance matrix $\mathbf{\Sigma}_k$, while the weight of each component is given by $\pi_k$.
+
     If we knew the relevant component, $k_n$, for patch $\mathbf{x}_n$ we could derive the conditional log-prior distribution directly from Equation~\ref{eq:gmm}:
@@
     %
-    where $\mathbf{P}_n$ is again the matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed.
+    where $\mathbf{P}_n$ is again the matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed and $\pi_{\hat{k}_n}$ the weight of the component $\hat{k}_n$, which maximizes the log-likelihood for the n-th patch.
 
@@
 This improves the computational performance of the method.
-We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction is slightly faster with the same reconstruction quality.
-However for all results shown later in the manuscript we chose the simpler cycle spinning described in the previous paragraph.
+We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction was slightly faster with the same reconstruction quality.
+However we found (a) practical issues with reproducibility of results when using the method on a GPU and (b) a lot of code complexity to handle the edge of images correctly.
+Give the performance improvement was only small,
+    we decided to just stick with the much simpler regular grid and cycle spinning, described in the previous paragraph.
 
@@
         \label{eq:model-npred-calibration}
-        \mathbf{\lambda}_j = \mathbf{E}_j \cdot  \left(\mathrm{PSF}_j \circledast \phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})\right) + \alpha_j \cdot \mathbf{B}_j
+        \boldsymbol{\lambda}_j = \mathbf{E}_j \cdot  \left(\mathrm{PSF}_j \circledast \phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})\right) + \alpha_j \cdot \mathbf{B}_j
     \end{equation}
@@
     \subsection{\jolideco Framework}
-    The goal of the reconstruction process is to optimize the a-posteriori likelihood defined by Equation~\ref{eq:total}.
+    The goal of the reconstruction process is to find the mode of the posterior distribution defined by Equation~\ref{eq:total}.
 Given that there is a parameter for each pixel in the image, this is a high dimensional optimization problem.
@@
     The patch-based image prior described in Section~\ref{sec:patch-prior} requires a pre-trained GMM.
-We train the GMM by choosing a set of reference images, splitting them into patches of size $8\times8$ pixels and learning a GMM with $K$ components from the whole distribution of patches.
+We train the GMM by choosing a set of reference images, splitting them into patches of size $8\times8$ pixels and learning a GMM with $K=128$ components from the whole distribution of patches.
 In general the strength of the GMM prior is its high \enquote{expressiveness}.
 This means the prior distribution contains a large variety of structural shapes and has freedom to adapt to the data in the optimization process by choosing the most likely GMM component for each patch in the image.
+\cite{Zoran2012} empirically found that the reconstruction quality depended on the number of components of the GMM.
+A higher number of components clearly lead to an improved reconstruction quality, as the GMM was more expressive.
+This also aligns with the intuitive argument that GMMs are universal function approximators; with a sufficient number of components they can approximate any distribution.
+\cite{Zoran2012} found the reconstruction quality started to saturate once the number of components was large enough.
+Empirically they measured a number of 32 components to be sufficient in practice for natural images.
+We decided to adopt a more conservative number of 128.
+
     With radio data, \cite{Bouman2016} found their results to be mostly independent of the choice of data used for learning the GMM prior.
-
 However, in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of prior, simply because the prior distribution is more influential when the data is less informative.
@@
 We used the ADAM algorithm \citep{Kingma2014}, a stochastic gradient descent method, without decay and a fixed learning rate of $\mathrm{lr}=10^{-3}$.
-To further improve the rate of convergence of the optimization process we applied the following strategy:
+In practice we found the convergence of the method to be very stable, however we applied the following strategy to speed up the optimization process:
 
@@
 This corresponds approximately to a reconstruction obtained with the standard RL algorithm.
+As the uniform prior is much faster to evaluate ($\mathcal{O(100)}$), we quickly arrive at a much better starting estimate for the reconstructed image.
         \item[2.] We freeze the image parameters and optimize the parameters associated with the systematic error described in Equation~\ref{eq:model-npred-calibration}.
+This way we arrive at a better starting estimate for those.
+Again the process is fast, because the number of parameters is very small.
         \item[3.] Finally we simultaneously optimize
@@
 
-        \item[\bf M1.] \textbf{Pylira}: we used the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
+        \item[\bf M1.] \textbf{\jolideco (Uniform, n=10)}: we used \jolideco with a uniform prior on $\mathbf{x}$ and ran the optimizer for 10 iterations.
+We consider this as a baseline method reference similar to RL.
+While the optimization procedure is different, we expect similar behaviour for the local correlations of pixels.
+This ad hoc approach of early stopping is often used in practice to regularise the RL output.
+
+        \item[\bf M2.] \textbf{\jolideco (Uniform, n=1000)}:  we used \jolideco with a uniform prior on $\mathbf{x}$, but running the optimizer for 1000 iterations.
+This is the same as above but without early stopping.
+This gives rise to the issue of RL decomposing extended emission into point sources.
+
+        \item[\bf M3.] \textbf{Pylira}: we used the LIRA method \citep{Esch2004} via the Pylira Python wrapper \citep{Donath2022}.
 We relied on the default prior definition and kept the background norm fixed.
@@
 
-        \item[\bf M2.] \textbf{\jolideco (Uniform, n=10)}: we used \jolideco with a uniform prior on $\mathbf{x}$ and ran the optimizer for 10 iterations.
-We consider this as a baseline method reference similar to RL.
-While the optimization procedure is different, we expect similar behaviour for the local correlations of pixels.
-This ad hoc approach of early stopping is often used in practice to regularise the RL output.
-
-        \item[\bf M3.] \textbf{\jolideco (Uniform, n=1000)}:  we used \jolideco with a uniform prior on $\mathbf{x}$, but running the optimizer for 1000 iterations.
-This is the same as above but without early stopping.
-This gives rise to the issue of RL decomposing extended emission into point sources.
-
-        \item[\bf M4.] \textbf{\jolideco (Patch, GLEAM v0.1)}: we used \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalization described by Equation~\ref{eq:patch-norm}.
-We used the optimization strategy described in Section~\ref{sec:opt-strategy} with 2000 epochs.
-
-        \item[\bf M5.] \textbf{\jolideco (Patch, Zoran-Weiss)}: we used \jolideco with the patch prior provided by \cite{Zoran2011}.
+        \item[\bf M4.] \textbf{\jolideco (Patch, Zoran-Weiss)}: we used \jolideco with the patch prior provided by \cite{Zoran2011}.
 To be consistent with how the GMM was learned we only subtracted the mean of the patch and skipped the division by the mean we introduced in Equation~\ref{eq:patch-norm}.
@@
 In practice this could be estimated from the brightest pixel in the data and the shape of the PSF.}.
+
+        \item[\bf M5.] \textbf{\jolideco (Patch, GLEAM v0.1)}: we used \jolideco with a patch prior learned on the GLEAM data, described in Section~\ref{sssec:gleam-radio-data} and the patch normalization described by Equation~\ref{eq:patch-norm}.
+We used the optimization strategy described in Section~\ref{sec:opt-strategy} with 2000 epochs.
+
     \end{enumerate}
@@
 The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but remain blurred along the direction of their neighbours.
-This a similar situation as in the lower left of the image in the A1 point source scenario, when sources are to close by.
+Thids a similar situation as in the lower left of the image in the A1 point source scenario, when sources are to close by.
 
@@
 While the emission is barely visible in the counts image it is clearly evident above the background in the \jolideco reconstruction.
-The reconstruction leaves a visible extension in the point-like source.
-However, at this level of analysis and signal to noise, both scenarios remain plausible: a real intrinsic extension of the feature, as well as a remaining reconstructed extension in a real point source because of low signal to noise\footnote{We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.}
+Visually the reconstruction does not result in a point source, but leaves a visible extension of a very few pixels.
+
+    However, at this level of analysis and signal to noise, both scenarios remain plausible: a real intrinsic extension of the feature, as well as a remaining reconstructed extension in a real point source because of low signal to noise, which has also been observed on the simulated point source dataset discussed in Section~\ref{subsec:test-datasets}\footnote{We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.}.
 
@@
         \label{eq:approx-sigma}
-        \rho(N_{\mathrm{Data}}, N_{\mathrm{Pred}}) \approx \frac{1}{\sqrt{\pi \sigma^2}}\frac{(N_{\mathrm{Data}} - N_{\mathrm{Pred}}) \circledast g_{\sigma}} {\sqrt{N_{\mathrm{Pred}}\circledast g_{\sigma}}}.
-    \end{equation}
-
-    where $g_{\sigma}$ is a Gaussian smoothing kernel of width $\sigma=5$ pixels.
+        \rho(\mathbf{D}, \boldsymbol{\lambda}) \approx \frac{1}{\sqrt{\pi \sigma^2}}\frac{(\mathbf{D} - \boldsymbol{\lambda}) \circledast g_{\sigma}} {\sqrt{\boldsymbol{\lambda}\circledast g_{\sigma}}}.
+    \end{equation}
+
+    where $\mathbf{D}$ is the measured counts image, $\boldsymbol{\lambda}$ the predicted counts image  and $g_{\sigma}$ is a Gaussian smoothing kernel of width $\sigma=5$ pixels.
+The Gaussian smoothing kernel approximates the shape and size of the \fermi PSF.
+Together with the definition above, the standardized residuals approximately represent the significance of detecting a point source at the given pixel.
+Structures smaller than the PSF cannot be real.
+
     The result is shown in the right panel of Figure~\ref{fig:example-fermi-lat}.

### 2024-05-24 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     %
+
+    \begin{table*}
+    \centering
+        \begin{tabular}{ c|c|c|c|c|c } 
+            \input{output/metrics-table-bkg.tex}
+        \end{tabular}
+        \label{tab:metrics}
+        \script{metrics-table-bkg.py}
+        \caption{Image metrics for the different signal to noise ratios shown in Figure~\ref{fig:comparison-signal-noise}.
+The first number in a cell shows the structural similarity index (SSI, the closer to unity, the better) and the second number shows the normalized root mean square (NRMSE, the lower the better).}
+    \end{table*}
+
     As a second experiment we explore the dependency of the results on the background level and signal strength.
@@
     Alternatively we can use MCMC to obtain a sampling from the full posterior distribution, enabling us to explore the distribution and quantify  uncertainty both in the parameters and functions of the parameters constructed to represent structures in the image.
+    Estimating errors for the reconstruction would also include propagating systematic uncertainties on the PSF to the reconstructed image and handling a PSF that varies across the field of view, as recently proposed by \cite{Sakai2023}.
 

### 2024-05-24 src/scripts/metrics-table-bkg.py
Add metrics table for s/n scenarios

@@ -1,0 +1,99 @@
+import logging
+from io import StringIO
+
+import paths
+import yaml
+from astropy.table import Table
+
+log = logging.getLogger(__name__)
+
+
+METRICS = ["MSE", "NMI", "SSI", "NRMSE"]
+SCENARIOS = {"point1": "A1", "aster3": "B3", "disk3": "C3", "spiral4": "D4"}
+
+
+method_titles = {
+    # "gt": "Ground Truth",
+    "jolideco-uniform-prior=n=10": r"\thead[c]{Jolideco\\(Uni, n=10)}",
+    "jolideco-uniform-prior=n=1000": r"\thead[c]{Jolideco\\(Uni., n=1000)}",
+    "pylira": r"Pylira",
+    "jolideco-patch-prior-zoran-weiss": r"\thead[c]{Jolideco\\(Zoran-Weiss)}",
+    "jolideco-patch-prior-gleam-v0.1": r"\thead[c]{Jolideco\\(GLEAM v0.1)}",
+}
+
+
+def get_metrics(path):
+    with open(path) as f:
+        metrics = yaml.safe_load(f)
+
+    return metrics
+
+
+def get_parameters(filename):
+    parts = filename.parts
+    return {
+        "Method": parts[-2],
+        "Bkg. Level": parts[-4],
+        "Scenario": parts[-5],
+        "Instrument": parts[-3],
+    }
+
+
+colnames = [
+    "Method",
+    "Bkg. Level",
+    "Scenario",
+    "Instrument",
+]
+names = colnames + METRICS
+
+dtypes = ["S20"] * len(colnames) + ["f8"] * len(METRICS)
+
+table = Table(names=names, dtype=dtypes)
+
+filenames = paths.jolideco_repo_comparison.glob("results/*/bg*/*/*/metrics.yaml")
+
+
+for filename in filenames:
+    data = get_metrics(filename)
+    data.update(get_parameters(filename))
+    table.add_row(data)
+
+
+selection = (table["Instrument"] == "chandra") & (table["Bkg. Level"] == "bg1")
+table = table[selection]
+
+
+table_metrics = Table(
+    names=["Scenario"] + list(method_titles.values()),
+    dtype=["S2"] + ["S10"] * len(method_titles),
+)
+
+for scenario in SCENARIOS:
+    data = table[table["Scenario"] == scenario]
+
+    values = {}
+    for method, title in method_titles.items():
+        selection = data["Method"] == method
[…]

### 2024-05-24 src/scripts/metrics-table-bkg.py
Adapt table script

@@ -9,16 +9,20 @@ log = logging.getLogger(__name__)
 
 
 METRICS = ["MSE", "NMI", "SSI", "NRMSE"]
-SCENARIOS = {"point1": "A1", "aster3": "B3", "disk3": "C3", "spiral4": "D4"}
+SCENARIOS = {
+    "spiral1": "D1",
+    "spiral2": "D2",
+    "spiral3": "D3",
+    "spiral4": "D4",
+    "spiral5": "D5",
+}
 
+METHOD = "jolideco-patch-prior-gleam-v0.1"
 
-method_titles = {
-    # "gt": "Ground Truth",
-    "jolideco-uniform-prior=n=10": r"\thead[c]{Jolideco\\(Uni, n=10)}",
-    "jolideco-uniform-prior=n=1000": r"\thead[c]{Jolideco\\(Uni., n=1000)}",
-    "pylira": r"Pylira",
-    "jolideco-patch-prior-zoran-weiss": r"\thead[c]{Jolideco\\(Zoran-Weiss)}",
-    "jolideco-patch-prior-gleam-v0.1": r"\thead[c]{Jolideco\\(GLEAM v0.1)}",
+bkg_level_titles = {
+    "bg1": "Bkg 1",
+    "bg2": "Bkg 2",
+    "bg3": "Bkg 3",
 }
 
 
@@ -60,21 +64,21 @@ for filename in filenames:
     table.add_row(data)
 
 
-selection = (table["Instrument"] == "chandra") & (table["Bkg. Level"] == "bg1")
+selection = (table["Instrument"] == "chandra") & (table["Method"] == METHOD)
 table = table[selection]
 
 
 table_metrics = Table(
-    names=["Scenario"] + list(method_titles.values()),
-    dtype=["S2"] + ["S10"] * len(method_titles),
+    names=["Scenario"] + list(bkg_level_titles.values()),
+    dtype=["S2"] + ["S10"] * len(bkg_level_titles),
 )
 
 for scenario in SCENARIOS:
     data = table[table["Scenario"] == scenario]
 
     values = {}
-    for method, title in method_titles.items():
-        selection = data["Method"] == method
+    for bkg_level, title in bkg_level_titles.items():
+        selection = data["Bkg. Level"] == bkg_level
         v = [float(data[selection][name]) for name in ["SSI", "NRMSE"]]
         values[title] = f"{v[0]:.2f} / {v[1]:.2f}"
 

### 2024-08-02 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-        We present a new method for joint likelihood deconvolution (\jolideconospace) of a set of astronomical observations of the same sky region in the presence of Poisson noise. 
+        We present a new framework for joint likelihood deconvolution (\jolideconospace) of a set of astronomical observations of the same sky region in the presence of Poisson noise. 
         The observations may be obtained from different instruments with  different resolution, and different point spread functions.
-\jolideco reconstructs a single flux image by optimizing the posterior distribution based on the joint Poisson likelihood of all observations under a patch-based image prior.
-The patch prior is parameterised via a Gaussian Mixture model which we train on high-signal-to-noise astronomical images, including data from the  James Webb Telescope and the GLEAM radio survey.
+\jolideco reconstructs a single flux image by optimizing the posterior distribution based on the joint Poisson likelihood of all observations under one of several prior distributions.
+Most notably we employ a patch-based image prior, that is parameterised via a Gaussian Mixture model which we train on high-signal-to-noise astronomical images, including data from the James Webb Telescope and the GLEAM radio survey.
 This prior favors correlation structures among the reconstructed pixel intensities that are characteristic of those observed in the training images.
@@
 Most importantly this lead to the introduction of regularised RL methods, such as use of total variation \citep{Dey2006} or sparse representations based on \enquote{wavelets} or \enquote{curvelets} \citep{Starck2003}.
-The challenge is rooted in two fundamentally contradicting goals: a deconvolution process that favors point sources will decompose extend structures present in the image, while introducing local correlations between neighbouring pixels will lead to less sharp reconstruction of point sources.
+The challenge is rooted in two fundamentally contradicting goals: a deconvolution process that favors point sources will decompose extend structures present in the image, while introducing local correlations between neighboring pixels will lead to less sharp reconstruction of point sources.
 
@@
 
-    \cite{Selig2015A} and \cite{Pumpe2018} approach the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory.
-Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they are able to deconvolve \fermi observations
-    into a mixture of point-like and diffuse emission components.
-While their method works well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it showed artifacts around the Galactic Plane, when applied to gamma-ray data from the Fermi-LAT \cite{Selig2015B}.
+    \cite{Selig2015A} and \cite{Pumpe2018} approach the problem of deconvolution of Poisson noise data implicitly using the framework of information field theory (IFT).
+Based on physical prior assumptions on the spatial distribution of point sources and local correlation structures of diffuse emission, they are able to deconvolve \fermi observations into a mixture of point-like and diffuse emission components.
+While their method works well for large-scale diffuse emission, such as the Galactic diffuse gamma-ray emission, it shows artifacts around the Galactic Plane, when applied to gamma-ray data from the Fermi-LAT \citep{Selig2015B}.
+
+    \cite{Westerkamp2024} applied the same IFT framework to a Chandra x-ray observation of the supernova remnant (SNR) SN1006.
+The authors demonstrated that it is possible to separate the point like emission of the extra-galactic background sources from the diffuse foreground emission of the SNR.
+The method delivered good reconstruction quality on synthetic data.
+When applied to observational data the authors found plausible reconstructions that include small artifacts, which they attributed to a mismatch between the modelled and actual PSF.
 
@@
         \label{eq:cash}
-        \mathcal{C}\left( \mathbf{D}_j | \boldsymbol{\lambda}_j \right) = \sum_{i=1}^{N_j} \left(\lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}\right),
-    \end{equation}
-    %  
-    By summing over all observations we obtain the joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
+        \mathcal{C}\left( \mathbf{D}_j | \boldsymbol{\lambda}_j(\mathbf{x}) \right) = \sum_{i=1}^{N_j} \left(\lambda_{j,i} - D_{j, i} \log{\lambda_{j,i}}\right),
+    \end{equation}
+    %  
+    By summing over all observations we obtain the (negative) joint log-likelihood of measuring a set of counts images $\mathbf{D}$ given an unknown flux image $\mathbf{x}$:
     %
@@
         \label{eq:joint}
-        \mathcal{L}\left( \mathbf{D} | \mathbf{x} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right)
+        \mathcal{L}\left( \mathbf{D} | \mathbf{x} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \boldsymbol{\lambda}_j(\mathbf{x}) \right)
     \end{equation}
@@
     When reconstructing images in the context of inverse problems we are operating in a high dimensional parameter space, because each pixel in the image represents a parameter in the optimization process.
+High resolution \xray-images are typically composed of
+    %one can expect 
+    up to $\mathcal{O}(10^6)$ pixels.
 By using prior information we can introduce correlations among the parameters, to reduce the \enquote{effective dimensionality} of the problem and guide the optimization process toward unique and more stable solutions.
@@
     The Maximum A Posteriori (MAP) estimate of $\mathbf{x}$ is the value that maximizes Equation~\ref{eq:bayes}.
-    Taking the logarithm of Equation~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Equation~\ref{eq:joint} and dropping the normalization term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we obtain the following expression for the log-posterior distribution
+    Taking the logarithm of Equation~\ref{eq:bayes}, replacing the definition of the likelihood $P(\mathbf{D}|\mathbf{x})$ with Equation~\ref{eq:joint} and dropping the normalization term $P(\mathbf{D})$ which is independent of $\mathbf{x}$, we obtain the following expression for the (negative) log-posterior distribution
     $\mathcal{L}$:
@@
         \label{eq:total}
-        \mathcal{L}\left(\mathbf{x} | \mathbf{D} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right) - \beta \cdot \mathcal{P}(\mathbf{x}),
-    \end{equation}
-    %
-    where $\mathcal{C}\left( \mathbf{D}_j | \mathbf{x} \right)$ represents the summed log-likelihood for an individual observation $j$ and $\mathcal{P}(\mathbf{x})$ represents the log of the prior distribution with the factor $\beta$ adjusting the weight of the prior relative to the joint log likelihood term.
+        \mathcal{L}\left(\mathbf{x} | \mathbf{D} \right) = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \boldsymbol{\lambda}_j(\mathbf{x}) \right) - \beta \cdot \mathcal{P}(\mathbf{x}),
+    \end{equation}
+    %
+    where $\mathcal{C}\left( \mathbf{D}_j | \boldsymbol{\lambda}_j(\mathbf{x}) \right)$ represents the summed log-likelihood for an individual observation $j$ and $\mathcal{P}(\mathbf{x})$ represents the log of the prior distribution with the factor $\beta$ adjusting the weight of the prior relative to the joint log likelihood term.
 The parameter $\beta$ can be viewed as a hyper-parameter, chosen by the user to adjust the strength of the prior distribution relative to the likelihood.
@@
 
-    A patch is defined as a small, typically square, region of size $N_p \times N_p$ pixels, representing a local neighbourhood in a given image.
+    A patch is defined as a small, typically square, region of size $N_p \times N_p$ pixels, representing a local neighborhood in a given image.
 Mathematically we can formulate the extraction of such patches as:
@@
     %
-    where $\mathbf{P}_n$ represents a neighbourhood matrix to extract the $n$-th patch from the image $\mathbf{x}$ and where $\mathbf{x}_n$ is the vector of length $N_p^2$ representing the \enquote{flattened} image patch.
+    where $\mathbf{P}_n$ represents a neighborhood matrix to extract the $n$-th patch from the image $\mathbf{x}$ and where $\mathbf{x}_n$ is the vector of length $N_p^2$ representing the \enquote{flattened} image patch.
 By obtaining a large number of patches we can model the distribution of pixel intensities within the patches using a Gaussian Mixture Model (GMM) \citep{McLachlan2004}.
@@
     \end{equation}
-    %
-
-    Where $\mathcal{N}$ is a multivariate Gaussian normal distribution.
-The distribution is parameterized by the vector $\mathbf{\mu_k}$, which a dimension equivalent to the number of pixels in a patch and represents the mean of each Gaussian component.
-The pairwise correlation between pixels is represented by the corresponding covariance matrix $\mathbf{\Sigma}_k$, while the weight of each component is given by $\pi_k$.
+    where $\mathcal{N}$ represents a multivariate Gaussian normal distribution, $\mathbf{\mu_k}$ is the vector of Gaussian means (with dimension equal to the number of pixels in each patch), $\mathbf{\Sigma}_k$ is the variance-covariance matrix of the Gaussian distribution (which tabulates the variances and pairwise covariances of the patch pixels), and  $\pi_k$ is the weight of component $k$ of the GMM.
 
@@
         \mathcal{P}(\mathbf{x}, \hat{\mathbf{k}}) = 
-        %\mathcal{P}(\mathbf{x} | \hat{\mathbf{k}})  + \mathcal{P}(\hat{\mathbf{k}}) =
         \sum_{n = 1}^N \mathcal{P}_{\rm GMM}(\mathbf{P}_n \mathbf{x} | \hat{k}_n) +
@@
     %
-    where $\mathbf{P}_n$ is again the matrix that extracts the $n$-th patch from the image $\mathbf{x}$ to be reconstructed and $\pi_{\hat{k}_n}$ the weight of the component $\hat{k}_n$, which maximizes the log-likelihood for the n-th patch.
+    where $\mathbf{P}_n$ is again the matrix that extracts the $n$-th patch from the image $\mathbf{x}$ and $\pi_{\hat{k}_n}$ is the weight of GMM component $\hat{k}_n$, with $\hat{k}_n$ being the index of the GMM component that maximizes the log-prior distribution for patch $n$.
 
@@
 The bottom row shows the red example patch $\mathbf{x}_n$ on the left.
-The three other patches show the example patch represented by a linear combination of the six largest Eigenvectors of the covariance matrices of the 3 most likely GMM components $k = 105, 77, 17$.
+The three other patches show this example patch represented by a linear combination of the six largest Eigenvectors of the covariance matrices of the 3 most likely GMM components $k = 105, 77, 17$.
 This example uses the GMM learned from the JWST Cas A image.
@@
     Apart from this, the process for choosing the most likely GMM prior component remains unmodified.
-However, we note that we neglected the prior dependence between neighbouring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixels and are thus clearly not \aprioir independent.}.
+However, we note that we neglected the prior dependence between neighboring patches\footnote{That is, we continue to evaluate the log-prior distribution of the full image by summing over the overlapping patches as in Equation~\ref{eq:prior-total}, even though overlapping patches include common pixels and are thus clearly not \aprioir independent.}.
 As the choice of the GMM component per patch is discrete, a simultaneous gradient based optimization of all patches is not easily possible, because we cannot compute gradients across GMM components.
@@
         \label{eq:patch-norm}
-        \tilde{\mathbf{x}}_n = \frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n}
+        \widetilde{\mathbf{P}_n\mathbf{x}}
+        = \frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n}.
     \end{equation}
@@
 The prior distribution simply regularizes the structure in the image, while the overall intensities are typically well constrained by data as quantified by the Poisson likelihood term.
-Thus we simply assume a uniform prior distribution for the patch intensities.
-Algorithmically, we replace $\mathbf{x}_n$ with $\tilde{\mathbf{x}}_n$ when evaluating Equations~\ref{eq:gmm} and \ref{eq:khat} and transform $\mathbf{P}_n\mathbf{x}$ via Equation~\ref{eq:patch-norm} when evaluating Equation~\ref{eq:prior-total}.
 
@@
 We also implemented the evaluation of the patch prior on a randomized patch grid for comparison and found similar results as \cite{Parameswaran2018}: the reconstruction was slightly faster with the same reconstruction quality.
-However we found (a) practical issues with reproducibility of results when using the method on a GPU and (b) a lot of code complexity to handle the edge of images correctly.
-Give the performance improvement was only small,
-    we decided to just stick with the much simpler regular grid and cycle spinning, described in the previous paragraph.
+We found, however,  (a) there are practical issues with reproducibility of results when using this method on a GPU and (b) the method requires significant code complexity to handle the edge of images correctly.
+Given that the performance improvement was small,
+    we thus decided to use the simpler regular grid and cycle spinning, as described in the previous paragraph.
 
@@
         \label{eq:model-npred-calibration}
-        \boldsymbol{\lambda}_j = \mathbf{E}_j \cdot  \left(\mathrm{PSF}_j \circledast \phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})\right) + \alpha_j \cdot \mathbf{B}_j
+        \begin{aligned}
+        \boldsymbol{\lambda}_j(\mathbf{x}, \delta_{x,j}, \delta_{y,j}, \alpha_j) = \mathbf{E}_j \cdot  \left(\mathrm{PSF}_j \circledast \phi_j(\mathbf{x}| \delta_{x,j}, \delta_{y,j})\right) \\ + \alpha_j \cdot \mathbf{B}_j
+        \end{aligned}
     \end{equation}
@@
 An example of the effect of the positional shift and background normalization can be seen in Figure~\ref{fig:example-fermi-lat-non-calibrated}.
+
+    Modifying the (negative) log-posterior distribution given in Equation~\ref{eq:total} for the normalization of the $\mathbf{x}_n$ in Equation~\ref{eq:patch-norm}  and the adjustment for systematic effects in Equation~\ref{eq:model-npred-calibration} yields,
+    \begin{equation}
+        \label{eq:total-final}
+        \begin{aligned}
+        \mathcal{L}\left(\mathbf{x}, \mathbf{k}, \boldsymbol{\delta}, \boldsymbol{\alpha} | \mathbf{D} \right) 
+        = \sum_{j=1}^J \mathcal{C}\left( \mathbf{D}_j | \boldsymbol{\lambda}_j(\mathbf{x}, \delta_{x,j}, \delta_{y,j},\alpha_j) \right) 
+        \\ - \beta \left\{
+         \sum_{n = 1}^N \mathcal{P}_{\rm GMM}(\widetilde{\mathbf{P}_n \mathbf{x}} | {k}_n) +
+        \sum_{n = 1}^N \log \pi_{{k}_n} \right\},
+        \end{aligned}
+    \end{equation}
+    where $\mathbf{k} = (k_1, \ldots k_N)$, $\boldsymbol{\delta} = (\delta_{x,1},\delta_{y,1},\ldots, \delta_{x,J},\delta_{y,J})$ and $\boldsymbol{\alpha} = (\alpha_1,\ldots, \alpha_J)$.
+For fixed $\mathbf{x}$, Equation~\ref{eq:total-final} is optimized as a function of $\mathbf{k}$ by Equation~\ref{eq:khat}, but with $\mathbf{x}_n$ replaced by $\widetilde{\mathbf{P}_n \mathbf{x}}$.
+The joint prior distribution of $(\mathbf{x}, \mathbf{k}, \boldsymbol{\delta}, \boldsymbol{\alpha})$ is given by the term in Equation~\ref{eq:total-final} within curly brackets.
+Note that this places uniform prior distributions on $\boldsymbol{\delta}$ and $\boldsymbol{\alpha}$ and formally sets the prior on $\mathbf{P}_n\mathbf{x}$ to the GMM evaluated at  $\widetilde{\mathbf{P}_n \mathbf{x}}$.
+Since this does not depend on $\mathbf{\bar x}_n$, we implicitly assume a uniform prior on each $\mathbf{\bar x}_n$.
+In practice, we do not expect the choice of prior distribution on the scale of each patch to influence the final fit, but some users may prefer to assume a flat prior on the log of each $\mathbf{\bar x}_n$ by adding $\sum_{n=1}^N \mathbf{\bar{x}}_n$ within the curly brackets on the right-hand-side of Equation~\ref{eq:total-final}.
 
@@
 
+    How well these bootstrap error estimates approximate the true posterior uncertainty and/or the frequency coverage of the derived bootstrap intervals is a topic of future study. 
     We also experimented with computing the diagonal of the Hessian of the posterior distribution evaluated at the MAP estimate.
@@
     \subsection{\jolideco Framework}
-    The goal of the reconstruction process is to find the mode of the posterior distribution defined by Equation~\ref{eq:total}.
+    The goal of the reconstruction process is to find the mode of the posterior distribution defined by Equation~\ref{eq:total-final}.
 Given that there is a parameter for each pixel in the image, this is a high dimensional optimization problem.
@@
 
-    \subsection{Learning GMMs}
+    \subsection{Learning the GMMs}
     \label{ssec:jolideco-gmm-library}
@@
 This means the prior distribution contains a large variety of structural shapes and has freedom to adapt to the data in the optimization process by choosing the most likely GMM component for each patch in the image.
-\cite{Zoran2012} empirically found that the reconstruction quality depended on the number of components of the GMM.
-A higher number of components clearly lead to an improved reconstruction quality, as the GMM was more expressive.
-This also aligns with the intuitive argument that GMMs are universal function approximators; with a sufficient number of components they can approximate any distribution.
-\cite{Zoran2012} found the reconstruction quality started to saturate once the number of components was large enough.
-Empirically they measured a number of 32 components to be sufficient in practice for natural images.
-We decided to adopt a more conservative number of 128.
+\cite{Zoran2012} found empirically that the reconstruction quality depends on the number of GMM components.
+A higher number of components clearly leads to improved reconstruction quality, as the GMM was more expressive.
+This also aligns with the intuitive argument that GMMs are universal function approximators; with a sufficiently large number of components they can approximate any distribution.
+\cite{Zoran2012} found the reconstruction quality begins to saturate with about 32 components, at least for natural images.
+We decided to adopt a more conservative number with 128 components.
 
     With radio data, \cite{Bouman2016} found their results to be mostly independent of the choice of data used for learning the GMM prior.
-However, in the low signal-to-noise regime we typically expect a higher dependence of the results on the choice of prior, simply because the prior distribution is more influential when the data is less informative.
+In the low signal-to-noise regime, however, we typically expect a higher dependence of the results on the choice of prior, simply because the prior distribution is more influential when the data is less informative.
 Thus, there is the potential for the choice of GMM training data to be influential on results and the prior should be adapted to the particular analysis scenario in order to avoid bias.
-For this reason and for purposes of testing we learned and provide a selection of GMMs to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-library}}.
+For this reason and for purposes of testing we learned and provide a selection of GMMs to be used with the patch prior for download in a \textit{GitHub} repository\footnote{\url{https://github.com/jolideco/jolideco-gmm-prior-library}}; illustrative examples of the training images are also provided in this repository.
 
@@
     \label{sec:opt-strategy}
-    Maximising the \aposteriori likelihood defined by Equation~\ref{eq:total} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
+    Maximising the \aposteriori likelihood defined by Equation~\ref{eq:total-final} with respect to the model parameters $\mathbf{x}$ is a high dimensional optimization problem.
 We found the convergence greatly improved when the optimizer operates on $\log{\mathbf{x}}$.
-This is to be expected, as the brightness in pixels of astronomical can span multiple orders of magnitudes.
+This is to be expected, as the brightness in pixels of astronomical image can span multiple orders of magnitudes.
 We used the ADAM algorithm \citep{Kingma2014}, a stochastic gradient descent method, without decay and a fixed learning rate of $\mathrm{lr}=10^{-3}$.
@@
         \item[1.] We start from a random image where each pixel was drawn from a normal distribution with the mean corresponding to the total mean of the flux in the image and a standard deviation of 10\% of the mean.
-We first estimate $\mathbf{x}$ by using a uniform prior and early stopping after 50 iterations.
+We first estimate $\mathbf{x}$ using a uniform prior and early stopping after 50 iterations.
 This corresponds approximately to a reconstruction obtained with the standard RL algorithm.
-As the uniform prior is much faster to evaluate ($\mathcal{O(100)}$), we quickly arrive at a much better starting estimate for the reconstructed image.
+As the uniform prior is much faster to evaluate ($\mathcal{O}(100)$ times faster), this step quickly produces a much better starting value for the optimization with the patch prior described in Step~3.
         \item[2.] We freeze the image parameters and optimize the parameters associated with the systematic error described in Equation~\ref{eq:model-npred-calibration}.
-This way we arrive at a better starting estimate for those.
-Again the process is fast, because the number of parameters is very small.
-        \item[3.] Finally we simultaneously optimize
-        the image $\mathbf{x}$, the GMM component indicators for each patch, $k_n$ and the parameters associated with systematic error simultaneously until convergence.
-Convergence is verified visually by inspecting the time series of the log posterior distribution evaluated at the iterates or the models parameters.
+Again, this procedure quickly delivers better starting values for the optimization in Step 3.
+Computation is fast because the number of parameters is very small (and scales linearly with the number of datasets).
+        \item[3.] Finally we simultaneously optimize the image $\mathbf{x}$, the GMM component indicators for each patch, $k_n$ and the parameters associated with systematic error until convergence.
+Algorithmically, this is accomplished by iteratively updating (a) $\mathbf{k}$ for fixed $\mathbf{x}, \boldsymbol{\alpha}$, and $\boldsymbol{\delta}$ (via Equation~\ref{eq:khat} with $\mathbf{x}_n$ replaced by $\widetilde{\mathbf{P}_n\mathbf{x}}$) and (b) $(\mathbf{x}, \boldsymbol{\alpha}, \boldsymbol{\delta})$ for fixed $\mathbf{k}$ via SGD.
+        Convergence is verified visually by inspecting the series of values of the log posterior distribution evaluated at the iterates or the models parameters.
 We adjust the number of epochs (number of passes through the whole set of observations) such that the curve had flattened out for the last few hundred iterations.
+This is also the point in the iteration, where the noise in the loss, introduced by SGD and the cycle spinning, clearly dominates any remaining decrease in the mean loss.
     \end{itemize}
@@
     \centering
-        \begin{tabular}{ c|c|c|c|c|c } 
+        \begin{tabular}{cccccc} 
             \input{output/metrics-table.tex}
         \end{tabular}
-        \label{tab:metrics}
         \script{metrics-table.py}
         \caption{Image metrics for the different source scenarios and methods shown in Figure~\ref{fig:comparison-scenarios}.
-The first number in a cell shows the structural similarity index (SSI, the closer to unity, the better) and the second number shows the normalized root mean square (NRMSE, the lower the better).}
+The first number in each cell shows the structural similarity index (SSI, the closer to unity, the better) and the second number shows the normalized root mean square (NRMSE, the lower the better).}
+        \label{tab:metrics}
     \end{table*}
@@
     \centering
-        \begin{tabular}{ c|c|c|c|c|c } 
+        \begin{tabular}{cc@{\hspace{2pc}}c@{\hspace{2pc}}c} 
             \input{output/metrics-table-bkg.tex}
         \end{tabular}
-        \label{tab:metrics}
         \script{metrics-table-bkg.py}
         \caption{Image metrics for the different signal to noise ratios shown in Figure~\ref{fig:comparison-signal-noise}.
-The first number in a cell shows the structural similarity index (SSI, the closer to unity, the better) and the second number shows the normalized root mean square (NRMSE, the lower the better).}
+The first number in each cell shows the structural similarity index (SSI, the closer to unity, the better) and the second number shows the normalized root mean square (NRMSE, the lower the better).}
+        \label{tab:metrics-bkg}
     \end{table*}
@@
 The ring structure is sharpened considerably in all cases as well.
-The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but remain blurred along the direction of their neighbours.
-Thids a similar situation as in the lower left of the image in the A1 point source scenario, when sources are to close by.
+The near-by point sources on the left and right of the spiral arm structure cannot be separated into individual point sources, but remain blurred along the direction of their neighbors.
+This is a similar situation as in the lower left of the image in the A1 point source scenario, when sources are to close by.
 
@@
 The latter suggests that the GMM prior is not strong enough to maintain the pixel to pixel correlations in the case of high signal strength.
+This observation is confirmed in the metrics shown in Table~\ref{tab:metrics-bkg}, where scenario D5 shows lower SSI values than D4 for the same background level.
 The strength of the prior could be increased with the $\beta$ parameter, but for this study we use the default settings and do not tweak individual parameters.
@@
 While the emission is barely visible in the counts image it is clearly evident above the background in the \jolideco reconstruction.
-Visually the reconstruction does not result in a point source, but leaves a visible extension of a very few pixels.
-
-    However, at this level of analysis and signal to noise, both scenarios remain plausible: a real intrinsic extension of the feature, as well as a remaining reconstructed extension in a real point source because of low signal to noise, which has also been observed on the simulated point source dataset discussed in Section~\ref{subsec:test-datasets}\footnote{We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.}.
+Visually the reconstruction does not result in a point source, but leaves a visible extension of a few pixels.
+
+    However, at this level of analysis and signal to noise, both scenarios remain plausible: a real intrinsic extension of the feature, or a real point source with a residual extension in its reconstruction, owing to the low signal to noise.
+We observed the second possibility in
+    the simulated point source dataset discussed in Section~\ref{subsec:test-datasets}\footnote{We note that, as illustrated in Section~\ref{subsec:methods} for Scenario~A, the remaining extension of the point source after deconvolution may be smaller if the source is brighter.}.
 
@@
 Despite the clear improvement in spatial resolution, systematic issues such as the proper-motion of structures and calibration uncertainties, might limit the quality of the result.
-The full analysis example is available at \url{https://github.com/jolideco/jolideco-chandra-examples}.
+The full analysis example, with results and residuals is available at \url{https://github.com/jolideco/jolideco-chandra-examples}.
 
@@
 
-    To further check the quality of the reconstructed flux we compute a map of standardized residuals defined by:
-
+    To further check the quality of the reconstructed flux we compute a map of smoothed standardized residuals defined by
     \begin{equation}
         \label{eq:approx-sigma}
-        \rho(\mathbf{D}, \boldsymbol{\lambda}) \approx \frac{1}{\sqrt{\pi \sigma^2}}\frac{(\mathbf{D} - \boldsymbol{\lambda}) \circledast g_{\sigma}} {\sqrt{\boldsymbol{\lambda}\circledast g_{\sigma}}}.
-    \end{equation}
-
-    where $\mathbf{D}$ is the measured counts image, $\boldsymbol{\lambda}$ the predicted counts image  and $g_{\sigma}$ is a Gaussian smoothing kernel of width $\sigma=5$ pixels.
-The Gaussian smoothing kernel approximates the shape and size of the \fermi PSF.
-Together with the definition above, the standardized residuals approximately represent the significance of detecting a point source at the given pixel.
-Structures smaller than the PSF cannot be real.
+        \rho(\mathbf{D}, \boldsymbol{\lambda}) \approx 2\sqrt{\pi \sigma^2}\frac{(\mathbf{D} - \boldsymbol{\lambda}) \circledast g_{\sigma}} {\sqrt{\boldsymbol{\lambda}\circledast g_{\sigma}}},
+    \end{equation}
+    where $\mathbf{D}$ is the measured counts image, $\boldsymbol{\lambda}$ is the expected counts image,  and $g_{\sigma}$ is a Gaussian smoothing kernel (normalized to integrate to unity) with width $\sigma=5$ pixels.
+We apply the smoothing to enhance possible structures in the sparse data, while the normalisation factor ensures the smoothed residual pixel values are still distributed following a unit Gaussian distribution.
 
@@
 In Figure~\ref{fig:example-fermi-lat-non-calibrated} we also show the residuals per PSF class with and without the correction defined by Equation~\ref{eq:model-npred-calibration}.
-More details of the \fermi analysis are available at \url{https://github.com/jolideco/jolideco-fermi-examples}
+More details of the \fermi analysis including results and residuals are available at \url{https://github.com/jolideco/jolideco-fermi-examples}.
 
@@
     We imagine that \jolideco is the first step of a larger project building ML-inspired methods for the reconstruction of astronomical images that are dominated by Poisson noise.
-While \jolideco has already achieved results that are superior to any other existing method, it still has significant potential for future extension and improvements.
+While \jolideco has already demonstrated excellent reconstruction quality in multiple scenarios, it still has significant potential for future extension and improvements.
 
@@
 As with a GMM, we can evaluate the NF-based prior distribution and thus construct an explicit posterior distribution for optimization and computation of the MAP estimate.
-\citet{Ulyanov2017} introduced another promising prior distribution, known as the \enquote{Deep Image Prior} and showed that prior structure for an image can be built into a deep neural network as an \enquote{inductive bias}, where the architecture of the network encodes the prior information on the correlation structure among neighbouring pixels.
+\citet{Ulyanov2017} introduced another promising prior distribution, known as the \enquote{Deep Image Prior} and showed that prior structure for an image can be built into a deep neural network as an \enquote{inductive bias}, where the architecture of the network encodes the prior information on the correlation structure among neighboring pixels.
 The authors showed, that the deep image prior successfully imposes self similarity on structures in the image.
@@
 Instruments such as \fermi combine instrument responses that vary strongly with energy along with a limited overall energy resolution.
-This configuration introduces correlations between images in neighbouring energy bands.
+This configuration introduces correlations between images in neighboring energy bands.
 Accounting for energy data in the reconstruction would allow us to handle these correlations and also open up the possibility of merging multiple \xray datasets in the joint spectral/spatial domain,  thus improving both  angular and energy resolution.
@@
 However we plan to extend \jolideco to enable it to handle multiple source components at the same time.
-This allows us in principle, as shown by \cite{Selig2015} and \citet{Pumpe2018} to separate extended sources from point-like sources, based on different prior assumptions on the spatial correlation and distribution of pixels for each model component.
+This allows us in principle, as shown by \cite{Selig2015A} and \citet{Pumpe2018} to separate extended sources from point-like sources, based on different prior assumptions on the spatial correlation and distribution of pixels for each model component.
 
@@
 Since we can compute the full posterior distribution, however, we could build an approximation to the covariance matrix of the MAP estimate, for example, by using a low-rank or sparse representation.
-    Alternatively we can use MCMC to obtain a sampling from the full posterior distribution, enabling us to explore the distribution and quantify  uncertainty both in the parameters and functions of the parameters constructed to represent structures in the image.
+Alternatively we can use MCMC to obtain a sample from the full posterior distribution, enabling us to explore the distribution and quantify  uncertainty both in the parameters and functions of the parameters constructed to represent structures in the image.
 Estimating errors for the reconstruction would also include propagating systematic uncertainties on the PSF to the reconstructed image and handling a PSF that varies across the field of view, as recently proposed by \cite{Sakai2023}.
@@
     This work was conducted under the auspices of the CHASC International Astrostatistics Center.
-    CHASC is supported by NSF grants DMS-21-13615, DMS-21-13397, and DMS-21-13605; by the UK Engineering
-    and Physical Sciences Research Council [EP/W015080/1]; and by NASA APRA Grant 80-NSSC21-K0285.
+CHASC is supported by NSF grants DMS-21-13615, DMS-21-13397, and DMS-21-13605; by the UK Engineering and Physical Sciences Research Council [EP/W015080/1]; and by NASA APRA Grant 80-NSSC21-K0285.
 
     We thank CHASC members for many helpful discussions, especially Xiao-Li Meng and Katy McKeough.
-    DvD was also supported in part by a Marie-Skodowska-Curie RISE Grant (H2020-MSCA-RISE-2019-873089)
-    provided by the European Commission.
+    DvD was also supported in part by a Marie-Skodowska-Curie RISE Grant (H2020-MSCA-RISE-2019-873089) provided by the European Commission.
 
@@
 
-    This research has made use of data obtained from the Chandra Data Archive and software provided by the Chandra X-ray Center (CXC) in the application packages CIAO \citep{Fruscione2006} and {\it Sherpa} \citep{Freeman2001,Burke2022}.
+    This research has made use of data obtained from the Chandra Data Archive, contained in~\dataset[DOI: 10.25574/cdc.244]{https://doi.org/10.25574/cdc.244}.
+This research also made use of software provided by the Chandra X-ray Center (CXC) in the application packages CIAO \citep{Fruscione2006} and {\it Sherpa} \citep{Freeman2001,Burke2022}.
 
@@
         \end{tabular}
-        \label{tab:chandra_obs}
         \script{chandra-obs-table.py}
@@
 The fractional exposure column, gives the exposure of each observation as a fraction of the total exposure.}
+        \label{tab:chandra_obs}
     \end{table}
